### 2016-12-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added a template for paper

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}
\usepackage{etex}

%\usepackage[english]{babel}
%
\usepackage[utf8]{inputenc}
% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
\usepackage[disable]{todonotes}
%\usepackage{todonotes}
\usepackage[backend=bibtex,bibstyle=authoryear,citestyle=authoryear,
firstinits=true,doi=false,isbn=false,url=false,eprint=false,dashed=false,natbib=true]{biblatex}
%\renewcommand*{\bibfont}{\small}
\addbibresource{References.bib}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp

\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

\newcommand{\mypar}[1]{\bigskip\noindent\textbf{#1.}~}

\newcommand{\e}[1]{\times 10^{#1}}

\graphicspath{{figures/}}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

%For the references, the following commands make the titles 
%lowercase while keep the initial letters of journal names 
%uppercase
\DeclareFieldFormat{titlecase}{\MakeSentenceCase*{#1}}
\newbibmacro*{journal}{%
	\iffieldundef{journaltitle}
	{}
	{\printtext[journaltitle]{%
			\printfield[myplain]{journaltitle}%
			\setunit{\subtitlepunct}%
			\printfield[myplain]{journalsubtitle}}}}
\DeclareFieldFormat{myplain}{#1}

%Remove the quotation marks for the titles in the reference
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{citetitle}{#1}
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{title}{#1}
\DeclareNameAlias{author}{last-first}

%%Using \DeclarePairedDelimiter from mathtools, you could define 
%%macros \ceil and \floor, which will scale the delimiters 
%%properly (if starred):
%\usepackage{mathtools}
%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\pgfplotsset{
	compat=newest,
	xlabel near ticks,
	ylabel near ticks
}
\newcommand{\Astar}{A$^{\!\star}$\xspace}
\newcommand{\tstar}{\ensuremath{t\xspace}}
\newcommand{\Pistar}{\ensuremath{\Pi}} % {\Pi_{\mathrm{start}}(\tstar)}
\newcommand{\Pstart}{\ensuremath{\mathpzc{P}_\mathrm{start}}\xspace}
\newcommand{\Pgoal}{\ensuremath{\mathpzc{P}_\mathrm{goal}}\xspace}
\newcommand{\Pnode}{\ensuremath{\mathpzc{P}_{t,i}}\xspace}
\newcommand{\Tgoal}{\ensuremath{T_\mathrm{goal}}\xspace}

\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.99}
\renewcommand{\dbltopfraction}{0.99} % fit big float above 
%2-col. text
%\renewcommand\thesection{\arabic{section}}
%\renewcommand\thesubsection{\thesection.\arabic{subsection}}

\newcolumntype{x}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}b{#1}}
\newcolumntype{y}[1]{>{\centering\arraybackslash\hspace{0pt}}b{#1}}
%\newcolumntype{y}[2]{>{\centering\arraybackslash\hspace{0pt}}D{.}{.}{#1}b{#2}}
%\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcolumntype{L}{>{$}l<{$}}% math-mode version of "l" column 
%type
\newcolumntype{R}{>{$}r<{$}}% math-mode version of "r" column 
%type
\newcolumntype{C}{>{$}c<{$}}% math-mode version of "c" column 
%type

%This style looks better than $\mathrm{non-comp}$ in which "-" 
%looks like the symbol of minus 
\newcommand\nonhyphencomp{\operatorname{non-comp}}
\newcommand\inthyphenleng{\operatorname{int-leng}}
\newcommand\goalhyphentype{\operatorname{goal-type}}
\newcommand\goalhyphennon{\operatorname{goal-non}}
\newcommand\goalhyphenshape{\operatorname{goal-shape}}
%\newcolumntype{y}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}p{#1}}
%\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Title \protect\\ title 
	}
\titlerunning{title running}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%\author{Dongliang Peng, Alexander Wolff, and Jan-Henrik Haunert}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
% \institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
% \and Name of Second Author \at Name, Address of Institute
% \email{name@email.address}}
\institute{
%	Dongliang Peng 
%	\at Chair of Computer Science I, University of W\"urzburg, 
%	Germany \\
%	\email{dongliang.peng@uni-wuerzburg.de}
%	\and
%	% 
%	Alexander Wolff 
%	\at Chair of Computer Science I, University 
%	of W\"urzburg, Germany \\
%	\url{URL: 
%	
%http://www1.informatik.uni-wuerzburg.de/en/staff/wolff_alexander}
%	\and
%	%
%	Jan-Henrik Haunert 
%	\at Institute for Geoinformatics and Remote Sensing (IGF), 
%	University of Osnabr\"uck, Germany \\
%	\email{janhhaunert@uni-osnabrueck.de}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\newcommand{\myabstract}{text}

\abstract*{\myabstract}

\abstract{\myabstract}

\keywords{Text, Text}

\section{Introduction}
\label{sec:Introduction}

\begin{figure}[tb]
	\centering
	\includegraphics{SubdivisionName}
	\caption{The subdivision graph $G$ whose nodes are the
          subdivisions \Pnode, and there is an edge
          from~\Pnode to~$\mathpzc{P}_{t+1,j}$ if
          $\mathpzc{P}_{t+1,j}$ is the result of aggregating a
          smallest polygon~$p$ of~\Pnode into a neighbor
          of~$p$.}
	\label{fig:SubdivisionName}
\end{figure}

\mypar{Notation}
Text.

\section{Section Title}
\label{sec:AStarAlgorithm}

Text.

\subsection{Text}
\label{sec:Formalizing}

\section{Conclusions}
\label{sec:Conclusions}

Text

\printbibliography
%\bibliographystyle{plainnat}
%%	\bibliography{References}
%\input{referenc}
\end{document}

### 2016-12-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
moved most of the content from Google Docs to our latex file

@@
 \usepackage{afterpage}
-\usepackage[disable]{todonotes}
+%\usepackage[disable]{todonotes}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
 %\usepackage{todonotes}
@@
 \usepackage{capt-of}
+%\usepackage{marginnote}
+\usepackage{xargs}   % Use more than one 
+%optional parameter in a new commands
 %\usepackage{siunitx} %for scientific 
@@
 
+\newcommandx{\marginalcomment}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+
 \renewcommand{\textfraction}{0.01}
@@
 
-\title*{Title \protect\\ title 
-	}
-\titlerunning{title running}
+\title*{Continuous Generalization of Buildings}
+\titlerunning{Continuous Generalization of Buildings}
 % Use \titlerunning{Short Title} for an abbreviated version of
@@
 
-\section{Introduction}
-\label{sec:Introduction}
+\section{Discussion}
+\label{sec:Discussion}
 
@@
 	\centering
-	\includegraphics{SubdivisionName}
-	\caption{The subdivision graph $G$ whose nodes are the
-          subdivisions \Pnode, and there is an edge
-          from~\Pnode to~$\mathpzc{P}_{t+1,j}$ if
-          $\mathpzc{P}_{t+1,j}$ is the result of aggregating a
-          smallest polygon~$p$ of~\Pnode into a neighbor
-          of~$p$.}
-	\label{fig:SubdivisionName}
+	\includegraphics{Framework}
+	\caption{Framework.}
+	\label{fig:Framework}
 \end{figure}
+
+We discussed two ways of achieving continuous generalization of 
+buildings.
+
+The first way is that we cover the smallest block at each step. 
+Should we consider the density of the buildings? 
+\marginalcomment{relevant comment. If small buildings exist in 
+	all blocks, there will be small buildings remaining at small 
+	scales in the blocks that have not been covered.}
+A disadvantage 
+is that some small buildings in a large block may exist very 
+long.
+Alternatively, we may cover two buildings together if they are 
+close enough, say the distance is smaller than d. We can 
+increase d so that we will cover more and more buildings 
+together. To avoid overlap between two covers, we may need to 
+use Voronoi diagrams of the original buildings. We can cover 
+buildings without overlap if we always use a cover inside the 
+Voronoi cells of these buildings. This idea about Voronoi cells 
+is used in Topologically Safe Curved Schematization (van Goethem 
+et al. 2013). We may need to try different possible covers. 
+Unfortunately, this trying may be very time-consuming, probably 
+NP-hard.
+
+The second way is that we grow buildings by buffering with an 
+increasing radius, and then merge the buffers overlapping each 
+other. A disadvantage is that the corners of the buffers 
+\marginalcomment{this may be avoided by using square buffers 
+(the Minkowski sum is done with a square rather than a circle), 
+don't know if it's available in ESRI products}
+\marginalcomment{We can also think about the method described at 
+%\url{http://stackoverflow.com/questions/1109536/an-algorithm-for-inflating-deflating-offsetting-buffering-polygons#}
+ }
+are not 
+orthogonal anymore. Two kinds of buffer:
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth]{BufferRoundJoint}
+	\caption{BufferRoundJoint.}
+	\label{fig:BufferRoundJoint}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth]{BufferMiterJoint}
+	\caption{BufferMiterJoint.}
+	\label{fig:BufferMiterJoint}
+\end{figure}
+
+A disadvantage of buffering based on miter joint is that the 
+method is sensitive to noise. By sensitive, if there is a short 
+edge at the end or a sharp corner, then the result will be very 
+different to the case that there is no such short edge. In 
+contrary, buffers based on round joint are continuous and stable.
+
+This method should be easier to implement than the first method.
+\marginalcomment{We can erode back in order to keep enough 
+distance between buildings. The operator of growing and 
+shrinking of buffers are mentioned in paper Automated Processing 
+for Map Generalization with Modular Operator Services (Neun 
+2009).
+} 
+We may not need to erode back after buffering. In this second 
+strategy, undesired very small shapes or holes might appear at 
+some point, and should be reverted until the growing totally 
+collapses the hole or makes the small parts big enough. As 
+buffers are not allowed to cross roads, we may clip some parts 
+of the buffers off along the roads.
+If we buffer with miter joint, it can happen that a very sharp 
+angle yields a very long buffer. Fortunately, we do not have 
+this situation so far. Otherwise, we may need to cut the long 
+buffer at some point.
+We may have small holes after buffering and merging the buffers 
+of the buildings, which is not nice. See below as an example, 
+where we can find a small “white” hole in the middle. We may 
+simply fill out all the holes having small area.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth/2]{BufferWithHole}
+	\caption{BufferWithHole.}
+	\label{fig:BufferWithHole}
+\end{figure}
+
+We have two maps at different scales. We generalize the 
+buildings on the larger-scale map, and we use the boundaries of 
+the buildings on the smaller-scale map as the limits of the 
+generalization (including growing).
+
+We have a requirement that the buildings should not cross 
+existing roads. Therefore, we need to cut the the enlarged 
+buildings by the roads. If we do this cut, then some buildings 
+may almost touch each other, but separated by roads. The 
+too-close buildings will look ugly. To avoid the ugly 
+performance, we should also make buffers for roads, and require 
+that the enlarged buildings should be outside the buffers of the 
+roads. Should we use the same radius that we used for enlarging 
+buildings? With the buffers of roads growing, we may need to 
+move enlarged buildings, otherwise, the enlarged buildings will 
+overlap the buffers of roads. 
+We may move by a method based on least-squares adjustment. In 
+this method, we may assign large weight for keeping the distance 
+between a road and a building. We may assign small weight for 
+keeping the distance between buildings because buildings will be 
+buffered and merged later.
+
+We want to enlarge the buildings by a radius r, and require that 
+the distance between any two buildings after the enlargement 
+should be 2d at least. To achieve this aim, we first buffer the 
+buildings by a radius r+d, and then buffer the enlarged 
+buildings by a radius -d. Following is an example, where r=10 
+and d=15.
+
+Buffering the original buildings with radius 25
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth]{BufferRadius25}
+	\caption{BufferRadius25.}
+	\label{fig:BufferRadius25}
+\end{figure}
+
+Buffering the enlarged buildings with radius -15 (erosion). We 
+call the result Map A. Unfortunately, we produced some spikes by 
+this erosion. Since we used the miter joint and we allow the 
+enlargements twice of radius r=10 away from the original 
+buildings, the corners of the enlarged buildings can be 2r=20 
+from the original buildings. After erosion, the smallest 
+distance between two buildings can be as small as 0. I will give 
+more details.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth]{MapA}
+	\caption{MapA.}
+	\label{fig:MapA}
+\end{figure}
+
+Buffering the original buildings with radius 10. We call the 
+result Map B.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\linewidth]{MapB}
+	\caption{MapB.}
+	\label{fig:MapB}
+\end{figure}
+
+To remove the spikes in Map A, we may subtract Map B from Map A. 
+Then we get some leftovers in Map A. The outward triangles of 
+the leftovers are the spikes which we want to remove. We 
+subtract those outward triangles from Map A, which may guarantee 
+that we will have removed the spikes in Map A.
+
+To remove the spikes in Map A, Guillaume suggested that we could 
+%buffer by a small value -ɛ, and then buffer again by ɛ.
+
+Should we buffer from the original buildings or buffer from the 
+buildings from the previous step?
+
+Elimination
+If every building should have area 4d2at least, we buffer 
+buildings with radius xd (x<2). After the buffering, some too 
+small buildings will be eliminated. The small buildings which 
+manage to merge with other buildings may survive. The eliminated 
+buildings should not participate in next buffering step, which 
+uses larger d.
+
+Issues regarding the data:
+
+%How were the layers of data road_25k and road_100k produced?
+%Was road_25k produced by surveying?
+%Was road_100k generalized from road_25k?
+%
+%How were the layers of data building_15k, building_25k, 
+%urban_area_50k, and urban_area_100k produced?
+%Was building_15k produced by surveying?
+%Was building_25k derived from building_15k by the methods 
+%illustrated in paper Optimization Approaches for Generalization 
+%and Data Abstraction (Sester, 2005)?
+%Was urban_area_50k derived from building_15k by constructing 
+%buffers and filling out the holes of the buffers?
+%Was urban_area_100k derived from building_15k by constructing 
+%buffers and filling out the holes of the buffers?
+
+\section{Introduction}
+\label{sec:Introduction}
 

### 2017-01-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added the text about "An idea of continuously generalising buildings"

@@
 
-\section{Introduction}
-\label{sec:Introduction}
+\section{An idea of continuously generalising buildings}
+We have an input map at scale $1:15 \mathrm{k}$.
+We want to generate, by generalisation, $10$ maps which are at 
+scale $1:20\mathrm{k}$, $1:25\mathrm{k}$, 
+$1:30\mathrm{k}$, $\dots$, $1:65\mathrm{k}$.
+We always produce a map by generalising the 
+immediate-larger-scale map. For example, we produce the map at 
+scale $1:25\mathrm{k}$ by generalising, instead of the input 
+map, the map at scale $1:20\mathrm{k}$.
+This production 
+guarantees consistency. Namely, if a building does not exist on 
+a map at a certain scale, then the building will never exist on 
+a map at a smaller scale.
 
-\mypar{Notation}
-Text.
+We have two requirements for an output map.
+The first one is that the distance between two 
+buildings should be at least $d$.
+The second requirement is that a building with area less than 
+$d^2$ should be eliminated.
+In order to make sure that some small buildings will be 
+eliminated, the radius $r$ that we use to buffer buildings 
+should be smaller than $d$. We simply use $r=\frac{1}{2}d$.
+Our buildings may have been buffered with radius, in total, $r_0 
+(r_0 < r)$ from previous steps.
+Therefore, we only need to buffer with radius $r-r_0$ at the new 
+step.
+
+Our generalisation is as follows. We buffer buildings with 
+radius $d+r-r_0$, then we buffer the results with $-d$. In order 
+to 
+remove some spikes from the buffering, we buffer the results 
+with $-\epsilon$, and then again with $\epsilon$. We simply set 
+$\epsilon=\frac{1}{10}d$. After these buffering operations, we 
+eliminate the buildings with area less than $d^2$.
 
@@
 
+\mypar{Notation}
 Text.

### 2017-01-13 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
wrote some instructions in ReadMe.docx

@@
 Our generalisation is as follows. We buffer buildings with 
-radius $d+r-r_0$, then we buffer the results with $-d$. In order 
-to 
-remove some spikes from the buffering, we buffer the results 
+radius $d+r-r_0$, and merge the buffers overlapping each 
+other.
+Then we buffer the results with $-d$.
+In order to 
+remove some spikes from the buffering, we buffer the new results 
 with $-\epsilon$, and then again with $\epsilon$. We simply set 

### 2017-03-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished implementing a rough idea about continuous building generalization

--- 2016-12-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
@@
 
-\section{Introduction}
-\label{sec:Introduction}
+\section{An idea of continuously generalising buildings}
+We have an input map at scale $1:15 \mathrm{k}$.
+We want to generate, by generalisation, $10$ maps which are at 
+scale $1:20\mathrm{k}$, $1:25\mathrm{k}$, 
+$1:30\mathrm{k}$, $\dots$, $1:65\mathrm{k}$.
+We always produce a map by generalising the 
+immediate-larger-scale map. For example, we produce the map at 
+scale $1:25\mathrm{k}$ by generalising, instead of the input 
+map, the map at scale $1:20\mathrm{k}$.
+This production 
+guarantees consistency. Namely, if a building does not exist on 
+a map at a certain scale, then the building will never exist on 
+a map at a smaller scale.
 
-\mypar{Notation}
-Text.
+We have two requirements for an output map.
+The first one is that the distance between two 
+buildings should be at least $d_i=0.2 \mathrm{mm}/S_i$, where 
+$S_i$ is the scale of map $i$.
+The second requirement is that a building with area less than 
+$A_i=0.16\mathrm{mm}^2/S^2_i$ should be eliminated. Roughly, a 
+building with width less than 
+$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S$ should be eliminated.
+In order to make sure that some small buildings will be 
+eliminated, the radius $r_i$ that we use to buffer buildings 
+should be smaller than $\frac{1}{2}w_i$. We simply use 
+$r_i=\frac{1}{4}w_i$.
+Our buildings may have been buffered with radius, in total, 
+$r_{i-1}$ from previous steps.
+Therefore, we only need to buffer with radius $r_i-r_{i-1}$ at 
+the new 
+step.
+
+Our generalisation is as follows. We buffer buildings with 
+radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
+overlapping 
+each 
+other.
+Then we buffer the results with $-\frac{1}{2}d_i$.
+In order to 
+remove some spikes from the buffering, we buffer the new results 
+with $-\epsilon_i$, and then again with $\epsilon_i$. We simply 
+set 
+$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
+operations, we 
+eliminate the buildings with area less than $d^2_i$.
 

### 2017-03-14 ContinuousGeneralizer/ContinuousGeneralizer/FrmContinuousGeneralizer.cs

@@ -44,8 +44,8 @@ namespace ContinuousGeneralizer
     {
         private void FrmContinuousGeneralizer_Shown(object sender, EventArgs e)
         {
-            //var frmCurrent = new FrmBuildingGrowing(_DataRecords);
-            var frmCurrent = new FrmCAMDijkstra(_DataRecords);
+            var frmCurrent = new FrmBuildingGrowing(_DataRecords);
+            //var frmCurrent = new FrmCAMDijkstra(_DataRecords);
             //var frmCurrent = new FrmCGABM(_DataRecords);
             //var frmCurrent = new FrmExtractPossibleFiles();
             frmCurrent.Show();
@@ -649,33 +649,35 @@ namespace ContinuousGeneralizer
 
         private void mnuAnyTest_Click(object sender, EventArgs e)
         {
-            var cptlt= CHelperFunction .GetTestCptEb().ToList();
+            tspbMain.Value = 15;
 
-            CPolygon cpg = new CPolygon(1, cptlt);
-            cpg.CptLtLt.Add(cptlt);
-            cpg.CptLtLt.Add(cptlt);
+            //var cptlt= CHelperFunction .GetTestCptEb().ToList();
 
-
-
-
+            //CPolygon cpg = new CPolygon(1, cptlt);
+            //cpg.CptLtLt.Add(cptlt);
+            //cpg.CptLtLt.Add(cptlt);
 
 
-            CHelperFunction.testmemory();
-
-            //IList<IList<double>> intltlt = new List<IList<double>>();
-
-            //while (intltlt.Count < 40)
-            //{
-            //    intltlt.Add(testttt());
-            //}
 
 
-            //while (true)
-            //{
-            //    intltlt.Add(testttt());
-            //}
 
-            //int st = 5;        
+
+            //CHelperFunction.testmemory();
+
+            ////IList<IList<double>> intltlt = new List<IList<double>>();
+
+            ////while (intltlt.Count < 40)
+            ////{
+            ////    intltlt.Add(testttt());
+            ////}
+
+
+            ////while (true)
+            ////{
+            ////    intltlt.Add(testttt());
+            ////}
+
+            ////int st = 5;        
         }
 
         private IList<double> testttt()

### 2017-03-14 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphingExtend/FrmSimultaneity.cs

@@ -87,7 +87,7 @@ namespace ContinuousGeneralizer.FrmMorphingExtend
             //_adblAngle0 = new double[intPtCount - 2];
             //for (int i = 0; i < intPtCount - 2; i++)
             //{
-            //    _adblAngle0[i] = CGeometricMethods.CalAngle2(cpl.CptLt[i], cpl.CptLt[i + 1], cpl.CptLt[i + 2]);                
+            //    _adblAngle0[i] = CGeometricMethods.CalAngle_Counterclockwise(cpl.CptLt[i], cpl.CptLt[i + 1], cpl.CptLt[i + 2]);                
             //}
 
         }

### 2017-03-14 ContinuousGeneralizer/MorphingClass/CAid/CMatchAndMergePolylines.cs

@@ -37,10 +37,10 @@ namespace MorphingClass.CAid
         public void MatchAndMergePolylines()
         {
             CParameterInitialize ParameterInitialize = _ParameterInitialize;
-            //List<CPolyline> pCPlLt = this.ObjCGeoLtLt[0].ToExpectedClass<CPolyline, object>().ToList();
+            //List<CPolyline> pCPlLt = this.ObjCGeoLtLt[0].AsExpectedClass<CPolyline, object>().ToList();
 
-            List<CPolyline> LSCPlLt = this.ObjCGeoLtLt[0].ToExpectedClass<CPolyline, object>().ToList();
-            List<CPolyline> SSCPlLt = this.ObjCGeoLtLt[1].ToExpectedClass<CPolyline, object>().ToList();
+            List<CPolyline> LSCPlLt = this.ObjCGeoLtLt[0].AsExpectedClass<CPolyline, object>().ToList();
+            List<CPolyline> SSCPlLt = this.ObjCGeoLtLt[1].AsExpectedClass<CPolyline, object>().ToList();
 
             long lngStartTime = System.Environment.TickCount;
             List<CPolyline> LSAttentionCPlLt = new List<CPolyline>();
@@ -259,7 +259,7 @@ namespace MorphingClass.CAid
             //double dblFrDiffY = LSCPlLt[i].pBaseLine.ToCpt.Y - LSCPlLt[i].pBaseLine.FrCpt.Y;
             //double dblToDiffX = SSCPlLt[i].pBaseLine.ToCpt.X - SSCPlLt[i].pBaseLine.FrCpt.X;
             //double dblToDiffY = SSCPlLt[i].pBaseLine.ToCpt.Y - SSCPlLt[i].pBaseLine.FrCpt.Y;
-            //double dblAngleDiff = CGeometricMethods.CalAngle2(dblFrDiffX, dblFrDiffY, dblToDiffX, dblToDiffY);
+            //double dblAngleDiff = CGeometricMethods.CalAngle_Counterclockwise(dblFrDiffX, dblFrDiffY, dblToDiffX, dblToDiffY);
 
             //if ((Math.Abs(dblAngleDiff) > (Math.PI / 2) && Math.Abs(dblAngleDiff) < (3 * Math.PI / 2)))
             //{

### 2017-03-14 ContinuousGeneralizer/MorphingClass/CAid/CTemporary.cs

@@ -37,8 +37,8 @@ namespace MorphingClass.CAid
         {
             CParameterInitialize ParameterInitialize = _ParameterInitialize;
 
-            var pLSCPlLt = this.ObjCGeoLtLt[0].ToExpectedClass<CPolyline, object>().ToList();
-            //var pSSCPlLt = this.ObjCGeoLtLt[1].ToExpectedClass<CPolyline, object>().ToList();
+            var pLSCPlLt = this.ObjCGeoLtLt[0].AsExpectedClass<CPolyline, object>().ToList();
+            //var pSSCPlLt = this.ObjCGeoLtLt[1].AsExpectedClass<CPolyline, object>().ToList();
 
             var subLSCplLt = new List<CPolyline>(pLSCPlLt.Count / 2);
             var subSSCplLt = new List<CPolyline>(pLSCPlLt.Count / 2);

### 2017-03-14 ContinuousGeneralizer/MorphingClass/CGeometry/CGeometryBase/CGeometricBase.cs

@@ -11,7 +11,7 @@ namespace MorphingClass.CGeometry.CGeometryBase
 {
     public class CGeometricBase<CGeo> : CBasicBase 
         where CGeo:class
-    //public class CGeometricBase<TGeo> :CBasicBase where TGeo : class    //it would be better if we could do it like this, but our current version doesn't support default generic type, which we need for one of the classes inheriting from this class
+        //public class CGeometricBase<TGeo> :CBasicBase where TGeo : class    //it would be better if we could do it like this, but our current version doesn't support default generic type, which we need for one of the classes inheriting from this class
     {
         
         protected int _tempID = -1;
@@ -33,11 +33,20 @@ namespace MorphingClass.CGeometry.CGeometryBase
         protected CGeo _CorrCGeo;
         protected List<CGeo> _CorrCGeoLt;
 
-        
 
-        //public virtual CGeometricBase()
+
+        public CGeometricBase()
+        {
+
+        }
+
+        public CGeometricBase(int intID, IGeometry pGeo)           
+        {
+
+        }
+
+        //public CGeometricBase<CGeo> ()
         //{
-
         //}
 
 

### 2017-03-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
improved the interpretation of our basic idea; removed some unused codes

@@
 %\let\newinsert\tmp
-
+\usepackage{enumitem} %make items indent when using 
+%\begin{enumerate}[(a)]
 \usepackage{verbatimbox}  %for \addvbuffer
@@
 
+%\pagebreak[4]
+%\newpage
+\clearpage
+
 \section{An idea of continuously generalising buildings}
@@
 
-Our generalisation is as follows. We buffer buildings with 
+Our generalisation is as following $4$ steps:
+\begin{enumerate}[label=(\alph*),leftmargin=2\parindent]
+	\item We buffer buildings with 
 	radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
-overlapping 
-each 
-other.
-Then we buffer the results with $-\frac{1}{2}d_i$.
-In order to 
-remove some spikes from the buffering, we buffer the new results 
-with $-\epsilon_i$, and then again with $\epsilon_i$. We simply 
-set 
+	overlapping each other.
+	\item Then we buffer the results with $-\frac{1}{2}d_i$.
+	\item In order to 
+	remove some spikes from the buffering, we buffer the new 
+	results with $-\epsilon_i$.
+	\item To compensate, we buffer with $\epsilon_i$.	
+\end{enumerate}
+We simply set 
 $\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
-operations, we 
-eliminate the buildings with area less than $d^2_i$.
+operations, we eliminate the buildings with area less than 
+$d^2_i$.
 

### 2017-03-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added some references for our introduction

@@
 %\usepackage{todonotes}
-\usepackage[backend=bibtex,bibstyle=authoryear,citestyle=authoryear,
-firstinits=true,doi=false,isbn=false,url=false,eprint=false,dashed=false,natbib=true]{biblatex}
-%\renewcommand*{\bibfont}{\small}
-\addbibresource{References.bib}
 \usepackage{subfigure}
@@
 % \newcommand{\ms}{\ensuremath{M_-}\xspace}
+
+\usepackage[backend=bibtex,
+bibstyle=authoryear, %without indices before names; year after 
+%names
+%style=authoryear,
+citestyle=authoryear,
+maxbibnames=20,maxcitenames=2,
+firstinits=true,
+%terseinits=true, %remove periods after initials of first names
+%style=apa, %
+%sorting=ydnt, %Sort bibliography by year (descending), name, 
+%title
+doi=false,isbn=false,url=false,
+eprint=false,dashed=false]{biblatex}
+
+%\renewcommand*{\bibfont}{\small} %set the font size of the 
+%references
+%\renewcommand*{\nameyeardelim}{\addspace} %\remove the comma 
+%between author and year citations
+%\renewcommand*{\revsdnamepunct}{} %remove commas between last 
+%%and first names in bibliography
+%\renewcommand{\labelnamepunct}{\addspace} %remove the 
+%%punctuation after the year in bibliography
+%\renewcommand{\finentrypunct}{} %remove the full stop at the 
+%%end of each bibliography entry
+\renewcommand*{\revsdnamepunct}{} %remove commas between last 
+%and first names in bibliography
+
+%remove "In:" for articles in bibliography
+\renewbibmacro{in:}{\ifentrytype{article}{}
+	{\printtext{\bibstring{in}\intitlepunct}}}
+
+\addbibresource{References.bib}
 
@@
 
+\section{Introduction}
+\label{sec:Introduction}
+
+The papers we may review:   
+\textcite{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},
+
+Rules for building simplification; see \textcite{Lee2005}
+
 \section{Discussion}
@@
 Voronoi cells of these buildings. This idea about Voronoi cells 
-is used in Topologically Safe Curved Schematization (van Goethem 
-et al. 2013). We may need to try different possible covers. 
+is used in \textcite{vanGoethem2013}. We may need to try 
+different 
+possible covers. 
 Unfortunately, this trying may be very time-consuming, probably 
@@
 building with width less than 
-$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S$ should be eliminated.
+$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S_i$ should be eliminated.
 In order to make sure that some small buildings will be 
@@
 operations, we eliminate the buildings with area less than 
-$d^2_i$.
+$A_i$.
 

### 2017-03-31 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
having written down our basic idea; implementing our method

@@
 }
-\newcommand{\Astar}{A$^{\!\star}$\xspace}
-\newcommand{\tstar}{\ensuremath{t\xspace}}
-\newcommand{\Pistar}{\ensuremath{\Pi}} % {\Pi_{\mathrm{start}}(\tstar)}
-\newcommand{\Pstart}{\ensuremath{\mathpzc{P}_\mathrm{start}}\xspace}
-\newcommand{\Pgoal}{\ensuremath{\mathpzc{P}_\mathrm{goal}}\xspace}
-\newcommand{\Pnode}{\ensuremath{\mathpzc{P}_{t,i}}\xspace}
-\newcommand{\Tgoal}{\ensuremath{T_\mathrm{goal}}\xspace}
 
@@
 %\renewcommand\thesubsection{\thesection.\arabic{subsection}}
-
-\newcolumntype{x}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}b{#1}}
-\newcolumntype{y}[1]{>{\centering\arraybackslash\hspace{0pt}}b{#1}}
-%\newcolumntype{y}[2]{>{\centering\arraybackslash\hspace{0pt}}D{.}{.}{#1}b{#2}}
-%\newcolumntype{d}[1]{D{.}{.}{#1}}
-\newcolumntype{L}{>{$}l<{$}}% math-mode version of "l" column 
-%type
-\newcolumntype{R}{>{$}r<{$}}% math-mode version of "r" column 
-%type
-\newcolumntype{C}{>{$}c<{$}}% math-mode version of "c" column 
-%type
-
-%This style looks better than $\mathrm{non-comp}$ in which "-" 
-%looks like the symbol of minus 
-\newcommand\nonhyphencomp{\operatorname{non-comp}}
-\newcommand\inthyphenleng{\operatorname{int-leng}}
-\newcommand\goalhyphentype{\operatorname{goal-type}}
-\newcommand\goalhyphennon{\operatorname{goal-non}}
-\newcommand\goalhyphenshape{\operatorname{goal-shape}}
-%\newcolumntype{y}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}p{#1}}
-%\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
 
@@
 
-\newcommand{\myabstract}{text}
+\newcommand{\myabstract}{We proposed a method to continuous 
+generalization of buildings from a start scale to a goal scale. 
+%
+For each building at the start scale, we generate its 
+generalized form at 
+the goal scale by enlarging and simplifying. Then we grow the  
+building to the 
+generalized form to realize continuous transformation. During 
+the 
+growing, we aggregate two buildings once they become too close 
+to each other. We generate a new generalized form at the goal 
+scale for 
+the aggregated building so that we can continue growing.
+%
+After finishing the growing, we take the goal scale as the 
+start scale and repeat our continuous generalization. The start 
+scale and the target scale should not be too far away because we 
+want the intermediate results to be somewhat simplified.
+
+Our contribution is as follows. First, the buildings 
+are enlarged continuously and at the same time are simplified. 
+Second, the distance between each pair of two buildings is 
+always larger than a specified distance. Third, there is no thin 
+part in our results.}
+
+%We proposed a method to continuous 
+%generalization of buildings from a start scale to a goal scale. 
+%%
+%For each building at the start scale, we enlarge it by 
+%buffering. We simplify the enlarged building by the operator of 
+%dilation-erosion-erosion-dilation. Then we merge the 
+%simplified form with the original 
+%building so that the merged result completely contains the 
+%original 
+%shape. We use the merged shape as the building at the goal 
+%scale, and grow the original building to the 
+%goal shape to realize continuous transformation. 
+%%
+%During the 
+%growing, if two buildings become too close to each other, we 
+%aggregate them to avoid narrow gap. To aggregate, we dilate and 
+%merge the two buildings, then we erode the merged shape. To 
+%avoid 
+%failure or thin parts from the aggregation, we construct a 
+%skeleton of the dilated and merged form. We make a buffer of 
+%the 
+%skeleton 
+%and merge the buffer with the eroded shape. We take the 
+%aggregated shape which may be merged with the skeleton buffer 
+%as 
+%a new 
+%building and generate its goal shape at the goal scale so that 
+%we can grow this new building.
+%
+%Once we arrive at the goal scale, we take the goal scale as the 
+%start scale and repeat our continuous generalization. The start 
+%scale and the target scale cannot be too far away because we 
+%want to see some simplification during the growing of buildings.
+%%
+%There are several advantages of our method. First, the 
+%buildings 
+%are enlarged continuously and the same time are simplified. 
+%Second, the distance between each pair of two buildings is 
+%always larger than a specified distance. Third, there is no 
+%thin 
+%part in our results.
 
@@
 Rules for building simplification; see \textcite{Lee2005}
+
+Straight skeletons for map generalization: 
+\textcite{Gold2003,Matuk2006}
+
+Geometric Simplication of Administrative Borders With Mixture of
+Irregular and Orthogonal Segments \parencite{Samsonov2016}
+
+\citetitle{Damen2008} \parencite{Damen2008}
 
@@
 
-Text
+Because of our aggregation with skeletons and original 
+buildings, we may have too many details in the intermediate 
+results.
+
+Some buildings are too small to be eroded. We have to generate 
+squares or MBR?
+
+To make it more efficient for on line displaying, we may need 
+some external memories. First, we store the data at some key 
+scales so that we may start a generalization from the immediate 
+larger scale; $O(n)$ space. Second, we store the target shape 
+for each building; $O(n)$ space. Third, we store the aggregation 
+time and the target form for the aggregated shape; $O(n^2)$ 
+space if we count vertex number.
+%
+The displaying time is dependent on buffering and clipping. The 
+two operators are from library Clipper. The efficiency of the 
+buffering function of this library has been evaluated by 
+\textcite{Palfrader2015}.
+
+One can also discuss about our growing speed.
 

### 2017-03-31 ContinuousGeneralizer/MorphingClass/CGeometry/CMBR/Geometry/Line2d.cs

@@ -1,0 +1,45 @@
+﻿//using System;
+//using U4LongLiveTheSquare;
+//using Eto.Drawing;
+
+//namespace Efalg5GeometrischeAlgo
+//{
+//	public class Line2d : IGeometry
+//	{
+//		/// <summary>
+//		/// Position Vector of line.
+//		/// </summary>
+//		/// <value>Position Vector</value>
+//		public Vector2d A{ get; set; }
+
+//		/// <summary>
+//		/// Direction Vector of the line.
+//		/// B - A
+//		/// </summary>
+//		/// <value>The direction.</value>
+//		public Vector2d R{ get; set; }
+
+//		public Line2d (Vector2d position, Vector2d direction)
+//		{
+//			A = position;
+//			R = direction;
+//		}
+
+//		#region IGeometry implementation
+
+//		public GraphicsPath GraphicsPath {
+//			get {
+//				var gp = new GraphicsPath ();
+
+//				var b = A + R;
+//				var lc = 10000f;
+//				gp.AddLine ((float)A.X - lc, (float)A.Y - lc, (float)b.X + lc, (float)b.Y + lc);
+
+//				return gp;
+//			}
+//		}
+
+//		#endregion
+//	}
+//}
+

### 2017-03-31 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CCGABM.cs

@@ -218,8 +218,11 @@ namespace MorphingClass.CMorphingMethods
             CDCEL pInterSSDCEL = new CDCEL(InterSSCplLt);
             pInterSSDCEL.ConstructDCEL();
 
-            var pInterLSCptLt = pInterLSDCEL.FaceCpgLt[1].TraverseFaceToGenerateCptLt();  //there are only two faces: the super face and a normal face
-            pInterSSDCEL.FaceCpgLt[1].TraverseFaceToGenerateCptLt();  //there are only two faces: the super face and a normal face
+            
+            //I need to check if we realy need a counter clockwise direction
+            var pInterLSCptLt = pInterLSDCEL.FaceCpgLt[1].GetOuterCptEb(false).ToList();  //there are only two faces: the super face and a normal face
+            //I need to check if we realy need a counter clockwise direction
+            pInterSSDCEL.FaceCpgLt[1].GetOuterCptEb(false).ToList();  //there are only two faces: the super face and a normal face
 
             var pInterLSCptSD = pInterLSCptLt.ToSD(cpt => cpt, new CCompareCptYX_VerySmall()); //we maintaine this SD so that for a point from single polyline, we can know whether this single point overlaps a point of a larger-scale polyline
 
@@ -487,7 +490,7 @@ namespace MorphingClass.CMorphingMethods
                 CareCEdgeLt.Add(CurrentCEdge);
                 CurrentCEdge = CurrentCEdge.cedgeNext;
 
-            } while (CurrentCEdge.indexID != cedge.indexID);
+            } while (CurrentCEdge.GID != cedge.GID);
 
             return CareCEdgeLt;
         }

### 2017-05-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished implementing the target forms of the buildings; removed some old results

@@
 
-Geometric Simplication of Administrative Borders With Mixture of
+Geometric Simplification of Administrative Borders With Mixture 
+of
 Irregular and Orthogonal Segments \parencite{Samsonov2016}
@@
 \citetitle{Damen2008} \parencite{Damen2008}
+
+An example of enlargement in aggregation: \citetitle{Neun2005}
+
+Using MST to group buildings: \textcite{Zhang2013, 
+Cetinkaya2015,Deng2017,Regnauld1996}
 

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmAid/FrmEnlargeLayer.cs

@@ -87,14 +87,14 @@ namespace ContinuousGeneralizer.FrmAid
             //SFD.ShowDialog();
             //string strPath = SFD.FileName;
             ////string strName=SFD.
-            //ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(strPath);
+            //ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(strPath);
 
 
             //long lngStartTime = System.Environment.TickCount; //记录开始时间
 
             //if ((pFeatureLayer.FeatureClass != null) && (pFeatureLayer.FeatureClass.ShapeType == esriGeometryType.esriGeometryPolyline))
             //{
-            //    List<CPolyline> CPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pFeatureLayer);
+            //    List<CPolyline> CPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pFeatureLayer);
             //    List<CPolyline> CPlLtNew = new List<CPolyline>();
             //    for (int i = 0; i < CPlLt.Count; i++)
             //    {
@@ -110,13 +110,13 @@ namespace ContinuousGeneralizer.FrmAid
             //        CPlLtNew.Add(newcpl);
             //    }
 
-            //    CHelperFunction.SaveCPlLt(CPlLtNew, pFeatureLayer.Name + "_Enlarged", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            //    CHelpFunc.SaveCPlLt(CPlLtNew, pFeatureLayer.Name + "_Enlarged", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
 
             //}
             //else if ((pFeatureLayer.FeatureClass != null) && (pFeatureLayer.FeatureClass.ShapeType == esriGeometryType.esriGeometryPolygon))
             //{
             //    //获取多边形数组
-            //    List<CPolygon> CPolygonLt = CHelperFunction.GetCPolygonLtByFeatureLayer(pFeatureLayer);
+            //    List<CPolygon> CPolygonLt = CHelpFunc.GetCPolygonLtByFeatureLayer(pFeatureLayer);
             //    List<CPolygon> CPolygonLtNew = new List<CPolygon>();
             //    for (int i = 0; i < CPolygonLt.Count; i++)
             //    {
@@ -132,7 +132,7 @@ namespace ContinuousGeneralizer.FrmAid
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmAid/FrmLookingForNeighboursGrids.cs

@@ -91,8 +91,8 @@ namespace ContinuousGeneralizer.FrmAid
             //SFD.ShowDialog();
             //string strPath = SFD.FileName;
             //ParameterInitialize.strSavePath = strPath;
-            //ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(strPath);
-            //List<CPoint> CptLt = CHelperFunction.GetCPtLtByFeatureLayer(pFeatureLayer);
+            //ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(strPath);
+            //List<CPoint> CptLt = CHelpFunc.GetCPtLtByFeatureLayer(pFeatureLayer);
             //for (int i = 0; i < CptLt.Count; i++)
             //{
             //    CptLt[i].GID = i;
@@ -140,8 +140,8 @@ namespace ContinuousGeneralizer.FrmAid
             //        //dbldetailedltlt.Add(dbldetailedlt);
             //    }
             //}
-            //CHelperFunctionExcel.ExportDataltltToExcelSW(dbldetailedltlt, CptLt.Count.ToString() + "_" + dblThreshold.ToString() + "Links", ParameterInitialize.strSavePath);
-            //CHelperFunction.SaveESRIObjltfast(iplobjlt, esriGeometryType.esriGeometryPolyline, CptLt.Count.ToString() + "_" + dblThreshold.ToString() + "Links", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            //CHelpFuncExcel.ExportDataltltToExcelSW(dbldetailedltlt, CptLt.Count.ToString() + "_" + dblThreshold.ToString() + "Links", ParameterInitialize.strSavePath);
+            //CHelpFunc.SaveESRIObjltfast(iplobjlt, esriGeometryType.esriGeometryPolyline, CptLt.Count.ToString() + "_" + dblThreshold.ToString() + "Links", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
         }
 
 
@@ -158,14 +158,14 @@ namespace ContinuousGeneralizer.FrmAid
             SFD.ShowDialog();
             string strPath = SFD.FileName;
             ParameterInitialize.strSavePath = strPath;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(strPath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(strPath);
 
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphing/FrmBLGOptCorMMSimplified.cs

@@ -73,7 +73,7 @@ namespace ContinuousGeneralizer.FrmMorphing
             SFD.ShowDialog();
             if (SFD.FileName == null || SFD.FileName == "") return;
             ParameterInitialize.strSavePath = SFD.FileName;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(ParameterInitialize.strSavePath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(ParameterInitialize.strSavePath);
 
             //¶ÁÈ¡Êý¾Ý
             try
@@ -95,73 +95,73 @@ namespace ContinuousGeneralizer.FrmMorphing
         private void btn010_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.1;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn020_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.2;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn030_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.3;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn040_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.4;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn050_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.5;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphing/FrmBSBLGOptCor.cs

@@ -75,7 +75,7 @@ namespace ContinuousGeneralizer.FrmMorphing
             SFD.ShowDialog();
             if (SFD.FileName == null || SFD.FileName == "") return;
             ParameterInitialize.strSavePath = SFD.FileName;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(ParameterInitialize.strSavePath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(ParameterInitialize.strSavePath);
 
             //¶ÁÈ¡Êý¾Ý
             try
@@ -97,73 +97,73 @@ namespace ContinuousGeneralizer.FrmMorphing
         private void btn010_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.1;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn020_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.2;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn030_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.3;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn040_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.4;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn050_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.5;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphing/FrmBSBLGOptCorMM.cs

@@ -75,7 +75,7 @@ namespace ContinuousGeneralizer.FrmMorphing
             SFD.ShowDialog();
             if (SFD.FileName == null || SFD.FileName == "") return;
             ParameterInitialize.strSavePath = SFD.FileName;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(ParameterInitialize.strSavePath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(ParameterInitialize.strSavePath);
 
             //¶ÁÈ¡Êý¾Ý
             try
@@ -97,73 +97,73 @@ namespace ContinuousGeneralizer.FrmMorphing
         private void btn010_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.1;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn020_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.2;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn030_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.3;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn040_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.4;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
         private void btn050_Click(object sender, EventArgs e)
         {
             _dblProportion = 0.5;
-            _RelativeInterpolationCpl = CHelperFunction.DisplayInterpolation(_DataRecords, _dblProportion);
+            _RelativeInterpolationCpl = CHelpFunc.DisplayInterpolation(_DataRecords, _dblProportion);
         }
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphingLSA/FrmALL.cs

@@ -47,7 +47,7 @@ namespace ContinuousGeneralizer.FrmMorphingLSA
             SFD.ShowDialog();
             if (SFD.FileName == null || SFD.FileName == "") return;
             ParameterInitialize.strSavePath = SFD.FileName;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(ParameterInitialize.strSavePath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(ParameterInitialize.strSavePath);
             _pALL = new CALL(_DataRecords);
             _RelativeInterpolationCpl = _DataRecords.ParameterResult.FromCpl;
         }
@@ -169,7 +169,7 @@ namespace ContinuousGeneralizer.FrmMorphingLSA
             List<CPolyline> cpllt = new List<CPolyline>();
             cpllt.Add(_RelativeInterpolationCpl);
             string strFileName = _dblProportion.ToString();
-            CHelperFunction.SaveCPlLt(cpllt, strFileName, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            CHelpFunc.SaveCPlLt(cpllt, strFileName, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
         }
 
 

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphingLSA/FrmApLALMulti.cs

@@ -60,11 +60,11 @@ namespace ContinuousGeneralizer.FrmMorphingLSA
             SFD.ShowDialog();
             if (SFD.FileName == null || SFD.FileName == "") return;
             ParameterInitialize.strSavePath = SFD.FileName;
-            ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(ParameterInitialize.strSavePath);
+            ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(ParameterInitialize.strSavePath);
             _pApLALMulti = new CApLALMulti(_DataRecords);
             _pApLALMulti.ApLALMultiMorphing();
 
-            CHelperFunction.SaveCPlLt(_DataRecords.ParameterResult.CResultPlLt, "ApLALMulti", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            CHelpFunc.SaveCPlLt(_DataRecords.ParameterResult.CResultPlLt, "ApLALMulti", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
         } 
     }
 }

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphingLSA/testinherit.Designer.cs

@@ -1,38 +1,0 @@
-﻿namespace ContinuousGeneralizer.FrmMorphingLSA
-{
-    partial class testinherit
-    {
-        /// <summary>
-        /// Required designer variable.
-        /// </summary>
-        private System.ComponentModel.IContainer components = null;
-
-        /// <summary>
-        /// Clean up any resources being used.
-        /// </summary>
-        /// <param name="disposing">true if managed resources should be disposed; otherwise, false.</param>
-        protected override void Dispose(bool disposing)
-        {
-            if (disposing && (components != null))
-            {
-                components.Dispose();
-            }
-            base.Dispose(disposing);
-        }
-
-        #region Windows Form Designer generated code
-
-        /// <summary>
-        /// Required method for Designer support - do not modify
-        /// the contents of this method with the code editor.
-        /// </summary>
-        private void InitializeComponent()
-        {
-            this.components = new System.ComponentModel.Container();
-            this.AutoScaleMode = System.Windows.Forms.AutoScaleMode.Font;
-            this.Text = "testinherit";
-        }
-
-        #endregion
-    }
-}

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmRoadNetwork/FrmClassification.cs

@@ -68,7 +68,7 @@ namespace ContinuousGeneralizer.RoadNetwork
             //SaveFileDialog SFD = new SaveFileDialog();
             //SFD.ShowDialog();
             //string strPath = SFD.FileName;
-            //ParameterInitialize.pWorkspace = CHelperFunction.OpenWorkspace(strPath);
+            //ParameterInitialize.pWorkspace = CHelpFunc.OpenWorkspace(strPath);
 
             ////获取当前选择的点要素图层
             ////大比例尺要素图层
@@ -82,12 +82,12 @@ namespace ContinuousGeneralizer.RoadNetwork
             //ParameterInitialize.pSSFLayer = pSSFLayer;
 
             ////获取线数组
-            //List<CPolyline> LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            //List<CPolyline> SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
+            //List<CPolyline> LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            //List<CPolyline> SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
 
             //CParameterThreshold ParameterThreshold = new CParameterThreshold();
-            //ParameterThreshold.dblBuffer = CGeometricMethods.CalMidLength(LSCPlLt);
-            //ParameterThreshold.dblVerySmall = CGeometricMethods.CalVerySmall(LSCPlLt);
+            //ParameterThreshold.dblBuffer = CGeoFunc.CalMidLength(LSCPlLt);
+            //ParameterThreshold.dblVerySmall = CGeoFunc.CalVerySmall(LSCPlLt);
             //double dblBound = 0.95;
             //ParameterThreshold.dblDLengthBound = dblBound;
             //ParameterThreshold.dblULengthBound = 1 / dblBound;
@@ -99,7 +99,7 @@ namespace ContinuousGeneralizer.RoadNetwork
 
 
             ////Save
-            //CHelperFunction.SaveCPlLt(SingleCPlLt, "SingleCPl", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            //CHelpFunc.SaveCPlLt(SingleCPlLt, "SingleCPl", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
 
 
[…]

### 2017-05-16 ContinuousGeneralizer/ContinuousGeneralizer/Program.cs

@@ -22,6 +22,9 @@ namespace ContinuousGeneralizer
                 }
             }
 
+            ESRI.ArcGIS.esriSystem.IAoInitialize ao = new ESRI.ArcGIS.esriSystem.AoInitialize();
+            ao.Initialize(ESRI.ArcGIS.esriSystem.esriLicenseProductCode.esriLicenseProductCodeAdvanced);
+
             Application.EnableVisualStyles();
             Application.SetCompatibleTextRenderingDefault(false);
             Application.Run(new FrmContinuousGeneralizer());

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CAid/CStatisticsOfDataSets.cs

@@ -59,9 +59,9 @@ namespace MorphingClass.CAid
                 AllPtLt.AddRange(cptlt);
             }
 
-            C5.LinkedList<CCorrCpts> CorrCptsLt = CGeometricMethods.LookingForNeighboursByGrids(EndPtLt, CConstants.dblVerySmall);
-            int intIntersection = CGeometricMethods.GetNumofIntersections(CorrCptsLt);
-            int intAlonePt = CGeometricMethods.CountAlonePt(EndPtLt);
+            C5.LinkedList<CCorrCpts> CorrCptsLt = CGeoFunc.LookingForNeighboursByGrids(EndPtLt, CConstants.dblVerySmallCoord);
+            int intIntersection = CGeoFunc.GetNumofIntersections(CorrCptsLt);
+            int intAlonePt = CGeoFunc.CountAlonePt(EndPtLt);
             int intRealPtNum = intInnerPtNum + intIntersection + intAlonePt;
 
 
@@ -71,7 +71,7 @@ namespace MorphingClass.CAid
 
             int intEdgeCount = GetAllReadCEdgeLt<CPolyline>().Count;
 
-            var pCEnv = CGeometricMethods.GetEnvelope(pCPlLt);
+            var pCEnv = CGeoFunc.GetEnvelope(pCPlLt);
 
 
             long lngEndTime = System.Environment.TickCount;//记录结束时间

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CAid/CUnifyIndicesPolylines.cs

@@ -77,7 +77,7 @@ namespace MorphingClass.CAid
             {
                 for (int j = 0; j < pSSCPlLt.Count; j++)
                 {
-                    double dblOverlapArea = CGeometricMethods.CalOverlapArea(pLSCPlLt[i].pBufferGeo, pSSCPlLt[j].pBufferGeo);
+                    double dblOverlapArea = CGeoFunc.CalOverlapArea(pLSCPlLt[i].pBufferGeo, pSSCPlLt[j].pBufferGeo);
                     double dblOverlapRatioLS = dblOverlapArea / pLSCPlLt[i].dblBufferArea;
                     double dblOverlapRatioSS = dblOverlapArea / pSSCPlLt[j].dblBufferArea;
 

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CCorrepondObjects/CCorrCpgSS.cs

@@ -18,7 +18,7 @@ namespace MorphingClass.CCorrepondObjects
 
         public int CompareTo(CCorrCpgSS other)
         {
-            return CCompareMethods.CompareColConsideringCount(FrCpgSS, ToCpgSS, cpg => cpg.GID);
+            return CCmpMethods.CmpColConsideringCount(FrCpgSS, ToCpgSS, cpg => cpg.GID);
         }
     }
 }

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CCorrepondObjects/CCorrCphs.cs

@@ -14,7 +14,7 @@ namespace MorphingClass.CCorrepondObjects
 {
     public class CCorrCphs : CBasicBase
     {
-        public static CCompareCCorrCphs_CphsGID pCompareCCorrCphs_CphsGID = new CCompareCCorrCphs_CphsGID();
+        public static CCmpCCorrCphs_CphsGID pCmpCCorrCphs_CphsGID = new CCmpCCorrCphs_CphsGID();
         private static int _intStaticGID;
         public CPatch FrCph { get; set; }
         public CPatch ToCph { get; set; }
@@ -79,9 +79,9 @@ namespace MorphingClass.CCorrepondObjects
 
         //public int CompareTo(CCorrCphs other)
         //{
-        //    return CCompareMethods.CompareDual(this, other, corrcphs => corrcphs.FrCph.GID, corrcphs => corrcphs.ToCph.GID, CConstants.ComparerInt);
+        //    return CCmpMethods.CmpDual(this, other, corrcphs => corrcphs.FrCph.GID, corrcphs => corrcphs.ToCph.GID, CConstants.ComparerInt);
 
-        //    //return CCompareMethods.Compare(this.FrCph.CpgSS, ToCpgSS, cpg => cpg.GID);
+        //    //return CCmpMethods.Cmp(this.FrCph.CpgSS, ToCpgSS, cpg => cpg.GID);
         //}
     }
 }

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CEvaluationMethods/CEvaluation.cs

@@ -204,8 +204,8 @@ namespace MorphingClass.CEvaluationMethods
         /// <returns>the integral distance between the two line segments</returns>
         private static double CalDeflection(CCorrCpts LastCorrCpts, CCorrCpts CurrentCorrCpts, double dblFrTotalLength, double dblToTotalLength)
         {
-            double dblfrlength = CGeometricMethods.CalDis(LastCorrCpts.FrCpt, CurrentCorrCpts.FrCpt);
-            double dbltolength = CGeometricMethods.CalDis(LastCorrCpts.ToCpt, CurrentCorrCpts.ToCpt);
+            double dblfrlength = CGeoFunc.CalDis(LastCorrCpts.FrCpt, CurrentCorrCpts.FrCpt);
+            double dbltolength = CGeoFunc.CalDis(LastCorrCpts.ToCpt, CurrentCorrCpts.ToCpt);
 
             return CalDeflectionSub(LastCorrCpts, CurrentCorrCpts, dblfrlength, dbltolength);
         }
@@ -257,7 +257,7 @@ namespace MorphingClass.CEvaluationMethods
             double dblIntegral = 0;
 
             //we have a>=0
-            if (CCompareMethods.CompareSquare(a, 0) == 0) //then b==0
+            if (CCmpMethods.CmpSquare(a, 0) == 0) //then b==0
             {
                 dblIntegral = Math.Sqrt(c);
             }
@@ -279,7 +279,7 @@ namespace MorphingClass.CEvaluationMethods
                 double dblSecondPart = 0;
 
                 //two line segments are parallel to each other is a special case of Delta=0, notice that the distance between the two parallel segments is changing
-                if (CCompareMethods.ComparePower4(pQuadraticEquation.dblDelta, 0) != 0)
+                if (CCmpMethods.CmpPower4(pQuadraticEquation.dblDelta, 0) != 0)
                 {
                     double dblSqrtA = Math.Sqrt(a);
                     double dblTwoSqrtA = 2 * dblSqrtA;

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CGeneralizationMethods/CGDNWDD.cs

@@ -53,7 +53,7 @@ namespace MorphingClass.CGeneralizationMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _CPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pFeatureLayer);
+            _CPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pFeatureLayer);
 
         }
 
@@ -64,7 +64,7 @@ namespace MorphingClass.CGeneralizationMethods
             //CParameterInitialize pParameterInitialize = _ParameterInitialize;
 
             //CParameterThreshold pParameterThreshold = new CParameterThreshold();
-            //pParameterThreshold.dblVerySmall = CGeometricMethods.CalVerySmall(CPlLt);
+            //pParameterThreshold.dblVerySmall = CGeoFunc.CalVerySmall(CPlLt);
             //List<CRiverNet> CRiverNetLt = BuildRiverNetLt(CPlLt, pParameterThreshold);     //依据线数据建立河网
             //CalWeightiness(CRiverNetLt, pParameterInitialize);                              //计算河流的重要性
 
@@ -75,7 +75,7 @@ namespace MorphingClass.CGeneralizationMethods
             //{
             //    CResultRiverLt.AddRange(CRiverNetLt[i].CRiverLt);
             //}
-            //CGeometricMethods.CalWeightinessUnitary(CResultRiverLt);
+            //CGeoFunc.CalWeightinessUnitary(CResultRiverLt);
 
 
 
@@ -93,7 +93,7 @@ namespace MorphingClass.CGeneralizationMethods
         public List<CRiverNet> BuildRiverNetLt(List<CPolyline> CPlLt, CParameterThreshold pParameterThreshold)
         {
 
-            double dblVerySmall = CConstants.dblVerySmall;
+            double dblVerySmall = CConstants.dblVerySmallCoord;
 
             //根据线数据生成河流数据
             List<CRiver> CAllRiverLt = new List<CRiver>();

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CGeometry/CFace.cs

@@ -148,7 +148,7 @@
 //            _CptLt = cptlt;
 
 //            _intID = intID;
-//            _CEdgeLt = CGeometricMethods.FormCEdgeLt(cptlt);
+//            _CEdgeLt = CGeoFunc.FormCEdgeLt(cptlt);
 //            //FormPolygon(cptlt);
 //        }
 
@@ -156,10 +156,10 @@
 //        {
 //            _intID = intID;
 //            this.pPolygon = pPolygon;
-//            List<CPoint> cptlt = CHelperFunction.GetCPtLtByIPG(pPolygon);
+//            List<CPoint> cptlt = CHelpFunc.GetCPtLtByIPG(pPolygon);
 //            _CptLt = cptlt;
 
-//            _CEdgeLt = CGeometricMethods.FormCEdgeLt(cptlt);
+//            _CEdgeLt = CGeoFunc.FormCEdgeLt(cptlt);
 //            //FormPolygon(cptlt);
 //        }
 
@@ -168,7 +168,7 @@
 //        {
 //            if (this .pPolygon ==null)
 //            {
-//                IPointCollection4 pPntCtl = CHelperFunction.GetPointCollectionFromCptLt(cptlt);
+//                IPointCollection4 pPntCtl = CHelpFunc.GetPointCollectionFromCptLt(cptlt);
 //                this.pPolygon = pPntCtl as IPolygon4;
 //                this.pPolygon.Close();
 //            }

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CGeometry/CPolygon.cs

@@ -34,9 +34,9 @@ namespace MorphingClass.CGeometry
         public int intType { get; set; }
         public int intTypeIndex { get; set; } //the index (0, 1, 2, ...) of a type; used for access type distance directly
 
-        public List<List<CEdge>> CEdgeLtLt { get; set; }
+        public CPolygon ParentCpg { get; set; }
 
-
+        public List<CPolygon> HoleCpgLt { get; set; }
         public CPoint CentroidCptSimple { get; set; }
 
         //public CPolygon AssigningFace { get; set; }
@@ -48,76 +48,163 @@ namespace MorphingClass.CGeometry
         private CPoint _LeftMostCpt;
         private bool _IsHole;
         private bool _IsMerged;
+        //private Func<IEnumerable<List<CPoint>>> getHoleCptLtEb;
 
         /// <summary>
         /// Initializes a new instance of a triangle
         /// </summary>
-        public CPolygon(int intID)
-            : this(intID, CHelperFunction.MakeLt<List<CPoint>>(0))
-        {
-        }
+        //public CPolygon(int intID=-2)
+        //    : this(intID, CHelpFunc.MakeLt<CPoint>(0))
+        //{
+        //}
 
-        /// <summary>
-        /// Initializes a new instance of a triangle
-        /// </summary>
-        public CPolygon()
-            : this(-2, CHelperFunction.MakeLt<List<CPoint>>(0))
-        {
-        }
+        ///// <summary>
+        ///// Initializes a new instance of a triangle
+        ///// </summary>
+        //public CPolygon()
+        //    : this(-2, CHelpFunc.MakeLt<List<CPoint>>(0))
+        //{
+        //}
 
 
 
         public CPolygon(int intID, IPolygon4 pPolygon, double dblFactor = 1)
-            : this(intID, CHelperFunction.GetCPtLtLtByIPG(pPolygon, dblFactor))
+            : this(intID, CHelpFunc.GetIpgExteriorCptLt(pPolygon, dblFactor).ToList(), 
+                  CHelpFunc.GetIpgInteriorCptLtEb(pPolygon, dblFactor))
         {
             this.pPolygon = pPolygon;
         }
 
-        public CPolygon(int intID, List<CPoint> cptlt)
-            : this(intID, CHelperFunction.MakeLt(1, cptlt))
+        //public CPolygon(int intID, List<CPoint> cptlt)
+        //    : this(intID, CHelpFunc.MakeLt(1, cptlt))
+        //{
+        //}
+
+        /// <summary>
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CGeometry/CPolyline.cs

@@ -28,7 +28,7 @@ namespace MorphingClass.CGeometry
         protected IPolyline5 _pPolyline;
 
 
-        //protected CHelperFunction _pHelperFunction=new CHelperFunction ();
+        //protected CHelpFunc _pHelperFunction=new CHelpFunc ();
         protected CPolyline _CorrCPl;
 
 
@@ -58,6 +58,7 @@ namespace MorphingClass.CGeometry
 
 
         public CPolyline()
+            : this(-2, CHelpFunc.MakeLt<CPoint>(0))
         {
 
         }
@@ -74,7 +75,7 @@ namespace MorphingClass.CGeometry
         }
 
         public CPolyline(int intID, IPolyline5 pPolyline)
-            : this(intID, CHelperFunction.GetCPtLtByIPl(pPolyline), false)
+            : this(intID, CHelpFunc.GetCPtLtByIPl(pPolyline), false)
         {
             this.pPolyline = pPolyline;
         }
@@ -92,13 +93,13 @@ namespace MorphingClass.CGeometry
         }
 
         public CPolyline(CPoint cpt, bool blnSetPolyline = false)
-            : this(cpt.ID, CHelperFunction.MakeLt<CPoint>(1, cpt, null, null), blnSetPolyline)
+            : this(cpt.ID, CHelpFunc.MakeLt<CPoint>(1, cpt, null, null), blnSetPolyline)
         {
 
         }
 
         public CPolyline(int intID, CPoint cpt, bool blnSetPolyline = false)
-            : this(intID, CHelperFunction.MakeLt<CPoint>(1, cpt, null, null), blnSetPolyline)
+            : this(intID, CHelpFunc.MakeLt<CPoint>(1, cpt, null, null), blnSetPolyline)
         {
 
         }
@@ -121,12 +122,12 @@ namespace MorphingClass.CGeometry
         }
 
         public CPolyline(CPoint cpt1, CPoint cpt2, bool blnSetPolyline = false)
-            : this(cpt1.ID, CHelperFunction.MakeLt<CPoint>(2, cpt1, cpt2, null), blnSetPolyline)
+            : this(cpt1.ID, CHelpFunc.MakeLt<CPoint>(2, cpt1, cpt2, null), blnSetPolyline)
         {
         }
 
         public CPolyline(int intID, CPoint cpt1, CPoint cpt2, bool blnSetPolyline = false)
-            : this(intID, CHelperFunction.MakeLt<CPoint>(2, cpt1, cpt2, null), blnSetPolyline)
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingAlgorithms/CVertexInsertionA.cs

@@ -104,10 +104,10 @@ namespace MorphingClass.CMorphingAlgorithms
         private void InsertVertex(List<CPoint> cptlt, int intInsertNum)
         {
             //将每个点及与其之前点的距离存入按距离从小到大存入数组
-            SortedList<double, CPoint> dblDisLt = new SortedList<double, CPoint>(new CCompareDbl());
+            SortedList<double, CPoint> dblDisLt = new SortedList<double, CPoint>(new CCmpDbl());
             for (int i = 1; i < cptlt.Count; i++)
             {
-                double dblDis = CGeometricMethods.CalDis(cptlt[i - 1], cptlt[i]);
+                double dblDis = CGeoFunc.CalDis(cptlt[i - 1], cptlt[i]);
                 dblDisLt.Add(dblDis, cptlt[i]);
             }
 

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingExtent/CBase.cs

@@ -62,7 +62,7 @@ namespace MorphingClass.CMorphingExtend
             IGraphicsContainer pGra = m_mapControl.Map as IGraphicsContainer;
             pGra.DeleteAllElements();
             m_mapControl.ActiveView.Refresh();
-            CHelperFunction.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
+            CHelpFunc.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
             return cpl;
         }
 
@@ -176,9 +176,9 @@ namespace MorphingClass.CMorphingExtend
             for (int i = 0; i < pCorrCptsLt.Count - 2; i++)
             {
                 //较大比例尺线状要素上的夹角
-                double dblfrAngle = CGeometricMethods.CalAngle_Counterclockwise(pCorrCptsLt[i].FrCpt, pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i + 2].FrCpt);
+                double dblfrAngle = CGeoFunc.CalAngle_Counterclockwise(pCorrCptsLt[i].FrCpt, pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i + 2].FrCpt);
                 //较小比例尺线状要素上的夹角
-                double dbltoAngle = CGeometricMethods.CalAngle_Counterclockwise(pCorrCptsLt[i].ToCpt, pCorrCptsLt[i + 1].ToCpt, pCorrCptsLt[i + 2].ToCpt);
+                double dbltoAngle = CGeoFunc.CalAngle_Counterclockwise(pCorrCptsLt[i].ToCpt, pCorrCptsLt[i + 1].ToCpt, pCorrCptsLt[i + 2].ToCpt);
 
                 //角度初始值
                 adblAngle0[i] = (1 - dblProportion) * dblfrAngle + dblProportion * dbltoAngle;
@@ -318,7 +318,7 @@ namespace MorphingClass.CMorphingExtend
                     }
                     else
                     {
-                        double dblNewAngle = CGeometricMethods.CalAngle_Counterclockwise(Xmix[2 * intSumCount + 0, 0], Xmix[2 * intSumCount + 1, 0],
+                        double dblNewAngle = CGeoFunc.CalAngle_Counterclockwise(Xmix[2 * intSumCount + 0, 0], Xmix[2 * intSumCount + 1, 0],
                                                                        Xmix[2 * intSumCount + 2, 0], Xmix[2 * intSumCount + 3, 0],
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CAdministrativeBoundaryMorphing.cs

@@ -61,9 +61,9 @@ namespace MorphingClass.CMorphingMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            _SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
-            _SgCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSgFLayer);
+            _LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            _SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
+            _SgCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSgFLayer);
         }
 
 
@@ -77,14 +77,14 @@ namespace MorphingClass.CMorphingMethods
             //List<CPolyline> SgCPlLt = _SgCPlLt;
 
             
-            ////int intBSNum = CHelperFunction.GetPtNumFromCplLt(LSCPlLt);
-            ////int intSSNum = CHelperFunction.GetPtNumFromCplLt(SSCPlLt);
-            ////int intSgNum = CHelperFunction.GetPtNumFromCplLt(SgCPlLt);
+            ////int intBSNum = CHelpFunc.GetPtNumFromCplLt(LSCPlLt);
+            ////int intSSNum = CHelpFunc.GetPtNumFromCplLt(SSCPlLt);
+            ////int intSgNum = CHelpFunc.GetPtNumFromCplLt(SgCPlLt);
 
             //CParameterInitialize pParameterInitialize = _ParameterInitialize;
             //CParameterThreshold pParameterThreshold = new CParameterThreshold();
-            //pParameterThreshold.dblBuffer =CGeometricMethods.CalMidLength(LSCPlLt);
-            //pParameterThreshold.dblVerySmall = CGeometricMethods.CalVerySmall(LSCPlLt);
+            //pParameterThreshold.dblBuffer =CGeoFunc.CalMidLength(LSCPlLt);
+            //pParameterThreshold.dblVerySmall = CGeoFunc.CalVerySmall(LSCPlLt);
             //pParameterThreshold.dblOverlapRatio = pParameterInitialize.dblOverlapRatio;
             //pParameterThreshold.dblAngleBound = 0.262;
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CMRL.cs

@@ -57,8 +57,8 @@ namespace MorphingClass.CMorphingMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            _SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
+            _LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            _SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
         }
 
         public void MRLMorphing()
@@ -69,9 +69,9 @@ namespace MorphingClass.CMorphingMethods
 
             //CParameterInitialize pParameterInitialize = _ParameterInitialize;
             //CParameterThreshold pParameterThreshold = new CParameterThreshold();
-            //pParameterThreshold.dblBuffer =CHelperFunction.CalBuffer(LSCPlLt, SSCPlLt);                      //计算缓冲区半径大小
+            //pParameterThreshold.dblBuffer =CHelpFunc.CalBuffer(LSCPlLt, SSCPlLt);                      //计算缓冲区半径大小
             //pParameterThreshold.dblVerySmall = pParameterThreshold.dblBuffer/200;
-            ////pParameterThreshold.dblVerySmall = CGeometricMethods.CalVerySmall(LSCPlLt);         //计算极小值
+            ////pParameterThreshold.dblVerySmall = CGeoFunc.CalVerySmall(LSCPlLt);         //计算极小值
             //pParameterThreshold.dblOverlapRatio = pParameterInitialize.dblOverlapRatio;
 
             //long lngTime1=0;
@@ -80,7 +80,7 @@ namespace MorphingClass.CMorphingMethods
             //List<CRiverNet> CBSRiverNetLt = BuildRiverNetLt(LSCPlLt, pParameterThreshold, ref lngTime1);     //依据线数据建立河网
             //List<CRiverNet> CSSRiverNetLt = BuildRiverNetLt(SSCPlLt, pParameterThreshold, ref lngTime2);     //依据线数据建立河网
 
-            //CHelperFunction.SaveBuffers(CBSRiverNetLt, CSSRiverNetLt, pParameterInitialize.pWorkspace, pParameterInitialize.m_mapControl);  //保存Buffer
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CRIBS.cs

@@ -64,8 +64,8 @@ namespace MorphingClass.CMorphingMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            _SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
+            _LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            _SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
         }
 
         //基于弯曲的Morphing方法
@@ -96,8 +96,8 @@ namespace MorphingClass.CMorphingMethods
             ////添加约束数据生成图层，以便于利用AE中的功能(ct:constraint)
             //List<CPolyline> frctcpllt = new List<CPolyline>(); frctcpllt.Add(frcpl); frctcpllt.Add(frchcpl);
             //List<CPolyline> toctcpllt = new List<CPolyline>(); toctcpllt.Add(tocpl); toctcpllt.Add(tochcpl);
-            //IFeatureLayer pBSFLayer = CHelperFunction.SaveCPlLt(frctcpllt, "frctcpllt" + _dblCDTNum, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
-            //IFeatureLayer pSSFLayer = CHelperFunction.SaveCPlLt(toctcpllt, "toctcpllt" + _dblCDTNum, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            //IFeatureLayer pBSFLayer = CHelpFunc.SaveCPlLt(frctcpllt, "frctcpllt" + _dblCDTNum, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            //IFeatureLayer pSSFLayer = CHelpFunc.SaveCPlLt(toctcpllt, "toctcpllt" + _dblCDTNum, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
 
             ////建立CDT并获取弯曲森林
             //CBendForest FromLeftBendForest = new CBendForest();
@@ -136,7 +136,7 @@ namespace MorphingClass.CMorphingMethods
             //List<CCorrespondBend> CorrespondBendLt = BendMatch(IndependCorrespondBendLt, ParameterThreshold, ParameterInitialize);
 
             ////提取对应线段
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CRIBSBLG.cs

@@ -63,8 +63,8 @@ namespace MorphingClass.CMorphingMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            _SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
+            _LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            _SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
         }
 
         //基于弯曲的Morphing方法
@@ -106,7 +106,7 @@ namespace MorphingClass.CMorphingMethods
             //    pBLGCorrespondSegmentLk.AddRange(OptMPBDPBL.DWByDPLADefine(pComplexCorrespondSegmentLk[j].CFrPolyline, pComplexCorrespondSegmentLk[j].CToPolyline, ParameterThreshold));
             //}
 
-            //C5.LinkedList<CCorrespondSegment> pCorrespondSegmentLk = CHelperFunction.DetectCorrespondSegment(frcpl, tocpl, pBLGCorrespondSegmentLk);
+            //C5.LinkedList<CCorrespondSegment> pCorrespondSegmentLk = CHelpFunc.DetectCorrespondSegment(frcpl, tocpl, pBLGCorrespondSegmentLk);
 
             ////按指定方式对对应线段进行点匹配，提取对应点
             //CAlgorithmsHelper pAlgorithmsHelper = new CAlgorithmsHelper();
@@ -114,8 +114,8 @@ namespace MorphingClass.CMorphingMethods
             //pResultPtLt = pAlgorithmsHelper.BuildPointCorrespondence(pCorrespondSegmentLk, "Linear");
 
             ////保存对应线
-            //CHelperFunction.SaveCtrlLine(pCorrespondSegmentLk, "CRIBSBLGControlLine", _ParameterInitialize.pWorkspace, _ParameterInitialize.m_mapControl);
-            //CHelperFunction.SaveCorrespondLine(pResultPtLt, "CRIBSBLGCorrLine", _ParameterInitialize.pWorkspace, _ParameterInitialize.m_mapControl);
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CRIBSBLGOptCor.cs

@@ -65,8 +65,8 @@ namespace MorphingClass.CMorphingMethods
             _ParameterInitialize = ParameterInitialize;
 
             //获取线数组
-            _LSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pBSFLayer);
-            _SSCPlLt = CHelperFunction.GetCPlLtByFeatureLayer(pSSFLayer);
+            _LSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pBSFLayer);
+            _SSCPlLt = CHelpFunc.GetCPlLtByFeatureLayer(pSSFLayer);
         }
 
         //基于弯曲的Morphing方法
@@ -109,15 +109,15 @@ namespace MorphingClass.CMorphingMethods
             //}
 
             ////获取基于结构分割后的对应线段
-            //C5.LinkedList<CCorrespondSegment> pCorrespondSegmentLk = CHelperFunction.DetectCorrespondSegment(frcpl, tocpl, pBLGCorrespondSegmentLk);
+            //C5.LinkedList<CCorrespondSegment> pCorrespondSegmentLk = CHelpFunc.DetectCorrespondSegment(frcpl, tocpl, pBLGCorrespondSegmentLk);
 
             ////**************OptCor处理过程**************//
             //COptCor OptOptCor = new COptCor();
             //C5.LinkedList<CCorrespondSegment> pOptCorCorrespondSegmentLk = new C5.LinkedList<CCorrespondSegment>();
             //for (int j = 0; j < pCorrespondSegmentLk.Count; j++)
             //{
-            //    List<CPolyline> CFrEdgeLt = CGeometricMethods.CreateCplLt(pCorrespondSegmentLk[j].CFrPolyline.CptLt);
-            //    List<CPolyline> CToEdgeLt = CGeometricMethods.CreateCplLt(pCorrespondSegmentLk[j].CToPolyline.CptLt);
+            //    List<CPolyline> CFrEdgeLt = CGeoFunc.CreateCplLt(pCorrespondSegmentLk[j].CFrPolyline.CptLt);
+            //    List<CPolyline> CToEdgeLt = CGeoFunc.CreateCplLt(pCorrespondSegmentLk[j].CToPolyline.CptLt);
 
             //    pOptCorCorrespondSegmentLk.AddRange(OptOptCor.DWByOptCor(frcpl, tocpl, CFrEdgeLt, CToEdgeLt, ParameterInitialize.intMaxBackK));
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethodsLSA/CALm.cs

@@ -70,7 +70,7 @@ namespace MorphingClass.CMorphingMethodsLSA
             IMapControl4 m_mapControl = _DataRecords.ParameterInitialize.m_mapControl;
             IGraphicsContainer pGra = m_mapControl.Map as IGraphicsContainer;
             pGra.DeleteAllElements();
-            CHelperFunction.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
+            CHelpFunc.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
             return cpl;
         }
 
@@ -91,8 +91,8 @@ namespace MorphingClass.CMorphingMethodsLSA
             double[] adblLength = new double[intPtNum - 1];   //可以变化的值
             for (int i = 0; i < pCorrCptsLt.Count - 1; i++)
             {
-                double dblfrsublength = CGeometricMethods.CalDis(pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i].FrCpt);
-                double dbltosublength = CGeometricMethods.CalDis(pCorrCptsLt[i + 1].ToCpt, pCorrCptsLt[i].ToCpt);
+                double dblfrsublength = CGeoFunc.CalDis(pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i].FrCpt);
+                double dbltosublength = CGeoFunc.CalDis(pCorrCptsLt[i + 1].ToCpt, pCorrCptsLt[i].ToCpt);
                 adblLength0[i] = (1 - dblProportion) * dblfrsublength + dblProportion * dbltosublength;
                 adblLength[i] = adblLength0[i];
             }
@@ -103,9 +103,9 @@ namespace MorphingClass.CMorphingMethodsLSA
             for (int i = 0; i < pCorrCptsLt.Count - 2; i++)
             {
                 //较大比例尺线状要素上的夹角
-                double dblfrAngle = CGeometricMethods.CalAngle_Counterclockwise(pCorrCptsLt[i].FrCpt, pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i + 2].FrCpt);
+                double dblfrAngle = CGeoFunc.CalAngle_Counterclockwise(pCorrCptsLt[i].FrCpt, pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i + 2].FrCpt);
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethodsLSA/CApLL.cs

@@ -200,7 +200,7 @@ namespace MorphingClass.CMorphingMethodsLSA
             //for (int i = 0; i < cpl.SubCPlLt.Count; i++)
             //{
             //    CPolyline subcpl = cpl.SubCPlLt[i];
-            //    CHelperFunction.ViewPolylineByRGB(m_mapControl, subcpl, subcpl.intRed, subcpl.intGreen, subcpl.intBlue);  //显示生成的线段
+            //    CHelpFunc.ViewPolylineByRGB(m_mapControl, subcpl, subcpl.intRed, subcpl.intGreen, subcpl.intBlue);  //显示生成的线段
             //}
 
             ////对缓冲区进行染色
@@ -246,7 +246,7 @@ namespace MorphingClass.CMorphingMethodsLSA
             //for (int i = 1; i < cpl.CptLt.Count-1; i++)
             //{
             //    CPoint cpt=cpl.CptLt[i];
-            //    CHelperFunction.ViewPolygonGeometryByRGB(m_mapControl, cpt.Buffer(5), cpt.intRed, cpt.intGreen, cpt.intBlue);  //显示缓冲区多边形
+            //    CHelpFunc.ViewPolygonGeometryByRGB(m_mapControl, cpt.Buffer(5), cpt.intRed, cpt.intGreen, cpt.intBlue);  //显示缓冲区多边形
             //}
 
             ////显示线段
@@ -259,7 +259,7 @@ namespace MorphingClass.CMorphingMethodsLSA
             IMapControl4 m_mapControl = _DataRecords.ParameterInitialize.m_mapControl;
             IGraphicsContainer pGra = m_mapControl.Map as IGraphicsContainer;
             pGra.DeleteAllElements();
-            CHelperFunction.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
+            CHelpFunc.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
 
 
             return cpl;
@@ -291,9 +291,9 @@ namespace MorphingClass.CMorphingMethodsLSA
             double[] adblToLength0 = new double[intPtNum - 1];
             for (int i = 0; i < pCorrCptsLt.Count - 1; i++)
             {
-                double dblfrsublength = CGeometricMethods.CalDis(pCorrCptsLt[i + 1].FrCpt, pCorrCptsLt[i].FrCpt);
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CMorphingMethodsLSA/CStraightLine.cs

@@ -47,14 +47,14 @@ namespace MorphingClass.CMorphingMethodsLSA
         /// <returns></returns>
         public CPolyline DisplayInterpolation(double dblProportion)
         {
-            //CPolyline cpl = CGeometricMethods.GetTargetcpl(dblProportion);
+            //CPolyline cpl = CGeoFunc.GetTargetcpl(dblProportion);
             //_DataRecords.ParameterInitialize.txtT.Text = "   t = " + dblProportion.ToString();
 
             //// 清除绘画痕迹
             //IMapControl4 m_mapControl = _DataRecords.ParameterInitialize.m_mapControl;
             //IGraphicsContainer pGra = m_mapControl.Map as IGraphicsContainer;
             //pGra.DeleteAllElements();
-            //CHelperFunction.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
+            //CHelpFunc.ViewPolyline(m_mapControl, cpl);  //显示生成的线段
             //return cpl;
             return null;
         }

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CUtility/CCheckRange.cs

@@ -35,7 +35,7 @@ namespace MorphingClass.CUtility
 
         public int CompareTo(CCheckRange other)
         {
-           return  CCompareMethods.CompareDual(this, other, checkrange => checkrange.strFileName, checkrange => checkrange.intStartline);
+           return  CCmpMethods.CmpDual(this, other, checkrange => checkrange.strFileName, checkrange => checkrange.intStartline);
         }
 
     }

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CUtility/CCompareClasses.cs

@@ -14,58 +14,67 @@ namespace MorphingClass.CUtility
     //the first variable is the new element, while the second variable has been already in the data structure
     //return  1:put the first variable after the second one
     //return -1:put the first variable in front of the second one
-    //public class CCompare
+    //public class CCmp
     //{
 
     //}
     
 
 
-    public class CCompareDbl_VerySmall : IComparer<double>
+    public class CCmpCoordDbl_VerySmall : Comparer<double>
     {
-        public static CCompareDbl_VerySmall pCompareDbl_VerySmall = new CCompareDbl_VerySmall();
+        public static CCmpCoordDbl_VerySmall pCmpCoordDbl_VerySmall = new CCmpCoordDbl_VerySmall();
 
-        public int Compare(double x, double y)
+        public override int Compare(double x, double y)
         {
-            return CCompareMethods.CompareDbl_VerySmall(x, y);
+            return CCmpMethods.CmpCoordDbl_VerySmall(x, y);
         }
     }
 
-    public class CCompareDbl : IComparer<double>
+    public class CCmpDbl : Comparer<double>
     {
         //CaseInsensitiveComparer MyCompare = new CaseInsensitiveComparer();
-        public int Compare(double x, double y)
+        public override int Compare(double x, double y)
         {
-            return CCompareMethods.CompareDblPostLocateEqual(x, y);
+            return CCmpMethods.CmpDblPostLocateEqual(x, y);
         }
     }
 
-    public class CAACCompare : IComparer<IList<object>>
+    public class CCmpCptEdgeDis_T : Comparer<CptEdgeDis>
     {
-        public int Compare(IList<object> lt1, IList<object> lt2)
+        public static CCmpCptEdgeDis_T pCmpCptEdgeDis_T = new CCmpCptEdgeDis_T();
+        public override int Compare(CptEdgeDis x, CptEdgeDis y)
         {
-            int intResult = CCompareMethods.CompareDbl_VerySmall(Convert.ToDouble(lt1[3]), Convert.ToDouble(lt2[3]));  //overesimation factor
+            return CCmpMethods.CmpDual(x,y, cptEdgeDis=> cptEdgeDis.t, cptEdgeDis=> cptEdgeDis.Cpt.GID);
+        }
+    }
+
+    public class CAACCmp : Comparer<IList<object>>
+    {
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CUtility/CIpeDraw.cs

@@ -40,8 +40,14 @@ namespace MorphingClass.CUtility
          */
         public static String drawIpeMark(int x, int y, String shape, String color, String size)
         {
-            return "<use name=\"mark/" + shape + "(sx)\" pos=\"" + x + " " + y
+            return "<use name=\"mark/" + shape + "(sx)\" pos=\"" + AddXY(x, y)
                     + "\" size=\"" + size + "\" stroke=\"" + color + "\"/>\n";
+        }
+
+        public static String drawIpeMark(double x, double y, String shape, CColor StrokeColor, String size)
+        {
+            return "<use name=\"mark/" + shape + "(sx)\" pos=\"" + AddXY(x, y)
+                    + "\" size=\"" + size + "\" stroke=\"" + AddColor(StrokeColor) + "\"/>\n";
         }
 
         /**
@@ -212,13 +218,24 @@ namespace MorphingClass.CUtility
         }
 
 
-
-
-
-
-        public static string DrawCpl(CPolyline cpl, IEnvelope pEnvelopeLayer, CEnvelope pEnvelopeIpe, CColor StrokeColor, string strWidth = "normal")
+        public static string DrawIpt(IPoint ipt, IEnvelope pEnvelopeLayer, CEnvelope pEnvelopeIpe, string strShape,
+    CColor StrokeColor, string strWidth = "normal")
         {
-            double dblFactor = (pEnvelopeIpe.XMax - pEnvelopeIpe.XMin) / pEnvelopeLayer.Width;
+            double dblFactor = pEnvelopeIpe.Height / pEnvelopeLayer.Height;
+            double dblx= CGeoFunc.CoordinateTransform(
+                    ipt.X, pEnvelopeLayer.XMin, pEnvelopeIpe.XMin, dblFactor);
+            double dbly = CGeoFunc.CoordinateTransform(
+                    ipt.Y, pEnvelopeLayer.YMin, pEnvelopeIpe.YMin, dblFactor);
+
+            return drawIpeMark(dblx, dbly, strShape, StrokeColor, strWidth);
+        }
+
+
+
+        public static string DrawCpl(CPolyline cpl, IEnvelope pEnvelopeLayer, CEnvelope pEnvelopeIpe, 
+            CColor StrokeColor, string strWidth = "normal")
+        {
+            double dblFactor = pEnvelopeIpe.Height / pEnvelopeLayer.Height;
 
             var cptlt = cpl.CptLt;
 
[…]

### 2017-05-16 ContinuousGeneralizer/MorphingClass/CUtility/CStrObjLtSD.cs

@@ -48,7 +48,7 @@ namespace MorphingClass.CUtility
             {
                 throw new ArgumentOutOfRangeException("Specified key doesn't exist!");
             }
-            objlt.SetLast_T(obj);
+            objlt.SetLastT(obj);
         }
 
         public void Merge(CStrObjLtSD StrObjLtSD)

### 2017-06-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
defined some parameters for building growing

@@
 \usepackage{graphicx}        % standard LaTeX graphics tool
-\usepackage{caption}
+\usepackage[size=small,labelfont=bf]{caption}
                              % when including figure files
@@
 %\usepackage[disable]{todonotes}
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\usepackage[colorinlistoftodos,prependcaption]{todonotes}
 %\usepackage{todonotes}
 \usepackage{subfigure}
-\usepackage[font=small,labelfont=bf]{caption}
 \usepackage{setspace}
@@
 \newcommand{\myabstract}{We proposed a method to continuous 
-generalization of buildings from a start scale to a goal scale. 
+	generalization of buildings from given start scale to any smaller goal 
+	scale. 
 	%
-For each building at the start scale, we generate its 
-generalized form at 
+	If several buildings are close to each other at the start 
+	scale, we bridge them by line segments and take the merge of these 
+	buildings 
+	and bridges as one building.
+	For each building, either an original one or a merged one, at the start 
+	scale, 
+	we generate its target shape at 
 	the goal scale by enlarging and simplifying. Then we grow the  
-building to the 
-generalized form to realize continuous transformation. During 
-the 
-growing, we aggregate two buildings once they become too close 
-to each other. We generate a new generalized form at the goal 
-scale for 
-the aggregated building so that we can continue growing.
+	building to the target shape. 
 	%
 	After finishing the growing, we take the goal scale as the 
-start scale and repeat our continuous generalization. The start 
-scale and the target scale should not be too far away because we 
-want the intermediate results to be somewhat simplified.
-
+	start scale and repeat our continuous generalization.
+	\newline\indent
 	Our contribution is as follows. First, the buildings 
-are enlarged continuously and at the same time are simplified. 
-Second, the distance between each pair of two buildings is 
-always larger than a specified distance. Third, there is no thin 
-part in our results.}
+	are enlarged continuously. At the same time, they are simplified. 
+	Second, we ensure that the distance between any pair of two buildings is 
+	always larger than a specified threshold.}
 
@@
 Elimination
-If every building should have area 4d2at least, we buffer 
-buildings with radius xd (x<2). After the buffering, some too 
+If every building should have area $4d^2$at least, we buffer 
+buildings with radius $xd$ (x<2). After the buffering, some too 
 small buildings will be eliminated. The small buildings which 
@@
 
+\section{Method}
+
+If several buildings are close to each other at the start 
+scale, we bridge them by line segments and take the merge of these 
+buildings 
+and bridges as one building.
+For each building, either an original one or a merged one, at the start 
+scale, 
+we generate its target shape at 
+the goal scale by enlarging and simplifying. Then we grow the  
+building to the target shape. 
+%
+After finishing the growing, we take the goal scale as the 
+start scale and repeat our continuous generalization.
+\newline\indent
+Our contribution is as follows. First, the buildings 
+are enlarged continuously. At the same time, they are simplified. 
+Second, we ensure that the distance between any pair of two buildings is 
+always larger than a specified threshold.
+
+If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
+grow at most $2d_\mathrm{G}$.
+The length of a bridge can be as large as
+\begin{equation}
+\label{eq:BridgeLength}
+l_b=4d_\mathrm{G}+d_\epsilon.
+\end{equation}
+\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+
+\subsection{Parameters for growing}
+The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
+($S_\mathrm{g}>S_\mathrm{s}$).
+The area of a building should be larger than $a$ mm$^2$ on a map.
+A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
+A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
+The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ mm.
+Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
+(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
+In order to eliminate some small buildings, we define our growing distance as
+\begin{equation}
+\label{eq:d_G}
+	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
+	mm} \quad 0 < \lambda <1,
+\end{equation}
+where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
+fewer buildings to be eliminated, and vice versa.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Growth}
+	\caption{Growth.}
+	\label{fig:Growth}
+\end{figure}
+
+The distance between two buildings should be larger than a threshold, say, 
+$\epsilon$ mm on map \parencite{Stoter2009}.
+In order to make the shape of a building simpler, we simplify buildings 
+using the Douglas--Peucker algorithm \parencite{Douglas1973} with preservation 
+of right angles.
+To avoid using too many thresholds, we also use $\epsilon$ mm for the 
+simplification algorithm, hence the real threshold distance 
+is
+\begin{equation}
+\label{eq:d_epsilon}
+d_\epsilon= \epsilon  S_\mathrm{g}.
+\end{equation}
+
+If we insist on that we should observe 
+the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
+sure that
+\begin{equation}
+\label{eq:a_limit}
+\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
+\end{equation}
+Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
+and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
+\begin{equation}
+a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
+\end{equation}
+\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
+on a map. We set our $\epsilon=0.2$.
+We also require 
+that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
+On one hand, we should have a large $x$ so that we will see the 
+growing most of the time.
+On the other hand, we wish to keep bridges short as bridges are intrusions to 
+our map, which means we should have a small $x$ and a large $\lambda$ so that 
+we will have a small 
+$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
+Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
+Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
+$\lambda$ as our $a$ is already much larger than $0.16$ mm$^2$ on 
+map, which is the area limit used by \textcite{Stoter2009}. As a result, we set 
+$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
+Using these setting, we have
+\begin{equation}
+a \ge 4.
+\end{equation}
+according to Eq.~\ref{eq:a_limit}.
+
+Therefore, we may grow up to distance 
+\[
+D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
+\]
+Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, where  
+variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
+
+A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
+A hole has area 
+slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
+growing with 
+distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
+unless the 
+area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
+that we do 
+not fill a hole even if the hole has a large area because a large hole may be 
+split into several small holes by filling. 
+Although our intermediate results may violate the rule that a hole should be at 
+least some size, we try to avoid the violation for a map at a goal scale.
+\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
+$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
+least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
+D_\mathrm{G}^2 \ge 8 S_g^2$.
+
+Now we discuss how to set the parameters according to our requirements. First, 
+we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
+grow $d_\mathrm{G}$. Only a small part will continue growing after the building 
+has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
+time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
+
+We cannot fulfill all the requirements.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{ExtraGrowth}
+	\caption{In the left figure, the green polygon represents a building, and 
+	the dashed polygon is the enlargement of the building. In the right 
+	figure, the dashed polygon has been simplified to a rectangle. In order to 
+	fill the rectangle, most parts of the (green) building needs to grow 
+	distance $d_\mathrm{G}$, but the pit needs to grow $d_G + d_\mathrm{e}$, 
+	where $d_\mathrm{e}$ is the extra growing distance.}
+	\label{fig:ExtraGrowth}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{GrowingExample}
+	\caption{GrowingExample.}
+	\label{fig:GrowingExample}
+\end{figure}
+
 \section{Section Title}
@@
 
+We our intermediate results may violate more cartographic rules, but we try to 
+make the results at goal scales violate as few rules as possible.
+
+Ideally, for a rectangle, the ratio of width to height should be kept.
+
+\todo[inline]{consider multi bridges; consider transparency of bridges in stead 
+of enlarging}
+
 \printbibliography

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmAid/FrmCreateRandomPointLayer.cs

@@ -48,14 +48,14 @@ namespace ContinuousGeneralizer.FrmAid
         private void FrmCreateRandomPointLayer_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.pMap = ParameterInitialize.m_mapControl.Map;
-            ParameterInitialize.m_mapFeature = new MapClass();
-            ParameterInitialize.m_mapAll = new MapClass();
+            
+            
+            
             //ParameterInitialize.cboLayer = this.cboLayer;
 
             //进行Load操作，初始化变量
             //_FrmOperation = new CFrmOperation(ref ParameterInitialize);
-            //_FrmOperation.FrmLoad();
+            //throw new ArgumentException("improve loading layesr!");
         }
 
         public void btnRun_Click(object sender, EventArgs e)

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmGeneralization/FrmBuildingGrowing.cs

@@ -34,13 +34,13 @@ using MorphingClass.CGeometry;
 
 namespace ContinuousGeneralizer.FrmGeneralization
 {
-    public partial class FrmBuildingGrowing : Form
+    public partial class FrmBldgGrow : Form
     {
         private CDataRecords _DataRecords;                    //数据记录
         private CFrmOperation _FrmOperation;
 
 
-        private CBuildingGrowing _pBuildingGrowing;
+        private CBldgGrow _pBldgGrow;
 
 
         private double _dblProportion = 0.5;
@@ -53,19 +53,19 @@ namespace ContinuousGeneralizer.FrmGeneralization
         }
 
 
-        public FrmBuildingGrowing()
+        public FrmBldgGrow()
         {
             InitializeComponent();
         }
 
-        public FrmBuildingGrowing(CDataRecords pDataRecords)
+        public FrmBldgGrow(CDataRecords pDataRecords)
         {
             InitializeComponent();
             _DataRecords = pDataRecords;
             pDataRecords.ParameterInitialize.frmCurrentForm = this;
         }
 
-        private void FrmBuildingGrowing_Load(object sender, EventArgs e)
+        private void FrmBldgGrow_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
             ParameterInitialize.cboLayerLt = new List<ComboBox>(2);
@@ -73,7 +73,7 @@ namespace ContinuousGeneralizer.FrmGeneralization
             ParameterInitialize.cboLayerLt.Add(this.cboSmallerScaleLayer);
             ParameterInitialize.cboLayerLt.Add(this.cboLSRoad);
             ParameterInitialize.cboLayerLt.Add(this.cboSSRoad);
-            CConstants.strMethod = "BuildingGrowing";
+            CConstants.strMethod = "BldgGrow";
 
             this.cboBufferStyle.SelectedIndex = 0;
 
@@ -89,8 +89,8 @@ namespace ContinuousGeneralizer.FrmGeneralization
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
 
             //读取数据
-            _pBuildingGrowing = new CBuildingGrowing(ParameterInitialize);
-            _pBuildingGrowing.BuildingGrowing(
+            _pBldgGrow = new CBldgGrow(ParameterInitialize);
+            _pBldgGrow.BldgGrow(
[…]

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmGeneralization/FrmCAMDijkstra.cs

@@ -1,516 +1,0 @@
-﻿using System;
-using System.Collections.Generic;
-using System.ComponentModel;
-using System.Data;
-using System.Drawing;
-using System.Text;
-using System.Windows.Forms;
-
-using ESRI.ArcGIS.Controls;
-using ESRI.ArcGIS.Carto;
-using ESRI.ArcGIS.Geodatabase;
-using ESRI.ArcGIS.Geometry;
-using ESRI.ArcGIS.GeoAnalyst;
-using ESRI.ArcGIS.Display;
-
-using ContinuousGeneralizer;
-using MorphingClass.CEvaluationMethods;
-using MorphingClass.CUtility;
-using MorphingClass.CGeneralizationMethods;
-using MorphingClass.CGeometry;
-
-using ILOG.Concert;
-using ILOG.CPLEX;
-
-namespace ContinuousGeneralizer.FrmMorphing
-{
-    /// <summary>
-    /// Continuous Aggregation of Maps based on Dijkstra: CAMDijkstra
-    /// </summary>
-    public partial class FrmCAMDijkstra : Form
-    {
-        private CDataRecords _DataRecords;                    //数据记录
-        private CFrmOperation _FrmOperation;
-
-
-        private CCAMDijkstra _pCAMDijkstra;
-
-
-        private double _dblProportion = 0.5;
-
-        /// <summary>属性：数据记录</summary>
-        public CDataRecords DataRecords
-        {
-            get { return _DataRecords; }
-            set { _DataRecords = value; }
-        }
-
-
-        public FrmCAMDijkstra()
-        {
-            InitializeComponent();
-        }
-        
-        public FrmCAMDijkstra(CDataRecords pDataRecords)
-        {
-            InitializeComponent();
-            _DataRecords = pDataRecords;
-            pDataRecords.ParameterInitialize.frmCurrentForm = this;
-        }
-
-        private void FrmCAMDijkstra_Load(object sender, EventArgs e)
-        {
-            CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.cboLayerLt = new List<ComboBox>(2);
-            ParameterInitialize.cboLayerLt.Add(this.cboLargerScaleLayer);
-            ParameterInitialize.cboLayerLt.Add(this.cboSmallerScaleLayer);
-            CConstants.strMethod = "AStar";
[…]

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphing/FrmMPBBSLDP.cs

@@ -55,16 +55,16 @@ namespace ContinuousGeneralizer.FrmMorphing
         private void FrmMPBBSLDP_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.pMap = ParameterInitialize.m_mapControl.Map;
-            ParameterInitialize.m_mapFeature = new MapClass();
-            ParameterInitialize.m_mapAll = new MapClass();
+            
+            
+            
             ParameterInitialize.cboLargerScaleLayer = this.cboLargerScaleLayer;
             ParameterInitialize.cboSmallerScaleLayer = this.cboSmallerScaleLayer;
             
             CConstants.strMethod = "MPBBSLDP";
             //进行Load操作，初始化变量
             _FrmOperation = new CFrmOperation(ref ParameterInitialize);
-            _FrmOperation.FrmLoadMulticbo();
+            throw new ArgumentException("improve loading layesr!");
         }
 
         public void btnRun_Click(object sender, EventArgs e)

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmMorphingExtend/FrmBase.cs

@@ -54,16 +54,16 @@ namespace ContinuousGeneralizer.FrmMorphingExtend
         private void FrmBase_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.pMap = ParameterInitialize.m_mapControl.Map;
-            ParameterInitialize.m_mapFeature = new MapClass();
-            ParameterInitialize.m_mapAll = new MapClass();
+            
+            
+            
             ParameterInitialize.cboLargerScaleLayer = this.cboLargerScaleLayer;
             ParameterInitialize.cboSmallerScaleLayer = this.cboSmallerScaleLayer;
             CConstants.strMethod = "Linear";
 
             //进行Load操作，初始化变量
             _FrmOperation = new CFrmOperation(ref ParameterInitialize);
-            _FrmOperation.FrmLoadMulticbo();
+            throw new ArgumentException("improve loading layesr!");
         }
 
         public virtual void btnRunShp_Click(object sender, EventArgs e)

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmRoadNetwork/FrmClassification.cs

@@ -49,15 +49,15 @@ namespace ContinuousGeneralizer.RoadNetwork
         private void FrmClassification_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.pMap = ParameterInitialize.m_mapControl.Map;
+            
             ParameterInitialize.m_mapPolyline = new MapClass();
-            ParameterInitialize.m_mapAll = new MapClass();
+            
             ParameterInitialize.cboLargerScaleLayer = this.cboLargerScaleLayer;
             ParameterInitialize.cboSmallerScaleLayer = this.cboSmallerScaleLayer;
 
             //进行Load操作，初始化变量
             _FrmOperation = new CFrmOperation(ref ParameterInitialize);
-            _FrmOperation.FrmLoadMulticbo();
+            throw new ArgumentException("improve loading layesr!");
         }
 
         public void btnRun_Click(object sender, EventArgs e)

### 2017-06-16 ContinuousGeneralizer/ContinuousGeneralizer/FrmRoadNetwork/FrmTransparencyMorphing.cs

@@ -39,15 +39,15 @@ namespace ContinuousGeneralizer.RoadNetwork
         private void FrmIntersectionExtract_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.pMap = ParameterInitialize.m_mapControl.Map;
+            
             ParameterInitialize.m_mapPolyline = new MapClass();
-            ParameterInitialize.m_mapAll = new MapClass();
+            
             ParameterInitialize.cboLargerScaleLayer = this.cboLargerScaleLayer;
             ParameterInitialize.cboSmallerScaleLayer = this.cboSmallerScaleLayer;
 
             //进行Load操作，初始化变量
             _FrmOperation = new CFrmOperation(ref ParameterInitialize);
-            _FrmOperation.FrmLoadMulticbo();
+            throw new ArgumentException("improve loading layesr!");
         }
 
 

### 2017-06-16 ContinuousGeneralizer/MorphingClass/CMorphingMethods/CMorphingMethodsBase/CMorphingBase.cs

@@ -6,7 +6,9 @@ using System.Text;
 using ESRI.ArcGIS.Geometry;
 using ESRI.ArcGIS.Carto;
 using ESRI.ArcGIS.Geodatabase;
+using ESRI.ArcGIS.Display;
 
+using MorphingClass.CAid;
 using MorphingClass.CUtility;
 using MorphingClass.CGeometry;
 using MorphingClass.CGeometry.CGeometryBase;
@@ -33,7 +35,8 @@ namespace MorphingClass.CMorphingMethods.CMorphingMethodsBase
 
         protected List<List<CCorrCpts>> _CorrCptsLtLt;
         protected List<List<CCorrCpts>> _SgCorrCptsLtLt;
-        
+
+        //protected SortedDictionary<int, ISymbol> _intTypeFillSymbolSD;
 
         protected CParameterResult _ParameterResult;
         protected CParameterInitialize _ParameterInitialize;
@@ -106,7 +109,9 @@ namespace MorphingClass.CMorphingMethods.CMorphingMethodsBase
 
             //we compute the parameters of distance according to the features in the first layer
             CGeoFunc.CalDistanceParameters<T, CGeo>(pFirstLayerObjCGeoLt.AsExpectedClass<T, object>().ToList());
-            
+
+
+
             //_CPlLt = pObjCGeoLtLt[0];
             this.strFieldNameLtLt = pstrFieldNameLtLt;
             this.esriFieldTypeLtLt = pesriFieldTypeLtLt;

### 2017-06-16 ContinuousGeneralizer/MorphingClass/CUtility/CParameterInitialize.cs

@@ -185,12 +185,12 @@ namespace MorphingClass.CUtility
         //}
 
 
-        /// <summary>属性：地图文档</summary>
-        public IMap pMap
-        {
-            get { return _pMap; }
-            set { _pMap = value; }
-        }
+        ///// <summary>属性：地图文档</summary>
+        //public IMap pMap
+        //{
+        //    get { return _pMap; }
+        //    set { _pMap = value; }
+        //}
 
         /// <summary>属性：线图层集</summary>
         public IMap m_mapPolyline
@@ -211,12 +211,12 @@ namespace MorphingClass.CUtility
             set { _m_mapFeature = value; }
         }
 
-        /// <summary>属性：所有图层集</summary>
-        public IMap m_mapAll
-        {
-            get { return _m_mapAll; }
-            set { _m_mapAll = value; }
-        }
+        ///// <summary>属性：所有图层集</summary>
+        //public IMap m_mapAll
+        //{
+        //    get { return _m_mapAll; }
+        //    set { _m_mapAll = value; }
+        //}
 
         /// <summary>属性：地图控件</summary>
         public IMapControl4 m_mapControl

### 2017-06-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added the results of growing from 15k to 50k

@@
 ($S_\mathrm{g}>S_\mathrm{s}$).
-The area of a building should be larger than $a$ mm$^2$ on a map.
+The area of a building should be larger than $a$ mm$^2$ on map.
 A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
@@
 
-A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
-A hole has area 
-slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
-growing with 
-distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
-unless the 
-area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
-that we do 
-not fill a hole even if the hole has a large area because a large hole may be 
-split into several small holes by filling. 
-Although our intermediate results may violate the rule that a hole should be at 
-least some size, we try to avoid the violation for a map at a goal scale.
 \textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
 $0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
-least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
-D_\mathrm{G}^2 \ge 8 S_g^2$.
+least $8$ mm$^2$ on map. Following their setting, we shrink a hole and 
+eliminate the hole one its size is smaller than $8$ mm$^2$ on map eliminate a 
+hole.
 
-Now we discuss how to set the parameters according to our requirements. First, 
-we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
-grow $d_\mathrm{G}$. Only a small part will continue growing after the building 
-has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
-time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
-
-We cannot fulfill all the requirements.
+%
+%A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
+%A hole has area 
+%slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
+%growing with 
+%distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
+%unless the 
+%area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
+%that we do 
+%not fill a hole even if the hole has a large area because a large hole may be 
+%split into several small holes by filling. 
+%Although our intermediate results may violate the rule that a hole should be 
+%at 
+%least some size, we try to avoid the violation for a map at a goal scale.
+%\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
+%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
+%least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
+%D_\mathrm{G}^2 \ge 8 S_g^2$.
+%
+%
+%Now we discuss how to set the parameters according to our requirements. First, 
+%we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
+%grow $d_\mathrm{G}$. Only a small part will continue growing after the 
+%building 
+%has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
+%time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
+%
+%
+%
+%
+%
+%We cannot fulfill all the requirements.
 

### 2017-06-19 ContinuousGeneralizer/MorphingClass/CGeometry/CPolygon.cs

@@ -30,11 +30,13 @@ namespace MorphingClass.CGeometry
         //private CPatch _cpatch;
 
         public double dblAreaSimple { get; set; }
+        public bool WasTooSmall { get; set; }
 
         public int intType { get; set; }
         public int intTypeIndex { get; set; } //the index (0, 1, 2, ...) of a type; used for access type distance directly
 
         public CPolygon ParentCpg { get; set; }
+        public CPolygon ClipCpg { get; set; }
 
         public List<CPolygon> HoleCpgLt { get; set; }
         public CPoint CentroidCptSimple { get; set; }
@@ -48,6 +50,7 @@ namespace MorphingClass.CGeometry
         private CPoint _LeftMostCpt;
         private bool _IsHole;
         private bool _IsMerged;
+
         //private Func<IEnumerable<List<CPoint>>> getHoleCptLtEb;
 
         /// <summary>

### 2017-07-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added some text to introduction

@@
 
-%We proposed a method to continuous 
-%generalization of buildings from a start scale to a goal scale. 
-%%
-%For each building at the start scale, we enlarge it by 
-%buffering. We simplify the enlarged building by the operator of 
-%dilation-erosion-erosion-dilation. Then we merge the 
-%simplified form with the original 
-%building so that the merged result completely contains the 
-%original 
-%shape. We use the merged shape as the building at the goal 
-%scale, and grow the original building to the 
-%goal shape to realize continuous transformation. 
-%%
-%During the 
-%growing, if two buildings become too close to each other, we 
-%aggregate them to avoid narrow gap. To aggregate, we dilate and 
-%merge the two buildings, then we erode the merged shape. To 
-%avoid 
-%failure or thin parts from the aggregation, we construct a 
-%skeleton of the dilated and merged form. We make a buffer of 
-%the 
-%skeleton 
-%and merge the buffer with the eroded shape. We take the 
-%aggregated shape which may be merged with the skeleton buffer 
-%as 
-%a new 
-%building and generate its goal shape at the goal scale so that 
-%we can grow this new building.
-%
-%Once we arrive at the goal scale, we take the goal scale as the 
-%start scale and repeat our continuous generalization. The start 
-%scale and the target scale cannot be too far away because we 
-%want to see some simplification during the growing of buildings.
-%%
-%There are several advantages of our method. First, the 
-%buildings 
-%are enlarged continuously and the same time are simplified. 
-%Second, the distance between each pair of two buildings is 
-%always larger than a specified distance. Third, there is no 
-%thin 
-%part in our results.
-
 \abstract*{\myabstract}
@@
 \label{sec:Introduction}
+
+Digital maps such as Google Maps and OpenStreetMap support zooming by 
+displaying maps at different levels. 
+This discrete strategy may results in sudden changes, which annoy users.
+To provide better zooming experience, continuous generalization aims to 
+produce 
+a sequence of maps with small incremental changes.
+To realize continuous generalization, \textcite{Sester2005_CG} discussed some 
+generalization operators for buildings and proposed to morph a building 
+between 
+its forms at different levels. Morphing has been used to generate intermediate 
+representations for two representations at different scales 
+\parencite{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
+Also aiming at 
+realize continuous generalization, \textcite{Chimani2014_Eat} generated a good 
+selection sequence for road networks, and 
+\textcite{Peng2017_AStar} tried to compute optimal aggregation sequences for 
+land-cover areas.
+
+When users zoom out on digital maps, buildings become closer with each other 
+and buildings themselves become smaller. 
+In order to make sure that the map is 
+easily perceived \parencite{Weibel1997}, small building should be eliminated, 
+some building should be enlarged, and buildings close to each other should be 
+aggregated.
+Although algorithms of simplifying buildings have been studied, e.g., 
+\textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
+when we have to aggregate buildings in the meantime.
+In order to aggregate, we should first group the buildings.
+
+\bigskip
 
@@
 
-\section{Discussion}
-\label{sec:Discussion}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics{Framework}
-	\caption{Framework.}
-	\label{fig:Framework}
-\end{figure}
-
-We discussed two ways of achieving continuous generalization of 
-buildings.
-
-The first way is that we cover the smallest block at each step. 
-Should we consider the density of the buildings? 
-\marginalcomment{relevant comment. If small buildings exist in 
-	all blocks, there will be small buildings remaining at small 
-	scales in the blocks that have not been covered.}
-A disadvantage 
-is that some small buildings in a large block may exist very 
-long.
-Alternatively, we may cover two buildings together if they are 
-close enough, say the distance is smaller than d. We can 
-increase d so that we will cover more and more buildings 
-together. To avoid overlap between two covers, we may need to 
-use Voronoi diagrams of the original buildings. We can cover 
-buildings without overlap if we always use a cover inside the 
-Voronoi cells of these buildings. This idea about Voronoi cells 
-is used in \textcite{vanGoethem2013}. We may need to try 
-different 
-possible covers. 
-Unfortunately, this trying may be very time-consuming, probably 
-NP-hard.
-
-The second way is that we grow buildings by buffering with an 
-increasing radius, and then merge the buffers overlapping each 
-other. A disadvantage is that the corners of the buffers 
-\marginalcomment{this may be avoided by using square buffers 
-(the Minkowski sum is done with a square rather than a circle), 
-don't know if it's available in ESRI products}
-\marginalcomment{We can also think about the method described at 
-%\url{http://stackoverflow.com/questions/1109536/an-algorithm-for-inflating-deflating-offsetting-buffering-polygons#}
- }
-are not 
-orthogonal anymore. Two kinds of buffer:
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth]{BufferRoundJoint}
-	\caption{BufferRoundJoint.}
-	\label{fig:BufferRoundJoint}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth]{BufferMiterJoint}
-	\caption{BufferMiterJoint.}
-	\label{fig:BufferMiterJoint}
-\end{figure}
-
-A disadvantage of buffering based on miter joint is that the 
-method is sensitive to noise. By sensitive, if there is a short 
-edge at the end or a sharp corner, then the result will be very 
-different to the case that there is no such short edge. In 
-contrary, buffers based on round joint are continuous and stable.
-
-This method should be easier to implement than the first method.
-\marginalcomment{We can erode back in order to keep enough 
-distance between buildings. The operator of growing and 
-shrinking of buffers are mentioned in paper Automated Processing 
-for Map Generalization with Modular Operator Services (Neun 
-2009).
-} 
-We may not need to erode back after buffering. In this second 
-strategy, undesired very small shapes or holes might appear at 
-some point, and should be reverted until the growing totally 
-collapses the hole or makes the small parts big enough. As 
-buffers are not allowed to cross roads, we may clip some parts 
-of the buffers off along the roads.
-If we buffer with miter joint, it can happen that a very sharp 
-angle yields a very long buffer. Fortunately, we do not have 
-this situation so far. Otherwise, we may need to cut the long 
-buffer at some point.
-We may have small holes after buffering and merging the buffers 
-of the buildings, which is not nice. See below as an example, 
-where we can find a small “white” hole in the middle. We may 
-simply fill out all the holes having small area.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth/2]{BufferWithHole}
-	\caption{BufferWithHole.}
-	\label{fig:BufferWithHole}
-\end{figure}
-
-We have two maps at different scales. We generalize the 
-buildings on the larger-scale map, and we use the boundaries of 
-the buildings on the smaller-scale map as the limits of the 
-generalization (including growing).
-
-We have a requirement that the buildings should not cross 
-existing roads. Therefore, we need to cut the the enlarged 
-buildings by the roads. If we do this cut, then some buildings 
-may almost touch each other, but separated by roads. The 
-too-close buildings will look ugly. To avoid the ugly 
-performance, we should also make buffers for roads, and require 
-that the enlarged buildings should be outside the buffers of the 
-roads. Should we use the same radius that we used for enlarging 
-buildings? With the buffers of roads growing, we may need to 
-move enlarged buildings, otherwise, the enlarged buildings will 
-overlap the buffers of roads. 
-We may move by a method based on least-squares adjustment. In 
-this method, we may assign large weight for keeping the distance 
-between a road and a building. We may assign small weight for 
-keeping the distance between buildings because buildings will be 
-buffered and merged later.
-
-We want to enlarge the buildings by a radius r, and require that 
-the distance between any two buildings after the enlargement 
-should be 2d at least. To achieve this aim, we first buffer the 
-buildings by a radius r+d, and then buffer the enlarged 
-buildings by a radius -d. Following is an example, where r=10 
-and d=15.
-
-Buffering the original buildings with radius 25
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth]{BufferRadius25}
-	\caption{BufferRadius25.}
-	\label{fig:BufferRadius25}
-\end{figure}
-
-Buffering the enlarged buildings with radius -15 (erosion). We 
-call the result Map A. Unfortunately, we produced some spikes by 
-this erosion. Since we used the miter joint and we allow the 
-enlargements twice of radius r=10 away from the original 
-buildings, the corners of the enlarged buildings can be 2r=20 
-from the original buildings. After erosion, the smallest 
-distance between two buildings can be as small as 0. I will give 
-more details.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth]{MapA}
-	\caption{MapA.}
-	\label{fig:MapA}
-\end{figure}
-
-Buffering the original buildings with radius 10. We call the 
-result Map B.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\linewidth]{MapB}
-	\caption{MapB.}
-	\label{fig:MapB}
-\end{figure}
-
-To remove the spikes in Map A, we may subtract Map B from Map A. 
-Then we get some leftovers in Map A. The outward triangles of 
-the leftovers are the spikes which we want to remove. We 
-subtract those outward triangles from Map A, which may guarantee 
-that we will have removed the spikes in Map A.
-
-To remove the spikes in Map A, Guillaume suggested that we could 
-%buffer by a small value -ɛ, and then buffer again by ɛ.
-
-Should we buffer from the original buildings or buffer from the 
-buildings from the previous step?
-
-Elimination
-If every building should have area $4d^2$at least, we buffer 
-buildings with radius $xd$ (x<2). After the buffering, some too 
-small buildings will be eliminated. The small buildings which 
-manage to merge with other buildings may survive. The eliminated 
-buildings should not participate in next buffering step, which 
-uses larger d.
-
-Issues regarding the data:
-
-%How were the layers of data road_25k and road_100k produced?
-%Was road_25k produced by surveying?
-%Was road_100k generalized from road_25k?
-%
-%How were the layers of data building_15k, building_25k, 
-%urban_area_50k, and urban_area_100k produced?
-%Was building_15k produced by surveying?
-%Was building_25k derived from building_15k by the methods 
-%illustrated in paper Optimization Approaches for Generalization 
-%and Data Abstraction (Sester, 2005)?
-%Was urban_area_50k derived from building_15k by constructing 
-%buffers and filling out the holes of the buffers?
-%Was urban_area_100k derived from building_15k by constructing 
-%buffers and filling out the holes of the buffers?
-
-%\pagebreak[4]
-%\newpage
-\clearpage
-
-\section{An idea of continuously generalising buildings}
-We have an input map at scale $1:15 \mathrm{k}$.
-We want to generate, by generalisation, $10$ maps which are at 
-scale $1:20\mathrm{k}$, $1:25\mathrm{k}$, 
-$1:30\mathrm{k}$, $\dots$, $1:65\mathrm{k}$.
-We always produce a map by generalising the 
-immediate-larger-scale map. For example, we produce the map at 
-scale $1:25\mathrm{k}$ by generalising, instead of the input 
-map, the map at scale $1:20\mathrm{k}$.
-This production 
-guarantees consistency. Namely, if a building does not exist on 
-a map at a certain scale, then the building will never exist on 
-a map at a smaller scale.
-
-We have two requirements for an output map.
-The first one is that the distance between two 
-buildings should be at least $d_i=0.2 \mathrm{mm}/S_i$, where 
-$S_i$ is the scale of map $i$.
-The second requirement is that a building with area less than 
-$A_i=0.16\mathrm{mm}^2/S^2_i$ should be eliminated. Roughly, a 
-building with width less than 
-$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S_i$ should be eliminated.
-In order to make sure that some small buildings will be 
-eliminated, the radius $r_i$ that we use to buffer buildings 
-should be smaller than $\frac{1}{2}w_i$. We simply use 
-$r_i=\frac{1}{4}w_i$.
-Our buildings may have been buffered with radius, in total, 
-$r_{i-1}$ from previous steps.
-Therefore, we only need to buffer with radius $r_i-r_{i-1}$ at 
-the new 
-step.
-
-Our generalisation is as following $4$ steps:
-\begin{enumerate}[label=(\alph*),leftmargin=2\parindent]
-	\item We buffer buildings with 
-	radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
-	overlapping each other.
-	\item Then we buffer the results with $-\frac{1}{2}d_i$.
-	\item In order to 
-	remove some spikes from the buffering, we buffer the new 
-	results with $-\epsilon_i$.
-	\item To compensate, we buffer with $\epsilon_i$.	
-\end{enumerate}
-We simply set 
-$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
-operations, we eliminate the buildings with area less than 
-$A_i$.
-
 \section{Method}
 
+\subsection{Growing}
 If several buildings are close to each other at the start 
@@
 
-\subsection{Parameters for growing}
+\subsection{Simplification}
+we use a buffer-based method, similar to \textcite{Damen2008,Meijers2016}, to 
+simplify our grown buildings.
+
+\subsection{Parameters for growing and simplification}
 The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
@@
 A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
-The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ mm.
+The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
+mm.
 Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
@@
 $\lambda$ as our $a$ is already much larger than $0.16$ mm$^2$ on 
-map, which is the area limit used by \textcite{Stoter2009}. As a result, we set 
+map, which is the area limit used by \textcite{Stoter2009}. As a result, we 
+set 
 $\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
@@
 \]
-Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, where  
+Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
+where  
 variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
@@
 least $8$ mm$^2$ on map. Following their setting, we shrink a hole and 
-eliminate the hole one its size is smaller than $8$ mm$^2$ on map eliminate a 
-hole.
+eliminate the hole once its size is smaller than $8$ mm$^2$ on map.
 
@@
 %least some size, we try to avoid the violation for a map at a goal scale.
-%\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
-%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
+%\textcite{Chaudhry2008} thought that a hole of a settlement should be at 
+%least 
+%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is 
+%at 
 %least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
@@
 %
-%Now we discuss how to set the parameters according to our requirements. First, 
+%Now we discuss how to set the parameters according to our requirements. 
+%First, 
 %we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
@@
 
-\todo[inline]{consider multi bridges; consider transparency of bridges in stead 
+\todo[inline]{consider multi bridges; consider transparency of bridges in 
+stead 
 of enlarging}

### 2017-07-18 ContinuousGeneralizer/ContinuousGeneralizer/FrmGeneralization/FrmBuildingGrowing.Designer.cs

@@ -62,6 +62,7 @@
             this.pbScale = new System.Windows.Forms.ProgressBar();
             this.btnSaveInterpolation = new System.Windows.Forms.Button();
             this.groupBox2 = new System.Windows.Forms.GroupBox();
+            this.btnDetailToIpe = new System.Windows.Forms.Button();
             this.btnMultiResults = new System.Windows.Forms.Button();
             this.txtProportion = new System.Windows.Forms.TextBox();
             this.btnInputedScale = new System.Windows.Forms.Button();
@@ -392,6 +393,7 @@
             this.btnAdd.TabIndex = 80;
             this.btnAdd.Text = "+";
             this.btnAdd.UseVisualStyleBackColor = true;
+            this.btnAdd.Click += new System.EventHandler(this.btnAdd_Click);
             // 
             // btnReduce
             // 
@@ -421,6 +423,7 @@
             // 
             // groupBox2
             // 
+            this.groupBox2.Controls.Add(this.btnDetailToIpe);
             this.groupBox2.Controls.Add(this.btnMultiResults);
             this.groupBox2.Controls.Add(this.btnAdd);
             this.groupBox2.Controls.Add(this.btnReduce);
@@ -447,6 +450,16 @@
             this.groupBox2.TabIndex = 79;
             this.groupBox2.TabStop = false;
             this.groupBox2.Text = "Display";
+            // 
+            // btnDetailToIpe
+            // 
+            this.btnDetailToIpe.Location = new System.Drawing.Point(174, 148);
+            this.btnDetailToIpe.Name = "btnDetailToIpe";
+            this.btnDetailToIpe.Size = new System.Drawing.Size(106, 25);
+            this.btnDetailToIpe.TabIndex = 83;
+            this.btnDetailToIpe.Text = "Detail To Ipe";
+            this.btnDetailToIpe.UseVisualStyleBackColor = true;
+            this.btnDetailToIpe.Click += new System.EventHandler(this.btnDetailToIpe_Click);
             // 
             // btnMultiResults
             // 
@@ -669,5 +682,6 @@
         private System.Windows.Forms.Label label10;
         private System.Windows.Forms.Label label13;
         private System.Windows.Forms.Label label11;
+        private System.Windows.Forms.Button btnDetailToIpe;
     }
 }

### 2017-07-18 ContinuousGeneralizer/MorphingClass/CUtility/CIpeDraw.cs

@@ -38,7 +38,7 @@ namespace MorphingClass.CUtility
          *            size: tiny, small, normal, large
          * @return
          */
-        public static String drawIpeMark(double x, double y, String shape= "disk", String color = "black", String size="normal")
+        public static String drawIpeMark(double x, double y, String shape = "disk", String color = "black", String size = "normal")
         {
             return "<use name=\"mark/" + shape + "(sx)\" pos=\"" + AddXY(x, y)
                     + "\" size=\"" + size + "\" stroke=\"" + color + "\"/>\n";
@@ -65,14 +65,14 @@ namespace MorphingClass.CUtility
          * @return
          */
         public static String drawIpeBox(int x1, int y1, int x2, int y2,
-                String outlinecolor= "black", String fillcolor = "white", String pen = "normal", String dash = "normal")
+                String outlinecolor = "black", String fillcolor = "white", String pen = "normal", String dash = "normal")
         {
             return "<path stroke=\"" + outlinecolor + "\" fill=\"" + fillcolor + "\" pen=\"" + pen + "\" dash=\""
                     + dash + "\">\n " + x1 + " " + y2 + " m\n " + x1 + " " + y1
                     + " l\n " + x2 + " " + y1 + " l\n " + x2 + " " + y2
                     + " l\n h\n" + "</path>\n";
         }
-        
+
 
         /**
          * Draws a path between points.
@@ -90,8 +90,8 @@ namespace MorphingClass.CUtility
          *            dotted
          * @return
          */
-        public static String drawIpePath(double[] x, double[] y, String color= "black",
-                String pen= "normal", String dash= "normal")
+        public static String drawIpePath(double[] x, double[] y, String color = "black",
+                String pen = "normal", String dash = "normal")
         {
             String s = "<path stroke=\"" + color + "\" pen=\"" + pen + "\" dash=\""
                     + dash + "\">\n" + AddXY(x[0], y[0]) + " m\n";
@@ -99,6 +99,19 @@ namespace MorphingClass.CUtility
             {
                 s += AddXY(x[i], y[i]) + " l\n";
             }
+            s += "</path>\n";
+            return s;
+        }
+
+        public static String drawIpeBoxPath(double dblXMin, double dblYMin, double dblXMax, double dblYMax, 
+            String color = "black", String pen = "normal", String dash = "normal")
+        {
[…]

### 2017-07-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixed bugs of concerning holes

@@
 % your contribution title if the original one is too long
-%\author{Dongliang Peng, Alexander Wolff, and Jan-Henrik Haunert}
+\author{Dongliang Peng and Guillaume Touya}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-% \institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
-% \and Name of Second Author \at Name, Address of Institute
-% \email{name@email.address}}
 \institute{
-%	Dongliang Peng 
-%	\at Chair of Computer Science I, University of W\"urzburg, 
-%	Germany \\
-%	\email{dongliang.peng@uni-wuerzburg.de}
-%	\and
-%	% 
-%	Alexander Wolff 
-%	\at Chair of Computer Science I, University 
-%	of W\"urzburg, Germany \\
-%	\url{URL: 
+	Dongliang Peng 
+	\at Chair of Computer Science I, University of W\"urzburg, 
+	Germany \\
+	\email{dongliang.peng@uni-wuerzburg.de}
+	\and
 	% 
-%http://www1.informatik.uni-wuerzburg.de/en/staff/wolff_alexander}
-%	\and
-%	%
-%	Jan-Henrik Haunert 
-%	\at Institute for Geoinformatics and Remote Sensing (IGF), 
-%	University of Osnabr\"uck, Germany \\
-%	\email{janhhaunert@uni-osnabrueck.de}
+	Guillaume Touya
+	\at COGIT, IGN, France \\
+	\email{guillaume.touya@ign.fr}
 }
@@
 \textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
-when we have to aggregate buildings in the meantime.
+when we have to aggregate buildings simultaneously.
 In order to aggregate, we should first group the buildings.
@@
 \section{Method}
+
+We grow all the buildings with the same speed.
+
+If several buildings are close to each other at the start 
+scale, we bridge them by line segments and take the merge of these 
+buildings 
+and bridges as one building.
+For each building, either an original one or a merged one, at the start 
+scale, 
+we generate its target shape at 
+the goal scale by enlarging and simplifying. Then we grow the  
+building to the target shape.
 
@@
 
-\subsection{Parameters for growing and simplification}
+\subsection{Parameters for growing and simplifying}
 The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
@@
 	\caption{In the left figure, the green polygon represents a building, and 
-	the dashed polygon is the enlargement of the building. In the right 
-	figure, the dashed polygon has been simplified to a rectangle. In order to 
-	fill the rectangle, most parts of the (green) building needs to grow 
-	distance $d_\mathrm{G}$, but the pit needs to grow $d_G + d_\mathrm{e}$, 
+	the gray polygon is the enlargement of the building. In the right 
+	figure, the gray polygon has been simplified to a rectangle. In order to 
+	fill the rectangle, most parts of the (green) building needs to grow with
+	distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
+	d_\mathrm{e}$, 
 	where $d_\mathrm{e}$ is the extra growing distance.}

### 2017-07-20 ContinuousGeneralizer/MorphingClass/CGeometry/CFace.cs

@@ -22,8 +22,8 @@
 
 //        private List<CPoint> _CptLt;      // vertices(clockwise)??? ; the first point and the last point in cptlt must have the same coordinates
 //        private List<CEdge> _CEdgeLt;     // cedges(clockwise)???
-//        private CEdge _cedgeOuterComponent;
-//        private List<CEdge> _cedgeLkInnerComponents;     //counter clockwise
+//        private CEdge _OuterCmptCEdge;
+//        private List<CEdge> _InnerCmptCEdgeLt;     //counter clockwise
 //        private SortedDictionary<CPolygon, LinkedList<CEdge>> _AdjacentSD;    //Why SortedDictionary? Because we may need to unite the adjacent elements of two elements, and we also need to consider the shared borders
 //        private CPatch _cpatch;
 //        private int _intType;
@@ -64,17 +64,17 @@
 //        /// <summary>
 //        /// (counter clockwise)
 //        /// </summary>
-//        public List<CEdge> cedgeLkInnerComponents
+//        public List<CEdge> InnerCmptCEdgeLt
 //        {
-//            get { return _cedgeLkInnerComponents; }
-//            set { _cedgeLkInnerComponents = value; }
+//            get { return _InnerCmptCEdgeLt; }
+//            set { _InnerCmptCEdgeLt = value; }
 //        }
 
 
-//        public CEdge cedgeOuterComponent
+//        public CEdge OuterCmptCEdge
 //        {
-//            get { return _cedgeOuterComponent; }
-//            set { _cedgeOuterComponent = value; }
+//            get { return _OuterCmptCEdge; }
+//            set { _OuterCmptCEdge = value; }
 //        }
 
 //        public SortedDictionary<CPolygon, LinkedList<CEdge>> AdjacentSD

### 2017-08-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the implementation of a basic version of growing buildings

@@
 
+$\bar{a}$
+
 \bigskip
@@
 \end{equation}
-\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
 
@@
 simplify our grown buildings.
+
+We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
+but we hoped to remove more points. We found that Imai--Iri simplification 
+algorithm \parencite{ImaiIri1988} fit our needs well.
 
@@
 
+The closest place of two buildings before enlarging is not necessarily the same 
+as the closest place after enlarging.
+
 \todo[inline]{consider multi bridges; consider transparency of bridges in 

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CAid/CMatchAndMergePolylines.cs

@@ -121,7 +121,7 @@ namespace MorphingClass.CAid
                     }
                     else if (intCount == 1)
                     {
-                        CCorrCplInfo pCorrCplInfo2 = pCorrCplInfoSD.Values.GetFirstT();
+                        CCorrCplInfo pCorrCplInfo2 = pCorrCplInfoSD.Values.First();
                         pLSCPlLt[i].CorrCGeoLt.Add(pCorrCplInfo2.pCorrCpl);
                         pCorrCplInfo2.pCorrCpl.CorrCGeoLt.Add(pLSCPlLt[i]);
                     }

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CCorrepondObjects/CValPair.cs

@@ -20,6 +20,7 @@ using MorphingClass.CUtility;
 
 namespace MorphingClass.CCorrepondObjects
 {
+
     public class CValPair<T1, T2> : IComparable<CValPair<T1, T2>>
     {
         public T1 val1 { get; set; }
@@ -45,38 +46,6 @@ namespace MorphingClass.CCorrepondObjects
         }
 
 
-    }
-
-
-    public class CPairValIncrease<T> : CValPair<T, T>
-        where T: IComparable<T>
-    {
-        public IComparer<T> cmp { get; set; }
-        public CPairValIncrease()
-        {
-
-        }
-
-
-        public CPairValIncrease(T pVal1, T pVal2, IComparer<T> pCmp = null)
-        {
-            this.val1 = pVal1;
-            this.val2 = pVal2;
-            this.cmp = CHelpFunc.SetOrDefaultCmp(pCmp);
-
-            //var 
-
-            if (this.cmp.Compare(pVal1, pVal2) == 1)
-            {
-                this.val1 = pVal2;
-                this.val2 = pVal1;
-            }
-        }
-
-        public int CompareTo(CPairValIncrease<T> other)
-        {
-            return CCmpMethods.CmpDual(this, other, valpair => valpair.val1, valpair => valpair.val2, this.cmp, this.cmp);
-        }
     }
 
 

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CEvaluationMethods/CIntegral.cs

@@ -199,7 +199,7 @@ namespace MorphingClass.CEvaluationMethods
             tocedge.SetLength();
 
 
-            if (CCmpMethods.CmpCEdgeCoordinates(frcedge, tocedge, true)==0 ||
+            if (CCmpMethods.CmpCEdgeCoord(frcedge, tocedge, true)==0 ||
                (frcedge.dblLength == 0 && tocedge.dblLength == 0))   //为了应付刚开始时有重合的对应点
             {
                 return 0;

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CGeometry/CDCEL.cs

@@ -68,7 +68,11 @@ namespace MorphingClass.CGeometry
             //report if there is a short edge
             //short edges may cause problems. Take a polygon as an example, an edge and its twin edge may refer to the same face
             CGeoFunc.CheckShortEdges(cedgelt);
-            CGeoFunc.RemoveLaterDuplicate(cedgelt, new CCmpCEdgeCoordinates());
+
+            if (CGeoFunc.ExistDuplicate(cedgelt, new CCmpEqCEdgeCoord())==true)
+            {
+                throw new ArgumentException("There are duplicated edges! Please keep one copy for each edge!");
+            }
 
             _HalfEdgeLt = ConstructHalfEdgeLt(cedgelt);  //already set indexID
             this.CptLt = ConstructVertexLt(_HalfEdgeLt);         //already set indexID
@@ -83,7 +87,7 @@ namespace MorphingClass.CGeometry
         /// <remarks>could be faster if we do it based on grid</remarks>
         private List<CEdge> ConstructHalfEdgeLt(List<CEdge> cedgelt)
         {
-            List<CEdge> fHalfEdgeLt = new List<CEdge>(cedgelt.Count * 2);
+            var fHalfEdgeLt = new List<CEdge>(cedgelt.Count * 2);
 
             foreach (CEdge cedge in cedgelt)
             {
@@ -93,22 +97,21 @@ namespace MorphingClass.CGeometry
                 fHalfEdgeLt.Add(cedge.cedgeTwin);
             }
 
-            SortedDictionary<CPoint, List<CEdge>> CoStartHalfCEdgeSD = IdentifyCoStartCEdge(fHalfEdgeLt);
-            ConstrcutRelationshipBetweenEdges(CoStartHalfCEdgeSD);
+            var CoStartHalfCEdgeDt = IdentifyCoStartCEdge(fHalfEdgeLt);
+            ConstrcutRelationshipBetweenEdges(CoStartHalfCEdgeDt);
 
             fHalfEdgeLt.SetIndexID();
 
             return fHalfEdgeLt;
         }
 
-        private SortedDictionary<CPoint, List<CEdge>> IdentifyCoStartCEdge(List<CEdge> fHalfEdgeLt)
+        private Dictionary<CPoint, List<CEdge>> IdentifyCoStartCEdge(List<CEdge> fHalfEdgeLt)
         {
[…]

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CGeometry/CEdge.cs

@@ -38,6 +38,8 @@ namespace MorphingClass.CGeometry
         private bool _isStartEdge2;
         private int _intIncrease;
 
+
+
         //private int _intTime = 0;       //匹配成功的次数
         //private CMoveInformation _pMoveInformation;
         //private ILine _pLine;
@@ -62,11 +64,15 @@ namespace MorphingClass.CGeometry
 
         private double _dblAxisAngle = CConstants.dblSpecialValue;
 
-        private CPolyline _BelongedCPolyline;
         private CEdge _ParentCEdge;   //used in the construction of compatible triangulations. we set Parent CEdge so that we know whether or not an edge has been traversed (we don't need to traverse its twin edge), and we know the sub edges of the edge
         private CEdge _CorrRglCEdge;
         private List<CEdge> _CorrRglSubCEdgeLt;
         public SortedDictionary<double, CPoint> BreakCptSD { get; set; }
+        public CPolygon LinkedFrCpg { get; set; }
+        public CPolygon LinkedToCpg { get; set; }
+        public CPolygon BelongedCpg { get; set; }
+        public CPolyline BelongedCpl { get; set; }
+
         //private string _strLabel;
 
         /// <summary>
@@ -270,6 +276,10 @@ namespace MorphingClass.CGeometry
         }
 
 
+        public void SetFrCptCEdge()
+        {
+            this.FrCpt.CEdge = this;
+        }
 
         public double SetLength()
         {
@@ -694,11 +704,7 @@ namespace MorphingClass.CGeometry
         //    set { _dblDifffromMovePtY = value; }
         //}
 
-        public CPolyline BelongedCPolyline
-        {
-            get { return _BelongedCPolyline; }
-            set { _BelongedCPolyline = value; }
-        }
+
 
         public CEdge CorrRglCEdge
         {

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CGeometry/CEdgeRelation.cs

@@ -40,20 +40,20 @@ namespace MorphingClass.CGeometry
                 case CEnumIntersectionType.FrFr:
                     this.pEnumDisMode = CEnumDisMode.FrFr;
                     this.cptEdgeDis = new CGeometry.CptEdgeDis
-                        (0, 0, _CEdge1.FrCpt, _CEdge2.FrCpt, _CEdge2, false);
+                        (0, 0, _CEdge1.FrCpt, _CEdge1, _CEdge2.FrCpt, _CEdge2, false);
                     break;
                 case CEnumIntersectionType.FrIn:
                     this.pEnumDisMode = CEnumDisMode.FrIn;
-                    this.cptEdgeDis = _CEdge1.FrCpt.DistanceTo(_CEdge2);
+                    this.cptEdgeDis = _CEdge1.FrCpt.DistanceTo(_CEdge2,false, _CEdge1);
                     break;
                 case CEnumIntersectionType.FrTo:
                     this.pEnumDisMode = CEnumDisMode.FrTo;
                     this.cptEdgeDis = new CGeometry.CptEdgeDis
-                        (0, 1, _CEdge1.FrCpt, _CEdge2.ToCpt, _CEdge2, false);
+                        (0, 1, _CEdge1.FrCpt, _CEdge1, _CEdge2.ToCpt, _CEdge2, false);
                     break;
                 case CEnumIntersectionType.InFr:
                     this.pEnumDisMode = CEnumDisMode.InFr;
-                    this.cptEdgeDis = _CEdge2.FrCpt.DistanceTo(_CEdge1);
+                    this.cptEdgeDis = _CEdge2.FrCpt.DistanceTo(_CEdge1, false, _CEdge2);
                     break;
                 case CEnumIntersectionType.InIn:
                     this.pEnumDisMode = CEnumDisMode.InIn;
@@ -61,23 +61,23 @@ namespace MorphingClass.CGeometry
                     break;
                 case CEnumIntersectionType.InTo:
                     this.pEnumDisMode = CEnumDisMode.InTo;
-                    this.cptEdgeDis = _CEdge2.ToCpt.DistanceTo(_CEdge1);
+                    this.cptEdgeDis = _CEdge2.ToCpt.DistanceTo(_CEdge1, false, _CEdge2);
                     break;
                 case CEnumIntersectionType.ToFr:
[…]

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CUtility/CCompareClasses.cs

@@ -1,297 +1,0 @@
-using System;
-using MorphingClass.CGeometry;
-using System.Collections.Generic;
-using System.Text;
-using System.Collections;
-
-//using MorphingClass;
-using MorphingClass.CGeometry.CGeometryBase;
-using MorphingClass.CCorrepondObjects;
-
-namespace MorphingClass.CUtility
-{
-    //Note:
-    //the first variable is the new element, while the second variable has been already in the data structure
-    //return  1:put the first variable after the second one
-    //return -1:put the first variable in front of the second one
-    //public class CCmp
-    //{
-
-    //}
-    
-
-
-    public class CCmpCoordDbl_VerySmall : Comparer<double>
-    {
-        public static CCmpCoordDbl_VerySmall pCmpCoordDbl_VerySmall = new CCmpCoordDbl_VerySmall();
-
-        public override int Compare(double x, double y)
-        {
-            return CCmpMethods.CmpCoordDbl_VerySmall(x, y);
-        }
-    }
-
-    public class CCmpDbl : Comparer<double>
-    {
-        //CaseInsensitiveComparer MyCompare = new CaseInsensitiveComparer();
-        public override int Compare(double x, double y)
-        {
-            return CCmpMethods.CmpDblPostLocateEqual(x, y);
-        }
-    }
-
-    public class CCmpCptEdgeDis_T : Comparer<CptEdgeDis>
-    {
-        public static CCmpCptEdgeDis_T pCmpCptEdgeDis_T = new CCmpCptEdgeDis_T();
-        public override int Compare(CptEdgeDis x, CptEdgeDis y)
-        {
-            return CCmpMethods.CmpDual(x,y, cptEdgeDis=> cptEdgeDis.t, cptEdgeDis=> cptEdgeDis.Cpt.GID);
-        }
-    }
-
-    public class CAACCmp : Comparer<IList<object>>
-    {
-        public override int Compare(IList<object> lt1, IList<object> lt2)
-        {
-            int intResult = CCmpMethods.CmpDbl_ConstVerySmall(Convert.ToDouble(lt1[3]), Convert.ToDouble(lt2[3]));  //overesimation factor
-            if (intResult == 0)
-            {
-                intResult = CCmpMethods.CmpDbl_ConstVerySmall(Convert.ToDouble(lt1[1]), Convert.ToDouble(lt2[1]));  //patch number
-            }
-            if (intResult == 0)
[…]

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CUtility/CConstants.cs

@@ -25,13 +25,14 @@ namespace MorphingClass.CUtility
         public static double _dblVerySmallDenominator = 1000000; //I test it many times. it seems 10 X e6 is appropriate value. This value may need change when we have different data sets
         private static double _dblSmallDisDenominator = 1000;
         public static double dblSpecialValue { set; get; } = -Math.Pow(Math.PI, 3);  //we use the special value to initial some number
-
         
         public static double dblVerySmallConst { set; get; } = 0.00000001;
         public static double dblTwoPI { set; get; } = 2 * Math.PI;
         public static double dblHalfPI { set; get; } = Math.PI/2;
         public static double dblThreeSecondPI { set; get; } = 3*Math.PI / 2;
         public static double dblFiveDegreeRad { set; get; } = Math.PI / 36;
+        public static double dblFclipper { set; get; } = 100000000;
+        public static double dblRationVerySmallFclipper { set; get; } = dblVerySmallCoord/ dblFclipper;
 
         private static double _dblTwoSqrtPI = 2 * Math .Sqrt ( Math.PI);
         private static double _dblHalfDoubleMax = double.MaxValue / 2;
@@ -52,6 +53,7 @@ namespace MorphingClass.CUtility
         public static string strMethod { set; get; }
         public static string strShapeConstraint { set; get; }
         public static CEnvelope pIpeEnv { set; get; } = new CEnvelope(0, 0, 128, 128);
+        
 
         //        var output = string.Format("{0,3}{1,10}{2,13}{3,10}{4,9}{5,10}{6,7}{7,22}{8,7}{9,22}",
         //    "ID:", this.ID, ";    indexID:", this.indexID , ";    GID:" , this.GID , ";    X:", this.X , ";    Y:", this.Y);
@@ -120,6 +122,8 @@ namespace MorphingClass.CUtility
                 _dblVerySmallSquare = 2 * X * y + yy;
                 _dblVerySmallPower3 = 3 * XX * y + 3 * X * yy + yyy;
                 _dblVerySmallPower4 = 4 * XXX * y + 6 * XX * yy + 4 * X * yyy + yyyy;
+
+                dblRationVerySmallFclipper = y / dblFclipper;
             }
         }
 

### 2017-08-07 ContinuousGeneralizer/MorphingClass/CUtility/CHelpFunc.cs

@@ -1,1278 +1,0 @@
-using System;
-using System.Diagnostics;
-using System.Collections.Generic;
-using System.Linq;
-using System.Text;
-using System.Windows.Forms;
-using System.IO;
-using System.Runtime.InteropServices;
-using System.Drawing;
-//using System.Windows;
-
-using SCG = System.Collections.Generic;
-using C5;
-using Microsoft.Office.Interop;
-
-using ESRI.ArcGIS.Controls;
-using ESRI.ArcGIS.Carto;
-using ESRI.ArcGIS.DataSourcesFile;
-using ESRI.ArcGIS.DataSourcesGDB;
-using ESRI.ArcGIS.Display;
-using ESRI.ArcGIS.Geodatabase;
-using ESRI.ArcGIS.Geometry;
-using ESRI.ArcGIS.Output;
-using ESRI.ArcGIS.esriSystem;
-
-using MorphingClass.CCorrepondObjects;
-using MorphingClass.CGeometry;
-using MorphingClass.CGeometry.CGeometryBase;
-using MorphingClass.CEntity;
-using MorphingClass.CMorphingMethods.CMorphingMethodsBase;
-using VBClass;
-//using EasyMorphing.
-//using MorphingClass.
-
-namespace MorphingClass.CUtility
-{
-
-
-
-    public static class CHelpFunc
-    {
-        //private static string _strDataFolderName = "Jiangxi";
-        //private static string _strDataFolderName = "CompatibleTriangulationTestVerySimple";
-        //private static string _strDataFolderName = "JiangxiOneCounty";
-        //private static string _strDataFolderName = "rail梅集线Test";
-        //private static string _strPath = "C:\\Study\\Data\\Morphing Data\\Rail Data\\" + _strDataFolderName + "\\";
-
-        //private static string _strDataFolderName = "MainlandChina-Yunnan";
-        //private static string _strDataFolderName = "MainlandChina-Guangxi";
-        //private static string _strDataFolderName = "MainlandChina-Tianjin";
-        //private static string _strDataFolderName = "MainlandChina-Animation";
-        //private static string _strDataFolderName = "Tianjin-Animation"; 
-        //private static string _strDataFolderName = "MainlandChina-Animation-complicated";
-        //private static string _strDataFolderName = "MainlandChina-Shanghai";
-        //private static string _strDataFolderName = "MainlandChina";
-        //private static string _strDataFolderName = "CompatibleTriangulation";
[…]

### 2017-08-10 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
basically finished programming. construct cover of buildings by iteratively merging dilated buildings

@@
 
-\newcommand{\myabstract}{We proposed a method to continuous 
-	generalization of buildings from given start scale to any smaller goal 
-	scale. 
+\newcommand{\myabstract}{We propose a method to continuously 
+	generalize buildings from a given start scale to a smaller goal scale. 
 	%
 	If several buildings are close to each other at the start 
-	scale, we bridge them by line segments and take the merge of these 
-	buildings 
-	and bridges as one building.
+	scale, we bridge them by line segments and merge the several buildings into 
+	one 
+	building.
 	For each building, either an original one or a merged one, at the start 
@@
 	we generate its target shape at 
-	the goal scale by enlarging and simplifying. Then we grow the  
-	building to the target shape. 
+	the goal scale by enlarging and simplifying. 
+	Then we grow the building to the target shape.
 	%
-	After finishing the growing, we take the goal scale as the 
-	start scale and repeat our continuous generalization.
+	After finishing the growing, we can take the goal scale as the 
+	start scale and repeat the process.
 	\newline\indent
-	Our contribution is as follows. First, the buildings 
+	The advantages of our method are as follows. First, the buildings 
 	are enlarged continuously. At the same time, they are simplified. 
@@
 We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
-but we hoped to remove more points. We found that Imai--Iri simplification 
+but we hoped to remove more points. We found that Imai--Iri 
 algorithm \parencite{ImaiIri1988} fit our needs well.
+
+Imai--Iri algorithm finds all the valid shortcuts, and then
 

### 2017-08-10 ContinuousGeneralizer/ContinuousGeneralizer/FrmAid/FrmCreateRandomPointLayer.cs

@@ -108,7 +108,7 @@ namespace ContinuousGeneralizer.FrmAid
                 //{
                 //    objshapelt.Add(cptlt[i]);
 
-                //    List<object> objvaluelt = new List<object>(1);
+                //    List<object> objvaluelt = new List<object>();
                 //    objvaluelt.Add(i);
                 //    objectvalueltlt.Add(objvaluelt);
                 //}

### 2017-08-10 ContinuousGeneralizer/ContinuousGeneralizer/FrmAid/FrmMergeAndSplitPolylines.cs

@@ -60,7 +60,7 @@ namespace ContinuousGeneralizer.FrmAid
         private void FrmMergeAndSplitPolylines_Load(object sender, EventArgs e)
         {
             CParameterInitialize ParameterInitialize = _DataRecords.ParameterInitialize;
-            ParameterInitialize.cboLayerLt = new List<ComboBox>(1);
+            ParameterInitialize.cboLayerLt = new List<ComboBox>();
             ParameterInitialize.cboLayerLt.Add(this.cboLayer);
 
             //进行Load操作，初始化变量

### 2017-08-10 ContinuousGeneralizer/ContinuousGeneralizer/FrmGeneralization/FrmBldgGrow.Designer.cs

@@ -31,6 +31,8 @@
             this.groupBox3 = new System.Windows.Forms.GroupBox();
             this.txtEvaluation = new System.Windows.Forms.TextBox();
             this.groupBox1 = new System.Windows.Forms.GroupBox();
+            this.label14 = new System.Windows.Forms.Label();
+            this.cboSimplification = new System.Windows.Forms.ComboBox();
             this.label13 = new System.Windows.Forms.Label();
             this.label11 = new System.Windows.Forms.Label();
             this.txtOutput = new System.Windows.Forms.TextBox();
@@ -43,8 +45,6 @@
             this.label10 = new System.Windows.Forms.Label();
             this.txtMiterLimit = new System.Windows.Forms.TextBox();
             this.label4 = new System.Windows.Forms.Label();
-            this.txtBufferRadius = new System.Windows.Forms.TextBox();
-            this.label3 = new System.Windows.Forms.Label();
             this.label1 = new System.Windows.Forms.Label();
             this.cboBufferStyle = new System.Windows.Forms.ComboBox();
             this.label8 = new System.Windows.Forms.Label();
@@ -79,8 +79,6 @@
             this.btn080 = new System.Windows.Forms.Button();
             this.btn070 = new System.Windows.Forms.Button();
             this.btn090 = new System.Windows.Forms.Button();
-            this.label14 = new System.Windows.Forms.Label();
-            this.cboSimplification = new System.Windows.Forms.ComboBox();
             this.groupBox3.SuspendLayout();
             this.groupBox1.SuspendLayout();
             this.groupBox2.SuspendLayout();
@@ -120,8 +118,6 @@
             this.groupBox1.Controls.Add(this.label10);
             this.groupBox1.Controls.Add(this.txtMiterLimit);
             this.groupBox1.Controls.Add(this.label4);
-            this.groupBox1.Controls.Add(this.txtBufferRadius);
-            this.groupBox1.Controls.Add(this.label3);
             this.groupBox1.Controls.Add(this.label1);
             this.groupBox1.Controls.Add(this.cboBufferStyle);
             this.groupBox1.Controls.Add(this.label8);
@@ -139,6 +135,30 @@
             this.groupBox1.TabIndex = 78;
             this.groupBox1.TabStop = false;
             this.groupBox1.Text = "Parameters";
+            // 
+            // label14
+            // 
+            this.label14.AutoSize = true;
+            this.label14.Location = new System.Drawing.Point(6, 134);
[…]

### 2017-08-10 ContinuousGeneralizer/MorphingClass/CAid/CCreatePointLayer.cs

@@ -58,7 +58,7 @@ namespace MorphingClass.CAid
                 
                 for (int j = 0; j < CPolylineLt[i].CptLt .Count; j++)
                 {
-                    //var pobjectValueLt = new List<object>(1);
+                    //var pobjectValueLt = new List<object>();
                     //pobjectValueLt.Add(j);
                     //pobjectValueLtLt.Add(pobjectValueLt);
 

### 2017-08-10 ContinuousGeneralizer/MorphingClass/CGeometry/CEdge.cs

@@ -71,6 +71,7 @@ namespace MorphingClass.CGeometry
         public CPolygon LinkedFrCpg { get; set; }
         public CPolygon LinkedToCpg { get; set; }
         public CPolygon BelongedCpg { get; set; }
+        public CPolygon BelongedOriginalCpg { get; set; }
         public CPolyline BelongedCpl { get; set; }
 
         //private string _strLabel;
@@ -259,6 +260,7 @@ namespace MorphingClass.CGeometry
                 _cedgeTwin = TwinCEdge;
                 JudgeAndSetAxisAngle();
                 SetTwinCEdgeAxisAngle();
+                //TwinCEdge.BelongedOriginalCpg = this.BelongedOriginalCpg;
             }
 
             SetCEdgePrevNextAsTwin();

### 2017-08-10 ContinuousGeneralizer/MorphingClass/CGeometry/CPolygon.cs

@@ -9,6 +9,7 @@ using ESRI.ArcGIS.Geometry;
 using MorphingClass.CUtility;
 using MorphingClass.CEntity;
 using MorphingClass.CGeometry.CGeometryBase;
+using MorphingClass.CCorrepondObjects;
 
 using ClipperLib;
 using Path = System.Collections.Generic.List<ClipperLib.IntPoint>;
@@ -46,7 +47,7 @@ namespace MorphingClass.CGeometry
         public CPolygon ExteriorOffsetCpg { get; set; }
         //public cp CPolygon ClipBridge { get; set; }
 
-        public Paths CpgPaths { get; set; }
+        public Paths ExteriorPaths { get; set; }
         public PolyTree pPolyTree { get; set; }
 
         public List<CPolygon> HoleCpgLt { get; set; }
@@ -55,6 +56,8 @@ namespace MorphingClass.CGeometry
         public List<CPolygon> SubCpgLt { get; set; }
         public SortedSet<CptEdgeDis> BridgeCptEdgeDisSS { get; set; }
         
+        public Dictionary<CValPairIncr<CPolygon>, CptEdgeDis> CpipeDt { get; set; }
+
         //public CPolygon AssigningFace { get; set; }
         //public List<CPolygon> AssignedFaceLt { get; set; }
 
@@ -368,30 +371,7 @@ namespace MorphingClass.CGeometry
             }
         }
 
-        public IEnumerable<CPoint> GetInnerCptEb(CEdge cedgeComponent, bool clockwise = true, bool blnIdentical = true)
-        {
-            var pOuterCmptCEdge = cedgeComponent;
-
-            if (clockwise == true)  //for an inner path, the edges are stored clockwise in DCEL
-            {
-                foreach (var cpt in TraverseToGetCptEb(pOuterCmptCEdge, true))
-                {
-                    yield return cpt;
-                }
-            }
-            else
-            {
-                foreach (var cpt in TraverseToGetCptEb(pOuterCmptCEdge, false))
-                {
-                    yield return cpt;
-                }
-            }
-
-            if (blnIdentical == true)
-            {
-                yield return pOuterCmptCEdge.FrCpt;
-            }
-        }
+       
 
         /// <summary>
         /// 
@@ -405,6 +385,25 @@ namespace MorphingClass.CGeometry
             do
             {
                 yield return currentcedge.FrCpt;
+
+                if (blnNext == true)
+                {
+                    currentcedge = currentcedge.cedgeNext;
+                }
[…]

### 2017-08-10 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -26,16 +26,17 @@ namespace MorphingClass.CUtility
         public static Paths Offset_Paths(Paths inputpaths, double dbldelta,
            string strBufferStyle = "Miter", double dblMiterLimit = 2)
         {
+            //Console.WriteLine("dblMiterLimit = " + dblMiterLimit);
+
             //keep in mind that the first point and the last point of a output path are not identical
-            //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon
-            ClipperOffset pClipperOffset = new ClipperOffset();
+            //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon            
+            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit);
             switch (strBufferStyle)
             {
                 case "Miter":
                     //Property MiterLimit sets the maximum distance in multiples of delta that vertices can be offset from 
                     //their original positions before squaring is applied. (Squaring truncates a miter by 'cutting it off' 
                     //at 1 × delta distance from the original vertex.)
-                    pClipperOffset.MiterLimit = dblMiterLimit;
                     pClipperOffset.AddPaths(inputpaths, JoinType.jtMiter, EndType.etClosedPolygon);
                     break;
                 case "Round":
@@ -58,16 +59,17 @@ namespace MorphingClass.CUtility
         public static PolyTree Offset_PolyTree(Paths inputpaths, double dbldelta, string strBufferStyle = "Miter",
             double dblMiterLimit = 2)
         {
+            //Console.WriteLine("dblMiterLimit = " + dblMiterLimit);
+
             //keep in mind that the first point and the last point of a path are not identical
             //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon
-            ClipperOffset pClipperOffset = new ClipperOffset();
+            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit);
             switch (strBufferStyle)
             {
                 case "Miter":
[…]

### 2017-08-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
removed some unused figures; added the description of Imai-Iri algorithm

@@
 \newcommand{\e}[1]{\times 10^{#1}}
+\newcommand{\fig}{Fig.~}
+\newcommand{\eq}{Eq.~}
 
@@
 
-\title*{Continuous Generalization of Buildings}
+\title*{Continuous Generalization of Buildings \protect\\ by Growing and 
+Merging}
 \titlerunning{Continuous Generalization of Buildings}
@@
 We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
-but we hoped to remove more points. We found that Imai--Iri 
-algorithm \parencite{ImaiIri1988} fit our needs well.
+but we hoped to remove more points. We found that the Imai--Iri 
+algorithm \parencite{ImaiIri1988} fit our needs well. Although a version with a 
+lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
+version.
 
-Imai--Iri algorithm finds all the valid shortcuts, and then
+The Imai--Iri algorithm first finds all the valid shortcuts of a polyline.
+For a sequence of points on a polyline, 
+if their distances to their shortcut are 
+at most specified value $\epsilon$, then the shortcut is valid (see 
+\fig\ref{fig:ImaiIri_Shortcut}). 
+Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
+of a polyline to the end, using breadth-first search.
+The sequence of valid shortcuts is an approximation of the polyline, 
+and has the least number of line segments.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{ImaiIri_Shortcut}
+	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
+	\label{fig:ImaiIri_Shortcut}
+\end{figure}
+
+We add three more constraints for a shortcut to be valid
+when we use the Imai--Iri algorithm. 
+That is, 
+a shortcut is not allowed to intersect the boundary of the original building, 
+is not allowed to intersect the boundary of the grown building, 
+and must be inside the grown building.
+For the first constraint, 
+if a shortcut intersects the boundary of the original building, 
+we will need to shrink the building, which we do not want.
+For the second and the third constraints,
+if a shortcut is outside the grown building,
+we are not able to arrive at the shortcut by growing.
 

### 2017-08-11 ContinuousGeneralizer/MorphingClass/CGeneralizationMethods/CDPSimplify.cs

@@ -754,31 +754,31 @@ namespace MorphingClass.CGeneralizationMethods
             CNodeQueue.Enqueue(startCNode);
             bool isFoundGoal = false;
 
-            while (CNodeQueue.Count>0 && isFoundGoal ==false)
+            while (CNodeQueue.Count > 0 && isFoundGoal == false)
             {
                 var currentCNode = CNodeQueue.Dequeue();
                 foreach (var nbrcnode in currentCNode.NbrCNodeLt)
                 {
-                    if (nbrcnode.strColor=="white")
+                    if (nbrcnode.strColor == "white")
                     {
                         nbrcnode.strColor = "gray";
-                        nbrcnode.PrevCNode = currentCNode;                        
+                        nbrcnode.PrevCNode = currentCNode;
 
                         CNodeQueue.Enqueue(nbrcnode);
                     }
 
-                    if (nbrcnode.GID== goalCNode.GID)
+                    if (nbrcnode.GID == goalCNode.GID)
                     {
                         isFoundGoal = true;
                     }
                 }
                 currentCNode.strColor = "black";
             }
-            
+
 
             // set NextCNode for each Node on the path
             var backCNode = goalCNode;
-            while (backCNode.GID!= startCNode.GID)
+            while (backCNode.GID != startCNode.GID)
             {
                 backCNode.PrevCNode.NextCNode = backCNode;
 

### 2017-08-11 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -193,7 +193,7 @@ namespace MorphingClass.CUtility
                 }
                 GroupedCpgLtLt = newGroupedCpgLtLt;
                 ++intRound;
-                Console.WriteLine("IterativeGroupCpgsByOverlapIndependently: " + intRound);
+                //Console.WriteLine("IterativeGroupCpgsByOverlapIndependently: " + intRound);
             }
         }
 

### 2017-08-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
writing the paper

@@
 
-\section{Method}
+\section{Methodology}
 
@@
 \subsection{Simplification}
-we use a buffer-based method, similar to \textcite{Damen2008,Meijers2016}, to 
-simplify our grown buildings.
+We use an offset-based method, similar to \textcite{Damen2008,Meijers2016}, to 
+simplify our grown buildings. We first dilate the grown buildings to remove 
+pits, and then erode the results to remove spikes.
 
+After carrying out the offset-based method, we simplify the grown buildings 
 We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
@@
 
-We add three more constraints for a shortcut to be valid
+\todo[inline]{more details in the below paragraph?}
+We add two more constraints for a shortcut to be valid
 when we use the Imai--Iri algorithm. 
-That is, 
-a shortcut is not allowed to intersect the boundary of the original building, 
-is not allowed to intersect the boundary of the grown building, 
-and must be inside the grown building.
-For the first constraint, 
-if a shortcut intersects the boundary of the original building, 
-we will need to shrink the building, which we do not want.
-For the second and the third constraints,
-if a shortcut is outside the grown building,
+The first one is that
+a shortcut must be completely inside the grown building.
+If a shortcut is outside,
 we are not able to arrive at the shortcut by growing.
+The second constraint is that a shortcut is not allowed to intersect the 
+boundary of the original building.
+If a shortcut does intersect, 
+we will need to shrink the building instead of growing. Of course, we do not 
+want to shrink.
 
@@
 
-\section{Section Title}
-\label{sec:AStarAlgorithm}
+\section{Case Study}
+\label{sec:CaseStudy}
+We have implemented our method based on C\# (Microsoft Visual 
+Studio 
+2015) and ArcObjects SDK \revise{for the Microsoft .Net Framework}{}10.2. 
+We ran our case study under 64-bit 
+Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
+%As ArcObjects SDK for the Microsoft .Net Framework 10.2 can 
+%only  run under a 32-bit platform, we set a Post-build 
+%event\footnote{The details of the setting can be found at 	
+%\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio}.},
+%in Microsoft Visual Studio 2012
+%so that we managed to use up to 3GM of RAM.
+We measured processing time by the built-in C\# class 
+\emph{Stopwatch}.
+We tested our method on a dataset from the German topographic 
+database ATKIS DLM 50. The dataset represents the place 
+``Buchholz in der Nordheide'' at scale $1:50{,}000$. Our start 
+map is the map after the collapse of areas by \citet[pp. 
+61--66]{haunert2008f}, which has $5{,}537$ polygons. Our goal 
+map was generalized from the start map by 
+\citet{haunertwolff2010b} setting the scale at $1:250{,}000$ 
+(see Fig.~\ref{fig:Data}). The goal map has $734$ polygons, 
+which means that \revise{we have}{there are $N=734$} regions.
 
@@
 \label{sec:Conclusions}
-
-Because of our aggregation with skeletons and original 
-buildings, we may have too many details in the intermediate 
-results.
-
-Some buildings are too small to be eroded. We have to generate 
-squares or MBR?
 
@@
 
-One can also discuss about our growing speed.
-
 We our intermediate results may violate more cartographic rules, but we try to 
@@
 
-Ideally, for a rectangle, the ratio of width to height should be kept.
-
-The closest place of two buildings before enlarging is not necessarily the same 
-as the closest place after enlarging.
+Eventually, our result is a set of settlement boundaries. An interesting 
+problem is to compare our method with \textcite{Chaudhry2008}.
 

### 2017-08-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added description of "grouping buildings based on buffering"

@@
 
-\subsection{Growing}
-If several buildings are close to each other at the start 
-scale, we bridge them by line segments and take the merge of these 
-buildings 
-and bridges as one building.
-For each building, either an original one or a merged one, at the start 
-scale, 
-we generate its target shape at 
-the goal scale by enlarging and simplifying. Then we grow the  
-building to the target shape. 
-%
-After finishing the growing, we take the goal scale as the 
-start scale and repeat our continuous generalization.
-\newline\indent
-Our contribution is as follows. First, the buildings 
-are enlarged continuously. At the same time, they are simplified. 
-Second, we ensure that the distance between any pair of two buildings is 
-always larger than a specified threshold.
+\subsection{Grouping buildings based on buffering}
+We group buildings based on the buffers of the buildings. 
+We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
+where distance $d_G$ is the growing amount of each building. 
+Parameter $d_\epsilon$ is the least distance allowed between two buildings.
+We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
+the corresponding two buildings will become too close during our growing step.
+The two buildings are in the same group.
 
-If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
-grow at most $2d_\mathrm{G}$.
-The length of a bridge can be as large as
-\begin{equation}
-\label{eq:BridgeLength}
-l_b=4d_\mathrm{G}+d_\epsilon.
-\end{equation}
-%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+We merge the buffers which overlap each others so that we have some large units.
+Now we iteratively remove small ``bays''.
+Each iteration consists of three steps, i.e., 
+buffering with distance $r_H$, buffering with distance $-r_H$, and
+merging overlapping units.
+The iterative process stops when the number of units do not decrease anymore.
 
-\subsection{Simplification}
-We use an offset-based method, similar to \textcite{Damen2008,Meijers2016}, to 
-simplify our grown buildings. We first dilate the grown buildings to remove 
+All the buildings overlapping with the same unit belong to the same group.
+
+\subsection{Enlarging and merging buildings}
+
+\subsection{Simplifying merged buildings}
+We use an buffering-based method, 
+similar to \textcite{Damen2008,Meijers2016}, 
+to simplify our grown buildings. 
+We first dilate the grown buildings to remove 
 pits, and then erode the results to remove spikes.
@@
 want to shrink.
+
+\subsection{Growing}
+If several buildings are close to each other at the start 
+scale, we bridge them by line segments and take the merge of these 
+buildings 
+and bridges as one building.
+For each building, either an original one or a merged one, at the start 
+scale, 
+we generate its target shape at 
+the goal scale by enlarging and simplifying. Then we grow the  
+building to the target shape. 
+%
+After finishing the growing, we take the goal scale as the 
+start scale and repeat our continuous generalization.
+\newline\indent
+Our contribution is as follows. First, the buildings 
+are enlarged continuously. At the same time, they are simplified. 
+Second, we ensure that the distance between any pair of two buildings is 
+always larger than a specified threshold.
+
+If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
+grow at most $2d_\mathrm{G}$.
+The length of a bridge can be as large as
+\begin{equation}
+\label{eq:BridgeLength}
+l_b=4d_\mathrm{G}+d_\epsilon.
+\end{equation}
+%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
 
@@
 Studio 
-2015) and ArcObjects SDK \revise{for the Microsoft .Net Framework}{}10.2. 
+2015) and ArcObjects SDK 10.4.1. 
 We ran our case study under 64-bit 
 Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
-%As ArcObjects SDK for the Microsoft .Net Framework 10.2 can 
-%only  run under a 32-bit platform, we set a Post-build 
-%event\footnote{The details of the setting can be found at 	
-%\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio}.},
-%in Microsoft Visual Studio 2012
-%so that we managed to use up to 3GM of RAM.
 We measured processing time by the built-in C\# class 
 \emph{Stopwatch}.
-We tested our method on a dataset from the German topographic 
-database ATKIS DLM 50. The dataset represents the place 
-``Buchholz in der Nordheide'' at scale $1:50{,}000$. Our start 
-map is the map after the collapse of areas by \citet[pp. 
-61--66]{haunert2008f}, which has $5{,}537$ polygons. Our goal 
-map was generalized from the start map by 
-\citet{haunertwolff2010b} setting the scale at $1:250{,}000$ 
-(see Fig.~\ref{fig:Data}). The goal map has $734$ polygons, 
-which means that \revise{we have}{there are $N=734$} regions.
+We tested our method on a dataset from French Mapping Agency (IGN).
+The dataset represents four towns (communes in French), i.e., Aussevielle, 
+Denguin,  Poey-de-Lescar, and Siros, in the 
+Pyr\'en\'ees-Atlantiques department, south-western France.
+The scale of the dataset is $1:15{,}000$.
+Our goal scale is $1:50{,}000$.
 
@@
 
+We did not include streets. We can either put them above the settlement 
+boundaries on map, or use them as restriction for building growing.
+
 \todo[inline]{consider multi bridges; consider transparency of bridges in 

### 2017-08-16 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -183,18 +183,25 @@ namespace MorphingClass.CUtility
             }
 
             int intRound = 0;
+            var newGroupedCpgLtLt = new List<List<CPolygon>>();
             while (true)
             {
-                var newGroupedCpgLtLt = DilateAndOverlapPaths(cpglt, GroupedCpgLtLt,
+                newGroupedCpgLtLt = DilateAndOverlapPaths(cpglt, GroupedCpgLtLt,
                     dblGrow, dblDilation, dblEpsilon, strBufferStyle, dblMiterLimit);
-                if (newGroupedCpgLtLt.Count== GroupedCpgLtLt.Count)
+                if (newGroupedCpgLtLt.Count == GroupedCpgLtLt.Count)
                 {
-                    return newGroupedCpgLtLt;
+                    break;
                 }
                 GroupedCpgLtLt = newGroupedCpgLtLt;
                 ++intRound;
-                //Console.WriteLine("IterativeGroupCpgsByOverlapIndependently: " + intRound);
             }
+
+            if (intRound > 1)
+            {
+                Console.WriteLine("IterativeGroupCpgsByOverlapIndependently: " + intRound);
+            }
+
+            return newGroupedCpgLtLt;
         }
 
 

### 2017-08-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added texts of sections Methodology and Case study

@@
 \newcommand{\eq}{Eq.~}
+\newcommand{\sect}{Sec.~}
 
@@
 \subsection{Grouping buildings based on buffering}
+\label{sec:Grouping}
 We group buildings based on the buffers of the buildings. 
@@
 
-\subsection{Enlarging and merging buildings}
+\subsection{Enlarging and merging buildings for goal map}
+For each pair of buildings in the same group, 
+we find the smallest distance between them.
+We connect the buildings by adding an edge from the nearest points.
+We find a minimum spanning tree of the buildings using Prim's algorithm 
+\parencite{Prim1957}.
+We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
 

### 2017-08-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixed a bug and added Data.pdf

@@
 
-\subsection{Simplifying merged buildings}
+\subsection{Simplifying merged buildings considering right angles}
+
 We use an buffering-based method, 
@@
 
-After carrying out the offset-based method, we simplify the grown buildings 
+After carrying out the offset-based method, we simplify the grown buildings. 
 We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
@@
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Data}
+	\caption{scale.}
+	\label{fig:Data}
+\end{figure}
+
 \mypar{Notation}
@@
 
+At some point, we should remove the requirement of keeping right angles. Right 
+angles may not be important anymore when we deal with settlement boundaries.
+
 \todo[inline]{consider multi bridges; consider transparency of bridges in 

### 2017-08-18 ContinuousGeneralizer/MorphingClass/CGeometry/CPolygon.cs

@@ -54,7 +54,7 @@ namespace MorphingClass.CGeometry
         public CPoint CentroidCptSimple { get; set; }
 
         public List<CPolygon> SubCpgLt { get; set; }
-        public SortedSet<CptEdgeDis> BridgeCptEdgeDisSS { get; set; }
+        public HashSet<CptEdgeDis> BridgeCptEdgeDisSS { get; set; }
         
         public Dictionary<CValPairIncr<CPolygon>, CptEdgeDis> CpipeDt { get; set; }
 
@@ -119,6 +119,14 @@ namespace MorphingClass.CGeometry
             this.GID = _intStaticGID++;
             _intID = intID;
             this.strShape = "Polygon";
+
+            if (cptlt != null && cptlt.Count > 0)
+            {
+                cptlt[cptlt.Count - 1] = cptlt[0];  //make sure that the first vertex and the last vertex are identical
+            }
+            
+
+
             FormPolyBase(cptlt);
 
 
@@ -159,15 +167,15 @@ namespace MorphingClass.CGeometry
             }
         }
 
-        public override void SetCEdgeLtFrCptCEdge()
+        public override void SetCEdgeToCpts()
         {
-            this.CEdgeLt.ForEach(cedge => cedge.SetFrCptCEdge());
+            this.CEdgeLt.ForEach(cedge => cedge.SetCEdgeToCpts());
 
             if (this.HoleCpgLt != null)
             {
                 foreach (var holecpg in this.HoleCpgLt)
                 {
-                    holecpg.SetCEdgeLtFrCptCEdge();
+                    holecpg.SetCEdgeToCpts();
                 }
             }
         }

### 2017-08-18 ContinuousGeneralizer/MorphingClass/CGeometry/CGeometryBase/CPolyBase.cs
fixing the bug of a hole in a hole

@@ -47,13 +47,7 @@ namespace MorphingClass.CGeometry.CGeometryBase
         /// </summary>
         /// <remarks>如果已经生成过边，则直接返回</remarks>
         public virtual void FormPolyBase(List<CPoint> fcptlt)
-        {
-            if (fcptlt!=null && fcptlt.Count>0)
-            {
-                _FrCpt = fcptlt[0];
-                _ToCpt = fcptlt.GetLastT();
-            }            
-
+        { 
             this.CptLt = fcptlt;
             //this.CEdgeLt = CGeoFunc.FormCEdgeEb(fcptlt).ToList();
         }
@@ -147,6 +141,11 @@ namespace MorphingClass.CGeometry.CGeometryBase
             this.CEdgeLt = CGeoFunc.FormCEdgeEb(this.CptLt).ToList();
 
             //FormCEdgeLtLt();
+        }
+
+        public virtual int GetEdgeCount()
+        {
+            return this.CEdgeLt.Count;
         }
 
         //public virtual void FormCEdgeLtLt()

### 2017-08-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixing the bug of a hole in a hole
added section of growing based on buffering

@@
 
-\citetitle{Damen2008} \parencite{Damen2008}
-
 An example of enlargement in aggregation: \citetitle{Neun2005}
@@
 
+\subsection{Growing based on buffering}
+We grow building based on buffering. 
+There are two typical ways of buffering polygons, i.e.,
+one with round joins and the other with miter joins (see 
+\fig\ref{fig:Buffer_TwoKinds}).
+As buildings are usually rectangles, 
+we choose the second way because it is 
+better at keeping the right angles.
+If an angle is acute, however, an excessively long \emph{spike} will be 
+produced.
+This spike may go across other buildings 
+(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
+To avoid this kind of interruptions, 
+we require that for an angle if a vertex of the 
+buffer is more than $\alpha d_G$, where $d_G$ is the growing distance, away 
+from the original vertex, 
+a \emph{square} joining is applied
+(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
+To keep right angles of buildings, 
+we must have $\alpha d_G \geq \sqrt{2}$. 
+We set $\alpha d_G = 1.5$ so that a square joining is applied when an angle is 
+smaller than $83.6 \degree$.
+
+We use value $1.5$ so that we can keep
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Buffer_TwoKinds}
+	\caption{Buffering a polygon using different kinds of joins.}
+	\label{fig:Buffer_TwoKinds}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Buffer_MiterLimits}
+	\caption{Two typical ways of buffering a polygon.}
+	\label{fig:Buffer_MiterLimits}
+\end{figure}
+
+If several buildings are close to each other at the start 
+scale, we bridge them by line segments and take the merge of these 
+buildings 
+and bridges as one building.
+For each building, either an original one or a merged one, at the start 
+scale, 
+we generate its target shape at 
+the goal scale by enlarging and simplifying. Then we grow the  
+building to the target shape. 
+%
+After finishing the growing, we take the goal scale as the 
+start scale and repeat our continuous generalization.
+\newline\indent
+Our contribution is as follows. First, the buildings 
+are enlarged continuously. At the same time, they are simplified. 
+Second, we ensure that the distance between any pair of two buildings is 
+always larger than a specified threshold.
+
+If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
+grow at most $2d_\mathrm{G}$.
+The length of a bridge can be as large as
+\begin{equation}
+	\label{eq:BridgeLength}
+	l_b=4d_\mathrm{G}+d_\epsilon.
+\end{equation}
+%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+
 We grow all the buildings with the same speed.
+
+\textcite{Johnson2014}
 
@@
 the corresponding two buildings will become too close during our growing step.
-The two buildings are in the same group.
+The two buildings are identified as in the same group.
 
@@
 
-\subsection{Simplifying merged buildings considering right angles}
+\subsection{Simplifying merged buildings}
 
-We use an buffering-based method, 
+We use a buffering-based method, 
 similar to \textcite{Damen2008,Meijers2016}, 
@@
 boundary of the original building.
-If a shortcut does intersect, 
-we will need to shrink the building instead of growing. Of course, we do not 
-want to shrink.
+If we allow this intersection, 
+we need to shrink the building instead of growing. 
+Of course, we do not want to shrink.
 
-\subsection{Growing}
-If several buildings are close to each other at the start 
-scale, we bridge them by line segments and take the merge of these 
-buildings 
-and bridges as one building.
-For each building, either an original one or a merged one, at the start 
-scale, 
-we generate its target shape at 
-the goal scale by enlarging and simplifying. Then we grow the  
-building to the target shape. 
-%
-After finishing the growing, we take the goal scale as the 
-start scale and repeat our continuous generalization.
-\newline\indent
-Our contribution is as follows. First, the buildings 
-are enlarged continuously. At the same time, they are simplified. 
-Second, we ensure that the distance between any pair of two buildings is 
-always larger than a specified threshold.
-
-If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
-grow at most $2d_\mathrm{G}$.
-The length of a bridge can be as large as
-\begin{equation}
-\label{eq:BridgeLength}
-l_b=4d_\mathrm{G}+d_\epsilon.
-\end{equation}
-%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+To avoid using too many thresholds, we also use $\epsilon$ mm for the 
+simplification algorithm.
 
 \subsection{Parameters for growing and simplifying}
-The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
-($S_\mathrm{g}>S_\mathrm{s}$).
-The area of a building should be larger than $a$ mm$^2$ on map.
-A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
-A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
+Suppose that our start map is at scale $1:S_\mathrm{s}$, 
+and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
+The area of a building on map should be at least $a$ mm$^2$ so that the 
+building is large enough to be perceived.
+Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
+mm$^2$ at least, and
+a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
 The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
-mm.
-Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
-In order to eliminate some small buildings, we define our growing distance as
+mm (see \fig\ref{fig:Growth}).
+A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
+(S_\mathrm{g}-S_\mathrm{s})$ mm so that it can survive when users zoom out from 
+the start map to the goal map.
+In order to eliminate small buildings, we define our growing distance as
 \begin{equation}
@@
 \end{equation}
-where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
+where variable $\lambda$ is a growing factor. A larger $\lambda$ results in  
 fewer buildings to be eliminated, and vice versa.
@@
 	\includegraphics{Growth}
-	\caption{Growth.}
+	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
 	\label{fig:Growth}
@@
 The distance between two buildings should be larger than a threshold, say, 
-$\epsilon$ mm on map \parencite{Stoter2009}.
-In order to make the shape of a building simpler, we simplify buildings 
-using the Douglas--Peucker algorithm \parencite{Douglas1973} with preservation 
-of right angles.
-To avoid using too many thresholds, we also use $\epsilon$ mm for the 
-simplification algorithm, hence the real threshold distance 
-is
+$\epsilon$ mm on map.
+The real threshold distance is
 \begin{equation}
@@
 The scale of the dataset is $1:15{,}000$.
+There are $2{,}590$ buildings (see \fig\ref{fig:Data}), 
+which has $19{,}255$ edges in total.
 Our goal scale is $1:50{,}000$.

### 2017-08-23 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
merge new buildings with the buildings of the immediate-previous step

@@
 To keep right angles of buildings, 
-we must have $\alpha d_G \geq \sqrt{2}$. 
-We set $\alpha d_G = 1.5$ so that a square joining is applied when an angle is 
+we must have $\alpha \geq \sqrt{2}$. 
+We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
 smaller than $83.6 \degree$.
-
-We use value $1.5$ so that we can keep
 
@@
 
-If several buildings are close to each other at the start 
+If two buildings become too close to each other during growing, we merge them 
+by adding a bridge.
+
+at the start 
 scale, we bridge them by line segments and take the merge of these 

### 2017-08-23 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -14,6 +14,7 @@ using MorphingClass.CUtility;
 using MorphingClass.CGeometry;
 using MorphingClass.CGeometry.CGeometryBase;
 using MorphingClass.CCorrepondObjects;
+using MorphingClass.CGeneralizationMethods;
 
 using ClipperLib;
 using Path = System.Collections.Generic.List<ClipperLib.IntPoint>;
@@ -305,9 +306,9 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
 
 
             int intRound = 0;
-            CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(clipperMethods.ConvertPathsToCEdgeLt(
-    Clipper.PolyTreeToPaths(grownPolyTree), true), 1 / CConstants.dblFclipper),
-    intRound.ToString() + CHelpFunc.GetTimeStampWithPrefix());
+    //        CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(clipperMethods.ConvertPathsToCEdgeLt(
+    //Clipper.PolyTreeToPaths(grownPolyTree), true), 1 / CConstants.dblFclipper),
+    //intRound.ToString() + CHelpFunc.GetTimeStampWithPrefix());
 
 
             var IterativeGrownPathsLt = grownPathsLt;
@@ -329,9 +330,9 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
                 newIterativeGrownPathsLt = GetOneLevelPathsEbFromPolyTree(finalPolyTree).ToList();
 
                 intRound++;
-                CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(clipperMethods.ConvertPathsToCEdgeLt(
-    Clipper.PolyTreeToPaths(finalPolyTree), true), 1 / CConstants.dblFclipper),
-    intRound.ToString() + CHelpFunc.GetTimeStampWithPrefix());
+    //            CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(clipperMethods.ConvertPathsToCEdgeLt(
+    //Clipper.PolyTreeToPaths(finalPolyTree), true), 1 / CConstants.dblFclipper),
+    //intRound.ToString() + CHelpFunc.GetTimeStampWithPrefix());
 
[…]

### 2017-08-24 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixed a bug and added section of merge polygons by introducing bridges

@@
 %		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
-% \newcommand{\ml}{\ensuremath{M_+}\xspace}
-% \newcommand{\ms}{\ensuremath{M_-}\xspace}
+ \newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
+ \newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}
 
@@
 \section{Methodology}
+We name the input map as start map \maps.
+We generate goal map \mapg by generalizing \maps. 
+We use parameter $t\in[0,1]$ to define the continuous generalization
+process. 
+We require that the generalization yields exactly \maps when $t=0$, 
+\mapg when $t=1$, and that \maps is continuously
+generalized into \mapg when $t$ increases
+from~$0$ to~$1$.
 
-\subsection{Growing based on buffering}
+\subsection{Grow based on buffering}
 We grow building based on buffering. 
@@
 	\includegraphics{Buffer_MiterLimits}
-	\caption{Two typical ways of buffering a polygon.}
+	\caption{}
 	\label{fig:Buffer_MiterLimits}
@@
 
-If two buildings become too close to each other during growing, we merge them 
-by adding a bridge.
+\subsection{Merge close buildings by introducing bridges}
+If two buildings become too close to each other during growing, 
+we merge them by introducing a bridge connecting the newarest points 
+(see \fig\ref{fig:GrowAndBridge}).
 
-at the start 
-scale, we bridge them by line segments and take the merge of these 
-buildings 
-and bridges as one building.
-For each building, either an original one or a merged one, at the start 
-scale, 
-we generate its target shape at 
-the goal scale by enlarging and simplifying. Then we grow the  
-building to the target shape. 
-%
-After finishing the growing, we take the goal scale as the 
-start scale and repeat our continuous generalization.
-\newline\indent
-Our contribution is as follows. First, the buildings 
-are enlarged continuously. At the same time, they are simplified. 
-Second, we ensure that the distance between any pair of two buildings is 
-always larger than a specified threshold.
+\begin{figure}[tb]
+	\centering
+	\includegraphics{GrowAndBridge}
+	\caption{Merge buildings by introducing bridges when the buildings become 
+	too close.
+		Although the bridges appear at different time, 
+		their widths are the same (see the figure with $t=1$).}
+	\label{fig:GrowAndBridge}
+\end{figure}
 
-If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
-grow at most $2d_\mathrm{G}$.
-The length of a bridge can be as large as
-\begin{equation}
-	\label{eq:BridgeLength}
-	l_b=4d_\mathrm{G}+d_\epsilon.
-\end{equation}
-%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
-
-We grow all the buildings with the same speed.
-
-\textcite{Johnson2014}
-
-If several buildings are close to each other at the start 
-scale, we bridge them by line segments and take the merge of these 
-buildings 
-and bridges as one building.
-For each building, either an original one or a merged one, at the start 
-scale, 
-we generate its target shape at 
-the goal scale by enlarging and simplifying. Then we grow the  
-building to the target shape.
-
-\subsection{Grouping buildings based on buffering}
-\label{sec:Grouping}
-We group buildings based on the buffers of the buildings. 
-We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
-where distance $d_G$ is the growing amount of each building. 
-Parameter $d_\epsilon$ is the least distance allowed between two buildings.
-We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
-the corresponding two buildings will become too close during our growing step.
-The two buildings are identified as in the same group.
-
-We merge the buffers which overlap each others so that we have some large units.
-Now we iteratively remove small ``bays''.
-Each iteration consists of three steps, i.e., 
-buffering with distance $r_H$, buffering with distance $-r_H$, and
-merging overlapping units.
-The iterative process stops when the number of units do not decrease anymore.
-
-All the buildings overlapping with the same unit belong to the same group.
-
-\subsection{Enlarging and merging buildings for goal map}
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\parencite{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
-
-\subsection{Simplifying merged buildings}
+\subsection{Simplify merged buildings}
 
@@
 simplification algorithm.
+
+%at the start 
+%scale, we bridge them by line segments and take the merge of these 
+%buildings 
+%and bridges as one building.
+%For each building, either an original one or a merged one, at the start 
+%scale, 
+%we generate its target shape at 
+%the goal scale by enlarging and simplifying. Then we grow the  
+%building to the target shape. 
+%%
+%After finishing the growing, we take the goal scale as the 
+%start scale and repeat our continuous generalization.
+%\newline\indent
+%Our contribution is as follows. First, the buildings 
+%are enlarged continuously. At the same time, they are simplified. 
+%Second, we ensure that the distance between any pair of two buildings is 
+%always larger than a specified threshold.
+%
+%If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
+%grow at most $2d_\mathrm{G}$.
+%The length of a bridge can be as large as
+%\begin{equation}
+%	\label{eq:BridgeLength}
+%	l_b=4d_\mathrm{G}+d_\epsilon.
+%\end{equation}
+%%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
+
+\subsection{Grouping buildings based on buffering}
+\label{sec:Grouping}
+We group buildings based on the buffers of the buildings. 
+We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
+where distance $d_G$ is the growing amount of each building. 
+Parameter $d_\epsilon$ is the least distance allowed between two buildings.
+We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
+the corresponding two buildings will become too close during our growing step.
+The two buildings are identified as in the same group.
+
+We merge the buffers which overlap each others so that we have some large units.
+Now we iteratively remove small ``bays''.
+Each iteration consists of three steps, i.e., 
+buffering with distance $r_H$, buffering with distance $-r_H$, and
+merging overlapping units.
+The iterative process stops when the number of units do not decrease anymore.
+
+All the buildings overlapping with the same unit belong to the same group.
+
+\subsection{Enlarging and merging buildings for goal map}
+For each pair of buildings in the same group, 
+we find the smallest distance between them.
+We connect the buildings by adding an edge from the nearest points.
+We find a minimum spanning tree of the buildings using Prim's algorithm 
+\parencite{Prim1957}.
+We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
 
@@
 \label{sec:CaseStudy}
-We have implemented our method based on C\# (Microsoft Visual 
-Studio 
-2015) and ArcObjects SDK 10.4.1. 
+We have implemented our method based on
+C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
+The buffer function and clip function are from library \emph{Clipper} 
+of \textcite{Johnson2014}.
+An evaluation of Clipper can be found in \textcite{Palfrader2015}.
 We ran our case study under 64-bit 
@@
 %
-The displaying time is dependent on buffering and clipping. The 
-two operators are from library Clipper. The efficiency of the 
-buffering function of this library has been evaluated by 
-\textcite{Palfrader2015}.
+The displaying time is dependent on buffering and clipping.
 

### 2017-08-24 ContinuousGeneralizer/MorphingClass/CGeometry/CEdge.cs

@@ -437,7 +437,12 @@ namespace MorphingClass.CGeometry
             Console.WriteLine(string.Format(CConstants.strFmtIDs6, "ID:", this.ID, ";    indexID:", this.indexID, ";    GID:", this.GID));
             this.FrCpt.PrintMySelf();
             this.ToCpt.PrintMySelf();
+            if (this.cedgePrev != null)
+            {
+                Console.WriteLine("Previous GID: " + this.cedgePrev.GID + "    Next GID: " + this.cedgeNext.GID + "    Twin GID:" + this.cedgeTwin.GID);
+            }
             Console.WriteLine("***********************End Print an Edge**************************");
+            Console.WriteLine("");
         }
 
         //public CEdge LargerAxisAngleCEdge()

### 2017-08-24 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
working on merge close buildings by introducing edges

@@
 
-$\bar{a}$
-
 \bigskip
@@
 \section{Methodology}
-We name the input map as start map \maps.
-We generate goal map \mapg by generalizing \maps. 
+We name the input map as start map \maps,
+and generate goal map \mapg by generalizing \maps. 
 We use parameter $t\in[0,1]$ to define the continuous generalization
@@
 We require that the generalization yields exactly \maps when $t=0$, 
-\mapg when $t=1$, and that \maps is continuously
+\mapg when $t=1$, 
+and that \maps is continuously 
 generalized into \mapg when $t$ increases
@@
 we require that for an angle if a vertex of the 
-buffer is more than $\alpha d_G$, where $d_G$ is the growing distance, away 
+buffer is more than $\alpha d_\mathrm{G}$, where $d_\mathrm{G}$ is the growing 
+distance, away 
 from the original vertex, 
@@
 
+Suppose that our start map is at scale $1:S_\mathrm{s}$, 
+and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
+The area of a building on map should be at least $a$ mm$^2$ so that the 
+building is large enough to be perceived.
+In \sect\ref{sec:Simplify}, we show that we set $a=4$.
+Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
+mm$^2$ at least, and
+a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
+The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
+mm (see \fig\ref{fig:Growth}).
+A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
+(S_\mathrm{g}-S_\mathrm{s})$ mm so that 
+it can survive when users zoom out from 
+the start map to the goal map.
+In order to eliminate small buildings, 
+we define our growing distance as
+\begin{equation}
+\label{eq:d_G}
+d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
+	mm} \quad 0 < \lambda <1,
+\end{equation}
+where variable $\lambda$ is a growing factor. 
+A larger $\lambda$ results in  
+fewer buildings to be eliminated, and vice versa.
+During our growing, the growth at time $t$ is
+\[
+d_{\mathrm{G}, t} = t \cdot d_\mathrm{G}.
+\]
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Growth}
+	\caption{Growth.}
+	\label{fig:Growth}
+\end{figure}
+
 \subsection{Merge close buildings by introducing bridges}
+The distance between two buildings should be larger than a threshold
+\parencite{Regnauld2001,Li2004}.
+Following \textcite{Basaraner2008,Stoter2009}, we set the separation threshold 
+$\epsilon= 0.2~\text{mm}$ on map. The separation threshold at time $t$ is
+\[
+d_{\epsilon, t} = t \cdot \epsilon (S_\mathrm{g}-S_\mathrm{s}).
+\]
+
 If two buildings become too close to each other during growing, 
-we merge them by introducing a bridge connecting the newarest points 
+we merge them by introducing a bridge connecting the nearest points 
 (see \fig\ref{fig:GrowAndBridge}). 
+Note that the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have the 
+same widths.
+We know where we should add bridges at time $t=0$. 
+We grow the bridges together with the buildings.
+We do not show the bridges until the two buildings are close enough 
+which means that, in our case, 
+the distance of two buildings is smaller than $d_{\epsilon,t}$.
+
+%The distance between two buildings should be larger than a threshold, say, 
+%$\epsilon$ mm on map.
+%The real threshold distance is
+%\begin{equation}
+%\label{eq:d_epsilon}
+%d_\epsilon= \epsilon  S_\mathrm{g}.
+%\end{equation}
+%
+%If we insist on that we should observe 
+%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
+%sure that
+%\begin{equation}
+%\label{eq:a_limit}
+%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
+%\end{equation}
+%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
+%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
+%\begin{equation}
+%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
+%\end{equation}
+%\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
+%on a map. We set our $\epsilon=0.2$.
 
@@
 
-\subsection{Simplify merged buildings}
-
+\subsection{Simplify grown buildings}
+\label{sec:Simplify}
 We use a buffering-based method, 
@@
 	\includegraphics{ImaiIri_Shortcut}
-	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
+	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
 	\label{fig:ImaiIri_Shortcut}
@@
 
-\subsection{Grouping buildings based on buffering}
+\subsection{Unite buildings of the immediate previous step}
+\label{sec:Unite}
+
+As we simplify buildings after growing, 
+some parts of the buildings may shrink 
+comparing to themselves at the previous steps.
+We unite a building with itself at the immediate previous step so that the 
+united building is always larger than both of the united parts.
+
+\subsection{Eliminate small buildings}
+\label{sec:Eliminate}
+We eliminate a building if the area of this building is smaller than a 
+threshold.
+For a group of buildings, we consider the area sum of all the buildings.
+
+\subsection{Group buildings based on buffering}
 \label{sec:Grouping}
@@
 \subsection{Parameters for growing and simplifying}
-Suppose that our start map is at scale $1:S_\mathrm{s}$, 
-and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
-The area of a building on map should be at least $a$ mm$^2$ so that the 
-building is large enough to be perceived.
-Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
-mm$^2$ at least, and
-a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
-The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
-mm (see \fig\ref{fig:Growth}).
-A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-(S_\mathrm{g}-S_\mathrm{s})$ mm so that it can survive when users zoom out from 
-the start map to the goal map.
-In order to eliminate small buildings, we define our growing distance as
-\begin{equation}
-\label{eq:d_G}
-	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
-	mm} \quad 0 < \lambda <1,
-\end{equation}
-where variable $\lambda$ is a growing factor. A larger $\lambda$ results in  
-fewer buildings to be eliminated, and vice versa.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics{Growth}
-	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
-	\label{fig:Growth}
-\end{figure}
-
-The distance between two buildings should be larger than a threshold, say, 
-$\epsilon$ mm on map.
-The real threshold distance is
-\begin{equation}
-\label{eq:d_epsilon}
-d_\epsilon= \epsilon  S_\mathrm{g}.
-\end{equation}
 
@@
 \end{equation}
-\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
-on a map. We set our $\epsilon=0.2$.
 We also require 
@@
 
-At some point, we should remove the requirement of keeping right angles. Right 
-angles may not be important anymore when we deal with settlement boundaries.
+Show some results obtained by ArcGIS.
 

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added figures/ErosionBreak.pdf

@@
 \usepackage{makeidx}         % allows index generation
-\usepackage{graphicx}        % standard LaTeX graphics tool
+\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
 \usepackage[size=small,labelfont=bf]{caption}
@@
 \newcommand{\sect}{Sec.~}
+
+\newcommand{\dtrm}[1]{d_{\mathrm{#1},t}}
 
@@
 \subsection{Grow based on buffering}
+\label{sec:Grow}
 We grow building based on buffering. 
@@
 During our growing, the growth at time $t$ is
-\[
-d_{\mathrm{G}, t} = t \cdot d_\mathrm{G}.
-\]
+\begin{equation}
+\label{eq:d_Gt}
+\dtrm{G} = t \cdot d_\mathrm{G}.
+\end{equation}
 
@@
 \parencite{Regnauld2001,Li2004}.
-Following \textcite{Basaraner2008,Stoter2009}, we set the separation threshold 
-$\epsilon= 0.2~\text{mm}$ on map. The separation threshold at time $t$ is
+Following \textcite{Basaraner2008,Stoter2009}, 
+we set the separation threshold $\epsilon= 0.2~\text{mm}$ for target map. 
+The separation threshold at time $t$ is
 \[
-d_{\epsilon, t} = t \cdot \epsilon (S_\mathrm{g}-S_\mathrm{s}).
+d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
 \]
@@
 (see \fig\ref{fig:GrowAndBridge}).
-Note that the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have the 
-same widths.
-We know where we should add bridges at time $t=0$. 
-We grow the bridges together with the buildings.
-We do not show the bridges until the two buildings are close enough 
-which means that, in our case, 
-the distance of two buildings is smaller than $d_{\epsilon,t}$.
-
-%The distance between two buildings should be larger than a threshold, say, 
-%$\epsilon$ mm on map.
-%The real threshold distance is
-%\begin{equation}
-%\label{eq:d_epsilon}
-%d_\epsilon= \epsilon  S_\mathrm{g}.
-%\end{equation}
-%
-%If we insist on that we should observe 
-%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
-%sure that
-%\begin{equation}
-%\label{eq:a_limit}
-%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
-%\end{equation}
-%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
-%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
-%\begin{equation}
-%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
-%\end{equation}
-%\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
-%on a map. We set our $\epsilon=0.2$.
+No matter a bridge appear earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
+the same widths.
+This setting is achieved by following.
+We detect nearest points for each pair of buildings at time $t=0$ so that 
+we know where we should add bridges. 
+We grow the bridges together with the buildings,
+but we do not show the bridges until the two buildings are close enough. 
+\todo[inline]{actually larger than $d_{\epsilon, t}$.}
 
@@
 	\centering
-	\includegraphics{GrowAndBridge}
+	\includegraphics[draft=false]{GrowAndBridge}
 	\caption{Merge buildings by introducing bridges when the buildings become 
@@
 pits, and then erode the results to remove spikes.
+At time $t$, we dilate with distance $\dtrm{D}$, 
+erode with distance $\dtrm{D}+\dtrm{E}$,
+and dilate back with distance $\dtrm{E}$.
+
+The buildings have been grown with distance $\dtrm{G}$ 
+(see \sect\ref{sec:Grow}).
+During the erosion, a part can be eroded with distance 
+$\alpha (\dtrm{D}+\dtrm{E})$ at most.
+In order not to break a building, the following condition must hold:
+\[
+\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
+\]
+which means
+\[
+\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
+\]
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{ErosionBreak}
+	\caption{.}
+	\label{fig:ErosionBreak}
+\end{figure}
+s
+
+The separation threshold at time $t$ is
+\[
+d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.s
+\]
+One may expect that we define 
+$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
+so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
+The reason we do not define it as this way is that 
+our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
+is small.
+In \sect\ref{sec:Simplify}, the erosion operator requires that
 
@@
 simplification algorithm.
+
+\subsection{Group buildings based on buffering}
+\label{sec:Grouping}
+We group buildings based on the buffers of the buildings. 
+We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
+where distance $d_G$ is the growing amount of each building. 
+Parameter $d_\epsilon$ is the least distance allowed between two buildings.
+We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
+the corresponding two buildings will become too close during our growing step.
+The two buildings are identified as in the same group.
+
+We merge the buffers which overlap each others so that we have some large units.
+Now we iteratively remove small ``bays''.
+Each iteration consists of three steps, i.e., 
+buffering with distance $r_H$, buffering with distance $-r_H$, and
+merging overlapping units.
+The iterative process stops when the number of units do not decrease anymore.
+
+All the buildings overlapping with the same unit belong to the same group.
 
@@
 For a group of buildings, we consider the area sum of all the buildings.
-
-\subsection{Group buildings based on buffering}
-\label{sec:Grouping}
-We group buildings based on the buffers of the buildings. 
-We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
-where distance $d_G$ is the growing amount of each building. 
-Parameter $d_\epsilon$ is the least distance allowed between two buildings.
-We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
-the corresponding two buildings will become too close during our growing step.
-The two buildings are identified as in the same group.
-
-We merge the buffers which overlap each others so that we have some large units.
-Now we iteratively remove small ``bays''.
-Each iteration consists of three steps, i.e., 
-buffering with distance $r_H$, buffering with distance $-r_H$, and
-merging overlapping units.
-The iterative process stops when the number of units do not decrease anymore.
-
-All the buildings overlapping with the same unit belong to the same group.
 
@@
 Show some results obtained by ArcGIS.
+Show the data at $1:50{,}000$.
 
@@
 \printbibliography
-%\bibliographystyle{plainnat}
-%%	\bibliography{References}
-%\input{referenc}
 \end{document}

### 2017-08-25 ContinuousGeneralizer/MorphingClass/CHelpFunc.cs

@@ -88,7 +88,8 @@ namespace MorphingClass.CUtility
         //private static string _strDataFolderName = "France_Presenting";
         //private static string _strDataFolderName = "France_Presenting_DifferentBuffers";
         //private static string _strDataFolderName = "France_Presenting_DifferentMiterLimits";
-        private static string _strDataFolderName = "France_Presenting_AddBridges";
+        //private static string _strDataFolderName = "France_Presenting_AddBridges";
+        private static string _strDataFolderName = "France_Presenting_ErodeBreak";
         //private static string _strDataFolderName = "France_Problematic";
         //private static string _strDataFolderName = "France_Problematic2";
         //private static string _strDataFolderName = "France_WithOneHole";

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
working on simplify grown buildings

@@
 	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
+	\includegraphics{GrowAndBridge}
 	\caption{Merge buildings by introducing bridges when the buildings become 
@@
 We first dilate the grown buildings to remove 
-pits, and then erode the results to remove spikes.
+pits, and then erode the results to remove spikes
+(see \fig\ref{fig:RemovePitAndSpike}).
 At time $t$, we dilate with distance $\dtrm{D}$, 
@@
 and dilate back with distance $\dtrm{E}$.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{RemovePitAndSpike}
+	\caption{.
+	}
+	\label{fig:RemovePitAndSpike}
+\end{figure}
 
@@
 	\includegraphics[draft=false]{ErosionBreak}
-	\caption{.}
+	\caption{Dilate the gray polygon, then erode the dilated polygon.
+		(a) Dilate and erode with distance $d_1$.
+		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
+		In (a) the result of dilation and erosion is the same as the original 
+		polygon, while in (b) the result consists of two parts.
+	}
 	\label{fig:ErosionBreak}
 \end{figure}
-s
 
@@
 \[
-d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.s
+d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.
 \]

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished description of simplifying by dilating and eroding

@@
 \newcommand{\sect}{Sec.~}
+\newcommand{\tab}{Tab.~}
+
+%\newcommand{\myeqref}[1]{Eq.~\ref{#1}}
+%\newcommand{\mysectref}[1]{Sec.~\ref{#1}}
+%\newcommand{\myfigref}[1]{Fig.~\ref{#1}}
+%\newcommand{\mytabref}[1]{Tab.~\ref{#1}}
 
@@
 This spike may go across other buildings 
-(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
+(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
 To avoid this kind of interruptions, 
 we require that for an angle if a vertex of the 
-buffer is more than $\alpha d_\mathrm{G}$, where $d_\mathrm{G}$ is the growing 
-distance, away 
-from the original vertex, 
+buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
+where $d_\mathrm{G}$ is the growing distance, 
+away from the original vertex, 
 a \emph{square} joining is applied
@@
 The separation threshold at time $t$ is
-\[
+\begin{equation}
+\label{eq:d_epsilont}
 d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
-\]
+\end{equation}
 
@@
 (see \fig\ref{fig:RemovePitAndSpike}).
-At time $t$, we dilate with distance $\dtrm{D}$, 
-erode with distance $\dtrm{D}+\dtrm{E}$,
-and dilate back with distance $\dtrm{E}$.
 
@@
 	\includegraphics[draft=false]{RemovePitAndSpike}
-	\caption{.
+	\caption{Remove a pit by dilating and then remove a spike by eroding.
+		(a) a polygon with a pit and a spike;
+		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
+		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
+		(d) dilate the polygon in (c) with distance $d$ so that the result has 
+		the same size as the polygon in (a).
 	}
@@
 
-The buildings have been grown with distance $\dtrm{G}$ 
-(see \sect\ref{sec:Grow}).
-During the erosion, a part can be eroded with distance 
-$\alpha (\dtrm{D}+\dtrm{E})$ at most.
-In order not to break a building, the following condition must hold:
+At time $t$, we grow buildings with distance $\dtrm{G}$,
+dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
+erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
+and dilate back with distance $\dtrm{E}$.
+A problem we may have is that we may break a building by eroding.
+The reason is that 
+some parts of a building may be increased (by growing and dilating) 
+with distance $\dtrm{G}+\dtrm{D}$, 
+but be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
+If  $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
+and a building is not thick enough, 
+the building may be broken into several parts
+(see \fig\ref{fig:ErosionBreak}).
+In order to avoid this problem, we require that
 \[
@@
 which means
-\[
+\begin{equation}
+\label{eq:d_Dt}
 \dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
-\]
+\end{equation}
 
@@
 
-The separation threshold at time $t$ is
+We would like to use $\dtrm{E}=d_{\epsilon, t}/2$
+(see \eq\ref{eq:d_epsilont}) so that
+any pits and spikes narrower than $d_{\epsilon, t}$ will be removed.
+According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
+when $t$ is small, 
+but $d_{\epsilon, t}$ is at least $\epsilon S_s$. 
+In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
+which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
+As a compromise, we use
 \[
-d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.
+\dtrm{E} =t \cdot \epsilon S_\mathrm{g}.
 \]
-One may expect that we define 
-$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
-so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
-The reason we do not define it as this way is that 
-our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
-is small.
-In \sect\ref{sec:Simplify}, the erosion operator requires that
+Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
+$t \cdot \frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})-
+t \cdot \epsilon S_\mathrm{g} >0$.
+As a result, we should make sure that
+\begin{equation}
+\label{eq:S_g}
+S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-2\epsilon} S_s.
+\end{equation}
+
+We wish to remove ``bays'' which have ``widths'' less than $2\sqrt{a_h/\pi}$.
+\todo{why? more details}
+Usually, our $\dtrm{D}$ is not large enough to do so.
+We use the upper bound in \eq\ref{eq:d_Dt}, that is,
+\[
+\dtrm{D} = \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
+\]
 

### 2017-08-26 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added figures/RemovePitAndSpike.pdf and added section of running time analysis

@@
 \section{Methodology}
-We name the input map as start map \maps,
-and generate goal map \mapg by generalizing \maps. 
-We use parameter $t\in[0,1]$ to define the continuous generalization
+
+\todo[inline]{a brief introduction of our method.}
+We name our input map as start map \maps,
+and denote the scale of the start maps by $1:S_\mathrm{s}$.
+We generate goal map \mapg at scale $1:S_\mathrm{g}$ 
+($S_\mathrm{g} > S_\mathrm{s}$) by generalizing \maps. 
+We use time $t\in[0,1]$ to define the continuous generalization
 process. 
@@
 \mapg when $t=1$, 
-and that \maps is continuously 
-generalized into \mapg when $t$ increases
-from~$0$ to~$1$.
+and that \maps is continuously generalized into \mapg 
+when $t$ increases from~$0$ to~$1$.
+We define a simple function between scale and time, that is,
+$S_t= S_\mathrm{s} + t(S_\mathrm{g}-S_\mathrm{s})$.
 
@@
 
-Suppose that our start map is at scale $1:S_\mathrm{s}$, 
-and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
-The area of a building on map should be at least $a$ mm$^2$ so that the 
+The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that the 
 building is large enough to be perceived.
 In \sect\ref{sec:Simplify}, we show that we set $a=4$.
-Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
-mm$^2$ at least, and
-a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
-The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
-mm (see \fig\ref{fig:Growth}).
+Accordingly, a square at the start map should have 
+area $a S_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
+a square at the goal map should have 
+area $a S_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
+The difference of the side lengths is 
+$\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ 
+ (see \fig\ref{fig:Growth}).
 A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-(S_\mathrm{g}-S_\mathrm{s})$ mm so that 
+(S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ so that 
 it can survive when users zoom out from 
@@
 \label{eq:d_G}
-d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
-	mm} \quad 0 < \lambda <1,
+d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm} 
+\quad 0 < \lambda <1,
 \end{equation}
@@
 Following \textcite{Basaraner2008,Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2~\text{mm}$ for target map. 
+we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$ for target map. 
 The separation threshold at time $t$ is
@@
 \label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
+d_{\epsilon, t} = \epsilon \cdot S_t.
 \end{equation}
@@
 	\centering
-	\includegraphics[draft=false]{RemovePitAndSpike}
+	\includegraphics[draft=true]{RemovePitAndSpike}
 	\caption{Remove a pit by dilating and then remove a spike by eroding.
@@
 	\centering
-	\includegraphics[draft=false]{ErosionBreak}
+	\includegraphics[draft=true]{ErosionBreak}
 	\caption{Dilate the gray polygon, then erode the dilated polygon.
@@
 
-We would like to use $\dtrm{E}=d_{\epsilon, t}/2$
+We would like to use $\dtrm{E}=\frac{l}{2} \cdot S_t$
 (see \eq\ref{eq:d_epsilont}) so that
-any pits and spikes narrower than $d_{\epsilon, t}$ will be removed.
+any pits and spikes narrower than $l$ will be removed. 
+We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
+\textcite{Regnauld2001,Li2004,Basaraner2008}.
 According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
 when $t$ is small, 
-but $d_{\epsilon, t}$ is at least $\epsilon S_s$. 
+but $d_{\epsilon, t}$ is at least $\frac{l}{2} S_\mathrm{s}$. 
 In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
@@
 \[
-\dtrm{E} =t \cdot \epsilon S_\mathrm{g}.
+\dtrm{E} =t \cdot \frac{l}{2} S_\mathrm{g}.
 \]
@@
 $t \cdot \frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})-
-t \cdot \epsilon S_\mathrm{g} >0$.
+t \cdot \frac{l}{2} S_\mathrm{g} >0$.
 As a result, we should make sure that
@@
 \label{eq:S_g}
-S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-2\epsilon} S_s.
+S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
 \end{equation}
@@
 
-After carrying out the offset-based method, we simplify the grown buildings. 
-We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
-but we hoped to remove more points. We found that the Imai--Iri 
-algorithm \parencite{ImaiIri1988} fit our needs well. Although a version with a 
-lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
-version.
-
-The Imai--Iri algorithm first finds all the valid shortcuts of a polyline.
-For a sequence of points on a polyline, 
-if their distances to their shortcut are 
-at most specified value $\epsilon$, then the shortcut is valid (see 
-\fig\ref{fig:ImaiIri_Shortcut}). 
+After carrying out the buffering-based methods, 
+we simplify the grown buildings using Imai--Iri algorithm 
+\parencite{ImaiIri1988}.
+This algorithm first finds all the valid shortcuts of a polyline.
+A shortcut is valid for a segment 
+if the distance between the segment and the shortcut is at most a specified 
+value.
+We set the value as $l$
+(see \fig\ref{fig:ImaiIri_Shortcut}). 
 Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
@@
 	\centering
-	\includegraphics{ImaiIri_Shortcut}
+	\includegraphics[draft=false]{ImaiIri_Shortcut}
 	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
@@
 \todo[inline]{more details in the below paragraph?}
-We add two more constraints for a shortcut to be valid
-when we use the Imai--Iri algorithm. 
-The first one is that
-a shortcut must be completely inside the grown building.
+We add two more constraints for a shortcut to be valid. 
+First, a shortcut must be completely inside the grown building.
 If a shortcut is outside,
 we are not able to arrive at the shortcut by growing.
-The second constraint is that a shortcut is not allowed to intersect the 
+Second, a shortcut is not allowed to intersect the 
 boundary of the original building.
@@
 
-To avoid using too many thresholds, we also use $\epsilon$ mm for the 
-simplification algorithm.
+We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
+but we hoped to remove more points. We found that the Imai--Iri 
+algorithm fit our needs better.
 
@@
 Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
-$\lambda$ as our $a$ is already much larger than $0.16$ mm$^2$ on 
+$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
 map, which is the area limit used by \textcite{Stoter2009}. As a result, we 
@@
 \textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
-$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
-least $8$ mm$^2$ on map. Following their setting, we shrink a hole and 
-eliminate the hole once its size is smaller than $8$ mm$^2$ on map.
+$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
+which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
+Following their setting, we shrink a hole and 
+eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.
 
@@
 %at 
-%least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
+%least $8\,\mathrm{mm}^2$ on the map. Following their setting, we wish to have 
+%$\pi 
 %D_\mathrm{G}^2 \ge 8 S_g^2$.
@@
 
+\subsection{Running time analysis}
+Although a version with a 
+lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
+version.
+
 \section{Case Study}
@@
 
-\mypar{Notation}
-Text.
+\todo[inline]{comparison of simplification between Douglas--Peucker and 
+Imai--Iri}
 
@@
 
-\todo[inline]{consider multi bridges; consider transparency of bridges in 
-stead 
-of enlarging}
+\todo[inline]{consider multi bridges; 
+	consider transparency of bridges in stead of enlarging}
 

### 2017-08-29 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
working on shrinking examples

@@
 \usepackage{makeidx}         % allows index generation
-\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
+\usepackage[]{graphicx}
+%\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
 \usepackage[size=small,labelfont=bf]{caption}
@@
 
-\newcommand{\dtrm}[1]{d_{\mathrm{#1},t}}
+\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}
 
@@
 \textcite{Gold2003,Matuk2006}
-
-Geometric Simplification of Administrative Borders With Mixture 
-of
-Irregular and Orthogonal Segments \parencite{Samsonov2016}
 
@@
 	\centering
-	\includegraphics[draft=true]{ErosionBreak}
+	\includegraphics[draft=false]{ErosionBreak}
 	\caption{Dilate the gray polygon, then erode the dilated polygon.
@@
 As a compromise, we use
-\[
+\begin{equation}
+\label{eq:d_Et}
 \dtrm{E} =t \cdot \frac{l}{2} S_\mathrm{g}.
-\]
+\end{equation}
 Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
@@
 if the distance between the segment and the shortcut is at most a specified 
-value.
-We set the value as $l$
+value
 (see \fig\ref{fig:ImaiIri_Shortcut}).
+We set the value also as $l$. 
 Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
@@
 
+\subsection{Unite buildings of the immediate previous step}
+\label{sec:Unite}
+
+As shown in \eq\ref{eq:d_Et}, $\dtrm{E}$ increases along with time $t$.
+We illustrated in \fig\ref{fig:ErosionBreak} that 
+a larger $\dtrm{E}$ may result in the shrinking of a building.
+
+$\dtrm[1]{G} + \dtrm[1]{D}$
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{Shrink_Erosion}
+	\caption{.
+	}
+	\label{fig:Shrink_Erosion}
+\end{figure}
+
+As we simplify buildings after growing, 
+some parts of the buildings may shrink 
+comparing to themselves at the immediate previous steps.
+To avoid this shrink, we unite a building with itself at the immediate previous 
+step so that the 
+united building is always larger than both of the united parts.
+
+\subsection{Eliminate small buildings}
+\label{sec:Eliminate}
+We eliminate a building if the area of this building is smaller than a 
+threshold.
+For a group of buildings, we consider the area sum of all the buildings.
+
 \subsection{Group buildings based on buffering}
@@
 All the buildings overlapping with the same unit belong to the same group.
-
-%at the start 
-%scale, we bridge them by line segments and take the merge of these 
-%buildings 
-%and bridges as one building.
-%For each building, either an original one or a merged one, at the start 
-%scale, 
-%we generate its target shape at 
-%the goal scale by enlarging and simplifying. Then we grow the  
-%building to the target shape. 
-%%
-%After finishing the growing, we take the goal scale as the 
-%start scale and repeat our continuous generalization.
-%\newline\indent
-%Our contribution is as follows. First, the buildings 
-%are enlarged continuously. At the same time, they are simplified. 
-%Second, we ensure that the distance between any pair of two buildings is 
-%always larger than a specified threshold.
-%
-%If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
-%grow at most $2d_\mathrm{G}$.
-%The length of a bridge can be as large as
-%\begin{equation}
-%	\label{eq:BridgeLength}
-%	l_b=4d_\mathrm{G}+d_\epsilon.
-%\end{equation}
-%%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}
-
-\subsection{Unite buildings of the immediate previous step}
-\label{sec:Unite}
-
-As we simplify buildings after growing, 
-some parts of the buildings may shrink 
-comparing to themselves at the previous steps.
-We unite a building with itself at the immediate previous step so that the 
-united building is always larger than both of the united parts.
-
-\subsection{Eliminate small buildings}
-\label{sec:Eliminate}
-We eliminate a building if the area of this building is smaller than a 
-threshold.
-For a group of buildings, we consider the area sum of all the buildings.
 
@@
 
+We used radical law. We may also consider the fractal nature of maps proposed 
+by \textcite{Jiang2015}.
+
 We did not include streets. We can either put them above the settlement 

### 2017-08-29 ContinuousGeneralizer/ContinuousGeneralizer/FrmKARS/FrmExtractPossibleFiles.cs

@@ -130,8 +130,7 @@ namespace ContinuousGeneralizer.FrmKARS
                 strHeadLt.Add("End");
             }
 
-            CHelpFuncExcel.ExportToExcel(resultobjltlt,
-                CHelpFunc.GetTimeStampWithPrefix() + "_methods_position",
+            CHelpFuncExcel.ExportToExcel(resultobjltlt,"methods_position",
                 @"C:\Study\MyWork\CodesChecking\fsvw_common_KARS_DM_Out", strHeadLt);
 
             MessageBox.Show("done!");
@@ -213,8 +212,7 @@ namespace ContinuousGeneralizer.FrmKARS
             //CHelpFuncExcel.ExportToExcel(astrRemainLt,
             //    CHelpFunc.GetTimeStamp() + "_out_kars_Extracted_" + astrRemainLt.Count,
             //    @"C:\Study\MyWork\CodesChecking\fsvw_common_KARS_DM_Out");
-            CHelpFuncExcel.ExportToExcel(astrPasteLt,
-                CHelpFunc.GetTimeStampWithPrefix() + "_out_kars_ExtractedProcessed_" + astrPasteLt.Count,
+            CHelpFuncExcel.ExportToExcel(astrPasteLt, "out_kars_ExtractedProcessed_" + astrPasteLt.Count,
                 @"C:\Study\MyWork\CodesChecking\fsvw_common_KARS_DM_Out");
         }
 
@@ -335,8 +333,7 @@ namespace ContinuousGeneralizer.FrmKARS
                 strHeadLt.Add("End");
             }
 
-            CHelpFuncExcel.ExportToExcel(resultobjltlt,
-                CHelpFunc.GetTimeStampWithPrefix() + "_methods_position",
+            CHelpFuncExcel.ExportToExcel(resultobjltlt, "methods_position",
                 @"C:\Study\MyWork\CodesChecking\fsvw_common_KARS_DM_Out", strHeadLt);
 
             MessageBox.Show("done!");

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the descriptions of figures/Shrink_Erosion.pdf and figures/Shrink_Simplification.pdf

@@
 \usepackage{makeidx}         % allows index generation
-\usepackage[]{graphicx}
-%\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
+%\usepackage[]{graphicx}
+\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
 \usepackage[size=small,labelfont=bf]{caption}
@@
 \todo[inline]{a brief introduction of our method.}
-We name our input map as start map \maps,
-and denote the scale of the start maps by $1:S_\mathrm{s}$.
-We generate goal map \mapg at scale $1:S_\mathrm{g}$ 
-($S_\mathrm{g} > S_\mathrm{s}$) by generalizing \maps. 
+We name our input map as start map,
+and denote the scale of the start map by $1:M_\mathrm{s}$.
+We generate a goal map \mapg at scale $1:M_\mathrm{g}$ 
+($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
 We use time $t\in[0,1]$ to define the continuous generalization
 process. 
-We require that the generalization yields exactly \maps when $t=0$, 
-\mapg when $t=1$, 
-and that \maps is continuously generalized into \mapg 
+We require that the generalization yields exactly the start map when $t=0$, 
+the goal map when $t=1$, 
+and that the start map is continuously generalized into the goal map 
 when $t$ increases from~$0$ to~$1$.
-We define a simple function between scale and time, that is,
-$S_t= S_\mathrm{s} + t(S_\mathrm{g}-S_\mathrm{s})$.
+For the sake of convenience, we define parameter
+$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.
 
@@
 We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
-smaller than $83.6 \degree$.
+smaller (more acute) than $83.6 \degree$.
 
@@
 Accordingly, a square at the start map should have 
-area $a S_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
+area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
 a square at the goal map should have 
-area $a S_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
+area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
 The difference of the side lengths is 
-$\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ 
+$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
  (see \fig\ref{fig:Growth}).
 A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-(S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ so that 
+(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
 it can survive when users zoom out from 
@@
 \label{eq:d_G}
-d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm} 
+d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
 \quad 0 < \lambda <1,
@@
 \label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot S_t.
+d_{\epsilon, t} = \epsilon \cdot M_t.
 \end{equation}
@@
 
-We would like to use $\dtrm{E}=\frac{l}{2} \cdot S_t$
+We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
 (see \eq\ref{eq:d_epsilont}) so that
@@
 when $t$ is small, 
-but $d_{\epsilon, t}$ is at least $\frac{l}{2} S_\mathrm{s}$. 
+but $d_{\epsilon, t}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
 In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
@@
 \label{eq:d_Et}
-\dtrm{E} =t \cdot \frac{l}{2} S_\mathrm{g}.
+\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
 \end{equation}
 Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
-$t \cdot \frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})-
-t \cdot \frac{l}{2} S_\mathrm{g} >0$.
+$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
+t \cdot \frac{l}{2} M_\mathrm{g} >0$.
 As a result, we should make sure that
@@
 \label{eq:S_g}
-S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
+M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
 \end{equation}
@@
 We set the value also as $l$.
+That is, at time $t$, the threshold distance is
+\begin{equation}
+\label{eq:d_lt}
+d_{l,t}= l \cdot M_t.
+\end{equation}
 Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
@@
 	\includegraphics[draft=false]{Shrink_Erosion}
-	\caption{.
+	\caption{A building shrinks during growing because of dilation and erosion, 
+	where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
+		The small gray polygons represent the original building.
+		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
+		$\dtrm[1]{D}$, respectively;
+		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
+		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
+		(d) The large gray polygon is the target shape on goal map.
+		The process for (e), (f), and (g) is the same as the process of (a), 
+		(b), and (c).
+		The darker gray piece in (g) shows 
+		the part which is included in the grown polygon of (c), 
+		but not in the grown polygon of (g).
 	}
 	\label{fig:Shrink_Erosion}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{Shrink_Simplification}
+	\caption{A building shrinks during growing because of line simplification, 
+		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
+		The small gray polygons represent the original building.
+		The process for (a), (b), and (c), and 
+		the process for (e), (f), and (g) are the same as 
+		the processes in \fig\ref{fig:Shrink_Erosion}.
+		(d) The large gray polygon is the target shape on goal map.
+		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
+		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
+		which is why the Imai--Iri algorithm does not 
+		remove any point of the polygon in (c),
+		but removes two points of the polygon in (g).
+		The darker gray pieces in (h) show 
+		the parts which are included in the polygon of (c), 
+		but not in the polygon of (h).
+	}
+	\label{fig:Shrink_Simplification}
 \end{figure}
@@
 
-\subsection{Text}
-\label{sec:Formalizing}
+The area on start map is $some number\,\text{mm}^2$.
+Our area on map is $some number\,\text{mm}^2$.
+According to \eq4 of paper \textcite{Topfer1966}, 
+the area on map should be $some number\,\text{mm}^2$
 

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added figures/Shrink_Uniting.pdf

@@
 \usepackage{etex}
+
+\newcommand{\blndraft}{true}
+%\newcommand{\blndraft}{false}
 
@@
 	\centering
-	\includegraphics[draft=false]{ErosionBreak}
+	\includegraphics[draft=\blndraft]{ErosionBreak}
 	\caption{Dilate the gray polygon, then erode the dilated polygon.
@@
 	\centering
-	\includegraphics[draft=false]{ImaiIri_Shortcut}
+	\includegraphics[draft=\blndraft]{ImaiIri_Shortcut}
 	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
@@
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{Shrink_Uniting}
+	\caption{Unite a polygon with the polygon at the immediately previous step.
+		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
+		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
+		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
+		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
+	}
+	\label{fig:Shrink_Uniting}
+\end{figure}
+
 As we simplify buildings after growing, 
 some parts of the buildings may shrink 
-comparing to themselves at the immediate previous steps.
-To avoid this shrink, we unite a building with itself at the immediate previous 
+comparing to themselves at the immediately previous steps.
+To avoid this shrink, we unite a building with itself at the immediately 
+previous 
 step so that the 

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the section unite buildings of the immediately previous step.

@@
 
-As shown in \eq\ref{eq:d_Et}, $\dtrm{E}$ increases along with time $t$.
-We illustrated in \fig\ref{fig:ErosionBreak} that 
-a larger $\dtrm{E}$ may result in the shrinking of a building.
-
-$\dtrm[1]{G} + \dtrm[1]{D}$
+Both the erosion and line simplification may results in shrinking of a building.
+\fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
+examples respectively.
+To avoid these kinds of shrinking,
+we unite a building with itself at the immediately previous step.
+For example, if the grown polygons of 
+\fig\ref{fig:Shrink_Erosion}~(c) and~(g) 
+are from a sequence of $10$ steps, 
+i.e., $t \in \{0.1, 0.2, \dots, 1\}$, 
+then we compute the result of $t=0.8$ by uniting 
+the grown polygon obtained independently at $t=0.8$ and 
+the grown polygon at $t=0.7$. 
+\fig\ref{fig:Shrink_Uniting}~(a) shows the result,
+which is the union of the two grown polygons in 
+\fig\ref{fig:Shrink_Erosion}~(c) and~(g).
+Similarly, \fig\ref{fig:Shrink_Uniting}~(b) shows the union of the two grown 
+polygons in 
+\fig\ref{fig:Shrink_Simplification}~(c) and~(h).
 
@@
 
-As we simplify buildings after growing, 
-some parts of the buildings may shrink 
-comparing to themselves at the immediately previous steps.
-To avoid this shrink, we unite a building with itself at the immediately 
-previous 
-step so that the 
-united building is always larger than both of the united parts.
-
-\subsection{Eliminate small buildings}
-\label{sec:Eliminate}
-We eliminate a building if the area of this building is smaller than a 
-threshold.
-For a group of buildings, we consider the area sum of all the buildings.
-
 \subsection{Group buildings based on buffering}
@@
 We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
+
+\subsection{Eliminate small buildings}
+\label{sec:Eliminate}
+We eliminate a building if the area of this building is smaller than a 
+threshold.
+For a group of buildings, we consider the area sum of all the buildings.
 

### 2017-08-31 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished section merge close buildings by introducing bridges

@@
 \newcommand{\tab}{Tab.~}
+\newcommand{\figs}{Figs.~}
+\newcommand{\eqs}{Eqs.~}
+\newcommand{\sects}{Secs.~}
+\newcommand{\tabs}{Tabs.~}
 
@@
 
-\subsection{Merge close buildings by introducing bridges}
-The distance between two buildings should be larger than a threshold
-\parencite{Regnauld2001,Li2004}.
-Following \textcite{Basaraner2008,Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$ for target map. 
-The separation threshold at time $t$ is
-\begin{equation}
-\label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot M_t.
-\end{equation}
-
-If two buildings become too close to each other during growing, 
-we merge them by introducing a bridge connecting the nearest points 
-(see \fig\ref{fig:GrowAndBridge}).
-No matter a bridge appear earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
-the same widths.
-This setting is achieved by following.
-We detect nearest points for each pair of buildings at time $t=0$ so that 
-we know where we should add bridges. 
-We grow the bridges together with the buildings,
-but we do not show the bridges until the two buildings are close enough. 
-\todo[inline]{actually larger than $d_{\epsilon, t}$.}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics{GrowAndBridge}
-	\caption{Merge buildings by introducing bridges when the buildings become 
-	too close.
-		Although the bridges appear at different time, 
-		their widths are the same (see the figure with $t=1$).}
-	\label{fig:GrowAndBridge}
-\end{figure}
-
 \subsection{Simplify grown buildings}
@@
 	\centering
-	\includegraphics[draft=true]{RemovePitAndSpike}
+	\includegraphics[]{RemovePitAndSpike}
 	\caption{Remove a pit by dilating and then remove a spike by eroding.
@@
 	\centering
-	\includegraphics[draft=\blndraft]{ErosionBreak}
+	\includegraphics[]{ErosionBreak}
 	\caption{Dilate the gray polygon, then erode the dilated polygon.
@@
 	\centering
-	\includegraphics[draft=\blndraft]{ImaiIri_Shortcut}
+	\includegraphics[]{ImaiIri_Shortcut}
 	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
@@
 
-We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
-but we hoped to remove more points. We found that the Imai--Iri 
+We tried simplifying using 
+the Douglas--Peucker algorithm \parencite{Douglas1973}, 
+but we hoped to remove more points. 
+We found that the Imai--Iri 
 algorithm fit our needs better.
 
-\subsection{Unite buildings of the immediate previous step}
+\subsection{Unite buildings of the immediately previous step}
 \label{sec:Unite}
@@
 	\centering
-	\includegraphics[draft=false]{Shrink_Erosion}
+	\includegraphics[]{Shrink_Erosion}
 	\caption{A building shrinks during growing because of dilation and erosion, 
@@
 	\centering
-	\includegraphics[draft=false]{Shrink_Simplification}
+	\includegraphics[]{Shrink_Simplification}
 	\caption{A building shrinks during growing because of line simplification, 
@@
 	\centering
-	\includegraphics[draft=false]{Shrink_Uniting}
+	\includegraphics[]{Shrink_Uniting}
 	\caption{Unite a polygon with the polygon at the immediately previous step.
@@
 \end{figure}
+
+\subsection{Merge close buildings by introducing bridges}
+The distance between two buildings on a map should be larger than a threshold
+\parencite{Regnauld2001,Li2004}.
+Following \textcite{Basaraner2008,Stoter2009}, 
+we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
+The real separation distance at time $t$ is
+\begin{equation}
+	\label{eq:d_epsilont}
+	d_{\epsilon, t} = \epsilon \cdot M_t.
+\end{equation}
+
+If a group of buildings become too close during growing,
+we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
+We will talk about where to add bridges in \sect\ref{sec:Goal}.
+No matter a bridge appear earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
+the same widths.
+This setting is achieved by following.
+We detect nearest points for each pair of buildings at time $t=0$ so that 
+we know where we should add bridges.
+At time $t$, we group buildings that are too close to each other,
+then we merge them by adding the precomputed bridges.
+For this merged building, we grow, simplify, and unite as described in 
+\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
+We may unite the processed merged building with several separate parts 
+because the group of buildings may be in several smaller groups
+in the immediately previous step.
+
+\todo[inline]{actually larger than $d_{\epsilon, t}$.}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Merge buildings by introducing bridges when the buildings become 
+		too close.
+		Although the bridges appear at different time, 
+		their widths are the same (see the figure with $t=1$).}
+	\label{fig:GrowAndBridge}
+\end{figure}
+
+For each pair of buildings in the same group, 
+we find the smallest distance between them.
+We connect the buildings by adding an edge from the nearest points.
+We find a minimum spanning tree of the buildings using Prim's algorithm 
+\parencite{Prim1957}.
+We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
 
@@
 
-\subsection{Enlarging and merging buildings for goal map}
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\parencite{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
+\subsection{Generate buildings on goal map}
+\label{sec:Goal}
+We group
 

### 2017-09-03 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
move to the format of ACM Sigspatial

\documentclass[sigconf, authordraft]{acmart}

\graphicspath{{figures/}}

\usepackage{booktabs} % For formal tables
\usepackage{xspace}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{gensymb}  % for degree sign, e.g., temperature

%Sometimes, the links are created by the bibliography, from items with URL 
%fields. A solution that helps in this case and preserves clickable links is to 
%make sure that each \bibitem is typeset without column or page breaks:
\let\oldbibitem\bibitem
\def\bibitem{\vfill\oldbibitem}

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}
\newcommand{\figs}{Figs.~}
\newcommand{\eqs}{Eqs.~}
\newcommand{\sects}{Secs.~}
\newcommand{\tabs}{Tabs.~}
\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

\acmSubmissionID{123-A12-B3}

\begin{document}
\title{Continuous Generalization of Buildings by Growing and 
	Merging}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Chair of Computer Science I, University of W\"urzburg}
  \streetaddress{Am Hubland}
  \city{W\"urzburg} 
  \state{Germany} 
  \postcode{97074}
}
\email{dongliang.peng@uni-wuerzburg.de}

\author{Guillaume Touya}
%\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{COGIT, IGN}
  \streetaddress{73 avenue de Paris}
  \city{Saint-Mand\'e Cedex} 
  \state{France} 
  \postcode{94165}
}
\email{guillaume.touya@ign.fr}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{D. Peng and G. Touya}

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start scale to a smaller goal scale. 
%
If several buildings are close to each other at the start 
scale, we bridge them by line segments and merge the several buildings into 
one 
building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. 
Then we grow the building to the target shape.
%
After finishing the growing, we can take the goal scale as the 
start scale and repeat the process.
\newline\indent
The advantages of our method are as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\input{PaperBody}

\bibliographystyle{ACM-Reference-Format}
\bibliography{References}

\end{document}

### 2017-09-03 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
move to the format of ACM Sigspatial

--- 2017-08-31 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
@@
-%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% sample root file for your "contribution" to a contributed volume
-%
-% Use this file as a template for your own input.
-%
-%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[graybox]{svmult}
-\usepackage{etex}
-
-\newcommand{\blndraft}{true}
-%\newcommand{\blndraft}{false}
-
-%\usepackage[english]{babel}
-%
-\usepackage[utf8]{inputenc}
-% choose options for [] as required from the list
-% in the Reference Guide
-
-\usepackage{mathptmx}       % selects Times Roman as basic font
-\usepackage{helvet}         % selects Helvetica as sans-serif font
-\usepackage{courier}        % selects Courier as typewriter font
-\usepackage{type1cm}        % activate if the above 3 fonts are
-                            % not available on your system
-%
-\usepackage{makeidx}         % allows index generation
-%\usepackage[]{graphicx}
-\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
-\usepackage[size=small,labelfont=bf]{caption}
-                             % when including figure files
-\usepackage{multicol}        % used for the two-column index
-\usepackage[bottom]{footmisc}% places footnotes at page bottom
-\usepackage{pdflscape}
-%\usepackage{rotating}
-\usepackage{afterpage}
-%\usepackage[disable]{todonotes}
-\usepackage[colorinlistoftodos,prependcaption]{todonotes}
-%\usepackage{todonotes}
-\usepackage{subfigure}
-\usepackage{setspace}
-\usepackage{epstopdf}
-\usepackage{flafter} %make sure that the floats are not placed 
-%before their definition
-\usepackage{times}
-\usepackage{bm}
-\usepackage{gensymb}  % for degree sign, e.g., temperature
-\usepackage{amsmath}
-\usepackage{amstext}
-\usepackage{array}  %for define the fomats of columns in a table
-\usepackage{dcolumn}
-\usepackage[T1]{fontenc}
-\usepackage{pgfplots}
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage{tabularx}
-\usepackage{adjustbox}
-\usepackage{capt-of}
-%\usepackage{marginnote}
-\usepackage{xargs}   % Use more than one 
-%optional parameter in a new commands
-%\usepackage{siunitx} %for scientific 
-%notation
-%%we do this because of a bug of package floatrow
-%\let\tmp\newinsert
-%\let\newinsert\newbox
-%\usepackage{floatrow}
-%\let\newinsert\tmp
-\usepackage{enumitem} %make items indent when using 
-%\begin{enumerate}[(a)]
-\usepackage{verbatimbox}  %for \addvbuffer
-\usepackage{hyperref}
-\usepackage{tikz}
-\usepackage{xspace}
-%\usepackage{pdfcomment}
-%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
-%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
-%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
-%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
-\newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
-\newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}
-
-\usepackage[backend=bibtex,
-bibstyle=authoryear, %without indices before names; year after 
-%names
-%style=authoryear,
-citestyle=authoryear,
-maxbibnames=20,maxcitenames=2,
-firstinits=true,
-%terseinits=true, %remove periods after initials of first names
-%style=apa, %
-%sorting=ydnt, %Sort bibliography by year (descending), name, 
-%title
-doi=false,isbn=false,url=false,
-eprint=false,dashed=false]{biblatex}
-
-%\renewcommand*{\bibfont}{\small} %set the font size of the 
-%references
-%\renewcommand*{\nameyeardelim}{\addspace} %\remove the comma 
-%between author and year citations
-%\renewcommand*{\revsdnamepunct}{} %remove commas between last 
-%%and first names in bibliography
-%\renewcommand{\labelnamepunct}{\addspace} %remove the 
-%%punctuation after the year in bibliography
-%\renewcommand{\finentrypunct}{} %remove the full stop at the 
-%%end of each bibliography entry
-\renewcommand*{\revsdnamepunct}{} %remove commas between last 
-%and first names in bibliography
-
-%remove "In:" for articles in bibliography
-\renewbibmacro{in:}{\ifentrytype{article}{}
-	{\printtext{\bibstring{in}\intitlepunct}}}
-
-\addbibresource{References.bib}
-
-\newcommand{\mypar}[1]{\bigskip\noindent\textbf{#1.}~}
-
-\newcommand{\e}[1]{\times 10^{#1}}
-\newcommand{\fig}{Fig.~}
-\newcommand{\eq}{Eq.~}
-\newcommand{\sect}{Sec.~}
-\newcommand{\tab}{Tab.~}
-\newcommand{\figs}{Figs.~}
-\newcommand{\eqs}{Eqs.~}
-\newcommand{\sects}{Secs.~}
-\newcommand{\tabs}{Tabs.~}
-
-%\newcommand{\myeqref}[1]{Eq.~\ref{#1}}
-%\newcommand{\mysectref}[1]{Sec.~\ref{#1}}
-%\newcommand{\myfigref}[1]{Fig.~\ref{#1}}
-%\newcommand{\mytabref}[1]{Tab.~\ref{#1}}
-
-\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}
-
-\graphicspath{{figures/}}
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
-
-%For the references, the following commands make the titles 
-%lowercase while keep the initial letters of journal names 
-%uppercase
-\DeclareFieldFormat{titlecase}{\MakeSentenceCase*{#1}}
-\newbibmacro*{journal}{%
-	\iffieldundef{journaltitle}
-	{}
-	{\printtext[journaltitle]{%
-			\printfield[myplain]{journaltitle}%
-			\setunit{\subtitlepunct}%
-			\printfield[myplain]{journalsubtitle}}}}
-\DeclareFieldFormat{myplain}{#1}
-
-%Remove the quotation marks for the titles in the reference
-\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{citetitle}{#1}
-\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{title}{#1}
-\DeclareNameAlias{author}{last-first}
-
-%%Using \DeclarePairedDelimiter from mathtools, you could define 
-%%macros \ceil and \floor, which will scale the delimiters 
-%%properly (if starred):
-%\usepackage{mathtools}
-%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-%\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\pgfplotsset{
-	compat=newest,
-	xlabel near ticks,
-	ylabel near ticks
-}
-
-\newcommandx{\marginalcomment}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-
-\renewcommand{\textfraction}{0.01}
-\renewcommand{\topfraction}{0.99}
-\renewcommand{\bottomfraction}{0.99}
-\renewcommand{\dbltopfraction}{0.99} % fit big float above 
-%2-col. text
-%\renewcommand\thesection{\arabic{section}}
-%\renewcommand\thesubsection{\thesection.\arabic{subsection}}
-
-% see the list of further useful packages
-% in the Reference Guide
-
-\makeindex             % used for the subject index
-                       % please use the style svind.ist with
-                       % your makeindex program
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title*{Continuous Generalization of Buildings \protect\\ by Growing and 
-Merging}
-\titlerunning{Continuous Generalization of Buildings}
-% Use \titlerunning{Short Title} for an abbreviated version of
-% your contribution title if the original one is too long
-\author{Dongliang Peng and Guillaume Touya}
-% Use \authorrunning{Short Title} for an abbreviated version of
-% your contribution title if the original one is too long
-\institute{
-	Dongliang Peng 
-	\at Chair of Computer Science I, University of W\"urzburg, 
-	Germany \\
-	\email{dongliang.peng@uni-wuerzburg.de}
-	\and
-	% 
-	Guillaume Touya
-	\at COGIT, IGN, France \\
-	\email{guillaume.touya@ign.fr}
-}
-%
-% Use the package "url.sty" to avoid
-% problems with special characters
-% used in your e-mail or web address
-%
-\maketitle
-
-\newcommand{\myabstract}{We propose a method to continuously 
-	generalize buildings from a given start scale to a smaller goal scale. 
-	%
-	If several buildings are close to each other at the start 
-	scale, we bridge them by line segments and merge the several buildings into 
-	one 
-	building.
-	For each building, either an original one or a merged one, at the start 
-	scale, 
-	we generate its target shape at 
-	the goal scale by enlarging and simplifying. 
-	Then we grow the building to the target shape.
-	%
-	After finishing the growing, we can take the goal scale as the 
-	start scale and repeat the process.
-	\newline\indent
-	The advantages of our method are as follows. First, the buildings 
-	are enlarged continuously. At the same time, they are simplified. 
-	Second, we ensure that the distance between any pair of two buildings is 
-	always larger than a specified threshold.}
-
-\abstract*{\myabstract}
-
-\abstract{\myabstract}
-
-\keywords{Text, Text}
-
 \section{Introduction}
@@
 a sequence of maps with small incremental changes.
-To realize continuous generalization, \textcite{Sester2005_CG} discussed some 
+To realize continuous generalization, \citet{Sester2005_CG} discussed some 
 generalization operators for buildings and proposed to morph a building 
 between 
-its forms at different levels. Morphing has been used to generate intermediate 
+its forms at different levels. 
+Morphing has been used to generate intermediate 
 representations for two representations at different scales 
-\parencite{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
+\citep{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
 Also aiming at 
-realize continuous generalization, \textcite{Chimani2014_Eat} generated a good 
+realize continuous generalization, \citet{Chimani2014_Eat} generated a good 
 selection sequence for road networks, and 
-\textcite{Peng2017_AStar} tried to compute optimal aggregation sequences for 
+\citet{Peng2017_AStar} tried to compute optimal aggregation sequences for 
 land-cover areas.
@@
 In order to make sure that the map is 
-easily perceived \parencite{Weibel1997}, small building should be eliminated, 
+easily perceived \citep{Weibel1997}, small building should be eliminated, 
 some building should be enlarged, and buildings close to each other should be 
@@
 Although algorithms of simplifying buildings have been studied, e.g., 
-\textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
+\citet{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
 when we have to aggregate buildings simultaneously.
@@
 The papers we may review:   
-\textcite{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},
+\citet{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},
 
-Rules for building simplification; see \textcite{Lee2005}
+Rules for building simplification; see \citet{Lee2005}
 
 Straight skeletons for map generalization: 
-\textcite{Gold2003,Matuk2006}
+\citet{Gold2003,Matuk2006}
 
-An example of enlargement in aggregation: \citetitle{Neun2005}
+An example of enlargement in aggregation: \citet{Neun2005}
 
-Using MST to group buildings: \textcite{Zhang2013, 
+Using MST to group buildings: \citet{Zhang2013, 
 	Cetinkaya2015,Deng2017,Regnauld1996}
@@
 and denote the scale of the start map by $1:M_\mathrm{s}$.
-We generate a goal map \mapg at scale $1:M_\mathrm{g}$ 
+We generate a goal map at scale $1:M_\mathrm{g}$ 
 ($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
@@
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
 	\centering
@@
 	\label{fig:Buffer_MiterLimits}
-\end{figure}
+\end{figure*}
 
-The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that the 
+The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
+the 
 building is large enough to be perceived.
@@
 \label{eq:d_G}
-d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
+d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
+(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
 \quad 0 < \lambda <1,
@@
 	\label{fig:Growth}
-\end{figure}
+\end{figure*}
 
@@
 We use a buffering-based method, 
-similar to \textcite{Damen2008,Meijers2016}, 
+similar to \citet{Damen2008,Meijers2016}, 
 to simplify our grown buildings. 
@@
 	\label{fig:RemovePitAndSpike}
-\end{figure}
+\end{figure*}
 
@@
 We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
-\textcite{Regnauld2001,Li2004,Basaraner2008}.
-According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
-when $t$ is small, 
-but $d_{\epsilon, t}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
+\citet{Regnauld2001,Li2004,Basaraner2008}.
+Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
+but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
 In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
@@
 we simplify the grown buildings using Imai--Iri algorithm 
-\parencite{ImaiIri1988}.
+\citep{ImaiIri1988}.
 This algorithm first finds all the valid shortcuts of a polyline.
@@
 We tried simplifying using 
-the Douglas--Peucker algorithm \parencite{Douglas1973}, 
+the Douglas--Peucker algorithm \citep{Douglas1973}, 
 but we hoped to remove more points. 
@@
 
-Both the erosion and line simplification may results in shrinking of a building.
+Both the erosion and line simplification may results in shrinking of a 
+building.
 \fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
@@
 	\label{fig:Shrink_Erosion}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
 	\centering
@@
 	\label{fig:Shrink_Simplification}
-\end{figure}
+\end{figure*}
 
@@
 The distance between two buildings on a map should be larger than a threshold
-\parencite{Regnauld2001,Li2004}.
-Following \textcite{Basaraner2008,Stoter2009}, 
+\citep{Regnauld2001,Li2004}.
+Following \citet{Basaraner2008,Stoter2009}, 
 we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
@@
 	\label{fig:GrowAndBridge}
-\end{figure}
+\end{figure*}
 
@@
 We find a minimum spanning tree of the buildings using Prim's algorithm 
-\parencite{Prim1957}.
+\citep{Prim1957}.
 We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
@@
 We group buildings based on the buffers of the buildings. 
-We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
-where distance $d_G$ is the growing amount of each building. 
-Parameter $d_\epsilon$ is the least distance allowed between two buildings.
-We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
-the corresponding two buildings will become too close during our growing step.
-The two buildings are identified as in the same group.
+We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
+(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
+We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
+the corresponding two buildings will become too close at time $t$.
+As a result, the two buildings are identified as in the same group.
 
-We merge the buffers which overlap each others so that we have some large units.
+We merge the buffers which overlap each others so that we have some large 
+units.
 Now we iteratively remove small ``bays''.
@@
 $\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
-map, which is the area limit used by \textcite{Stoter2009}. As a result, we 
+map, which is the area limit used by \citet{Stoter2009}. As a result, we 
 set 
@@
 
-\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
+\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
 $0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
@@
 %least some size, we try to avoid the violation for a map at a goal scale.
-%\textcite{Chaudhry2008} thought that a hole of a settlement should be at 
+%\citet{Chaudhry2008} thought that a hole of a settlement should be at 
 %least 
@@
 		the gray polygon is the enlargement of the building. In the right 
-	figure, the gray polygon has been simplified to a rectangle. In order to 
-	fill the rectangle, most parts of the (green) building needs to grow with
+		figure, the gray polygon has been simplified to a rectangle. In order 
+to 
+		fill the rectangle, most parts of the (green) building needs to grow 
+with
 		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
@@
 	\label{fig:ExtraGrowth}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
 	\centering
@@
 	\label{fig:GrowingExample}
-\end{figure}
+\end{figure*}
 
@@
 Although a version with a 
-lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
+lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
 version.
@@
 The buffer function and clip function are from library \emph{Clipper} 
-of \textcite{Johnson2014}.
-An evaluation of Clipper can be found in \textcite{Palfrader2015}.
+of \citet{Johnson2014}.
+An evaluation of Clipper can be found in \citet{Palfrader2015}.
 We ran our case study under 64-bit 
@@
 	\label{fig:Data}
-\end{figure}
+\end{figure*}
 
@@
 Our area on map is $some number\,\text{mm}^2$.
-According to \eq4 of paper \textcite{Topfer1966}, 
+According to \eq4 of paper \citet{Topfer1966}, 
 the area on map should be $some number\,\text{mm}^2$
@@
 Eventually, our result is a set of settlement boundaries. An interesting 
-problem is to compare our method with \textcite{Chaudhry2008}.
+problem is to compare our method with \citet{Chaudhry2008}.
 
 We used radical law. We may also consider the fractal nature of maps proposed 
-by \textcite{Jiang2015}.
+by \citet{Jiang2015}.
 
@@
 
+A special kind of Voronoi diagram considering miter offset. A buildings is 
+allowed to grow inside its own zone.
+
 \todo[inline]{consider multi bridges; 
 	consider transparency of bridges in stead of enlarging}
-
-\printbibliography
-\end{document}

### 2017-09-03 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
move to the format of ACM Sigspatial

@@
 
-\newcommand{\blndraft}{true}
-%\newcommand{\blndraft}{false}
+\usepackage[]{graphicx}
+%\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
 
@@
 \usepackage{makeidx}         % allows index generation
-%\usepackage[]{graphicx}
-\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
+
 \usepackage[size=small,labelfont=bf]{caption}
@@
 %		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
-\newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
-\newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}
 
@@
 \graphicspath{{figures/}}
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
 
@@
 \textcite{Regnauld2001,Li2004,Basaraner2008}.
-According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
-when $t$ is small, 
-but $d_{\epsilon, t}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
+Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
+but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
 In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
@@
 
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\parencite{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
+%For each pair of buildings in the same group, 
+%we find the smallest distance between them.
+%We connect the buildings by adding an edge from the nearest points.
+%We find a minimum spanning tree of the buildings using Prim's algorithm 
+%\parencite{Prim1957}.
+%We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
 
@@
 We group buildings based on the buffers of the buildings. 
-We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
-where distance $d_G$ is the growing amount of each building. 
-Parameter $d_\epsilon$ is the least distance allowed between two buildings.
-We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
-the corresponding two buildings will become too close during our growing step.
-The two buildings are identified as in the same group.
+We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
+(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
+We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
+the corresponding two buildings will become too close at time $t$.
+As a result, the two buildings are identified as in the same group.
 
@@
 
+A special kind of Voronoi diagram considering miter offset. A buildings is 
+allowed to grow inside its own zone.
+
 \todo[inline]{consider multi bridges; 

### 2017-09-03 ContinuousGeneralizer/MorphingClass/CAid/CMatchAndMergePolygons.cs

@@ -46,9 +46,12 @@ namespace MorphingClass.CAid
             MatchCpg(ref pLSCPgLt, ref pSSCPgLt, ref InterLSAttentionCPgLt, ref SSAttentionCPgLt);
             List<CPolygon> ResultCPgLt = MergeCpg(ref pSSCPgLt);
 
-            CSaveFeature.SaveCGeoEb(SSAttentionCPgLt, esriGeometryType.esriGeometryPolygon, ParameterInitialize.cboLayerLt[1].Text + "_Attention", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);            
-            CSaveFeature.SaveCGeoEb(InterLSAttentionCPgLt, esriGeometryType.esriGeometryPolygon,ParameterInitialize.cboLayerLt[0].Text + "_Attention", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
-            CSaveFeature.SaveCGeoEb(ResultCPgLt, esriGeometryType.esriGeometryPolygon, ParameterInitialize.cboLayerLt[0].Text + "_Merged", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            CSaveFeature.SaveCGeoEb(SSAttentionCPgLt, esriGeometryType.esriGeometryPolygon, 
+                ParameterInitialize.cboLayerLt[1].Text + "_Attention");            
+            CSaveFeature.SaveCGeoEb(InterLSAttentionCPgLt, esriGeometryType.esriGeometryPolygon,
+                ParameterInitialize.cboLayerLt[0].Text + "_Attention");
+            CSaveFeature.SaveCGeoEb(ResultCPgLt, esriGeometryType.esriGeometryPolygon, 
+                ParameterInitialize.cboLayerLt[0].Text + "_Merged");
          }
 
         public static void MatchCpg(ref List<CPolygon> pLSCPgLt, ref List<CPolygon> pSSCPgLt, ref List<CPolygon> InterLSAttentionCPgLt, ref List<CPolygon> SSAttentionCPgLt)

### 2017-09-03 ContinuousGeneralizer/MorphingClass/CAid/CMergeAndSplitPolylines.cs

@@ -72,7 +72,7 @@ namespace MorphingClass.CAid
                 PreCptLt.AddRange(SucCptLt);
                 OutputCPlLt.Add(new CPolyline(intID++, PreCptLt));
             }
-            CSaveFeature.SaveCGeoEb(OutputCPlLt, esriGeometryType.esriGeometryPolyline, ParameterInitialize.pFLayerLt[0].Name + "MergeAndSplit", ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
+            CSaveFeature.SaveCGeoEb(OutputCPlLt, esriGeometryType.esriGeometryPolyline, ParameterInitialize.pFLayerLt[0].Name + "MergeAndSplit");
 
             long lngEndTime = System.Environment.TickCount;//记录结束时间
             ParameterInitialize.tsslTime.Text = "Running Time: " + Convert.ToString(lngEndTime - lngStartTime) + "ms";  //显示运行时

### 2017-09-03 ContinuousGeneralizer/MorphingClass/CAid/CTopologyChecker.cs

@@ -142,36 +142,18 @@ namespace MorphingClass.CAid
 
                 IntersectionLt = null;
 
-                CSaveFeature.SaveCGeoEb(UnLinkedCptLt, esriGeometryType.esriGeometryPoint, "UnLinkedCpt_" + i.ToString() + "__" + UnLinkedCptLt.Count, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl, blnVisible :false  );
+                CSaveFeature.SaveCGeoEb(UnLinkedCptLt, esriGeometryType.esriGeometryPoint, 
+                    "UnLinkedCpt_" + i.ToString() + "__" + UnLinkedCptLt.Count,  blnVisible :false  );
                 CHelpFunc.SetAEGeometryNull(UnLinkedCptLt);
                 
-                CSaveFeature.SaveCGeoEb(CrossCptLt, esriGeometryType.esriGeometryPoint, "Crosses_" + i.ToString() + "__" + CrossCptLt.Count, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl, blnVisible: false);
+                CSaveFeature.SaveCGeoEb(CrossCptLt, esriGeometryType.esriGeometryPoint, 
+                    "Crosses_" + i.ToString() + "__" + CrossCptLt.Count, blnVisible: false);
                 CHelpFunc.SetAEGeometryNull(CrossCptLt);
                 
-                CSaveFeature.SaveCGeoEb(OverlapCptLt, esriGeometryType.esriGeometryPoint, "OverlapCpt_" + i.ToString() + "__" + OverlapCptLt.Count, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl, blnVisible: false);
+                CSaveFeature.SaveCGeoEb(OverlapCptLt, esriGeometryType.esriGeometryPoint, 
+                    "OverlapCpt_" + i.ToString() + "__" + OverlapCptLt.Count,  blnVisible: false);
                 CHelpFunc.SetAEGeometryNull(OverlapCptLt);
-
-
-
-
-
-
-
-
-                //if (UnLinkedCptLt.Count > 0)
-                //{
-                //    CSaveFeature.SaveCGeoEb(UnLinkedCptLt, esriGeometryType.esriGeometryPoint, "UnLinkedCpt_" + i.ToString() + "__" + UnLinkedCptLt.Count, ParameterInitialize.pWorkspace, ParameterInitialize.m_mapControl);
-                //}
-
-                //if (CrossCptLt.Count > 0)
[…]

### 2017-09-03 ContinuousGeneralizer/MorphingClass/CGeometry/CTriangulation.cs

@@ -315,7 +315,7 @@ namespace MorphingClass.CGeometry
             return ITinEdgeLt;
         }
 
-        public void SaveDataAreaITinEdgeLt(CParameterInitialize parameterInitialize, string strName)
+        public void SaveDataAreaITinEdgeLt(string strName)
         {
             var ITinEdgeLt = _pTinEdgeLt;
             var CEdgeLt = new List<CEdge>(ITinEdgeLt.Count);
@@ -324,7 +324,7 @@ namespace MorphingClass.CGeometry
                 CEdgeLt.Add(new CEdge(pTinEdge));
             }
 
-            CSaveFeature.SaveCGeoEb(CEdgeLt, esriGeometryType.esriGeometryPolyline, "TIN_"+strName, parameterInitialize.pWorkspace, parameterInitialize.m_mapControl);
+            CSaveFeature.SaveCGeoEb(CEdgeLt, esriGeometryType.esriGeometryPolyline, "TIN_"+strName);
         }
 
         public void CompareCptltAndNode()

### 2017-09-03 ContinuousGeneralizer/MorphingClass/CUtility/CSaveFeature.cs

@@ -24,7 +24,7 @@ namespace MorphingClass.CUtility
     public class CSaveFeature
     {
         public IFeatureLayer pFeatureLayer { get; set; }
-        private const int _intColor=0;
+        private const int _intColor = 0;
         //private int _intKnown = 2;   //we don't need the first three FieldNames, i.e., "FID", "Shape"
 
         public CSaveFeature()
@@ -39,33 +39,35 @@ namespace MorphingClass.CUtility
         /// <param name="pstrPath">保存路径</param>
         /// <param name="pesriGeometryType">图层类型</param> 
         /// <remarks>If I have time, I will put the parameters of colors and width in one parameter!</remarks>
-        public CSaveFeature(esriGeometryType pesriGeometryType, string pstrLayerName, IWorkspace pWorkspace, IMapControl4 pm_mapControl,
-            List<string> pstrFieldNameLt = null, List<esriFieldType> pesriFieldTypeLt = null,
-            int fintRed = 0, int fintGreen = 0, int fintBlue = 0, double dblWidth = 1, 
-            string strSymbolLayerPath = null, bool blnVisible = true)
+        public CSaveFeature(esriGeometryType pesriGeometryType, string pstrLayerName,
+List<string> pstrFieldNameLt = null, List<esriFieldType> pesriFieldTypeLt = null,
+int fintRed = 0, int fintGreen = 0, int fintBlue = 0, double dblWidth = 1,
+esriSimpleFillStyle pesriSimpleFillStyle = esriSimpleFillStyle.esriSFSSolid,
+string strSymbolLayerPath = null, bool blnVisible = true)
         {
-            this.pFeatureLayer = CreateFeatureLayer(pesriGeometryType, pstrLayerName, pWorkspace, pm_mapControl, 
-                pstrFieldNameLt, pesriFieldTypeLt, fintRed, fintGreen, fintBlue, dblWidth,strSymbolLayerPath, blnVisible);
+            this.pFeatureLayer = CreateFeatureLayer(pesriGeometryType, pstrLayerName, pstrFieldNameLt, pesriFieldTypeLt,
+                fintRed, fintGreen, fintBlue, dblWidth, pesriSimpleFillStyle, strSymbolLayerPath, blnVisible);
         }
 
-        private IFeatureLayer CreateFeatureLayer(esriGeometryType pesriGeometryType, string pstrLayerName, 
-            IWorkspace pWorkspace, IMapControl4 pm_mapControl,
[…]

### 2017-09-04 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
finished the description of figures/RemoveBay.pdf

@@
 There are two typical ways of buffering polygons, i.e.,
-one with round joins and the other with miter joins (see 
-\fig\ref{fig:Buffer_TwoKinds}).
+one with round joins and the other with miter joins 
+(see \fig\ref{fig:Buffer_TwoKinds}).
 As buildings are usually rectangles, 
@@
 This spike may go across other buildings 
-(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
+(see \fig\ref{fig:Buffer_MiterLimits}a).
 To avoid this kind of interruptions, 
@@
 a \emph{square} joining is applied
-(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
+(see \fig\ref{fig:Buffer_MiterLimits}b).
 To keep right angles of buildings, 
@@
 
-\begin{figure*}[tb]
+\begin{figure}[tb]
 	\centering
@@
 	\label{fig:Buffer_MiterLimits}
-\end{figure*}
+\end{figure}
 
@@
 	\label{fig:RemovePitAndSpike}
-\end{figure*}
+\end{figure}
 
@@
 	\caption{Unite a polygon with the polygon at the immediately previous step.
-		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
-		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
-		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
-		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
+		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}c and the 
+		polygon of \fig\ref{fig:Shrink_Erosion}g;
+		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}c and 
+		the polygon of \fig\ref{fig:Shrink_Simplification}h;
 	}
@@
 \label{sec:Grouping}
-We group buildings based on the buffers of the buildings. 
+We group buildings based on the buffers of the buildings 
+(see \fig\ref{fig:RemoveBay} for example). 
 We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
@@
 All the buildings overlapping with the same unit belong to the same group.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{RemoveBay}
+	\caption{Group buildings iteratively.
+		(a) Original buildings.
+		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
+		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
+		(d) Dilate the polygons in (c) with distance 
+		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
+		If two polygons in (d) intersect, 
+		the original buildings in (a) will be put in the same group 
+		because they will become too close at time $t$.
+		Until this step, there two groups according to (d), 
+		one consists of the single middle building and 
+		the other group consists of the surrounding $9$ buildings.
+		The process of (e), (f), and (g) is similar to 
+		that of (b), (c), and (d).		
+		The difference is that 
+		instead of applying the operators to each single building, 
+		we do that for the buildings in the same group.
+		There is only one group left according to (g).
+		We iteratively group buildings in this way until the number of groups 
+		does not decrease.
+	}
+	\label{fig:RemoveBay}
+\end{figure*}
 

### 2017-09-04 ContinuousGeneralizer/ContinuousGeneralizer/FrmContinuousGeneralizer.cs

@@ -65,8 +65,9 @@ namespace ContinuousGeneralizer
             //var frmCurrent = new FrmExtractPossibleFiles();
             frmCurrent.Show();
             frmCurrent.btnRun_Click(sender, e);
-            //frmCurrent.btn090_Click(sender, e);
             frmCurrent.btnMultiResults_Click(sender, e);
+
+            //frmCurrent.btn090_Click(sender, e);
         }
 
         private object _Missing = Type.Missing;

### 2017-09-04 ContinuousGeneralizer/MorphingClass/CAid/CToIpe.cs

@@ -103,7 +103,7 @@ namespace MorphingClass.CAid
                 //this bound line should be under all other objectss
                 str += CIpeDraw.drawIpeEdge(pIpeEnv.XMin, pIpeEnv.YMin, pIpeEnv.XMin, pIpeEnv.YMax, "white");
             }
-
+            string strName = pFLayer.Name;
             IFeatureClass pFeatureClass = pFLayer.FeatureClass;
             int intFeatureCount = pFeatureClass.FeatureCount(null);
             IFeatureCursor pFeatureCursor = pFeatureClass.Search(null, false);    //注意此处的参数(****,false)！！！            
@@ -112,7 +112,6 @@ namespace MorphingClass.CAid
             {
                 //at the last round of this loop, pFeatureCursor.NextFeature() will return null
                 IFeature pFeature = pFeatureCursor.NextFeature();
-
                 switch (pFeatureClass.ShapeType)
                 {
                     case esriGeometryType.esriGeometryPoint:
@@ -149,7 +148,6 @@ namespace MorphingClass.CAid
             var ipt = pFeature.Shape as IPoint;
             return CIpeDraw.DrawIpt(ipt, pFLayerEnv, pIpeEnv, "disk", new CColor(pMarkerSymbolRgbColor), strBoundWidth);
         }
-
 
 
         /// <summary>
@@ -194,16 +192,19 @@ namespace MorphingClass.CAid
             //we are not allowed to directly use "var pFillRgbColor = pFillSymbol.Color as IRgbColor;"
             //Nor can we use "var pFillRgbColor = pFillSymbol.Color.RGB as IRgbColor;"
             //pFillSymbol.Color.RGB has type 'int'
-            var pSimpleFillSymbol = pFillSymbol as ISimpleFillSymbol;
-
             IColor pFillSymbolColor = new RgbColorClass();
             pFillSymbolColor.RGB = pFillSymbol.Color.RGB;
             CColor cColor = new CUtility.CColor(pFillSymbolColor as IRgbColor);
-            if (pSimpleFillSymbol.Style == esriSimpleFillStyle.esriSFSHollow ||
-                pSimpleFillSymbol.Style == esriSimpleFillStyle.esriSFSNull)
+            var pSimpleFillSymbol = pFillSymbol as ISimpleFillSymbol;
+            if (pSimpleFillSymbol!=null)
             {
-                cColor = null;
+                if (pSimpleFillSymbol.Style == esriSimpleFillStyle.esriSFSHollow ||
[…]

### 2017-09-06 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
made our program run faster

@@
 
-The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
-the 
-building is large enough to be perceived.
-In \sect\ref{sec:Simplify}, we show that we set $a=4$.
-Accordingly, a square at the start map should have 
-area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
-a square at the goal map should have 
-area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
-The difference of the side lengths is 
-$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
-(see \fig\ref{fig:Growth}).
-A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
-it can survive when users zoom out from 
-the start map to the goal map.
-In order to eliminate small buildings, 
-we define our growing distance as
-\begin{equation}
-\label{eq:d_G}
-d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
-(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
-\quad 0 < \lambda <1,
-\end{equation}
-where variable $\lambda$ is a growing factor. 
-A larger $\lambda$ results in  
-fewer buildings to be eliminated, and vice versa.
-During our growing, the growth at time $t$ is
+%The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
+%the 
+%building is large enough to be perceived.
+%In \sect\ref{sec:Simplify}, we show that we set $a=4$.
+%Accordingly, a square at the start map should have 
+%area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
+%a square at the goal map should have 
+%area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
+%The difference of the side lengths is 
+%$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
+%(see \fig\ref{fig:Growth}).
+%A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
+%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
+%it can survive when users zoom out from 
+%the start map to the goal map.
+%In order to eliminate small buildings, 
+%we define our growing distance as
+%\begin{equation}
+%\label{eq:d_G}
+%d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
+%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
+%\quad 0 < \lambda <1,
+%\end{equation}
+%where variable $\lambda$ is a growing factor. 
+%A larger $\lambda$ results in  
+%fewer buildings to be eliminated, and vice versa.
+%During our growing, the growth at time $t$ is
+%\begin{equation}
+%\label{eq:d_Gt}
+%\dtrm{G} = t \cdot d_\mathrm{G}.
+%\end{equation}
+%
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{Growth}
+%	\caption{Growth.}
+%	\label{fig:Growth}
+%\end{figure*}
+
+We denote by $d_\mathrm{G}$ the total growth. The growth at time $t$ is
 \begin{equation}
@@
 \end{equation}
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{Growth}
-	\caption{Growth.}
-	\label{fig:Growth}
-\end{figure*}
 
@@
 
-\subsection{Unite buildings of the immediately previous step}
+\subsection{Group buildings based on buffering}
+\label{sec:Group}
+We group buildings based on their buffers
+(see \fig\ref{fig:RemoveBay} for example).
+We wish to remove some ``bays'' 
+which have widths less than $2 \dtrm{D}$.
+A bay may appear after some buildings are merged by bridging
+(see for example \fig\ref{fig:RemoveBay}e).
+To remove a such kind of bay,
+we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
+and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
+with distance $\dtrm{D}$.
+There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
+so we iteratively group until the number of groups does not decrease.
+The result of having removed a bay is the outer polygon of 
+\fig\ref{fig:RemoveBay}h. 
+In comparison, the result is \fig\ref{fig:RemoveBay}e 
+if we do not remove a bay.
+Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
+kind of bay and will be removed by overgrowing.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{RemoveBay}
+	\caption{Group buildings iteratively.
+		(a) Original buildings.
+		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
+		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
+		(d) Dilate the polygons in (c) with distance 
+		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
+		If two polygons in (d) intersect, 
+		the original buildings in (a) will be put in the same group 
+		because they will become too close at time $t$.
+		Until this step, there two groups according to (d), 
+		one consists of the single middle building and 
+		the other group consists of the surrounding $9$ buildings.
+		(e) The result of growing and merging at time $t$ 
+		if we use $\dtrm{D}=0$.
+		The process of (f), (g), and (h) is similar to 
+		that of (b), (c), and (d).		
+		The difference is that 
+		instead of applying the operators to each single building, 
+		we do that for the buildings in the same group.
+		In (f), we manage to remove the bay in (e) by additionally dilating 
+		with distance $\dtrm{D}$.
+		There is only one group left according to (h).
+		We iteratively group buildings in this way until the number of groups 
+		does not decrease.
+	}
+	%in this example, we used _dblTotalGrow *= 5;
+	\label{fig:RemoveBay}
+\end{figure*}
+
+\subsection{Merge close buildings by introducing bridges}
+\label{sec:Merge}
+The distance between two buildings on a map should be larger than a threshold
+\citep{Regnauld2001,Li2004}.
+Following \citet{Basaraner2008,Stoter2009}, 
+we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
+The real separation distance at time $t$ is
+\begin{equation}
+\label{eq:d_epsilont}
+d_{\epsilon, t} = \epsilon \cdot M_t.
+\end{equation}
+
+If a group of buildings become too close during growing,
+we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
+We will talk about where to add bridges in \sect\ref{sec:Goal}.
+No matter a bridge appear earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
+the same widths.
+This setting is achieved by following.
+We detect nearest points for each pair of buildings at time $t=0$ so that 
+we know where we should add bridges.
+At time $t$, we group buildings that are too close to each other,
+then we merge them by adding the precomputed bridges.
+For this merged building, we grow, simplify, and unite as described in 
+\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
+We may unite the processed merged building with several separate parts 
+because the group of buildings may be in several smaller groups
+in the immediately previous step.
+
+\todo[inline]{actually larger than $d_{\epsilon, t}$.}
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Merge buildings by introducing bridges when the buildings become 
+		too close.
+		Although the bridges appear at different time, 
+		their widths are the same (see the figure with $t=1$).}
+	\label{fig:GrowAndBridge}
+\end{figure*}
+
+For each pair of buildings in the same group, 
+we find the smallest distance between them.
+We connect the buildings by adding an edge from the nearest points.
+We find a minimum spanning tree of the buildings using Prim's algorithm 
+\citep{Prim1957}.
+We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.
+
+\subsection{Generate the goal forms of buildings}
+\label{sec:Goal}
+To generate the goal forms of buildings, we set time $t=1$.
+We group (see \sect\ref{sec:Group}) 
+and merge (see \sect\ref{sec:Merge}) buildings on start map.
+Then we grow (see \sect\ref{sec:Grow}) 
+and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
+See for example \fig\ref{fig:Buffer_MiterLimits}, 
+the building at time $t=1$ is the goal form of the three buildings of $t=0$.
+
+\subsection{Generate buildings on intermediate maps}
 \label{sec:Unite}
@@
 \fig\ref{fig:Shrink_Simplification}~(c) and~(h).
+
+A building on an intermediate map should never exceed
+the goal form of the group of buildings 
+which include the united buildings. 
+Otherwise, the building will need to be shrunk.
+To guarantee the non-exceeding, 
+we clip the building by the goal form 
+and remove the parts outside.
+\todo{example?}
 
@@
 
-\subsection{Merge close buildings by introducing bridges}
-The distance between two buildings on a map should be larger than a threshold
-\citep{Regnauld2001,Li2004}.
-Following \citet{Basaraner2008,Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
-The real separation distance at time $t$ is
-\begin{equation}
-\label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot M_t.
-\end{equation}
-
-If a group of buildings become too close during growing,
-we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
-We will talk about where to add bridges in \sect\ref{sec:Goal}.
-No matter a bridge appear earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
-the same widths.
-This setting is achieved by following.
-We detect nearest points for each pair of buildings at time $t=0$ so that 
-we know where we should add bridges.
-At time $t$, we group buildings that are too close to each other,
-then we merge them by adding the precomputed bridges.
-For this merged building, we grow, simplify, and unite as described in 
-\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
-We may unite the processed merged building with several separate parts 
-because the group of buildings may be in several smaller groups
-in the immediately previous step.
-
-\todo[inline]{actually larger than $d_{\epsilon, t}$.}
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Merge buildings by introducing bridges when the buildings become 
-		too close.
-		Although the bridges appear at different time, 
-		their widths are the same (see the figure with $t=1$).}
-	\label{fig:GrowAndBridge}
-\end{figure*}
-
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\citep{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.
-
-\subsection{Group buildings based on buffering}
-\label{sec:Grouping}
-We group buildings based on the buffers of the buildings 
-(see \fig\ref{fig:RemoveBay} for example). 
-We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
-(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
-We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
-the corresponding two buildings will become too close at time $t$.
-As a result, the two buildings are identified as in the same group.
-
-We merge the buffers which overlap each others so that we have some large 
-units.
-Now we iteratively remove small ``bays''.
-Each iteration consists of three steps, i.e., 
-buffering with distance $r_H$, buffering with distance $-r_H$, and
-merging overlapping units.
-The iterative process stops when the number of units do not decrease anymore.
-
-All the buildings overlapping with the same unit belong to the same group.
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{RemoveBay}
-	\caption{Group buildings iteratively.
-		(a) Original buildings.
-		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
-		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
-		(d) Dilate the polygons in (c) with distance 
-		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
-		If two polygons in (d) intersect, 
-		the original buildings in (a) will be put in the same group 
-		because they will become too close at time $t$.
-		Until this step, there two groups according to (d), 
-		one consists of the single middle building and 
-		the other group consists of the surrounding $9$ buildings.
-		The process of (e), (f), and (g) is similar to 
-		that of (b), (c), and (d).		
-		The difference is that 
-		instead of applying the operators to each single building, 
-		we do that for the buildings in the same group.
-		There is only one group left according to (g).
-		We iteratively group buildings in this way until the number of groups 
-		does not decrease.
-	}
-	\label{fig:RemoveBay}
-\end{figure*}
-
-\subsection{Generate buildings on goal map}
-\label{sec:Goal}
-We group
-
 \subsection{Eliminate small buildings}
@@
 
-\subsection{Parameters for growing and simplifying}
-
-If we insist on that we should observe 
-the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
-sure that
-\begin{equation}
-\label{eq:a_limit}
-\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
-\end{equation}
-Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
-and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
-\begin{equation}
-a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
-\end{equation}
-We also require 
-that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
-On one hand, we should have a large $x$ so that we will see the 
-growing most of the time.
-On the other hand, we wish to keep bridges short as bridges are intrusions to 
-our map, which means we should have a small $x$ and a large $\lambda$ so that 
-we will have a small 
-$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
-Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
-Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
-$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
-map, which is the area limit used by \citet{Stoter2009}. As a result, we 
-set 
-$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
-Using these setting, we have
-\begin{equation}
-a \ge 4.
-\end{equation}
-according to Eq.~\ref{eq:a_limit}.
-
-Therefore, we may grow up to distance 
-\[
-D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
-\]
-Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
-where  
-variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
-
-\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
-$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
-which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
-Following their setting, we shrink a hole and 
-eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.
+%\subsection{Parameters for growing and simplifying}
+%
+%
+%
+%
+%If we insist on that we should observe 
+%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
+%sure that
+%\begin{equation}
+%\label{eq:a_limit}
+%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
+%\end{equation}
+%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
+%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
+%\begin{equation}
+%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
+%\end{equation}
+%We also require 
+%that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
+%On one hand, we should have a large $x$ so that we will see the 
+%growing most of the time.
+%On the other hand, we wish to keep bridges short as bridges are intrusions to 
+%our map, which means we should have a small $x$ and a large $\lambda$ so that 
+%we will have a small 
+%$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
+%Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
+%Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
+%$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
+%map, which is the area limit used by \citet{Stoter2009}. As a result, we 
+%set 
+%$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
+%Using these setting, we have
+%\begin{equation}
+%a \ge 4.
+%\end{equation}
+%according to Eq.~\ref{eq:a_limit}.
+%
+%
+%
+%
+%Therefore, we may grow up to distance 
+%\[
+%D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
+%\]
+%Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
+%where  
+%variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
+%
+%
+%\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
+%$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
+%which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
+%Following their setting, we shrink a hole and 
+%eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.
 
@@
 
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{ExtraGrowth}
-	\caption{In the left figure, the green polygon represents a building, and 
-		the gray polygon is the enlargement of the building. In the right 
-		figure, the gray polygon has been simplified to a rectangle. In order 
-to 
-		fill the rectangle, most parts of the (green) building needs to grow 
-with
-		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
-		d_\mathrm{e}$, 
-		where $d_\mathrm{e}$ is the extra growing distance.}
-	\label{fig:ExtraGrowth}
-\end{figure*}
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{ExtraGrowth}
+%	\caption{In the left figure, the green polygon represents a building, and 
+%		the gray polygon is the enlargement of the building. In the right 
+%		figure, the gray polygon has been simplified to a rectangle. In order 
+%to 
+%		fill the rectangle, most parts of the (green) building needs to grow 
+%with
+%		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
+%		d_\mathrm{e}$, 
+%		where $d_\mathrm{e}$ is the extra growing distance.}
+%	\label{fig:ExtraGrowth}
+%\end{figure*}
 
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{GrowingExample}
-	\caption{GrowingExample.}
-	\label{fig:GrowingExample}
-\end{figure*}
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{GrowingExample}
+%	\caption{GrowingExample.}
+%	\label{fig:GrowingExample}
+%\end{figure*}
 
-\subsection{Running time analysis}
-Although a version with a 
-lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
-version.
+%\subsection{Running time analysis}
+%Although a version with a 
+%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
+%version.
 
@@
 
+%Although a version with a 
+%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
+%version
+
 \section{Conclusions}
@@
 
-To make it more efficient for on line displaying, we may need 
-some external memories. First, we store the data at some key 
-scales so that we may start a generalization from the immediate 
-larger scale; $O(n)$ space. Second, we store the target shape 
-for each building; $O(n)$ space. Third, we store the aggregation 
-time and the target form for the aggregated shape; $O(n^2)$ 
-space if we count vertex number.
-%
-The displaying time is dependent on buffering and clipping.
-
-We our intermediate results may violate more cartographic rules, but we try to 
+Our intermediate results may violate more cartographic rules, but we try to 
 make the results at goal scales violate as few rules as possible.

### 2017-09-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
finished the description of figures/RemoveBay.pdf
working on the introduction

@@
 \newcommand{\e}[1]{\times 10^{#1}}
-\newcommand{\fig}{Fig.~}
-\newcommand{\eq}{Eq.~}
-\newcommand{\sect}{Sec.~}
-\newcommand{\tab}{Tab.~}
-\newcommand{\figs}{Figs.~}
-\newcommand{\eqs}{Eqs.~}
-\newcommand{\sects}{Secs.~}
-\newcommand{\tabs}{Tabs.~}
+\newcommand{\fig}{Figure~}
+\newcommand{\eq}{Equation~}
+\newcommand{\sect}{Section~}
+\newcommand{\tab}{Table~}
+\newcommand{\figs}{Figures~}
+\newcommand{\eqs}{Equations~}
+\newcommand{\sects}{Sections~}
+\newcommand{\tabs}{Tables~}
 \newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}
@@
 %Conference
-\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-  Paso, Texas USA} 
-\acmYear{1997}
-\copyrightyear{2016}
+\acmConference[UrbanGIS'17]{International Workshop on Smart Cities and Urban 
+Analytics}{November 2017}{Redondo Beach, California USA} 
+\acmYear{2017}
+\copyrightyear{2017}
 
@@
 \begin{document}
-\title{Continuous Generalization of Buildings by Growing and 
-	Merging}
+\title{Continuous Generalization of Buildings \\ by Growing and Aggregating}
 %\titlenote{Produces the permission block, and
@@
 If several buildings are close to each other at the start 
-scale, we bridge them by line segments and merge the several buildings into 
+scale, we bridge them by line segments and merge them into 
 one 
@@
 the goal scale by enlarging and simplifying. 
-Then we grow the building to the target shape.
+Then we grow all buildings to their target shapes.
 %
@@
 	<concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+	<concept_id>10010405.10010476.10010479</concept_id>
+	<concept_desc>Applied computing~Cartography</concept_desc>
 	<concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
 	</concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Applied computing~Cartography}
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{multiple representation, zooming, simplification, buffer}
 

### 2017-09-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on the introduction

@@
 
-Digital maps such as Google Maps and OpenStreetMap support zooming by 
-displaying maps at different levels. 
+Digital maps such as Google Maps and OpenStreetMap 
+support zooming by displaying maps at different levels. 
 This discrete strategy may results in sudden changes, which annoy users.
-To provide better zooming experience, continuous generalization aims to 
-produce 
-a sequence of maps with small incremental changes.
-To realize continuous generalization, \citet{Sester2005_CG} discussed some 
-generalization operators for buildings and proposed to morph a building 
-between 
-its forms at different levels. 
-Morphing has been used to generate intermediate 
-representations for two representations at different scales 
-\citep{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
-Also aiming at 
-realize continuous generalization, \citet{Chimani2014_Eat} generated a good 
-selection sequence for road networks, and 
-\citet{Peng2017_AStar} tried to compute optimal aggregation sequences for 
-land-cover areas.
+To provide better zooming experience, 
+we try to produce a sequence of maps 
+with small incremental changes.
+This process is known as \emph{continuous generalization}.
 
-When users zoom out on digital maps, buildings become closer with each other 
-and buildings themselves become smaller. 
-In order to make sure that the map is 
-easily perceived \citep{Weibel1997}, small building should be eliminated, 
-some building should be enlarged, and buildings close to each other should be 
-aggregated.
-Although algorithms of simplifying buildings have been studied, e.g., 
-\citet{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
-when we have to aggregate buildings simultaneously.
-In order to aggregate, we should first group the buildings.
+A way to realize continuous generalization is to use morphing.
+Often, a start map and a goal map, 
+respectively at a larger scale and a smaller scale, 
+are used as input, 
+and then maps at intermediate scales are produced 
+while the start map is morphed to the goal map.
+In order to morph, correspondences between two maps have to be defined.
+For example, corresponding points between a pair of polylines have been 
+investigated based on 
+dynamic programming \citep{mnwb-mpstc-08}, 
+Delaunay triangulations and binary line generalized tree (BLG-tree)  
+\citep{Deng2015},
+and simulated annealing \citep{Li2017_Annealing}.
+Between corresponding points, 
+straight-line trajectories are often used to interpolate.
+\citet{Peng2013_LSA} investigated the problem of defining interpolate 
+trajectories 
+based on least squares adjustment.
+Using morphing, \citet{Peng2016_Admin} continuously generalized between maps of 
+administrative boundaries based on compatible triangulations.
+
+Also aiming at continuous generalization,
+\citet{Danciger2009} grew polygons when a map was zoomed out. Their method 
+preserves polygons' topology, area-rations, and relative positions. 
+\citet{Chimani2014_Eat} generated a selection sequence for road network.
+They removed one road at each step while keeping the remaining roads connected.
+\citet{Peng2017_AStar} computed optimal aggregation sequences 
+for land-cover areas.
+
+Buildings are important elements on maps.
+There are many methods of generalizing buildings.
+For example, \citet{haunertwolff2010} generalized a set of buildings 
+without topological conflicts based an integer program. 
+Their method minimizes the number of edges of all the buildings 
+and guarantees that the errors are smaller than a user-defined tolerance.
+\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
+One advantage is that their method preserves orientations of the edges.
+
+When users zoom out on digital maps, 
+buildings become smaller and the distance between buildings become smaller too. 
+In order to make sure that the map is easily perceived, 
+an objective proposed by \citet{Weibel1997}, 
+some building should be enlarged,
+and buildings close to each other should be aggregated.
+The process of enlarging and aggregating can be used as a new way 
+to compute urban settlement boundaries as did by
+\citet{Chaudhry2008}, 
+who identified the boundaries based on calculating 'citeness'.
+If we have to consider enlarging, simplifying, 
+and aggregating buildings simultaneously,
+the continuous generalization becomes more complicated.
+
+In our method,
 
@@
 The papers we may review:   
-\citet{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},
+\citet{vanSmaalen2003, Stoter2009},
 
-Rules for building simplification; see \citet{Lee2005}
+Our contributions are as follows.
+In \sect\ref{sec:Methodology},
+we generalize buildings on a start map to obtain buildings on a goal map 
+by growing and merging. 
+We simplify the buildings on the 
+Using the start map and the goal map,
+we generate maps at intermediate scales.
 
-Straight skeletons for map generalization: 
-\citet{Gold2003,Matuk2006}
-
-An example of enlargement in aggregation: \citet{Neun2005}
-
-Using MST to group buildings: \citet{Zhang2013, 
-	Cetinkaya2015,Deng2017,Regnauld1996}
+a workflow based on compatible
+triangulations for generalizing administrative boundaries in a continuous and 
+topologically
+consistent way; see Section 2.We do a thorough case study with the boundaries
+of the counties and the provinces of Mainland China to test the effectiveness
+and the efficiency of our method; see Section 3. We conclude in Section 4.
 
 \section{Methodology}
-
+\label{sec:Methodology}
 \todo[inline]{a brief introduction of our method.}
@@
 
-\subsection{Grow based on buffering}
+\subsection{Growing buildings based on buffering}
 \label{sec:Grow}
@@
 
-\subsection{Simplify grown buildings}
+\subsection{Simplifying grown buildings}
 \label{sec:Simplify}
@@
 
-\subsection{Group buildings based on buffering}
+\subsection{Grouping buildings based on buffering}
 \label{sec:Group}
+There are many ways to group buildings.
+
+Using MST to group buildings: \citet{Zhang2013, 
+	Cetinkaya2015,Deng2017,Regnauld1996}
+
 We group buildings based on their buffers
@@
 
-\subsection{Merge close buildings by introducing bridges}
+\subsection{Merging close buildings by introducing bridges}
 \label{sec:Merge}
@@
 
-\subsection{Generate the goal forms of buildings}
+\subsection{Generating the goal forms of buildings}
 \label{sec:Goal}
@@
 
-\subsection{Generate buildings on intermediate maps}
+\subsection{Generating buildings on intermediate-scale maps}
 \label{sec:Unite}
@@
 
-\subsection{Eliminate small buildings}
+\subsection{Eliminating small buildings}
 \label{sec:Eliminate}
@@
 
-\section{Conclusions}
+\section{Conclusion}
 \label{sec:Conclusions}

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
finished section of introduction

@@
 we try to produce a sequence of maps 
-with small incremental changes.
+with small incremental changes from a level to another level.
 This process is known as \emph{continuous generalization}.
@@
 are used as input, 
-and then maps at intermediate scales are produced 
+then maps at intermediate scales are produced 
 while the start map is morphed to the goal map.
-In order to morph, correspondences between two maps have to be defined.
+In order to morph, correspondences between two maps need to be defined.
 For example, corresponding points between a pair of polylines have been 
@@
 and simulated annealing \citep{Li2017_Annealing}.
-Between corresponding points, 
-straight-line trajectories are often used to interpolate.
-\citet{Peng2013_LSA} investigated the problem of defining interpolate 
-trajectories 
-based on least squares adjustment.
-Using morphing, \citet{Peng2016_Admin} continuously generalized between maps of 
+From a point to its corresponding point,
+the straight-line trajectory is often used to interpolate.
+Using morphing, \citet{Peng2016_Admin} continuously generalized 
 administrative boundaries based on compatible triangulations.
@@
 Buildings are important elements on maps.
-There are many methods of generalizing buildings.
-For example, \citet{haunertwolff2010} generalized a set of buildings 
-without topological conflicts based an integer program. 
-Their method minimizes the number of edges of all the buildings 
+Many methods have been proposed to generalize them.
+For example, \citet{haunertwolff2010} simplified a set of buildings 
+based an integer program.
+Their simplification minimizes the number of edges of all the buildings 
 and guarantees that the errors are smaller than a user-defined tolerance.
+At the same time, no topological conflict is introduced by the simplification.
 \citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
 One advantage is that their method preserves orientations of the edges.
+\citet{Chaudhry2008} identified the boundaries of urban settlement by
+calculating `citeness' based on buildings.
+\citet{Li2017_Building} morphed between two buildings at different scales.
+They managed to preserve the orthogonal characteristics of buildings.
 
 When users zoom out on digital maps, 
-buildings become smaller and the distance between buildings become smaller too. 
-In order to make sure that the map is easily perceived, 
+buildings become smaller and the distances between buildings decrease. 
+In order to make sure that the information of a map is easily perceived, 
 an objective proposed by \citet{Weibel1997}, 
-some building should be enlarged,
+some building should be enlarged
 and buildings close to each other should be aggregated.
-The process of enlarging and aggregating can be used as a new way 
-to compute urban settlement boundaries as did by
-\citet{Chaudhry2008}, 
-who identified the boundaries based on calculating 'citeness'.
-If we have to consider enlarging, simplifying, 
-and aggregating buildings simultaneously,
-the continuous generalization becomes more complicated.
-
-In our method,
-
-\bigskip
-
-The papers we may review:   
-\citet{vanSmaalen2003, Stoter2009},
+Also, buildings should be simplified.
+We consider the three operations in our continuous generalization.
 
@@
 In \sect\ref{sec:Methodology},
-we generalize buildings on a start map to obtain buildings on a goal map 
-by growing and merging. 
-We simplify the buildings on the 
-Using the start map and the goal map,
-we generate maps at intermediate scales.
-
-a workflow based on compatible
-triangulations for generalizing administrative boundaries in a continuous and 
-topologically
-consistent way; see Section 2.We do a thorough case study with the boundaries
-of the counties and the provinces of Mainland China to test the effectiveness
-and the efficiency of our method; see Section 3. We conclude in Section 4.
+we generalize buildings on a start map to obtain buildings on a goal map.
+The generalization consists of aggregating, growing, and simplifying.
+We group buildings which will be too close at an output scale.
+We aggregate the grouped buildings by introducing bridges.
+We grow buildings by buffering,
+where we use so-called \emph{miter} joins to keep the right angles of buildings.
+Because of using this kind of joins instead of \emph{round} ones,
+we have to be more careful.
+We show how to solve the problems caused by miter joins.
+Eventually, we manage to generate buildings at any intermediate scales.
+We carry out a case study in \sect\ref{sec:CaseStudy}
+and discuss the performances of our method.
+We conclude our paper in \sect\ref{sec:Conclusion}.
 
@@
 \label{sec:Methodology}
-\todo[inline]{a brief introduction of our method.}
 We name our input map as start map,
@@
 process. 
-We require that the generalization yields exactly the start map when $t=0$, 
-the goal map when $t=1$, 
-and that the start map is continuously generalized into the goal map 
+We require that the generalization yields exactly the start map when $t=0$ 
+and the goal map when $t=1$.
+The start map should be continuously changed to the goal map 
 when $t$ increases from~$0$ to~$1$.
@@
 $M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.
+
+We group buildings which will be too close at time $t$
+and aggregate the buildings in the same group by introducing bridges.
+We grow the buildings by buffering with miter joins.
+Our building simplification consists of two steps.
+The first one is to use dilation and erosion to remove pits and spikes.
+The second step is to remove vertices using Imai--Iri algorithm.
+To make sure that the intermediate-scale buildings never shrink,
+we merge the shape of a building with the shape at the previously immediate 
+step. 
+Also, we clip the building using the shape on goal map.
+
+\subsection{Grouping buildings based on buffering}
+\label{sec:Group}
+There are many ways to group buildings.
+
+Using MST to group buildings: \citet{Zhang2013, 
+	Cetinkaya2015,Deng2017,Regnauld1996}
+
+We group buildings based on their buffers
+(see \fig\ref{fig:RemoveBay} for example).
+We wish to remove some ``bays'' 
+which have widths less than $2 \dtrm{D}$.
+A bay may appear after some buildings are merged by bridging
+(see for example \fig\ref{fig:RemoveBay}e).
+To remove a such kind of bay,
+we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
+and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
+with distance $\dtrm{D}$.
+There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
+so we iteratively group until the number of groups does not decrease.
+The result of having removed a bay is the outer polygon of 
+\fig\ref{fig:RemoveBay}h. 
+In comparison, the result is \fig\ref{fig:RemoveBay}e 
+if we do not remove a bay.
+Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
+kind of bay and will be removed by overgrowing.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{RemoveBay}
+	\caption{Group buildings iteratively.
+		(a) Original buildings.
+		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
+		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
+		(d) Dilate the polygons in (c) with distance 
+		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
+		If two polygons in (d) intersect, 
+		the original buildings in (a) will be put in the same group 
+		because they will become too close at time $t$.
+		Until this step, there two groups according to (d), 
+		one consists of the single middle building and 
+		the other group consists of the surrounding $9$ buildings.
+		(e) The result of growing and merging at time $t$ 
+		if we use $\dtrm{D}=0$.
+		The process of (f), (g), and (h) is similar to 
+		that of (b), (c), and (d).		
+		The difference is that 
+		instead of applying the operators to each single building, 
+		we do that for the buildings in the same group.
+		In (f), we manage to remove the bay in (e) by additionally dilating 
+		with distance $\dtrm{D}$.
+		There is only one group left according to (h).
+		We iteratively group buildings in this way until the number of groups 
+		does not decrease.
+	}
+	%in this example, we used _dblTotalGrow *= 5;
+	\label{fig:RemoveBay}
+\end{figure*}
+
+\subsection{Aggregating close buildings by introducing bridges}
+\label{sec:Merge}
+The distance between two buildings on a map should be larger than a threshold
+\citep{Regnauld2001,Li2004}.
+Following \citet{Basaraner2008,Stoter2009}, 
+we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
+The real separation distance at time $t$ is
+\begin{equation}
+	\label{eq:d_epsilont}
+	d_{\epsilon, t} = \epsilon \cdot M_t.
+\end{equation}
+
+If a group of buildings become too close during growing,
+we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
+We will talk about where to add bridges in \sect\ref{sec:Goal}.
+No matter a bridge appear earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
+the same widths.
+This setting is achieved by following.
+We detect nearest points for each pair of buildings at time $t=0$ so that 
+we know where we should add bridges.
+At time $t$, we group buildings that are too close to each other,
+then we merge them by adding the precomputed bridges.
+For this merged building, we grow, simplify, and unite as described in 
+\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
+We may unite the processed merged building with several separate parts 
+because the group of buildings may be in several smaller groups
+in the immediately previous step.
+
+\todo[inline]{actually larger than $d_{\epsilon, t}$.}
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Merge buildings by introducing bridges when the buildings become 
+		too close.
+		Although the bridges appear at different time, 
+		their widths are the same (see the figure with $t=1$).}
+	\label{fig:GrowAndBridge}
+\end{figure*}
+
+For each pair of buildings in the same group, 
+we find the smallest distance between them.
+We connect the buildings by adding an edge from the nearest points.
+We find a minimum spanning tree of the buildings using Prim's algorithm 
+\citep{Prim1957}.
+We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.
 
@@
 \end{figure}
-
-%The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
-%the 
-%building is large enough to be perceived.
-%In \sect\ref{sec:Simplify}, we show that we set $a=4$.
-%Accordingly, a square at the start map should have 
-%area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
-%a square at the goal map should have 
-%area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
-%The difference of the side lengths is 
-%$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
-%(see \fig\ref{fig:Growth}).
-%A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
-%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
-%it can survive when users zoom out from 
-%the start map to the goal map.
-%In order to eliminate small buildings, 
-%we define our growing distance as
-%\begin{equation}
-%\label{eq:d_G}
-%d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
-%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
-%\quad 0 < \lambda <1,
-%\end{equation}
-%where variable $\lambda$ is a growing factor. 
-%A larger $\lambda$ results in  
-%fewer buildings to be eliminated, and vice versa.
-%During our growing, the growth at time $t$ is
-%\begin{equation}
-%\label{eq:d_Gt}
-%\dtrm{G} = t \cdot d_\mathrm{G}.
-%\end{equation}
-%
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics{Growth}
-%	\caption{Growth.}
-%	\label{fig:Growth}
-%\end{figure*}
 
@@
 algorithm fit our needs better.
-
-\subsection{Grouping buildings based on buffering}
-\label{sec:Group}
-There are many ways to group buildings.
-
-Using MST to group buildings: \citet{Zhang2013, 
-	Cetinkaya2015,Deng2017,Regnauld1996}
-
-We group buildings based on their buffers
-(see \fig\ref{fig:RemoveBay} for example).
-We wish to remove some ``bays'' 
-which have widths less than $2 \dtrm{D}$.
-A bay may appear after some buildings are merged by bridging
-(see for example \fig\ref{fig:RemoveBay}e).
-To remove a such kind of bay,
-we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
-and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
-with distance $\dtrm{D}$.
-There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
-so we iteratively group until the number of groups does not decrease.
-The result of having removed a bay is the outer polygon of 
-\fig\ref{fig:RemoveBay}h. 
-In comparison, the result is \fig\ref{fig:RemoveBay}e 
-if we do not remove a bay.
-Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
-kind of bay and will be removed by overgrowing.
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{RemoveBay}
-	\caption{Group buildings iteratively.
-		(a) Original buildings.
-		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
-		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
-		(d) Dilate the polygons in (c) with distance 
-		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
-		If two polygons in (d) intersect, 
-		the original buildings in (a) will be put in the same group 
-		because they will become too close at time $t$.
-		Until this step, there two groups according to (d), 
-		one consists of the single middle building and 
-		the other group consists of the surrounding $9$ buildings.
-		(e) The result of growing and merging at time $t$ 
-		if we use $\dtrm{D}=0$.
-		The process of (f), (g), and (h) is similar to 
-		that of (b), (c), and (d).		
-		The difference is that 
-		instead of applying the operators to each single building, 
-		we do that for the buildings in the same group.
-		In (f), we manage to remove the bay in (e) by additionally dilating 
-		with distance $\dtrm{D}$.
-		There is only one group left according to (h).
-		We iteratively group buildings in this way until the number of groups 
-		does not decrease.
-	}
-	%in this example, we used _dblTotalGrow *= 5;
-	\label{fig:RemoveBay}
-\end{figure*}
-
-\subsection{Merging close buildings by introducing bridges}
-\label{sec:Merge}
-The distance between two buildings on a map should be larger than a threshold
-\citep{Regnauld2001,Li2004}.
-Following \citet{Basaraner2008,Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
-The real separation distance at time $t$ is
-\begin{equation}
-\label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot M_t.
-\end{equation}
-
-If a group of buildings become too close during growing,
-we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
-We will talk about where to add bridges in \sect\ref{sec:Goal}.
-No matter a bridge appear earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
-the same widths.
-This setting is achieved by following.
-We detect nearest points for each pair of buildings at time $t=0$ so that 
-we know where we should add bridges.
-At time $t$, we group buildings that are too close to each other,
-then we merge them by adding the precomputed bridges.
-For this merged building, we grow, simplify, and unite as described in 
-\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
-We may unite the processed merged building with several separate parts 
-because the group of buildings may be in several smaller groups
-in the immediately previous step.
-
-\todo[inline]{actually larger than $d_{\epsilon, t}$.}
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Merge buildings by introducing bridges when the buildings become 
-		too close.
-		Although the bridges appear at different time, 
-		their widths are the same (see the figure with $t=1$).}
-	\label{fig:GrowAndBridge}
-\end{figure*}
-
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\citep{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.
 
@@
 \section{Conclusion}
-\label{sec:Conclusions}
+\label{sec:Conclusion}
 

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
polished abstract and introduction

@@
 We propose a method to continuously 
-generalize buildings from a given start scale to a smaller goal scale. 
+generalize buildings from a given start map to a smaller-scale goal map.
+For the sake of convenience, 
+we name the buildings on the start map \emph{original buildings}.
 %
-If several buildings are close to each other at the start 
-scale, we bridge them by line segments and merge them into 
-one 
-building.
-For each building, either an original one or a merged one, at the start 
-scale, 
-we generate its target shape at 
-the goal scale by enlarging and simplifying. 
-Then we grow all buildings to their target shapes.
+For an intermediate scale, 
+we aggregate the original buildings that will be too close 
+by introducing bridges.
+We grow bridged original buildings based on buffering 
+and simplify the grown buildings.
+We take into account the shapes of the buildings 
+both at the previous map and goal map to make sure that 
+the buildings are always growing.
 %
-After finishing the growing, we can take the goal scale as the 
-start scale and repeat the process.
 \newline\indent
-The advantages of our method are as follows. First, the buildings 
-are enlarged continuously. At the same time, they are simplified. 
-Second, we ensure that the distance between any pair of two buildings is 
+The advantages of our method are as follows. 
+First, the buildings grow continuously 
+and, at the same time, are simplified.
+Second, right angles of buildings are preserved during growing. 
+Third, the distances between buildings are 
 always larger than a specified threshold.
+We do a case study to show the performances of our method.
 \end{abstract}

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished abstract and introduction

@@
 In \sect\ref{sec:Methodology},
-we generalize buildings on a start map to obtain buildings on a goal map.
+we generalize buildings on a start map 
+to obtain buildings on a smaller-scale goal map.
 The generalization consists of aggregating, growing, and simplifying.
-We group buildings which will be too close at an output scale.
-We aggregate the grouped buildings by introducing bridges.
+We aggregate buildings which will be too close at an output scale 
+by introducing bridges.
 We grow buildings by buffering,
@@
 (see for example \fig\ref{fig:RemoveBay}e).
-To remove a such kind of bay,
+To remove such kind of bay,
 we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved our abstract and introduction a little bit

@@
 In \sect\ref{sec:Methodology},
-we generalize buildings on a start map 
-to obtain buildings on a smaller-scale goal map.
+we continuously generalize a start map, of buildings, 
+to a smaller-scale goal map.
 The generalization consists of aggregating, growing, and simplifying.
-We aggregate buildings which will be too close at an output scale 
+We aggregate original buildings which will be too close at an output scale 
 by introducing bridges.
-We grow buildings by buffering,
+We grow (bridged) original buildings by buffering,
 where we use so-called \emph{miter} joins to keep the right angles of buildings.
 Because of using this kind of joins instead of \emph{round} ones,
-we have to be more careful.
-We show how to solve the problems caused by miter joins.
-Eventually, we manage to generate buildings at any intermediate scales.
-We carry out a case study in \sect\ref{sec:CaseStudy}
-and discuss the performances of our method.
+we have more problems.
+We show how to solve these problems.
+We also simplify the buildings at the output scale.
+We carry out a case study 
+and discuss the performances of our method in \sect\ref{sec:CaseStudy}.
 We conclude our paper in \sect\ref{sec:Conclusion}.

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polishing section of methodology

@@
 
-We group buildings which will be too close at time $t$
+We find buildings which will be too close at time $t$
 and aggregate the buildings in the same group by introducing bridges.
-We grow the buildings by buffering with miter joins.
+We grow the (bridged) original buildings by buffering with miter joins.
 Our building simplification consists of two steps.
@@
 To make sure that the intermediate-scale buildings never shrink,
-we merge the shape of a building with the shape at the previously immediate 
-step. 
+we merge the shape of a building 
+with the shape at the previously immediate step. 
 Also, we clip the building using the shape on goal map.
+
+Our aggregation is based on growing and some of simplifying. 
+So we present the two operators before aggregating.
+
+\subsection{Growing buildings based on buffering}
+\label{sec:Grow}
+We grow building based on buffering. 
+There are two typical ways of buffering a polygon, i.e.,
+one with round joins and the other with miter joins 
+(see \fig\ref{fig:Buffer_TwoKinds}).
+As buildings are usually rectangles, 
+we choose the second way to
+better preserve the right angles.
+If an angle is acute, however, an excessively long \emph{spike} will be 
+produced.
+This spike may go across other buildings 
+(see \fig\ref{fig:Buffer_MiterLimits}a).
+To avoid this kind of interruptions, 
+we require that if a vertex of the 
+buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
+away from the original vertex, 
+a \emph{square} join is applied
+(see \fig\ref{fig:Buffer_MiterLimits}b).
+Distance $\dtrm{G}$ is the growth at time $t$.
+We denote by $d_\mathrm{G}$ the growth for goal map.
+Then we define
+\begin{equation}
+\label{eq:d_Gt}
+\dtrm{G} = t \cdot d_\mathrm{G}.
+\end{equation}
+To keep right angles of buildings, 
+we must have $\alpha \geq \sqrt{2}$. 
+We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
+smaller (more acute) than $83.6 \degree$.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Buffer_TwoKinds}
+	\caption{Buffering a polygon using different kinds of joins.}
+	\label{fig:Buffer_TwoKinds}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Buffer_MiterLimits}
+	\caption{}
+	\label{fig:Buffer_MiterLimits}
+\end{figure}
+
+\subsection{Simplifying grown buildings}
+\label{sec:Simplify}
+\citet{Damen2008} generalized buildings using morphological operators.
+A drawback of this method is that the directions of the buildings have to be 
+concerned.
+\citet{Meijers2016} simplified buildings 
+based on offset curves generated from straight skeletons.
+We use a method based on buffering to remove pits and spikes of buildings.
+Our method is slightly different than \citet{Meijers2016},
+but there is an available library \textsc{Clipper} \citep{Johnson2014} 
+for the operations.
+\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
+We first dilate the grown buildings to remove 
+pits, and then erode the results to remove spikes.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{RemovePitAndSpike}
+	\caption{Remove a pit by dilating and then remove a spike by eroding.
+		(a) a polygon with a pit and a spike;
+		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
+		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
+		(d) dilate the polygon in (c) with distance $d$ so that the result has 
+		the same size as the polygon in (a).
+	}
+	\label{fig:RemovePitAndSpike}
+\end{figure}
+
+At time $t$, we grow buildings with distance $\dtrm{G}$,
+dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
+erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
+and dilate back with distance $\dtrm{E}$.
+A problem we may have is that 
+a building may be broken by eroding
+(see \fig\ref{fig:ErosionBreak} for example).
+The reason is that 
+some parts of a building may be increased (by growing and dilating) 
+with distance $\dtrm{G}+\dtrm{D}$, 
+but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
+If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
+and the building is not thick enough, 
+the thin part may disappear.
+In order to avoid this problem, we require that
+\[
+\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
+\]
+which means
+\begin{equation}
+\label{eq:d_Dt}
+\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
+\end{equation}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{ErosionBreak}
+	\caption{Dilate the gray polygon, then erode the dilated polygon.
+		(a) Dilate and erode with distance $d_1$.
+		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
+		In (a) the result of dilation and erosion is the same as the original 
+		polygon, while in (b) the result consists of two parts.
+	}
+	\label{fig:ErosionBreak}
+\end{figure}
+
+We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
+any pits and spikes narrower than $l$ will be removed. 
+We set $l=0.3\,\mathrm{mm}$, 
+which was used as a length threshold by, for example, 
+\citet{Regnauld2001}.
+Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
+but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
+In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
+which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
+As a compromise, we use
+\begin{equation}
+\label{eq:d_Et}
+\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
+\end{equation}
+%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
+%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
+%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
+Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
+$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
+As a result, we should make sure that
+\begin{equation}
+\label{eq:S_g}
+M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
+\end{equation}
+
+We wish to remove ``bays'' 
+which have ``widths'' less than $r_\mathrm{h} = 2\sqrt{a_\mathrm{h}/\pi}$.
+Variable $a_\mathrm{h}$ is the least area for a hole to be presented on map.
+Following \citep{Chaudhry2008}, we set $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
+Variable $r_\mathrm{h}$ is the radius of such a hole 
+supposing that the hole is a circle.
+Sometimes, our $\dtrm{D}$ is not large enough to do so 
+because of the limitation from \eq\ref{eq:d_Dt}.
+We define
+\[
+\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
+\]
+
+After carrying out the buffering-based methods, 
+we simplify the grown buildings using Imai--Iri algorithm 
+\citep{ImaiIri1988}.
+This algorithm first finds all the valid shortcuts of a polyline.
+A shortcut is valid for a segment 
+if the distance between the segment and the shortcut is at most a specified 
+value
+(see \fig\ref{fig:ImaiIri_Shortcut}).
+We set the value also as $l$.
+That is, at time $t$, the threshold distance is
+\begin{equation}
+\label{eq:d_lt}
+d_{l,t}= l \cdot M_t.
+\end{equation}
+Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
+of a polyline to the end, using breadth-first search.
+The sequence of valid shortcuts is an approximation of the polyline, 
+and has the least number of line segments.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{ImaiIri_Shortcut}
+	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
+	\label{fig:ImaiIri_Shortcut}
+\end{figure}
+
+\todo[inline]{more details in the below paragraph?}
+We add two more constraints for a shortcut to be valid. 
+First, a shortcut must be completely inside the grown building.
+If a shortcut is outside,
+we are not able to arrive at the shortcut by growing.
+Second, a shortcut is not allowed to intersect the 
+boundary of the original building.
+If we allow this intersection, 
+we need to shrink the building instead of growing. 
+Of course, we do not want to shrink.
+
+We tried simplifying using 
+the Douglas--Peucker algorithm \citep{Douglas1973}, 
+but we hoped to remove more points. 
+We found that the Imai--Iri 
+algorithm fit our needs better.
 
@@
 \label{sec:Group}
-There are many ways to group buildings.
+%There are many ways to group buildings.
+%
+%Using MST to group buildings: \citet{Zhang2013, 
+%	Cetinkaya2015,Deng2017,Regnauld1996}
 
-Using MST to group buildings: \citet{Zhang2013, 
-	Cetinkaya2015,Deng2017,Regnauld1996}
-
-We group buildings based on their buffers
+Original buildings grow according to time $t$.
+We put the original building in the same group if 
+they grow to become too close.
+We group buildings based on buffering.
 (see \fig\ref{fig:RemoveBay} for example).
@@
 		(a) Original buildings.
-		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
-		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
-		(d) Dilate the polygons in (c) with distance 
-		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
+		(b) Dilate each original building with distance 
+		$\dtrm{G}+\dtrm{D}$.		
+		(c) Erode the dilated polygons with distance $\dtrm{D}$.
+		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
 		If two polygons in (d) intersect, 
-		the original buildings in (a) will be put in the same group 
+		the original buildings will be put in the same group 
 		because they will become too close at time $t$.
-		Until this step, there two groups according to (d), 
-		one consists of the single middle building and 
-		the other group consists of the surrounding $9$ buildings.
+		There two groups according to (d).
+		One consists of the single middle building and 
+		the surrounding $9$ buildings comprise the other group.
 		(e) The result of growing and merging at time $t$ 
@@
 We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.
-
-\subsection{Growing buildings based on buffering}
-\label{sec:Grow}
-We grow building based on buffering. 
-There are two typical ways of buffering polygons, i.e.,
-one with round joins and the other with miter joins 
-(see \fig\ref{fig:Buffer_TwoKinds}).
-As buildings are usually rectangles, 
-we choose the second way because it is 
-better at keeping the right angles.
-If an angle is acute, however, an excessively long \emph{spike} will be 
-produced.
-This spike may go across other buildings 
-(see \fig\ref{fig:Buffer_MiterLimits}a).
-To avoid this kind of interruptions, 
-we require that for an angle if a vertex of the 
-buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
-where $d_\mathrm{G}$ is the growing distance, 
-away from the original vertex, 
-a \emph{square} joining is applied
-(see \fig\ref{fig:Buffer_MiterLimits}b).
-To keep right angles of buildings, 
-we must have $\alpha \geq \sqrt{2}$. 
-We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
-smaller (more acute) than $83.6 \degree$.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics{Buffer_TwoKinds}
-	\caption{Buffering a polygon using different kinds of joins.}
-	\label{fig:Buffer_TwoKinds}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics{Buffer_MiterLimits}
-	\caption{}
-	\label{fig:Buffer_MiterLimits}
-\end{figure}
-
-We denote by $d_\mathrm{G}$ the total growth. The growth at time $t$ is
-\begin{equation}
-	\label{eq:d_Gt}
-	\dtrm{G} = t \cdot d_\mathrm{G}.
-\end{equation}
-
-\subsection{Simplifying grown buildings}
-\label{sec:Simplify}
-We use a buffering-based method, 
-similar to \citet{Damen2008,Meijers2016}, 
-to simplify our grown buildings. 
-We first dilate the grown buildings to remove 
-pits, and then erode the results to remove spikes
-(see \fig\ref{fig:RemovePitAndSpike}).
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{RemovePitAndSpike}
-	\caption{Remove a pit by dilating and then remove a spike by eroding.
-		(a) a polygon with a pit and a spike;
-		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
-		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
-		(d) dilate the polygon in (c) with distance $d$ so that the result has 
-		the same size as the polygon in (a).
-	}
-	\label{fig:RemovePitAndSpike}
-\end{figure}
-
-At time $t$, we grow buildings with distance $\dtrm{G}$,
-dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
-erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
-and dilate back with distance $\dtrm{E}$.
-A problem we may have is that we may break a building by eroding.
-The reason is that 
-some parts of a building may be increased (by growing and dilating) 
-with distance $\dtrm{G}+\dtrm{D}$, 
-but be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
-If  $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
-and a building is not thick enough, 
-the building may be broken into several parts
-(see \fig\ref{fig:ErosionBreak}).
-In order to avoid this problem, we require that
-\[
-\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
-\]
-which means
-\begin{equation}
-\label{eq:d_Dt}
-\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
-\end{equation}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{ErosionBreak}
-	\caption{Dilate the gray polygon, then erode the dilated polygon.
-		(a) Dilate and erode with distance $d_1$.
-		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
-		In (a) the result of dilation and erosion is the same as the original 
-		polygon, while in (b) the result consists of two parts.
-	}
-	\label{fig:ErosionBreak}
-\end{figure}
-
-We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
-(see \eq\ref{eq:d_epsilont}) so that
-any pits and spikes narrower than $l$ will be removed. 
-We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
-\citet{Regnauld2001,Li2004,Basaraner2008}.
-Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
-but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
-In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
-which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
-As a compromise, we use
-\begin{equation}
-\label{eq:d_Et}
-\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
-\end{equation}
-Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
-$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
-t \cdot \frac{l}{2} M_\mathrm{g} >0$.
-As a result, we should make sure that
-\begin{equation}
-\label{eq:S_g}
-M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
-\end{equation}
-
-We wish to remove ``bays'' which have ``widths'' less than $2\sqrt{a_h/\pi}$.
-\todo{why? more details}
-Usually, our $\dtrm{D}$ is not large enough to do so.
-We use the upper bound in \eq\ref{eq:d_Dt}, that is,
-\[
-\dtrm{D} = \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
-\]
-
-After carrying out the buffering-based methods, 
-we simplify the grown buildings using Imai--Iri algorithm 
-\citep{ImaiIri1988}.
-This algorithm first finds all the valid shortcuts of a polyline.
-A shortcut is valid for a segment 
-if the distance between the segment and the shortcut is at most a specified 
-value
-(see \fig\ref{fig:ImaiIri_Shortcut}).
-We set the value also as $l$.
-That is, at time $t$, the threshold distance is
-\begin{equation}
-\label{eq:d_lt}
-d_{l,t}= l \cdot M_t.
-\end{equation}
-Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
-of a polyline to the end, using breadth-first search.
-The sequence of valid shortcuts is an approximation of the polyline, 
-and has the least number of line segments.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{ImaiIri_Shortcut}
-	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
-	\label{fig:ImaiIri_Shortcut}
-\end{figure}
-
-\todo[inline]{more details in the below paragraph?}
-We add two more constraints for a shortcut to be valid. 
-First, a shortcut must be completely inside the grown building.
-If a shortcut is outside,
-we are not able to arrive at the shortcut by growing.
-Second, a shortcut is not allowed to intersect the 
-boundary of the original building.
-If we allow this intersection, 
-we need to shrink the building instead of growing. 
-Of course, we do not want to shrink.
-
-We tried simplifying using 
-the Douglas--Peucker algorithm \citep{Douglas1973}, 
-but we hoped to remove more points. 
-We found that the Imai--Iri 
-algorithm fit our needs better.
 

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial_revised_Guillaume.tex
revision of abstract and introduction
I revised the abstract in the main tex file, the introduction in the new
paperbody file, and added two references in the bib file.

--- 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
@@
 \begin{abstract}
-We propose a method to continuously 
-generalize buildings from a given start map to a smaller-scale goal map.
+To enable smooth zooming, we propose a method to continuously 
+generalize buildings from a given start map to a smaller-scale goal map, where there are only built-up area polygons instead of individual building polygons.
 For the sake of convenience, 
@@
 by introducing bridges.
-We grow bridged original buildings based on buffering 
+We grow (bridge) original buildings based on buffering 
 and simplify the grown buildings.
@@
 and, at the same time, are simplified.
-Second, right angles of buildings are preserved during growing. 
+Second, right angles of buildings are preserved during growing: the merged buildings still look like buildings. 
 Third, the distances between buildings are 
@@
 
-\input{PaperBody}
+\input{PaperBody_revised_Guillaume}
 

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody_revised_Guillaume.tex
revision of abstract and introduction
I revised the abstract in the main tex file, the introduction in the new
paperbody file, and added two references in the bib file.

--- 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 
-Digital maps such as Google Maps and OpenStreetMap 
+Digital multi-scale maps such as Google Maps and OpenStreetMap 
 support zooming by displaying maps at different levels. 
-This discrete strategy may results in sudden changes, which annoy users.
+This discrete strategy may results in sudden changes, which disturb user navigation.
 To provide better zooming experience, 
@@
 
-A way to realize continuous generalization is to use morphing.
+A way to achieve continuous generalization is to use morphing.
 Often, a start map and a goal map, 
@@
 From a point to its corresponding point,
-the straight-line trajectory is often used to interpolate.
+a straight-line trajectory is often used to interpolate.
 Using morphing, \citet{Peng2016_Admin} continuously generalized 
 administrative boundaries based on compatible triangulations.
+When the number of line features is different in the start and goal maps, a continuous selection is required and \citet{Chimani2014_Eat} proposed to generate a selection sequence applicable for road network.
+They removed one road at each step while keeping the remaining roads connected.
 
-Also aiming at continuous generalization,
-\citet{Danciger2009} grew polygons when a map was zoomed out. Their method 
-preserves polygons' topology, area-rations, and relative positions. 
-\citet{Chimani2014_Eat} generated a selection sequence for road network.
-They removed one road at each step while keeping the remaining roads connected.
-\citet{Peng2017_AStar} computed optimal aggregation sequences 
-for land-cover areas.
+These methods are interesting but only work on lines and our problem of building polygon interpolation cannot be achieved by similar morphings.
+Regarding the continuous generalization of polygon map features,
+\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their method 
+preserves polygons' topology, area-ratios, and relative positions.
+In the case where the goal map is an aggregated version of start landcover map, \citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover areas.
 
-Buildings are important elements on maps.
-Many methods have been proposed to generalize them.
+Buildings are important elements on maps, many methods have been proposed to generalize them but not necessarily in a continuous way.
 For example, \citet{haunertwolff2010} simplified a set of buildings 
@@
 One advantage is that their method preserves orientations of the edges.
-\citet{Chaudhry2008} identified the boundaries of urban settlement by
-calculating `citeness' based on buildings.
-\citet{Li2017_Building} morphed between two buildings at different scales.
-They managed to preserve the orthogonal characteristics of buildings.
 
@@
 buildings become smaller and the distances between buildings decrease.
-In order to make sure that the information of a map is easily perceived, 
-an objective proposed by \citet{Weibel1997}, 
-some building should be enlarged
-and buildings close to each other should be aggregated.
-Also, buildings should be simplified.
-We consider the three operations in our continuous generalization.
+So simplification is not the only necessary operation, and buildings can also be aggregated to legible enough \cite{Weibel1997}.
+Several methods were proposed to aggregate buildings while preserving the shape of buildings (right angles remain) \cite{Regnauld2001}, \cite{RegnauldRevell07}, \cite{Damen2008}.
+These algorithms can be used as inspirations to define a continuous transformation of buildings.
+
+Algorithms were also proposed to create built-up area polygons (that appear in our goal map) from individual building polygons (that appear in our start map).
+For instance, \citet{Chaudhry2008} identified the boundaries of urban settlement by calculating `citiness' based on buildings.
+But the method cannot be adapted to provide a continuous transformation from the buildings to the built-up area.
+
+Finally, some papers directly tackle the continuous transformation of buildings when scale is reduced. \citet{Li2017_Building} morphed between two buildings at different scales.
+They managed to preserve the orthogonal characteristics of buildings, but their algorithm cannot be used in our case as the goal map does not contain buildings anymore.
+\citet{Touya17b} proposed a progressive transformation of buildings into a built-up area, where buildings are progressively replaced by the shape of the block they belong to.
+However, this last algorithm is not continuous enough, as each iteration directly transforms a set of buildings in a block into a polygon that covers the whole block.
+So there is no existing solution for the continuous generalization of building polygons into built-up area polygons.
 

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished section of aggregating close buildings by introducing bridges

@@
 
-Our aggregation is based on growing and some of simplifying. 
-So we present the two operators before aggregating.
+Our grouping is based on growing, aggregating and some of simplifying. 
+So we present the three operators before grouping.
 
@@
 \label{sec:Grow}
-We grow building based on buffering. 
+We grow buildings based on buffering. 
 There are two typical ways of buffering a polygon, i.e.,
@@
 \end{figure}
+
+\subsection{Aggregating close buildings by introducing bridges}
+\label{sec:Merge}
+
+If a group of buildings will become too close at time $t$ because of growing,
+we aggregate the original buildings by introducing bridges, 
+then we grow the bridged building (see \fig\ref{fig:GrowAndBridge}).
+We show how to group buildings for time $t$ in \sect\ref{sec:Group}.
+No matter a bridge appears earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Aggregate original buildings in the same group by introducing 
+	bridges.
+		Then grow the bridged buildings.}
+	\label{fig:GrowAndBridge}
+\end{figure*}
+
+For each pair of buildings in the same group, 
+we find a nearest pair of points.
+We connect the buildings by adding a line segment bridging the nearest points.
+If we consider each building as a node and each line segment as an edge, 
+then we have a graph.
+Using Prim's algorithm \citep{Prim1957}, 
+we find a minimum spanning tree (MST) in the graph
+taking the lengths of the line segments as the weights.
+As a results, the line segments corresponding to the edges in the MST
+are used as bridges to aggregate the buildings.
 
@@
 We wish to remove ``bays'' 
-which have ``widths'' less than $r_\mathrm{h} = 2\sqrt{a_\mathrm{h}/\pi}$.
-Variable $a_\mathrm{h}$ is the least area for a hole to be presented on map.
-Following \citep{Chaudhry2008}, we set $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
-Variable $r_\mathrm{h}$ is the radius of such a hole 
-supposing that the hole is a circle.
+which have ``widths'' less than $2 r_\mathrm{h}$. 
+Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
+is the radius of a hole which is just large enough to be presented on map.
+Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
 Sometimes, our $\dtrm{D}$ is not large enough to do so 
@@
 
-After carrying out the buffering-based methods, 
-we simplify the grown buildings using Imai--Iri algorithm 
+After carrying out the dilation-erosion-dilation-based method, 
+we simplify the buildings using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
-This algorithm first finds all the valid shortcuts of a polyline.
+First, this algorithm finds all the valid shortcuts of a polyline.
 A shortcut is valid for a segment 
@@
 of a polyline to the end, using breadth-first search.
-The sequence of valid shortcuts is an approximation of the polyline, 
-and has the least number of line segments.
+The sequence of valid shortcuts is an approximation of the polyline 
+and has the least number of line segments, with error smaller than $d_{l,t}$.
 
@@
 
-\todo[inline]{more details in the below paragraph?}
 We add two more constraints for a shortcut to be valid. 
@@
 we are not able to arrive at the shortcut by growing.
-Second, a shortcut is not allowed to intersect the 
-boundary of the original building.
+Second, a shortcut is not allowed to intersect with the aggregated building.
 If we allow this intersection, 
-we need to shrink the building instead of growing. 
+the building will have to be shrunk. 
 Of course, we do not want to shrink.
+\todo{a shortcut is not allowed to intersect with the building at the 
+immediately previous step?}
 
@@
 \label{sec:Group}
-%There are many ways to group buildings.
-%
-%Using MST to group buildings: \citet{Zhang2013, 
-%	Cetinkaya2015,Deng2017,Regnauld1996}
+There are many research works about grouping buildings.
+\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
+However, our two needs, 
+the distances between buildings are always larger than a specified threshold 
+and small bays should be removed, 
+motivate us to develop our own grouping method.
 
 Original buildings grow according to time $t$.
-We put the original building in the same group if 
+We put the original buildings in the same group if 
 they grow to become too close.
 We group buildings based on buffering.
-(see \fig\ref{fig:RemoveBay} for example).
-We wish to remove some ``bays'' 
+The basic idea is that 
+we buffer the original buildings with distance $\dtrm{G}$
+and an additional distance $\dtrm{C}$.
+If two buffers overlap, 
+then the original buildings are put in the same group.
+
+%(see \fig\ref{fig:RemoveBay} for example).
+As stated in \sect\ref{sec:Simplify}, 
+we wish to remove ``bays'' 
 which have widths less than $2 \dtrm{D}$.
-A bay may appear after some buildings are merged by bridging
-(see for example \fig\ref{fig:RemoveBay}e).
-To remove such kind of bay,
+A bay may come from a complex original building,
+or from bridging some buildings.
+\fig\ref{fig:RemoveBay}e shows an example of the latter case.
+To remove a bay,
 we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
@@
 so we iteratively group until the number of groups does not decrease.
-The result of having removed a bay is the outer polygon of 
+For the buildings in \fig\ref{fig:RemoveBay}a,
+the final result of removing a bay is the outer polygon of 
 \fig\ref{fig:RemoveBay}h. 
 In comparison, the result is \fig\ref{fig:RemoveBay}e 
-if we do not remove a bay.
+if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
 Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
@@
 
-\subsection{Aggregating close buildings by introducing bridges}
-\label{sec:Merge}
-The distance between two buildings on a map should be larger than a threshold
-\citep{Regnauld2001,Li2004}.
-Following \citet{Basaraner2008,Stoter2009}, 
+Definition of $\dtrm{C}$
+
+The distance between two buildings on a map should be larger than a threshold.
+Following \citet{Stoter2009}, 
 we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
@@
 \end{equation}
-
-If a group of buildings become too close during growing,
-we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
-We will talk about where to add bridges in \sect\ref{sec:Goal}.
-No matter a bridge appear earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
-the same widths.
-This setting is achieved by following.
-We detect nearest points for each pair of buildings at time $t=0$ so that 
-we know where we should add bridges.
-At time $t$, we group buildings that are too close to each other,
-then we merge them by adding the precomputed bridges.
-For this merged building, we grow, simplify, and unite as described in 
-\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
-We may unite the processed merged building with several separate parts 
-because the group of buildings may be in several smaller groups
-in the immediately previous step.
-
-\todo[inline]{actually larger than $d_{\epsilon, t}$.}
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Merge buildings by introducing bridges when the buildings become 
-		too close.
-		Although the bridges appear at different time, 
-		their widths are the same (see the figure with $t=1$).}
-	\label{fig:GrowAndBridge}
-\end{figure*}
-
-For each pair of buildings in the same group, 
-we find the smallest distance between them.
-We connect the buildings by adding an edge from the nearest points.
-We find a minimum spanning tree of the buildings using Prim's algorithm 
-\citep{Prim1957}.
-We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.
 
@@
 \todo{example?}
+
+We may unite the processed merged building with several separate parts 
+because the group of buildings may be in several smaller groups
+in the immediately previous step.
 
@@
 	\includegraphics{Data}
-	\caption{scale.}
+	\caption{data.}
 	\label{fig:Data}

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added README.txt, which illustrates our figures were made by Ipe

@@
 
-After carrying out the dilation-erosion-dilation-based method, 
+After carrying out the dilation-erosion-dilation method, 
 we simplify the buildings using Imai--Iri algorithm 
@@
 and an additional distance $\dtrm{C}$.
+We will talk about how to define $\dtrm{C}$ later.
 If two buffers overlap, 
@@
 or from bridging some buildings.
-\fig\ref{fig:RemoveBay}e shows an example of the latter case.
+\fig\ref{fig:RemoveBay}e shows an example of the later case.
 To remove a bay,
@@
 
+The prob
 Definition of $\dtrm{C}$
@@
 For a group of buildings, we consider the area sum of all the buildings.
+
+Following \citet{Stoter2009} and Following \citet{Chaudhry2008}, 
+we set
 

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
improved our abstract and introduction a little bit
integrated Guillaume's abstract and introduction

@@
 \begin{abstract}
-We propose a method to continuously 
-generalize buildings from a given start map to a smaller-scale goal map.
+To enable smooth zooming, we propose a method to continuously 
+generalize buildings from a given start map to a smaller-scale goal map, where 
+there are only built-up area polygons instead of individual building polygons.
 For the sake of convenience, 
@@
 and, at the same time, are simplified.
-Second, right angles of buildings are preserved during growing. 
+Second, right angles of buildings are preserved during growing: the merged 
+buildings still look like buildings. 
 Third, the distances between buildings are 

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
integrated Guillaume's abstract and introduction

@@
 
-Digital maps such as Google Maps and OpenStreetMap 
+Digital multi-scale maps such as Google Maps and OpenStreetMap 
 support zooming by displaying maps at different levels. 
-This discrete strategy may results in sudden changes, which annoy users.
+This discrete strategy may results in sudden changes, which disturb user 
+navigation.
 To provide better zooming experience, 
@@
 From a point to its corresponding point,
-the straight-line trajectory is often used to interpolate.
+a straight-line trajectory is often used to interpolate.
 Using morphing, \citet{Peng2016_Admin} continuously generalized 
-administrative boundaries based on compatible triangulations.
+administrative boundaries based on compatible triangulations. When the number 
+of line features is different in the start and goal maps, a continuous 
+selection is required and \citet{Chimani2014_Eat} proposed to generate a 
+selection sequence applicable for road network.
+They removed one road at each step while keeping the remaining roads connected.
 
-Also aiming at continuous generalization,
-\citet{Danciger2009} grew polygons when a map was zoomed out. Their method 
-preserves polygons' topology, area-rations, and relative positions. 
-\citet{Chimani2014_Eat} generated a selection sequence for road network.
-They removed one road at each step while keeping the remaining roads connected.
-\citet{Peng2017_AStar} computed optimal aggregation sequences 
-for land-cover areas.
+These methods are interesting but only work on lines and our problem of 
+building polygon interpolation cannot be achieved by similar morphings. 
+Regarding the continuous generalization of polygon map features,
+\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their 
+method 
+preserves polygons' topology, area-ratios, and relative positions.  In the case 
+where the goal map is an aggregated version of start landcover map, 
+\citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
+areas.
 
-Buildings are important elements on maps.
-Many methods have been proposed to generalize them.
+Buildings are important elements on maps, many methods have been proposed to 
+generalize them but not necessarily in a continuous way.
 For example, \citet{haunertwolff2010} simplified a set of buildings 
@@
 One advantage is that their method preserves orientations of the edges.
-\citet{Chaudhry2008} identified the boundaries of urban settlement by
-calculating `citeness' based on buildings.
-\citet{Li2017_Building} morphed between two buildings at different scales.
-They managed to preserve the orthogonal characteristics of buildings.
 
 When users zoom out on digital maps, 
-buildings become smaller and the distances between buildings decrease. 
-In order to make sure that the information of a map is easily perceived, 
-an objective proposed by \citet{Weibel1997}, 
-some building should be enlarged
-and buildings close to each other should be aggregated.
-Also, buildings should be simplified.
-We consider the three operations in our continuous generalization.
+buildings become smaller and the distances between buildings decrease. So 
+simplification is not the only necessary operation, and buildings can also be 
+aggregated to legible enough \cite{Weibel1997}. Several methods were proposed 
+to aggregate buildings while preserving the shape of buildings (right angles 
+remain) \cite{Regnauld2001}, \cite{RegnauldRevell07}, \cite{Damen2008}. These 
+algorithms can be used as inspirations to define a continuous transformation of 
+buildings.
+
+Algorithms were also proposed to create built-up area polygons (that appear in 
+our goal map) from individual building polygons (that appear in our start map). 
+For instance, \citet{Chaudhry2008} identified the boundaries of urban 
+settlement by calculating `citiness' based on buildings. But the method cannot 
+be adapted to provide a continuous transformation from the buildings to the 
+built-up area.
+
+Finally, some papers directly tackle the continuous transformation of buildings 
+when scale is reduced. \citet{Li2017_Building} morphed between two buildings at 
+different scales.
+They managed to preserve the orthogonal characteristics of buildings, but their 
+algorithm cannot be used in our case as the goal map does not contain buildings 
+anymore. \citet{Touya17b} proposed a progressive transformation of buildings 
+into a built-up area, where buildings are progressively replaced by the shape 
+of the block they belong to. However, this last algorithm is not continuous 
+enough, as each iteration directly transforms a set of buildings in a block 
+into a polygon that covers the whole block. So there is no existing solution 
+for the continuous generalization of building polygons into built-up area 
+polygons.
 
@@
 
-The prob
-Definition of $\dtrm{C}$
-
+Now we show how to define distance $\dtrm{C}$, 
+which is used to detect closeness.
 The distance between two buildings on a map should be larger than a threshold.

### 2017-09-13 ContinuousGeneralizer/MorphingClass/CHelpFunc.cs
removed tiny edges after growing

@@ -81,7 +81,7 @@ namespace MorphingClass.CUtility
         //private static string _strPath = "C:\\MyWork\\DailyWork\\ContinuousGeneralisation\\ContinuousGeneralisation_Data\\AreaAggregation\\" + _strDataFolderName + "\\";
 
         //private static string _strDataFolderName = "France";
-        private static string _strDataFolderName = "France_FourTowns";
+        //private static string _strDataFolderName = "France_FourTowns";
         //private static string _strDataFolderName = "France_Part";
         //private static string _strDataFolderName = "France_FourBuildings";
         //private static string _strDataFolderName = "France_Smallpart";
@@ -95,7 +95,7 @@ namespace MorphingClass.CUtility
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Simplification";
         //private static string _strDataFolderName = "France_Presenting_RemoveBay";
 
-        //private static string _strDataFolderName = "France_Problematic";
+        private static string _strDataFolderName = "France_Problematic";
         //private static string _strDataFolderName = "France_Problematic2";
         //private static string _strDataFolderName = "France_WithOneHole";
         //private static string _strDataFolderName = "France_OneSquare";

### 2017-09-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
removed tiny edges after growing
added figures/NearestPoints.pdf

@@
 preserves polygons' topology, area-ratios, and relative positions.  In the case 
-where the goal map is an aggregated version of start landcover map, 
+where the goal map is an aggregated version of start land-cover map, 
 \citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
@@
 
-\subsection{Aggregating close buildings by introducing bridges}
+\subsection{Aggregating close buildings by adding bridges}
 \label{sec:Merge}
 
-If a group of buildings will become too close at time $t$ because of growing,
-we aggregate the original buildings by introducing bridges, 
-then we grow the bridged building (see \fig\ref{fig:GrowAndBridge}).
-We show how to group buildings for time $t$ in \sect\ref{sec:Group}.
-No matter a bridge appears earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
+We aggregate buildings if they become too close because of growing.
+Our basic idea is to add bridges between buildings
+(see for example \fig\ref{fig:GrowAndBridge}).
 
@@
 
-For each pair of buildings in the same group, 
-we find a nearest pair of points.
-We connect the buildings by adding a line segment bridging the nearest points.
+At time $t=1$, we know that 
+which buildings will finally be aggregated into the same built-up area
+(see \sect\ref{sec:Group}).
+We connect each pair of these buildings by adding a line segment linking the 
+nearest points.
 If we consider each building as a node and each line segment as an edge, 
@@
 Using Prim's algorithm \citep{Prim1957}, 
-we find a minimum spanning tree (MST) in the graph
+we find a minimum spanning tree (MST) in the graph,
 taking the lengths of the line segments as the weights.
 As a results, the line segments corresponding to the edges in the MST
-are used as bridges to aggregate the buildings.
+are used as bridges.
+At any time $t$, we pick some of the bridges to aggregate the buildings.
+Then we grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
+No matter a bridge appears earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+We do not introduce bridges according to nearest points at time $t$
+because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
+example).
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{NearestPoints}
+	\caption{The nearest points between a pair of buildings may change because 
+	of growing. 
+		The two squares and the two circles respectively mark
+		the nearest points before and after growing.
+	}
+	\label{fig:NearestPoints}
+\end{figure}
 
@@
 we buffer the original buildings with distance $\dtrm{G}$
-and an additional distance $\dtrm{C}$.
-We will talk about how to define $\dtrm{C}$ later.
+and an additional distance $\dtrm{C}$
+(We will talk about how to define $\dtrm{C}$ later).
 If two buffers overlap, 
 then the original buildings are put in the same group.
+
+Now we show how to define distance $\dtrm{C}$, 
+which is used to detect closeness.
+The distance between two buildings on a map should be larger than a threshold.
+Following \citet{Stoter2009}, 
+we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
+The real separation distance at time $t$ is
+\begin{equation}
+	\label{eq:d_epsilont}
+	d_{\epsilon, t} = \epsilon \cdot M_t.
+\end{equation}
 
@@
 \end{figure*}
-
-Now we show how to define distance $\dtrm{C}$, 
-which is used to detect closeness.
-The distance between two buildings on a map should be larger than a threshold.
-Following \citet{Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
-The real separation distance at time $t$ is
-\begin{equation}
-\label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot M_t.
-\end{equation}
 

### 2017-09-14 ContinuousGeneralizer/MorphingClass/CBldgGrow.cs

@@ -250,11 +250,12 @@ namespace MorphingClass.CGeneralizationMethods
 
                 var clipcpgEb = GetClipCpgEb(mergedCpgLt);
                 CSaveFeature.SaveCpgEb(clipperMethods.ScaleCpgEb(clipcpgEb, 1 / dblFclipper),
-    strSimplification + "_" + dblTargetScale + "k_ClipForm" + dblTargetEpsilon + "m", intGreen: 255);
+    strSimplification + "_" + dblTargetScale + "k_ClipForm" + dblTargetEpsilon + "m", 
+    pesriSimpleFillStyle: esriSimpleFillStyle.esriSFSHollow, blnVisible: false);
 
-    //            CSaveFeature.SaveCpgEb(clipperMethods.ScaleCpgLt(mergedCpgLt, 1 / dblFclipper),
-    //strSimplification + "_" + dblTargetScale + "k_mergedcpg" + dblTargetEpsilon + "m_" +
-    //CHelpFunc.GetTimeStampWithPrefix(), intGreen: 255);
+                CSaveFeature.SaveCpgEb(clipperMethods.ScaleCpgEb(mergedCpgLt, 1 / dblFclipper),
+    strSimplification + "_" + dblTargetScale + "k_mergedcpg" + dblTargetEpsilon + "m_",
+    pesriSimpleFillStyle: esriSimpleFillStyle.esriSFSHollow, blnVisible: false);
 
                 #region Geoprocessor Samples
                 //// Initialize the geoprocessor. 

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved our method

@@
 are used as bridges.
-At any time $t$, we pick some of the bridges to aggregate the buildings.
-Then we grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
+A bridge is then picked to aggregate two buildings at time $t$ 
+if they become too close.
+We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
 No matter a bridge appears earlier or later, 
@@
 which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
-As a compromise, we use
+As a compromise, we set erosion distance
 \begin{equation}
@@
 		because they will become too close at time $t$.
-		There two groups according to (d).
+		There are two groups according to (d).
 		One consists of the single middle building and 

### 2017-09-15 ContinuousGeneralizer/MorphingClass/CUtility/CSaveFeature.cs

@@ -41,17 +41,20 @@ namespace MorphingClass.CUtility
         /// <remarks>If I have time, I will put the parameters of colors and width in one parameter!</remarks>
         public CSaveFeature(esriGeometryType pesriGeometryType, string pstrLayerName,
 List<string> pstrFieldNameLt = null, List<esriFieldType> pesriFieldTypeLt = null,
-int fintRed = 0, int fintGreen = 0, int fintBlue = 0, double dblWidth = 1,
+int intRed = 0, int intGreen = 0, int intBlue = 0, double dblWidth = 1,
+int intOutlineRed = _intColor, int intOutlineGreen = _intColor, int intOutlineBlue = _intColor,
 esriSimpleFillStyle pesriSimpleFillStyle = esriSimpleFillStyle.esriSFSSolid,
 string strSymbolLayerPath = null, bool blnVisible = true)
         {
             this.pFeatureLayer = CreateFeatureLayer(pesriGeometryType, pstrLayerName, pstrFieldNameLt, pesriFieldTypeLt,
-                fintRed, fintGreen, fintBlue, dblWidth, pesriSimpleFillStyle, strSymbolLayerPath, blnVisible);
+                intRed, intGreen, intBlue, dblWidth, 
+                intOutlineRed, intOutlineGreen, intOutlineBlue, pesriSimpleFillStyle, strSymbolLayerPath, blnVisible);
         }
 
         private IFeatureLayer CreateFeatureLayer(esriGeometryType pesriGeometryType, string pstrLayerName,
 List<string> pstrFieldNameLt = null, List<esriFieldType> pesriFieldTypeLt = null,
-int fintRed = 0, int fintGreen = 0, int fintBlue = 0, double dblWidth = 1,
+int intRed = _intColor, int intGreen = _intColor, int intBlue = _intColor, double dblWidth = 1,
+int intOutlineRed = _intColor, int intOutlineGreen = _intColor, int intOutlineBlue = _intColor,
 esriSimpleFillStyle pesriSimpleFillStyle = esriSimpleFillStyle.esriSFSSolid,
 string strSymbolLayerPath = null, bool blnVisible = true)
         {
@@ -66,8 +69,8 @@ string strSymbolLayerPath = null, bool blnVisible = true)
             pFLayer.Name = pFeatureClass.AliasName;
             pFLayer.SpatialReference = pm_mapControl.SpatialReference;
 
[…]

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/CloseDetect.pdf

@@
 nearest points.
-If we consider each building as a node and each line segment as an edge, 
+These line segments may cross each other or even intersect buildings.
+To make the topology simple, 
+we only select some of the line segments as bridges.  
+We consider each building as a node and each line segment as an edge, 
 then we have a graph.
@@
 As a results, the line segments corresponding to the edges in the MST
-are used as bridges.
-A bridge is then picked to aggregate two buildings at time $t$ 
-if they become too close.
+are identified as bridges.
+
+At any time $t$, some of the identified bridges are picked to aggregate 
+buildings 
+which grow to become too close.
+The buildings and the bridges already comprise some MSTs.
 We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
@@
 then the original buildings are put in the same group.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{CloseDetect}
+	\caption{bla.}
+	\label{fig:CloseDetect}
+\end{figure}
 

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on section of grouping buildings

@@
 we buffer the original buildings with distance $\dtrm{G}$
-and an additional distance $\dtrm{C}$
-(We will talk about how to define $\dtrm{C}$ later).
+and an additional distance $d_{\epsilon, t}/2$
+(the distance between two buildings should be at least $d_{\epsilon, t}$).
 If two buffers overlap, 
 then the original buildings are put in the same group.
+However, as some parts of a building grow faster than other parts, 
+this basic idea may cause problems.
+An example is shown in \fig\ref{fig:CloseDetect}c and~d.
+In \fig\ref{fig:CloseDetect}d, 
+the buffers of building $p$ and the buffer of building $q$ overlap each other, 
+but the two buffers do not overlap with the buffer of building $r$.
 
@@
 	\includegraphics[]{CloseDetect}
-	\caption{bla.}
+	\caption{Group buildings based on buffering.
+		(a) original buildings.
+		(b) bridges detected to aggregate the three buildings.
+		(c) grow the original buildings with distance $\dtrm{G}$.
+		(d) buffer the grown buildings in (c) 
+		with distance $d_{\epsilon, t} /2$ using round joins.
+		(e) buffer the original buildings 
+		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
+		using round joins, where $\alpha=2$.
+		(f) according to the buffer in (e), 
+		we put the three original buildings in the same group.
+		We aggregate the original buildings by adding the two bridges 
+		and grow the aggregated building with distance $\dtrm{G}$.
+	}
 	\label{fig:CloseDetect}

### 2017-09-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
adjusted the structure of section Methodology

--- 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 
-\subsection{Growing buildings based on buffering}
+\subsection{Growing buildings by buffering}
 \label{sec:Grow}
@@
 
-\subsection{Aggregating close buildings by adding bridges}
-\label{sec:Merge}
-
-We aggregate buildings if they become too close because of growing.
-Our basic idea is to add bridges between buildings
-(see for example \fig\ref{fig:GrowAndBridge}).
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Aggregate original buildings in the same group by introducing 
-		bridges.
-		Then grow the bridged buildings.}
-	\label{fig:GrowAndBridge}
-\end{figure*}
-
-At time $t=1$, we know that 
-which buildings will finally be aggregated into the same built-up area
-(see \sect\ref{sec:Group}).
-We connect each pair of these buildings by adding a line segment linking the 
-nearest points.
-These line segments may cross each other or even intersect buildings.
-To make the topology simple, 
-we only select some of the line segments as bridges.  
-We consider each building as a node and each line segment as an edge, 
-then we have a graph.
-Using Prim's algorithm \citep{Prim1957}, 
-we find a minimum spanning tree (MST) in the graph,
-taking the lengths of the line segments as the weights.
-As a results, the line segments corresponding to the edges in the MST
-are identified as bridges.
-
-At any time $t$, some of the identified bridges are picked to aggregate 
-buildings 
-which grow to become too close.
-The buildings and the bridges already comprise some MSTs.
-We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
-No matter a bridge appears earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-We do not introduce bridges according to nearest points at time $t$
-because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
-example).
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{NearestPoints}
-	\caption{The nearest points between a pair of buildings may change because 
-	of growing. 
-		The two squares and the two circles respectively mark
-		the nearest points before and after growing.
-	}
-	\label{fig:NearestPoints}
-\end{figure}
-
-\subsection{Simplifying grown buildings}
-\label{sec:Simplify}
+\subsection{Simplifying grown buildings based on dilation and erosion}
+\label{sec:DilationErosion}
 \citet{Damen2008} generalized buildings using morphological operators.
@@
 
-After carrying out the dilation-erosion-dilation method, 
-we simplify the buildings using Imai--Iri algorithm 
+\subsection{Iteratively aggregating close buildings by adding bridges}
+\label{sec:Aggregate}
+
+We aggregate buildings if they become too close because of growing.
+Our basic idea is to add bridges between buildings
+(see for example \fig\ref{fig:GrowAndBridge}).
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Aggregate original buildings in the same group by introducing 
+		bridges.
+		Then grow the bridged buildings.}
+	\label{fig:GrowAndBridge}
+\end{figure*}
+
+We grow each original building and, as illustrated in 
+\sect\ref{sec:DilationErosion}, simplify the grown building.
+If some buildings become too close after these operations,
+we aggregate them by adding bridges.
+Following \citet{Stoter2009}, 
+we define that two buildings are too close if their distance is less than
+$\epsilon= 0.2\,\mathrm{mm}$ on map.
+The real separation threshold at time $t$ is
+\begin{equation}
+\label{eq:d_epsilont}
+d_{\epsilon, t} = \epsilon \cdot M_t.
+\end{equation}
+
+Our way of detecting close buildings is simple.
+We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins.
+We merge the buffers that overlap each other.
+The buildings intersect with the same merged buffer 
+are identified as a group of close buildings.
+According to the group of buildings, 
+we find the group of corresponding original buildings.
+For each pair of the original buildings in a group,
+we connect them by adding a line segment linking the nearest points.
+The line segments for the group of original buildings may cross each other or 
+even intersect buildings.
+To make the topology simple, 
+we only select some of the line segments as \emph{bridges}.  
+We consider each building as a node and each line segment as an edge, 
+then we have a graph.
+Using Prim's algorithm \citep{Prim1957}, 
+we find a minimum spanning tree (MST) in the graph,
+taking the lengths of the line segments as the weights.
+As a results, the line segments corresponding to the edges in the MST
+are identified as bridges.
+We aggregate the group of original buildings by adding these bridges.
+
+Notice that after growing the additional bridges may be too close to buildings 
+from another group.
+We iteratively aggregate buildings.
+This time we grow the original buildings with bridges.
+Similar to what we do before, we aggregate buildings by introducing bridges.
+We stop this iteration until the number of group does not decrease anymore.
+
+%At any time $t$, some of the bridges are picked to aggregate buildings 
+%which grow to become too close.
+%The buildings and the bridges already comprise some MSTs.
+
+%
+%Original buildings grow according to time $t$.
+%We put the original buildings in the same group if 
+%they grow so that their distance is less than $d_{\epsilon, t}$.
+%Following \citet{Stoter2009}, 
+%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
+%The real separation threshold at time $t$ is
+%\begin{equation}
+%\label{eq:d_epsilont2}
+%d_{\epsilon, t} = \epsilon \cdot M_t.
+%\end{equation}
+%We group buildings based on buffering.
+%The basic idea is that 
+%we buffer the original buildings with distance $\dtrm{G}$
+%and an additional distance $d_{\epsilon, t}/2$
+%(the distance between two buildings should be at least $d_{\epsilon, t}$).
+%If two buffers overlap, 
+%then the original buildings are put in the same group.
+%However, as some parts of a building grow faster than other parts, 
+%this basic idea may cause problems.
+%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
+%In \fig\ref{fig:CloseDetect}d, 
+%the buffers of buildings $p$ and $q$ overlap each other.
+%So we should aggregate buildings $p$ and $q$ at time $t$
+%because they will grow to become too close.
+%According to the bridges in \fig\ref{fig:CloseDetect}b, 
+%buildings $p$ and $q$ should be aggregated via building $r$.
+%Unfortunately, neither $p$ or $q$ will be too close to $r$.
+%As we use bridges to aggregate buildings 
+%(see \sect\ref{sec:Aggregate}),
+%we are not able to aggregate buildings $p$ and $q$. 
+%To avoid this situation, 
+%we buffer original buildings with distance
+%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
+%This buffering guarantees 
+%that every part of a building grows with the same speed.
+%If the buffers of two buildings overlap with each other,
+%then the two buildings are surely aggregated into one.
+%Using this buffering, in most of cases 
+%two buildings are aggregated as soon as 
+%their separation distance is less than 
+%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
+%The advantage is that we guarantee that 
+%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
+%aggregated via bridges.
+%
+%\begin{figure}[tb]
+%	\centering
+%	\includegraphics[]{NearestPoints}
+%	\caption{The nearest points between a pair of buildings may change because 
+%		of growing. 
+%		The two squares and the two circles respectively mark
+%		the nearest points before and after growing.
+%	}
+%	\label{fig:NearestPoints}
+%\end{figure}
+
+\subsection{Simplifying buildings using Imai--Iri algorithm}
+\label{sec:ImaiIri}
+
+We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
+No matter a bridge appears earlier or later, 
+it has width $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+
+We simplify the buildings using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
@@
 
-\subsection{Grouping buildings based on buffering}
-\label{sec:Group}
-There are many research works about grouping buildings.
-\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
-However, our two needs, 
-the distances between buildings are always larger than a specified threshold 
-and small bays should be removed, 
-motivate us to develop our own grouping method.
+%\subsection{Grouping buildings based on buffering}
+%\label{sec:Group}
+%There are many research works about grouping buildings.
+%\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
+%However, our two needs, 
+%the distances between buildings are always larger than a specified threshold 
+%and small bays should be removed, 
+%motivate us to develop our own grouping method.
+%
+%Original buildings grow according to time $t$.
+%We put the original buildings in the same group if 
+%they grow so that their distance is less than $d_{\epsilon, t}$.
+%Following \citet{Stoter2009}, 
+%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
+%The real separation threshold at time $t$ is
+%%\begin{equation}
+%%\label{eq:d_epsilont}
+%%d_{\epsilon, t} = \epsilon \cdot M_t.
+%%\end{equation}
+%We group buildings based on buffering.
+%The basic idea is that 
+%we buffer the original buildings with distance $\dtrm{G}$
+%and an additional distance $d_{\epsilon, t}/2$
+%(the distance between two buildings should be at least $d_{\epsilon, t}$).
+%If two buffers overlap, 
+%then the original buildings are put in the same group.
+%However, as some parts of a building grow faster than other parts, 
+%this basic idea may cause problems.
+%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
+%In \fig\ref{fig:CloseDetect}d, 
+%the buffers of buildings $p$ and $q$ overlap each other.
+%So we should aggregate buildings $p$ and $q$ at time $t$
+%because they will grow to become too close.
+%According to the bridges in \fig\ref{fig:CloseDetect}b, 
+%buildings $p$ and $q$ should be aggregated via building $r$.
+%Unfortunately, neither $p$ or $q$ will be too close to $r$.
+%As we use bridges to aggregate buildings 
+%(see \sect\ref{sec:Aggregate}),
+%we are not able to aggregate buildings $p$ and $q$. 
+%To avoid this situation, 
+%we buffer original buildings with distance
+%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
+%This buffering guarantees 
+%that every part of a building grows with the same speed.
+%If the buffers of two buildings overlap with each other,
+%then the two buildings are surely aggregated into one.
+%Using this buffering, in most of cases 
+%two buildings are aggregated as soon as 
+%their separation distance is less than 
+%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
+%The advantage is that we guarantee that 
+%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
+%aggregated via bridges.
+%
+%\begin{figure}[tb]
+%	\centering
+%	\includegraphics[]{CloseDetect}
+%	\caption{Group buildings based on buffering.
+%		(a) original buildings.
+%		(b) bridges detected to aggregate the three buildings.
+%		(c) grow the original buildings with distance $\dtrm{G}$.
+%		(d) buffer the grown buildings in (c) 
+%		with distance $d_{\epsilon, t} /2$ using round joins.
+%		(e) buffer the original buildings 
+%		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
+%		using round joins, where $\alpha=1.5$
+%		(see \sect\ref{sec:Grow}).
+%		(f) according to the buffer in (e), 
+%		we put the three original buildings in the same group.
+%		We aggregate the original buildings by adding the two bridges 
+%		and grow the aggregated building with distance $\dtrm{G}$.
+%	}
+%	\label{fig:CloseDetect}
+%\end{figure}
 
-Original buildings grow according to time $t$.
-We put the original buildings in the same group if 
-they grow to become too close.
-We group buildings based on buffering.
-The basic idea is that 
-we buffer the original buildings with distance $\dtrm{G}$
-and an additional distance $\dtrm{C}$
-(We will talk about how to define $\dtrm{C}$ later).
-If two buffers overlap, 
-then the original buildings are put in the same group.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{CloseDetect}
-	\caption{bla.}
-	\label{fig:CloseDetect}
-\end{figure}
-
-Now we show how to define distance $\dtrm{C}$, 
-which is used to detect closeness.
-The distance between two buildings on a map should be larger than a threshold.
-Following \citet{Stoter2009}, 
-we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
-The real separation distance at time $t$ is
-\begin{equation}
-	\label{eq:d_epsilont}
-	d_{\epsilon, t} = \epsilon \cdot M_t.
-\end{equation}
-
-%(see \fig\ref{fig:RemoveBay} for example).
-As stated in \sect\ref{sec:Simplify}, 
-we wish to remove ``bays'' 
-which have widths less than $2 \dtrm{D}$.
-A bay may come from a complex original building,
-or from bridging some buildings.
-\fig\ref{fig:RemoveBay}e shows an example of the later case.
-To remove a bay,
-we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
-and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
-with distance $\dtrm{D}$.
-There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
-so we iteratively group until the number of groups does not decrease.
-For the buildings in \fig\ref{fig:RemoveBay}a,
-the final result of removing a bay is the outer polygon of 
-\fig\ref{fig:RemoveBay}h. 
-In comparison, the result is \fig\ref{fig:RemoveBay}e 
-if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
-Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
-kind of bay and will be removed by overgrowing.
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{RemoveBay}
-	\caption{Group buildings iteratively.
-		(a) Original buildings.
-		(b) Dilate each original building with distance 
-		$\dtrm{G}+\dtrm{D}$.		
-		(c) Erode the dilated polygons with distance $\dtrm{D}$.
-		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
-		If two polygons in (d) intersect, 
-		the original buildings will be put in the same group 
-		because they will become too close at time $t$.
-		There are two groups according to (d).
-		One consists of the single middle building and 
-		the surrounding $9$ buildings comprise the other group.
-		(e) The result of growing and merging at time $t$ 
-		if we use $\dtrm{D}=0$.
-		The process of (f), (g), and (h) is similar to 
-		that of (b), (c), and (d).		
-		The difference is that 
-		instead of applying the operators to each single building, 
-		we do that for the buildings in the same group.
-		In (f), we manage to remove the bay in (e) by additionally dilating 
-		with distance $\dtrm{D}$.
-		There is only one group left according to (h).
-		We iteratively group buildings in this way until the number of groups 
-		does not decrease.
-	}
-	%in this example, we used _dblTotalGrow *= 5;
-	\label{fig:RemoveBay}
-\end{figure*}
+%
+%As stated in \sect\ref{sec:DilationErosion}, 
+%we wish to remove ``bays'' 
+%which have widths less than $2 \dtrm{D}$.
+%A bay may come from a complex original building,
+%or from bridging some buildings.
+%\fig\ref{fig:RemoveBay}e shows an example of the later case.
+%To remove a bay,
+%we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
+%and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
+%with distance $\dtrm{D}$.
+%There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
+%so we iteratively group until the number of groups does not decrease.
+%For the buildings in \fig\ref{fig:RemoveBay}a,
+%the final result of removing a bay is the outer polygon of 
+%\fig\ref{fig:RemoveBay}h. 
+%In comparison, the result is \fig\ref{fig:RemoveBay}e 
+%if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
+%Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
+%kind of bay and will be removed by overgrowing.
+%
+%
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics[draft=false]{RemoveBay}
+%	\caption{Group buildings iteratively.
+%		(a) Original buildings.
+%		(b) Dilate each original building with distance 
+%		$\dtrm{G}+\dtrm{D}$.		
+%		(c) Erode the dilated polygons with distance $\dtrm{D}$.
+%		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
+%		If two polygons in (d) intersect, 
+%		the original buildings will be put in the same group 
+%		because they will become too close at time $t$.
+%		There are two groups according to (d).
+%		One consists of the single middle building and 
+%		the surrounding $9$ buildings comprise the other group.
+%		(e) The result of growing and merging at time $t$ 
+%		if we use $\dtrm{D}=0$.
+%		The process of (f), (g), and (h) is similar to 
+%		that of (b), (c), and (d).		
+%		The difference is that 
+%		instead of applying the operators to each single building, 
+%		we do that for the buildings in the same group.
+%		In (f), we manage to remove the bay in (e) by additionally dilating 
+%		with distance $\dtrm{D}$.
+%		There is only one group left according to (h).
+%		We iteratively group buildings in this way until the number of groups 
+%		does not decrease.
+%	}
+%	%in this example, we used _dblTotalGrow *= 5;
+%	\label{fig:RemoveBay}
+%\end{figure*}
 
@@
 We group (see \sect\ref{sec:Group}) 
-and merge (see \sect\ref{sec:Merge}) buildings on start map.
+and merge (see \sect\ref{sec:Aggregate}) buildings on start map.
 Then we grow (see \sect\ref{sec:Grow}) 
-and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
+and simplify (see \sect\ref{sec:DilationErosion}) the merged buildings.
 See for example \fig\ref{fig:Buffer_MiterLimits}, 

### 2017-09-16 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -313,37 +313,41 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
         }
 
 
-        public static List<List<CPolygon>> MergeGroupedCpgs(List<CPolygon> cpglt, List<CValPair<List<CPolygon>, List<CptEdgeDis>>> groupedcpgCptEdgeDisltlt,
+        public static List<List<CPolygon>> MergeGroupedCpgs(List<CPolygon> cpglt,
+List<CValPair<List<CPolygon>, List<CptEdgeDis>>> groupedcpgCptEdgeDisltlt,
 double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "Miter", double dblMiterLimit = 2)
         {
             //double dblDisOverlap = Math.Sqrt(5) * dblEpsilon / 2;
             double dblDisOverlap = dblEpsilon / 2;
 
 
-            int intGroupCount = 0;
+            //int intGroupCount = 0;
             int intRound = 0;
 
             //var alloverdilationPaths = new Paths();
-            //var allbackpaths = new Paths();
+            var allbackpaths = new Paths();
             var alloriginalPaths = new Paths();
             //var alloverlapGrownPaths = new Paths();
             //var allUnionPaths = new Paths();
             foreach (var groupedcpgCptEdgeDislt in groupedcpgCptEdgeDisltlt)
             {
-                //var groupedoriginalpaths = new Paths(groupedcpgCptEdgeDislt.val1.Count+ groupedcpgCptEdgeDislt.val2.Count);
+                var groupedoriginalpaths = new Paths(groupedcpgCptEdgeDislt.val1.Count + groupedcpgCptEdgeDislt.val2.Count);
                 foreach (var cpg in groupedcpgCptEdgeDislt.val1)
                 {
-                    alloriginalPaths.AddRange(cpg.GetAllPaths());
+                    groupedoriginalpaths.AddRange(cpg.GetAllPaths());
                 }
                 foreach (var cptEdgeDis in groupedcpgCptEdgeDislt.val2)
                 {
-                    alloriginalPaths.Add(GeneratePathByCEdge(cptEdgeDis.ConnectCEdge));
+                    groupedoriginalpaths.Add(GeneratePathByCEdge(cptEdgeDis.ConnectCEdge));
                 }
-
[…]

### 2017-09-17 ContinuousGeneralizer/MorphingClass/CGeometry/CEdge.cs
added figures/BridgeMoreBuilding.pdf

@@ -367,6 +367,8 @@ namespace MorphingClass.CGeometry
             }
         }
 
+
+
         public bool SetSlope()
         {
             this.dblIncrX = _ToCpt.X - _FrCpt.X;

### 2017-09-17 ContinuousGeneralizer/MorphingClass/CGeometry/CPolygon.cs

@@ -61,7 +61,7 @@ namespace MorphingClass.CGeometry
         public List<CPolygon> SubCpgLt { get; set; }
         public List<CptEdgeDis> BridgeCptEdgeDisLt { get; set; }
         
-        public Dictionary<CValPairIncr<CPolygon>, CptEdgeDis> BridgeCpipeDt { get; set; }
+        //public Dictionary<CValPairIncr<CPolygon>, CptEdgeDis> BridgeCpipeDt { get; set; }
 
         //public CPolygon AssigningFace { get; set; }
         //public List<CPolygon> AssignedFaceLt { get; set; }

### 2017-09-17 ContinuousGeneralizer/MorphingClass/CHelpFunc.cs

@@ -81,7 +81,7 @@ namespace MorphingClass.CUtility
         //private static string _strPath = "C:\\MyWork\\DailyWork\\ContinuousGeneralisation\\ContinuousGeneralisation_Data\\AreaAggregation\\" + _strDataFolderName + "\\";
 
         //private static string _strDataFolderName = "France";
-        private static string _strDataFolderName = "France_FourTowns";
+        //private static string _strDataFolderName = "France_FourTowns";
         //private static string _strDataFolderName = "France_Part";
         //private static string _strDataFolderName = "France_FourBuildings";
         //private static string _strDataFolderName = "France_Smallpart";
@@ -95,7 +95,8 @@ namespace MorphingClass.CUtility
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Simplification";
         //private static string _strDataFolderName = "France_Presenting_RemoveBay";
         //private static string _strDataFolderName = "France_Presenting_Grouping";
-
+        private static string _strDataFolderName = "France_Presenting_BridgeMoreBuilding";
+        
         //private static string _strDataFolderName = "France_Problematic";
         //private static string _strDataFolderName = "France_Problematic2";
         //private static string _strDataFolderName = "France_WithOneHole";

### 2017-09-17 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -31,8 +31,8 @@ namespace MorphingClass.CUtility
             //Console.WriteLine("dblMiterLimit = " + dblMiterLimit);
 
             //keep in mind that the first point and the last point of a output path are not identical
-            //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon            
-            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit, 0.25 * CConstants.dblFclipper);
+            //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon and a CPolygon           
+            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit, 0.1 * CConstants.dblFclipper);
             switch (strBufferStyle)
             {
                 case "Miter":
@@ -64,7 +64,7 @@ namespace MorphingClass.CUtility
 
             //keep in mind that the first point and the last point of a path are not identical
             //the direction of a path of outcome is counter-clockwise, whereas it is clockwise for a IPolygon
-            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit, 0.25 * CConstants.dblFclipper);
+            ClipperOffset pClipperOffset = new ClipperOffset(dblMiterLimit, 0.1 * CConstants.dblFclipper);
             switch (strBufferStyle)
             {
                 case "Miter":
@@ -324,7 +324,8 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
             //int intGroupCount = 0;
             int intRound = 0;
 
-            //var alloverdilationPaths = new Paths();
+            var alloverdilationPaths = new Paths();
+            var allersionPaths = new Paths();
             var allbackpaths = new Paths();
             var alloriginalPaths = new Paths();
             //var alloverlapGrownPaths = new Paths();
@@ -338,7 +339,7 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
                 }
                 foreach (var cptEdgeDis in groupedcpgCptEdgeDislt.val2)
                 {
[…]

### 2017-09-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/BridgeMoreBuilding.pdf
basically finished section of methodology

@@
 
-Notice that after growing the additional bridges may be too close to buildings 
-from another group.
-We iteratively aggregate buildings.
-This time we grow the original buildings with bridges.
-Similar to what we do before, we aggregate buildings by introducing bridges.
-We stop this iteration until the number of group does not decrease anymore.
+Aggregated buildings may become too close after growing because of bridges.
+\fig\ref{fig:BridgeMoreBuilding} shows such an example.
+We grow and buffer buildings $p$, $q$, and~$r$.
+As the buffers of $q$ and~$r$ overlap with each other
+(see \fig\ref{fig:BridgeMoreBuilding}c),
+we aggregated buildings $q$ and~$r$ by adding a bridge.
+There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
+Because of the bridge, when we grow and buffer the buildings in 
+\fig\ref{fig:BridgeMoreBuilding}d, 
+the buffer of building $p$ overlap with the buffer of the bridged $q$ and $r$
+(see \fig\ref{fig:BridgeMoreBuilding}f).
+We aggregate building $p$ with bridged $q$ and $r$
+(see \fig\ref{fig:BridgeMoreBuilding}g).
+There is one building left in \fig\ref{fig:BridgeMoreBuilding}g.
+Then we grow and buffer again.
+There is one building left after this process.
+The number of buildings does not decrease comparing to last process.
+The iteration stops.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[draft=false]{BridgeMoreBuilding}
+	\caption{Iteratively aggregating close buildings by adding bridges.
+		(a) original buildings $p$, $q$, and~$r$.
+		(b) grow the original buildings with distance $\dtrm{G}$.
+		(c) buffer the grown buildings with distance $d_{\epsilon,t}/2$ using 
+		round joins.
+		(d) aggregate buildings $q$ and~$r$ by adding a bridge,
+		as their buffer overlap with each other in (c).
+		(e) grow the buildings in (d) with distance $\dtrm{G}$.
+		(f) buffer the grown buildings in (e) with distance $d_{\epsilon,t}/2$ 
+		using round joins.
+		(g) aggregate buildings $p$, $q$ and~$r$ by adding bridges.
+		(h) grow the buildings in (g) with distance $\dtrm{G}$.
+		(i) buffer the grown buildings in (h) with distance $d_{\epsilon,t}/2$ 
+		using round joins.
+	}
+	\label{fig:BridgeMoreBuilding}
+\end{figure}
 
@@
 To generate the goal forms of buildings, we set time $t=1$.
-We group (see \sect\ref{sec:Group}) 
-and merge (see \sect\ref{sec:Aggregate}) buildings on start map.
+We aggregate original buildings (see \sect\ref{sec:Aggregate}).
 Then we grow (see \sect\ref{sec:Grow}) 
-and simplify (see \sect\ref{sec:DilationErosion}) the merged buildings.
-See for example \fig\ref{fig:Buffer_MiterLimits}, 
-the building at time $t=1$ is the goal form of the three buildings of $t=0$.
+and simplify 
+(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
+See for example \fig\ref{fig:GrowAndBridge}, 
+the building at time $t=1$ is the goal form of the three original buildings of.
 
@@
 To guarantee the non-exceeding, 
-we clip the building by the goal form 
+we clip the building using the goal form 
 and remove the parts outside.
-\todo{example?}
 

### 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
polished section of methodology

@@
 there are only built-up area polygons instead of individual building polygons.
-For the sake of convenience, 
-we name the buildings on the start map \emph{original buildings}.
+We name the buildings on the start map \emph{original buildings}.
 %
 For an intermediate scale, 
-we aggregate the original buildings that will be too close 
-by introducing bridges.
+we aggregate the original buildings that will become too close 
+by adding bridges.
 We grow (bridge) original buildings based on buffering 

### 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished section of methodology

@@
 
-We find buildings which will be too close at time $t$
-and aggregate the buildings in the same group by introducing bridges.
+We find original buildings which will grow to become too close at time $t$
+and aggregate them by introducing bridges.
 We grow the (bridged) original buildings by buffering with miter joins.
-Our building simplification consists of two steps.
+We simplify the grown buildings with two steps.
 The first one is to use dilation and erosion to remove pits and spikes.
 The second step is to remove vertices using Imai--Iri algorithm.
-To make sure that the intermediate-scale buildings never shrink,
-we merge the shape of a building 
-with the shape at the previously immediate step. 
+To make sure that buildings never shrink when $t$ is increasing,
+For a building, we merge its shape at time $t$ 
+and its shape at the immediately previous step (before $t$). 
 Also, we clip the building using the shape on goal map.
 
-Our grouping is based on growing, aggregating and some of simplifying. 
-So we present the three operators before grouping.
+Our aggregating relies on growing and dilation-erosion-based simplifying. 
+So we present the two operators before aggregating.
 
@@
 We grow buildings based on buffering. 
-There are two typical ways of buffering a polygon, i.e.,
-one with round joins and the other with miter joins 
-(see \fig\ref{fig:Buffer_TwoKinds}).
-As buildings are usually rectangles, 
-we choose the second way to
-better preserve the right angles.
-If an angle is acute, however, an excessively long \emph{spike} will be 
-produced.
-This spike may go across other buildings 
-(see \fig\ref{fig:Buffer_MiterLimits}a).
-To avoid this kind of interruptions, 
-we require that if a vertex of the 
-buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
-away from the original vertex, 
-a \emph{square} join is applied
-(see \fig\ref{fig:Buffer_MiterLimits}b).
-Distance $\dtrm{G}$ is the growth at time $t$.
 We denote by $d_\mathrm{G}$ the growth for goal map.
-Then we define
+At time $t$, the growth is
 \begin{equation}
@@
 \end{equation}
+
+There are two typical ways of buffering a polygon, i.e.,
+using round joins or using miter joins 
+(see \fig\ref{fig:Buffer_TwoKinds}).
+We choose the second way in order to
+preserve the right angles of buildings.
+If an angle is acute, however, 
+an excessively long \emph{spike} will be produced.
+This spike may go across other buildings 
+(see \fig\ref{fig:Buffer_MiterLimits}a).
+To avoid this kind of interruptions, 
+we require that if the tip of a spike 
+is more than $\alpha \dtrm{G} (\alpha \ge 1)$
+away from the original vertex, 
+a \emph{square} join is applied
+(see \fig\ref{fig:Buffer_MiterLimits}b).
 To keep right angles of buildings, 
@@
 	\includegraphics{Buffer_TwoKinds}
-	\caption{Buffering a polygon using different kinds of joins.}
+	\caption{Buffering a polygon using round joins and using miter joins.}
 	\label{fig:Buffer_TwoKinds}
@@
 	\includegraphics{Buffer_MiterLimits}
-	\caption{}
+	\caption{Using square joins instead of miter joins to avoid long spikes.
+	}
 	\label{fig:Buffer_MiterLimits}
@@
 based on offset curves generated from straight skeletons.
-We use a method based on buffering to remove pits and spikes of buildings.
-Our method is slightly different than \citet{Meijers2016},
-but there is an available library \textsc{Clipper} \citep{Johnson2014} 
-for the operations.
-\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
-We first dilate the grown buildings to remove 
-pits, and then erode the results to remove spikes.
+Our method is similar to \citet{Meijers2016}.
+We dilate and erode to remove ``dents'' and ``bumps'' of buildings
+(see \fig\ref{fig:RemovePitAndSpike}).
+The operations of dilation and erosion are available from library 
+\textsc{Clipper} \citep{Johnson2014}.
 
@@
 	\includegraphics[]{RemovePitAndSpike}
-	\caption{Remove a pit by dilating and then remove a spike by eroding.
-		(a) a polygon with a pit and a spike;
-		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
-		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
-		(d) dilate the polygon in (c) with distance $d$ so that the result has 
+	\caption{Removing a dent by dilating and then remove a bump by eroding.
+		(a) a polygon with a dent and a bump;
+		(b) dilating the polygon in (a) with distance $d$ to remove the dent;
+		(c) eroding the polygon in (b) with $2d$ to remove the bump;
+		(d) dilating the polygon in (c) with $d$ so that the result has 
 		the same size as the polygon in (a).
@@
 
-At time $t$, we grow buildings with distance $\dtrm{G}$,
-dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
-erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
-and dilate back with distance $\dtrm{E}$.
+At time $t$, we grow buildings with distance $\dtrm{G}$.
+We dilate with distance $\dtrm{D}$ ($\dtrm{D}>0$),
+erode with $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
+and dilate back with $\dtrm{E}$.
 A problem we may have is that 
@@
 and the building is not thick enough, 
-the thin part may disappear.
+a thin part may disappear.
 In order to avoid this problem, we require that
@@
 	\includegraphics[]{ErosionBreak}
-	\caption{Dilate the gray polygon, then erode the dilated polygon.
-		(a) Dilate and erode with distance $d_1$.
-		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
+	\caption{Dilating the gray polygon, then eroding the dilated polygon.
+		(a) Dilating and eroding with distance $d_1$.
+		(b) Dilating and eroding with $d_2$, where $d_2>d_1$.
 		In (a) the result of dilation and erosion is the same as the original 
@@
 \citet{Regnauld2001}.
-Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
+Unfortunately, distance $\dtrm{G}$ can be arbitrarily small 
+according to \eq\ref{eq:d_Gt}, 
 but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
@@
 %t \cdot \frac{l}{2} M_\mathrm{g} >0$.
-Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
+Still, we have to make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
 $t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
-As a result, we should make sure that
+As a result, we need to make sure that
 \begin{equation}
@@
 
-We aggregate buildings if they become too close because of growing.
-Our basic idea is to add bridges between buildings
-(see for example \fig\ref{fig:GrowAndBridge}).
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Aggregate original buildings in the same group by introducing 
-		bridges.
-		Then grow the bridged buildings.}
-	\label{fig:GrowAndBridge}
-\end{figure*}
-
 We grow each original building and, as illustrated in 
@@
 If some buildings become too close after these operations,
-we aggregate them by adding bridges.
+we aggregate them by adding bridges
+(see for example \fig\ref{fig:GrowAndBridge}).
 Following \citet{Stoter2009}, 
@@
 
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[draft=false]{GrowAndBridge}
+	\caption{Aggregating original buildings in the same group by introducing 
+		bridges.
+		Then grow the bridged buildings.}
+	\label{fig:GrowAndBridge}
+\end{figure*}
+
 Our way of detecting close buildings is simple.
@@
 We merge the buffers that overlap each other.
-The buildings intersect with the same merged buffer 
+The buildings intersect the same merged buffer 
 are identified as a group of close buildings.
-According to the group of buildings, 
-we find the group of corresponding original buildings.
-For each pair of the original buildings in a group,
+The corresponding original buildings 
+are identified as a group of original close buildings.
+For each pair of the original buildings in the same group,
 we connect them by adding a line segment linking the nearest points.
-The line segments for the group of original buildings may cross each other or 
+The line segments for a group of original buildings may cross each other or 
 even intersect buildings.
@@
 Aggregated buildings may become too close after growing because of bridges.
+Therefore we have to iterate the process of aggregating.
 \fig\ref{fig:BridgeMoreBuilding} shows such an example.
 We grow and buffer buildings $p$, $q$, and~$r$.
-As the buffers of $q$ and~$r$ overlap with each other
+As the buffers of $q$ and~$r$ overlap
 (see \fig\ref{fig:BridgeMoreBuilding}c),
-we aggregated buildings $q$ and~$r$ by adding a bridge.
+we aggregate buildings $q$ and~$r$ by adding a bridge
+(see \fig\ref{fig:BridgeMoreBuilding}d).
 There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
-Because of the bridge, when we grow and buffer the buildings in 
+We grow and buffer the buildings in 
 \fig\ref{fig:BridgeMoreBuilding}d, 
-the buffer of building $p$ overlap with the buffer of the bridged $q$ and $r$
+the buffer of building $p$ overlap the buffer of the bridge for $q$ and $r$
 (see \fig\ref{fig:BridgeMoreBuilding}f).
@@
 		(a) original buildings $p$, $q$, and~$r$.
-		(b) grow the original buildings with distance $\dtrm{G}$.
-		(c) buffer the grown buildings with distance $d_{\epsilon,t}/2$ using 
-		round joins.
-		(d) aggregate buildings $q$ and~$r$ by adding a bridge,
-		as their buffer overlap with each other in (c).
-		(e) grow the buildings in (d) with distance $\dtrm{G}$.
-		(f) buffer the grown buildings in (e) with distance $d_{\epsilon,t}/2$ 
+		(b) growing the original buildings with distance $\dtrm{G}$.
+		(c) buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
 		using round joins.
-		(g) aggregate buildings $p$, $q$ and~$r$ by adding bridges.
-		(h) grow the buildings in (g) with distance $\dtrm{G}$.
-		(i) buffer the grown buildings in (h) with distance $d_{\epsilon,t}/2$ 
-		using round joins.
+		(d) aggregating buildings $q$ and~$r$ by adding a bridge,
+		as their buffer overlap each other in (c).
+		(e) growing the buildings in (d) with distance $\dtrm{G}$.
+		(f) buffering the grown buildings in (e) with distance 
+		$d_{\epsilon,t}/2$ using round joins.
+		(g) aggregating buildings $p$, $q$ and~$r$ by adding bridges.
+		(h) growing the buildings in (g) with distance $\dtrm{G}$.
+		(i) buffering the grown buildings in (h) with distance 
+		$d_{\epsilon,t}/2$ using round joins.
 	}
@@
 %that every part of a building grows with the same speed.
-%If the buffers of two buildings overlap with each other,
+%If the buffers of two buildings overlap each other,
 %then the two buildings are surely aggregated into one.
@@
 
-We simplify the buildings using Imai--Iri algorithm 
+We simplify the grown buildings using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
@@
 we are not able to arrive at the shortcut by growing.
-Second, a shortcut is not allowed to intersect with the aggregated building.
+Second, a shortcut is not allowed to intersect the aggregated building.
 If we allow this intersection, 
@@
 Of course, we do not want to shrink.
-\todo{a shortcut is not allowed to intersect with the building at the 
+\todo{a shortcut is not allowed to intersect the building at the 
 	immediately previous step?}
@@
 
-\subsection{Generating the goal forms of buildings}
+\subsection{Generating the goal shapes of buildings}
 \label{sec:Goal}
-To generate the goal forms of buildings, we set time $t=1$.
+To generate the goal shapes of buildings, we set time $t=1$.
 We aggregate original buildings (see \sect\ref{sec:Aggregate}).
@@
 See for example \fig\ref{fig:GrowAndBridge}, 
-the building at time $t=1$ is the goal form of the three original buildings of.
+the building at time $t=1$ is the goal shape of the three original buildings.
 
@@
 
-Both the erosion and line simplification may results in shrinking of a 
+Both the erosion and line simplification may result in shrinking of a 
 building.
@@
 To avoid these kinds of shrinking,
-we unite a building with itself at the immediately previous step.
-For example, if the grown polygons of 
-\fig\ref{fig:Shrink_Erosion}~(c) and~(g) 
-are from a sequence of $10$ steps, 
-i.e., $t \in \{0.1, 0.2, \dots, 1\}$, 
-then we compute the result of $t=0.8$ by uniting 
-the grown polygon obtained independently at $t=0.8$ and 
-the grown polygon at $t=0.7$. 
-\fig\ref{fig:Shrink_Uniting}~(a) shows the result,
-which is the union of the two grown polygons in 
-\fig\ref{fig:Shrink_Erosion}~(c) and~(g).
-Similarly, \fig\ref{fig:Shrink_Uniting}~(b) shows the union of the two grown 
-polygons in 
-\fig\ref{fig:Shrink_Simplification}~(c) and~(h).
+for a building, we merge its shape at time $t$ 
+and its shape at the immediately previous step (before $t$). 
+For example, we generate a sequence of $10$ maps,
+which means $t \in \{0.1, 0.2, \dots, 1\}$.
+\fig\ref{fig:Shrink_Erosion}c shows the result at $t=0.6$.
+In \fig\ref{fig:Shrink_Erosion}g, 
+the dark-gray part included in the result at $t=0.6$,
+but not in the result at $t=0.7$.
+In other words, the result at $t=0.7$ shrinks at the dark-gray part.
+To prevent the shrinking at $t=0.7$, we merge the result at $t=0.7$ with the 
+result of immediately previous step, i.e., $t=0.6$.
+The merged result is shown in \fig\ref{fig:Shrink_Uniting}a.
+Similarly, \fig\ref{fig:Shrink_Uniting}b shows the merged result of buildings 
+in \fig\ref{fig:Shrink_Simplification}c and~h.
 
 A building on an intermediate map should never exceed
-the goal form of the group of buildings 
-which include the united buildings. 
+the goal shape of the aggregated building. 
 Otherwise, the building will need to be shrunk.
 To guarantee the non-exceeding, 
-we clip the building using the goal form 
+we clip the building using the goal shape 
 and remove the parts outside.
 
-We may unite the processed merged building with several separate parts 
-because the group of buildings may be in several smaller groups
-in the immediately previous step.
-
-\begin{figure*}[tb]
+\begin{figure}[tb]
 	\centering
 	\includegraphics[]{Shrink_Erosion}
-	\caption{A building shrinks during growing because of dilation and erosion, 
+	\caption{A building shrinks because of dilation and erosion, 
 		where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
-		The small gray polygons represent the original building.
-		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
+		The gray polygons represent the original building.
+		(a) Growing and Dilating the building with distances $\dtrm[1]{G}$ and 
 		$\dtrm[1]{D}$, respectively;
-		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
-		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
-		(d) The large gray polygon is the target shape on goal map.
-		The process for (e), (f), and (g) is the same as the process of (a), 
-		(b), and (c).
+		(b) Eroding the polygon in~(a) with $\dtrm[1]{D} + \dtrm[1]{E}$;
+		(c) Dilating the polygon in~(b) with $\dtrm[1]{E}$.
+		(d) The goal shape.
+		The process of (e), (f), and~(g) is the same as the process of (a), 
+		(b), and~(c).
 		The darker gray piece in (g) shows 
-		the part which is included in the grown polygon of (c), 
-		but not in the grown polygon of (g).
+		the part which is included in the polygon of~(c), 
+		but not in the polygon of~(g).
 	}
 	\label{fig:Shrink_Erosion}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[tb]
+\begin{figure}[tb]
 	\centering
 	\includegraphics[]{Shrink_Simplification}
-	\caption{A building shrinks during growing because of line simplification, 
+	\caption{A building shrinks because of line simplification, 
 		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
-		The small gray polygons represent the original building.
-		The process for (a), (b), and (c), and 
-		the process for (e), (f), and (g) are the same as 
+		The gray polygons represent the original building.
+		The process of (a), (b), and~(c), and 
+		the process of (e), (f), and~(g) are the same as 
 		the processes in \fig\ref{fig:Shrink_Erosion}.
-		(d) The large gray polygon is the target shape on goal map.
-		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
-		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
+		(d) The goal shape.
+		(h) Simplifying the polygon in~(g) using the Imai--Iri algorithm.
+		Note that $d_{l,t_1}<d_{l,t_2}$ (see \eq\ref{eq:d_lt}),
 		which is why the Imai--Iri algorithm does not 
-		remove any point of the polygon in (c),
-		but removes two points of the polygon in (g).
-		The darker gray pieces in (h) show 
-		the parts which are included in the polygon of (c), 
-		but not in the polygon of (h).
+		remove any vertex of the polygon in~(c),
+		but removes two vertices of the polygon in~(g).
+		The darker gray pieces in~(h) show 
+		the parts which are included in the polygon of~(c), 
+		but not in the polygon of~(h).
 	}
 	\label{fig:Shrink_Simplification}
-\end{figure*}
+\end{figure}
 
@@
 	\includegraphics[]{Shrink_Uniting}
-	\caption{Unite a polygon with the polygon at the immediately previous step.
-		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}c and the 
-		polygon of \fig\ref{fig:Shrink_Erosion}g;
-		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}c and 
-		the polygon of \fig\ref{fig:Shrink_Simplification}h;
+	\caption{Merging a polygon with the polygon at the immediately previous 
+	step.
+		(a) Merging the polygons of \fig\ref{fig:Shrink_Erosion}c and 
+		\fig\ref{fig:Shrink_Erosion}g;
+		(b) Merging the polygons of \fig\ref{fig:Shrink_Simplification}c and 
+		\fig\ref{fig:Shrink_Simplification}h;
 	}
@@
 threshold.
-For a group of buildings, we consider the area sum of all the buildings.
-
-Following \citet{Stoter2009} and Following \citet{Chaudhry2008}, 
-we set
+Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
+we set this threshold as $a=0.16\,\mathrm{mm}^2$ on map.
+The real threshold at time $t$ is
+\[
+a_t=a\cdot M_t^2.
+\]
+For a group of buildings that will be aggregated into one built-up area at time 
+$t=1$, we consider the area sum of all the buildings, 
+instead of considering each building individually.
 

### 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/GoalShape.pdf

@@
 C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
-The buffer function and clip function are from library \emph{Clipper} 
+The offsetting function and clipping function are from library \textsc{Clipper} 
 of \citet{Johnson2014}.
-An evaluation of Clipper can be found in \citet{Palfrader2015}.
+The offsetting function realizes 
+our operations of buffering, dilating, eroding, and merging.
+An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
 We ran our case study under 64-bit 
@@
 \emph{Stopwatch}.
-We tested our method on a dataset from French Mapping Agency (IGN).
-The dataset represents four towns (communes in French), i.e., Aussevielle, 
-Denguin,  Poey-de-Lescar, and Siros, in the 
-Pyr\'en\'ees-Atlantiques department, south-western France.
-The scale of the dataset is $1:15{,}000$.
-There are $2{,}590$ buildings (see \fig\ref{fig:Data}), 
-which has $19{,}255$ edges in total.
+\fig\ref{fig:Data} shows our testing data, 
+which is from the French Mapping Agency (IGN).
+The data represents the buildings of four towns (communes in French), 
+i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
+in the Pyr\'en\'ees-Atlantiques department, south-western France.
+
 Our goal scale is $1:50{,}000$.
 
-\begin{figure*}[tb]
+\begin{figure}[tb]
 	\centering
 	\includegraphics{Data}
-	\caption{data.}
+	\caption{Data.
+		There are $2{,}590$ buildings, 
+		which has $19{,}255$ edges in total.}
 	\label{fig:Data}
-\end{figure*}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{GoalShape}
+	\caption{Data for scale $1:15{,}000$.
+		There are $2{,}590$ buildings, 
+		which has $19{,}255$ edges in total.}
+	\label{fig:GoalShape}
+\end{figure}
 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
revision of the methodology section

--- 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 
-We find original buildings which will grow to become too close at time $t$
-and aggregate them by introducing bridges.
+The continuous generalization is carried by dilating the original buildings. When dilated buildings become too close at time $t$
+and we aggregate them by introducing bridges.
 We grow the (bridged) original buildings by buffering with miter joins.
-We simplify the grown buildings with two steps.
-The first one is to use dilation and erosion to remove pits and spikes.
-The second step is to remove vertices using Imai--Iri algorithm.
+At each time, the grown buildings need to be simplified to look like buildings and this simplification is carried out in two steps:
+the first one is to use dilation and erosion to remove pits and spikes; the second step is to remove vertices using Imai--Iri algorithm.
 To make sure that buildings never shrink when $t$ is increasing,
-For a building, we merge its shape at time $t$ 
+for a building, we merge its shape at time $t$ 
 and its shape at the immediately previous step (before $t$). 
-Also, we clip the building using the shape on goal map.
+Also, we clip the building using the shape on goal map to ensure some continuity.
 
-Our aggregating relies on growing and dilation-erosion-based simplifying. 
-So we present the two operators before aggregating.
+The two main operators of the proposed method, building growth and dilation-erosion-based simplification, are presented in the following subsections:
 
@@
 \label{sec:Grow}
-We grow buildings based on buffering. 
 We denote by $d_\mathrm{G}$ the growth for goal map.
@@
 \label{sec:DilationErosion}
-\citet{Damen2008} generalized buildings using morphological operators.
-A drawback of this method is that the directions of the buildings have to be 
-concerned.
+As mentioned earlier, building simplification methods have already been proposed. \citet{Damen2008} generalized buildings using morphological operators.
+A drawback of this method is that the orientation of the buildings have to be 
+identified.
 \citet{Meijers2016} simplified buildings 
@@
 Our method is similar to \citet{Meijers2016}.
-We dilate and erode to remove ``dents'' and ``bumps'' of buildings
+Our proposition is to dilate and erode the buildings, to remove ``dents'' and ``bumps'' that can occur when buildings grow.
 (see \fig\ref{fig:RemovePitAndSpike}).
@@
 A problem we may have is that 
-a building may be broken by eroding
+a building may be split into several parts by erosion
 (see \fig\ref{fig:ErosionBreak} for example).
@@
 any pits and spikes narrower than $l$ will be removed. 
-We set $l=0.3\,\mathrm{mm}$, 
+We set $l=0.3\,\mathrm{mm}$ in the map, 
 which was used as a length threshold by, for example, 
@@
 is the radius of a hole which is just large enough to be presented on map.
-Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
+Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ in the map.
 Sometimes, our $\dtrm{D}$ is not large enough to do so 
@@
 \]
+
+\todo{please explain in a figure what a bay is, and what is the width of the bay}
 
@@
 
-Aggregated buildings may become too close after growing because of bridges.
-Therefore we have to iterate the process of aggregating.
+Aggregated buildings may become too close because of the additional bridges.
+Therefore we have to iterate the aggregation process.
 \fig\ref{fig:BridgeMoreBuilding} shows such an example.
-We grow and buffer buildings $p$, $q$, and~$r$.
+For example, we grow and buffer buildings $p$, $q$, and~$r$.
 As the buffers of $q$ and~$r$ overlap
@@
 There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
-We grow and buffer the buildings in 
+We then grow and buffer the buildings in 
 \fig\ref{fig:BridgeMoreBuilding}d, 
@@
 (see \fig\ref{fig:BridgeMoreBuilding}f).
-We aggregate building $p$ with bridged $q$ and $r$
-(see \fig\ref{fig:BridgeMoreBuilding}g).
-There is one building left in \fig\ref{fig:BridgeMoreBuilding}g.
-Then we grow and buffer again.
-There is one building left after this process.
-The number of buildings does not decrease comparing to last process.
-The iteration stops.
+Finally, building $p$ is aggregated with bridged $q$ and $r$
+(see \fig\ref{fig:BridgeMoreBuilding}g), and
+there is only one building left in \fig\ref{fig:BridgeMoreBuilding}g.
+Then we grow and buffer again to get the final geometry of the group.
+As the number of buildings does not decrease comparing to last process (one building before, one building after),
+the iteration stops.
 
@@
 
-\subsection{Simplifying buildings using Imai--Iri algorithm}
+\subsection{Simplifying aggregated buildings using Imai--Iri algorithm}
 \label{sec:ImaiIri}
 
-We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
-No matter a bridge appears earlier or later, 
-it has width $2\dtrm{G}$ at time $t$.
+When buildings are grown and aggregated iteratively, bridges are added, 
+and these bridges have a width of $2\dtrm{G}$ at time $t$.
 This setting guarantees that no bridge is thin when $t=1$.
 
-We simplify the grown buildings using Imai--Iri algorithm 
+This agrregation process creates new small details that need to be removed. So, the aggregated buildings are simplified using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
@@
 If we allow this intersection, 
-the building will have to be shrunk. 
-Of course, we do not want to shrink.
-\todo{a shortcut is not allowed to intersect the building at the 
-	immediately previous step?}
+the building will have to be shrunk, which should be avoided.
 
-We tried simplifying using 
-the Douglas--Peucker algorithm \citep{Douglas1973}, 
-but we hoped to remove more points. 
-We found that the Imai--Iri 
-algorithm fit our needs better.
+The classical way to filter points in a polyline or polygon is the Douglas--Peucker algorithm \citep{Douglas1973}, 
+but it did not filter enough the geometry, or damaged too much the shapes when the threshold was bigger, so the Imai--Iri 
+algorithm was chosen as a better fit.
 
@@
 
-\subsection{Generating the goal shapes of buildings}
-\label{sec:Goal}
-To generate the goal shapes of buildings, we set time $t=1$.
-We aggregate original buildings (see \sect\ref{sec:Aggregate}).
-Then we grow (see \sect\ref{sec:Grow}) 
-and simplify 
-(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
-See for example \fig\ref{fig:GrowAndBridge}, 
-the building at time $t=1$ is the goal shape of the three original buildings.
+%
+%
+%\subsection{Generating the goal shapes of buildings}
+%\label{sec:Goal}
+%To generate the goal shapes of buildings, we set time $t=1$.
+%We aggregate original buildings (see \sect\ref{sec:Aggregate}).
+%Then we grow (see \sect\ref{sec:Grow}) 
+%and simplify 
+%(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
+%See for example \fig\ref{fig:GrowAndBridge}, 
+%the building at time $t=1$ is the goal shape of the three original buildings.
+%
+%
 
@@
 
-Both the erosion and line simplification may result in shrinking of a 
+Both the erosion and line simplification may result in shrinking a 
 building.
@@
 To prevent the shrinking at $t=0.7$, we merge the result at $t=0.7$ with the 
-result of immediately previous step, i.e., $t=0.6$.
+result of the immediate previous step, i.e., $t=0.6$.
 The merged result is shown in \fig\ref{fig:Shrink_Uniting}a.
@@
 
-A building on an intermediate map should never exceed
+Added to this shrinking problem, a building aggregate on an intermediate map should never exceed
 the goal shape of the aggregated building. 
-Otherwise, the building will need to be shrunk.
-To guarantee the non-exceeding, 
+Otherwise, the building will need to be shrunk to ensure continuity with the goal built-up polygon.
+To guarantee this consistency, 
 we clip the building using the goal shape 
-and remove the parts outside.
+and remove the outside parts.
 
@@
 \label{sec:Eliminate}
-We eliminate a building if the area of this building is smaller than a 
+Following the previous steps of continuous generalization may result in the creation of small isolated building aggregates that do not belong to the goal map polygon because of their isolation.
+That is why we eliminate a building aggregate if the area of this building is smaller than a 
 threshold.
@@
 For a group of buildings that will be aggregated into one built-up area at time 
-$t=1$, we consider the area sum of all the buildings, 
+$t=1$, we consider the area sum of all the buildings at time $t$, 
 instead of considering each building individually.

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/ExperimentalComparison.pdf

--- 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 
-Our goal scale is $1:50{,}000$.
+We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
+so that we can compare our result with the exiting data.
+Also, this setting makes \eq\ref{eq:S_g} hold, 
+where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
+and $l=0.3\,\mathrm{mm}$.
+In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
+according to our settings.
+As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
+where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
+according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
+
+Our program took $93.6\,\mathrm{s}$ 
+to compute the goal shapes of the built-up areas.
+\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
+In \fig\ref{fig:GoalShape}b,
+the $56$ built-up areas have $2{,}095$ edges before line simplification.
+Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
+In comparison, there are $1{,}597$ edges left if we simplify using
+the Douglas--Peucker algorithm.
 
@@
 		There are $2{,}590$ buildings, 
-		which has $19{,}255$ edges in total.}
+		which have $19{,}255$ edges in total.}
 	\label{fig:Data}
@@
 	\includegraphics{GoalShape}
-	\caption{Data for scale $1:15{,}000$.
-		There are $2{,}590$ buildings, 
-		which has $19{,}255$ edges in total.}
+	\caption{Some results for time $t=1$, at scale $1:50{,}000$.
+		(a) Bridged buildings.
+		(b) Goal shapes of the built-up areas, without removing small holes.
+		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+	}
 	\label{fig:GoalShape}
@@
 
-\todo[inline]{comparison of simplification between Douglas--Peucker and 
-	Imai--Iri}
+\begin{figure}[tb]
+	\centering
+	\includegraphics{ExperimentalComparison}
+	\caption{.
+	}
+	\label{fig:ExperimentalComparison}
+\end{figure}
 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on case study

--- 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 \emph{Stopwatch}.
-We tested our method on a dataset from French Mapping Agency (IGN).
-The dataset represents four towns (communes in French), i.e., Aussevielle, 
-Denguin,  Poey-de-Lescar, and Siros, in the 
-Pyr\'en\'ees-Atlantiques department, south-western France.
-The scale of the dataset is $1:15{,}000$.
-There are $2{,}590$ buildings (see \fig\ref{fig:Data}), 
-which has $19{,}255$ edges in total.
-Our goal scale is $1:50{,}000$.
+\fig\ref{fig:Data} shows our testing data, 
+which is from the French Mapping Agency (IGN).
+The data represents the buildings of four towns (communes in French), 
+i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
+in the Pyr\'en\'ees-Atlantiques department, south-western France.
+
+We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
+so that we can compare our result with the exiting data.
+Also, this setting makes \eq\ref{eq:S_g} hold, 
+where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
+and $l=0.3\,\mathrm{mm}$.
+In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
+according to our settings.
+As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
+where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
+according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
+
+Our program took $93.6\,\mathrm{s}$ 
+to compute the goal shapes of the built-up areas.
+\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
+In \fig\ref{fig:GoalShape}b,
+the $56$ built-up areas have $2{,}095$ edges before line simplification.
+Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
+In comparison, there are $1{,}597$ edges left if we simplify using
+the Douglas--Peucker algorithm.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Data}
+	\caption{Data.
+		There are $2{,}590$ buildings, 
+		which have $19{,}255$ edges in total.}
+	\label{fig:Data}
+\end{figure}
 
@@
 	\centering
-	\includegraphics{Data}
-	\caption{data.}
-	\label{fig:Data}
+	\includegraphics{GoalShape}
+	\caption{Bridged original buildings 
+		and goal shapes of the built-up areas (without removing small holes), 
+		at scale $1:50{,}000$.
+		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+	}
+	\label{fig:GoalShape}
 \end{figure*}
 
-\todo[inline]{comparison of simplification between Douglas--Peucker and 
-	Imai--Iri}
+\begin{figure*}[tb]
+	\centering
+	\includegraphics{ExperimentalComparison}
+	\caption{.
+	}
+	\label{fig:ExperimentalComparison}
+\end{figure*}
 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
removed some unused text and figures

@@
 
-The continuous generalization is carried by dilating the original buildings. When dilated buildings become too close at time $t$
+The continuous generalization is carried by dilating the original buildings. 
+When dilated buildings become too close at time $t$
 and we aggregate them by introducing bridges.
 We grow the (bridged) original buildings by buffering with miter joins.
-At each time, the grown buildings need to be simplified to look like buildings and this simplification is carried out in two steps:
-the first one is to use dilation and erosion to remove pits and spikes; the second step is to remove vertices using Imai--Iri algorithm.
+At each time, the grown buildings need to be simplified to look like buildings 
+and this simplification is carried out in two steps:
+the first one is to use dilation and erosion 
+to remove ``dents'' and ``bumps''; 
+the second step is to remove vertices using Imai--Iri algorithm.
 To make sure that buildings never shrink when $t$ is increasing,
@@
 and its shape at the immediately previous step (before $t$). 
-Also, we clip the building using the shape on goal map to ensure some continuity.
+Also, we clip the building using the shape on goal map to ensure some 
+continuity.
 
-The two main operators of the proposed method, building growth and dilation-erosion-based simplification, are presented in the following subsections:
+The two main operators of the proposed method, building growth and 
+dilation-erosion-based simplification, are presented in the following 
+subsections:
 
@@
 \label{sec:DilationErosion}
-As mentioned earlier, building simplification methods have already been proposed. \citet{Damen2008} generalized buildings using morphological operators.
+As mentioned earlier, building simplification methods have already been 
+proposed. \citet{Damen2008} generalized buildings using morphological operators.
 A drawback of this method is that the orientation of the buildings have to be 
@@
 Our method is similar to \citet{Meijers2016}.
-Our proposition is to dilate and erode the buildings, to remove ``dents'' and ``bumps'' that can occur when buildings grow.
-(see \fig\ref{fig:RemovePitAndSpike}).
+Our proposition is to dilate and erode the buildings, to remove dents and 
+bumps that can occur when buildings grow.
+(see \fig\ref{fig:RemoveDentAndBump}).
 The operations of dilation and erosion are available from library 
@@
 	\centering
-	\includegraphics[]{RemovePitAndSpike}
+	\includegraphics[]{RemoveDentAndBump}
 	\caption{Removing a dent by dilating and then remove a bump by eroding.
@@
 	}
-	\label{fig:RemovePitAndSpike}
+	\label{fig:RemoveDentAndBump}
 \end{figure}
@@
 We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
-any pits and spikes narrower than $l$ will be removed. 
+any dents and bumps narrower than $l$ will be removed. 
 We set $l=0.3\,\mathrm{mm}$ in the map, 
@@
 is the radius of a hole which is just large enough to be presented on map.
-Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ in the map.
+Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
+in the map.
 Sometimes, our $\dtrm{D}$ is not large enough to do so 
@@
 
-\todo{please explain in a figure what a bay is, and what is the width of the bay}
+\todo{please explain in a figure what a bay is, and what is the width of the 
+bay}
 
@@
 Then we grow and buffer again to get the final geometry of the group.
-As the number of buildings does not decrease comparing to last process (one building before, one building after),
+As the number of buildings does not decrease comparing to last process (one 
+building before, one building after),
 the iteration stops.
@@
 
-This agrregation process creates new small details that need to be removed. So, the aggregated buildings are simplified using Imai--Iri algorithm 
+This agrregation process creates new small details that need to be removed. So, 
+the aggregated buildings are simplified using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
@@
 
-The classical way to filter points in a polyline or polygon is the Douglas--Peucker algorithm \citep{Douglas1973}, 
-but it did not filter enough the geometry, or damaged too much the shapes when the threshold was bigger, so the Imai--Iri 
+The classical way to filter points in a polyline or polygon is the 
+Douglas--Peucker algorithm \citep{Douglas1973}, 
+but it did not filter enough the geometry, or damaged too much the shapes when 
+the threshold was bigger, so the Imai--Iri 
 algorithm was chosen as a better fit.
@@
 %and simplify 
-%(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
+%(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown 
+%buildings.
 %See for example \fig\ref{fig:GrowAndBridge}, 
@@
 
-Added to this shrinking problem, a building aggregate on an intermediate map should never exceed
+Added to this shrinking problem, a building aggregate on an intermediate map 
+should never exceed
 the goal shape of the aggregated building. 
-Otherwise, the building will need to be shrunk to ensure continuity with the goal built-up polygon.
+Otherwise, the building will need to be shrunk to ensure continuity with the 
+goal built-up polygon.
 To guarantee this consistency, 
@@
 \label{sec:Eliminate}
-Following the previous steps of continuous generalization may result in the creation of small isolated building aggregates that do not belong to the goal map polygon because of their isolation.
-That is why we eliminate a building aggregate if the area of this building is smaller than a 
+Following the previous steps of continuous generalization may result in the 
+creation of small isolated building aggregates that do not belong to the goal 
+map polygon because of their isolation.
+That is why we eliminate a building aggregate if the area of this building is 
+smaller than a 
 threshold.
@@
 instead of considering each building individually.
-
-%\subsection{Parameters for growing and simplifying}
-%
-%
-%
-%
-%If we insist on that we should observe 
-%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
-%sure that
-%\begin{equation}
-%\label{eq:a_limit}
-%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
-%\end{equation}
-%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
-%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
-%\begin{equation}
-%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
-%\end{equation}
-%We also require 
-%that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
-%On one hand, we should have a large $x$ so that we will see the 
-%growing most of the time.
-%On the other hand, we wish to keep bridges short as bridges are intrusions to 
-%our map, which means we should have a small $x$ and a large $\lambda$ so that 
-%we will have a small 
-%$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
-%Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
-%Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
-%$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
-%map, which is the area limit used by \citet{Stoter2009}. As a result, we 
-%set 
-%$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
-%Using these setting, we have
-%\begin{equation}
-%a \ge 4.
-%\end{equation}
-%according to Eq.~\ref{eq:a_limit}.
-%
-%
-%
-%
-%Therefore, we may grow up to distance 
-%\[
-%D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
-%\]
-%Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, 
-%where  
-%variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.
-%
-%
-%\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
-%$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
-%which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
-%Following their setting, we shrink a hole and 
-%eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.
-
-%
-%A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
-%A hole has area 
-%slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
-%growing with 
-%distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
-%unless the 
-%area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
-%that we do 
-%not fill a hole even if the hole has a large area because a large hole may be 
-%split into several small holes by filling. 
-%Although our intermediate results may violate the rule that a hole should be 
-%at 
-%least some size, we try to avoid the violation for a map at a goal scale.
-%\citet{Chaudhry2008} thought that a hole of a settlement should be at 
-%least 
-%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is 
-%at 
-%least $8\,\mathrm{mm}^2$ on the map. Following their setting, we wish to have 
-%$\pi 
-%D_\mathrm{G}^2 \ge 8 S_g^2$.
-%
-%
-%Now we discuss how to set the parameters according to our requirements. 
-%First, 
-%we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
-%grow $d_\mathrm{G}$. Only a small part will continue growing after the 
-%building 
-%has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
-%time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
-%
-%
-%
-%
-%
-%We cannot fulfill all the requirements.
-
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics{ExtraGrowth}
-%	\caption{In the left figure, the green polygon represents a building, and 
-%		the gray polygon is the enlargement of the building. In the right 
-%		figure, the gray polygon has been simplified to a rectangle. In order 
-%to 
-%		fill the rectangle, most parts of the (green) building needs to grow 
-%with
-%		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
-%		d_\mathrm{e}$, 
-%		where $d_\mathrm{e}$ is the extra growing distance.}
-%	\label{fig:ExtraGrowth}
-%\end{figure*}
-
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics{GrowingExample}
-%	\caption{GrowingExample.}
-%	\label{fig:GrowingExample}
-%\end{figure*}
 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on section of case study; i will submit the unfinished version, and update our submission later

@@
 	\caption{Removing a dent by dilating and then remove a bump by eroding.
-		(a) a polygon with a dent and a bump;
-		(b) dilating the polygon in (a) with distance $d$ to remove the dent;
-		(c) eroding the polygon in (b) with $2d$ to remove the bump;
-		(d) dilating the polygon in (c) with $d$ so that the result has 
+		(a) A polygon with a dent and a bump.
+		(b) Dilating the polygon in (a) with distance $d$ to remove the dent.
+		(c) Eroding the polygon in (b) with $2d$ to remove the bump.
+		(d) Dilating the polygon in (c) with $d$ so that the result has 
 		the same size as the polygon in (a).
@@
 \begin{equation}
-\label{eq:d_Dt}
+\label{eq:d_DtBound}
 \dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
@@
 In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
-which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
+which violates \eq\ref{eq:d_DtBound}, where $\dtrm{D}>0$.
 As a compromise, we set erosion distance
@@
 Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
-in the map.
+on map.
 Sometimes, our $\dtrm{D}$ is not large enough to do so 
-because of the limitation from \eq\ref{eq:d_Dt}.
+because of the limitation from \eq\ref{eq:d_DtBound}.
 We define
-\[
+\begin{equation}
+\label{eq:d_Dt}
 \dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
-\]
+\end{equation}
 
@@
 	\caption{Iteratively aggregating close buildings by adding bridges.
-		(a) original buildings $p$, $q$, and~$r$.
-		(b) growing the original buildings with distance $\dtrm{G}$.
-		(c) buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
+		(a) Original buildings $p$, $q$, and~$r$.
+		(b) Growing the original buildings with distance $\dtrm{G}$.
+		(c) Buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
 		using round joins.
-		(d) aggregating buildings $q$ and~$r$ by adding a bridge,
+		(d) Aggregating buildings $q$ and~$r$ by adding a bridge,
 		as their buffer overlap each other in (c).
-		(e) growing the buildings in (d) with distance $\dtrm{G}$.
-		(f) buffering the grown buildings in (e) with distance 
+		(e) Growing the buildings in (d) with distance $\dtrm{G}$.
+		(f) Buffering the grown buildings in (e) with distance 
 		$d_{\epsilon,t}/2$ using round joins.
-		(g) aggregating buildings $p$, $q$ and~$r$ by adding bridges.
-		(h) growing the buildings in (g) with distance $\dtrm{G}$.
-		(i) buffering the grown buildings in (h) with distance 
+		(g) Aggregating buildings $p$, $q$ and~$r$ by adding bridges.
+		(h) Growing the buildings in (g) with distance $\dtrm{G}$.
+		(i) Buffering the grown buildings in (h) with distance 
 		$d_{\epsilon,t}/2$ using round joins.
@@
 		(a) Merging the polygons of \fig\ref{fig:Shrink_Erosion}c and 
-		\fig\ref{fig:Shrink_Erosion}g;
+		\fig\ref{fig:Shrink_Erosion}g.
 		(b) Merging the polygons of \fig\ref{fig:Shrink_Simplification}c and 
-		\fig\ref{fig:Shrink_Simplification}h;
+		\fig\ref{fig:Shrink_Simplification}h.
 	}
@@
 That is why we eliminate a building aggregate if the area of this building is 
-smaller than a 
-threshold.
+smaller than a threshold.
 Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
@@
 instead of considering each building individually.
+
+As mentioned in \sect\ref{sec:DilationErosion}, 
+we remove holes that have area less than 
+$a_\mathrm{h} = 8\,\mathrm{mm}^2$ on map.
+The real area threshold for a hole at time $t$ is
+\[
+a_{\mathrm{h},t}=a_\mathrm{h}\cdot M_t^2.
+\]
 
@@
 and $l=0.3\,\mathrm{mm}$.
-In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
+In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
 according to our settings.
@@
 		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
+		for the region marked by the dashed circle.
 	}
 	\label{fig:GoalShape}
+\end{figure*}
+
+We produce a sequence of $10$ maps, which means $t \in \{0.1, 0.2, \dots, 1\}$.
+This production cost $668.2\,\mathrm{s}$ in total.
+We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
+the marked region in \fig\ref{fig:GoalShape}.
+
+\fig\ref{fig:ExperimentalComparison} shows a comparison of 
+our result at time $t=1$
+and the data from IGN at scale $1:50{,}000$.
+No small buildings are removed in our result or the IGN data.
+The boundaries of our built-up areas are more straight than that of IGN data, 
+where we have $1{,}135$ edges while the data has $4{,}968$ edges.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics{ContinuousGeneralization}
+	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
+		for the region marked in \fig\ref{fig:GoalShape}.
+	}
+	\label{fig:ContinuousGeneralization}
 \end{figure*}
@@
 	\includegraphics{ExperimentalComparison}
-	\caption{.
+	\caption{A comparison of our result and the existing data at scale 
+	$1:50{,}000$.
+		The brighter gray polygons represent the original buildings.
+		The darker gray polygons are our result at time $t=1$.
+		The gray polylines represent the data of the built-up areas at scale 
+		$1:50{,}000$ from IGN, where some built-up areas are split because some 
+		streets cross these areas.
 	}
@@
 
-The area on start map is $some number\,\text{mm}^2$.
-Our area on map is $some number\,\text{mm}^2$.
-According to \eq4 of paper \citet{Topfer1966}, 
-the area on map should be $some number\,\text{mm}^2$
+%The area on start map is $some number\,\text{mm}^2$.
+%Our area on map is $some number\,\text{mm}^2$.
+%According to \eq4 of paper \citet{Topfer1966}, 
+%the area on map should be $some number\,\text{mm}^2$
 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added a figure for number of buildings

@@
 		There are $2{,}590$ buildings, 
-		which have $19{,}255$ edges in total.}
+		which in total have $19{,}255$ edges and have area
+		$448{,}996.8\,\mathrm{mm}^2$.}
 	\label{fig:Data}
+\end{figure}
+
+%	axis x line=bottom,
+%axis y line=left,
+\begin{figure}[tb]
+	\centering
+	\begin{tikzpicture}[]
+	\begin{axis}[
+	width= \linewidth-0.1cm,
+	axis lines = left,
+%	axis x line=center,
+%	axis y line=left,
+	xtick={0.1,0.2,...,1},
+	ytick={500,1000,...,3000},
+	xlabel={$t$},
+	ylabel={number of buildings},
+%	xlabel style={below right},
+%	ylabel style={above left},
+	xmin=0,
+	xmax=1.1,
+	ymin=0,
+	ymax=3200,
+	cycle list name=black white,
+	]
+	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
+	\addplot+  coordinates {
+		(0,2590)
+		(0.1,1963)
+		(0.2,758)
+		(0.3,304)
+		(0.4,177)
+		(0.5,122)
+		(0.6,92)
+		(0.7,73)
+		(0.8,66)
+		(0.9,59)
+		(1,56)		
+	};
+	\legend{\quad $M=200{,}000$, \quad $M=400{,}000$}
+	\end{axis}
+	\end{tikzpicture}
+	\caption{The numbers of regions where our approach was 
+		forced to use the given overestimation factors in order 
+		to 
+		find a solution without exploring more than $M \in 
+		\{200{,}000,~400{,}000\}$ nodes of the subdivision 
+		graph.}
+	\label{fig:OverestimationStatistics}
 \end{figure}
@@
 where we have $1{,}135$ edges while the data has $4{,}968$ edges.
+From this perspective, we would say that our result is 
+more reasonable than the existing data.
+A questionnaire, however, is needed to compare our result with the data.
+
+Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.
 
@@
 
+We proposed a method to continuously generalize buildings to built-up areas
+by aggregating and growing.
+Using
+
 Our intermediate results may violate more cartographic rules, but we try to 

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
an available version

@@
 
+When buildings are grown and aggregated iteratively, bridges are added, 
+and these bridges have a width of $2\dtrm{G}$ at time $t$.
+This setting guarantees that no bridge is thin when $t=1$.
+As we aggregated all buildings that will be too close, 
+we are able to guarantee that 
+there is no pair of buildings 
+which has separation distance less than $d_{\epsilon, t}$.
+
 \begin{figure}[tb]
@@
 
-When buildings are grown and aggregated iteratively, bridges are added, 
-and these bridges have a width of $2\dtrm{G}$ at time $t$.
-This setting guarantees that no bridge is thin when $t=1$.
-
-This agrregation process creates new small details that need to be removed. So, 
-the aggregated buildings are simplified using Imai--Iri algorithm 
+As the scale is decreasing ($M_t$ increases), 
+we should remove more and more details. 
+So, the aggregated and grown buildings are simplified using Imai--Iri algorithm 
 \citep{ImaiIri1988}.
@@
 If a shortcut is outside,
-we are not able to arrive at the shortcut by growing.
+we may be not able to arrive at the shortcut by growing.
 Second, a shortcut is not allowed to intersect the aggregated building.
@@
 which is from the French Mapping Agency (IGN).
-The data represents the buildings of four towns (communes in French), 
+The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
+It represents the buildings of four towns (communes in French), 
 i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
@@
 
-We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
+We set our goal scale at $1:50{,}000$, which means $M_\mathrm{g}=50{,}000$,
+and $d_\mathrm{G}=25\,\mathrm{m}$
 so that we can compare our result with the exiting data.
 Also, this setting makes \eq\ref{eq:S_g} hold, 
-where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
-and $l=0.3\,\mathrm{mm}$.
+where $l=0.3\,\mathrm{mm}$.
 In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
@@
 
-%	axis x line=bottom,
-%axis y line=left,
+We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
+This production cost $668.2\,\mathrm{s}$ in total.
+We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
+the marked region in \fig\ref{fig:GoalShape}.
+We counted the numbers of buildings in our results,
+and compared our numbers to the numbers calculated by T\"opfer's radical law
+(see \fig\ref{fig:BuilidngNumber}).
+We have unexaggerated-area symbols, 
+so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
+As a result, we computed the number according to
+\[
+n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
+\]
+where $n_s=2{,}590$ is the number of buildings on start map
+and $n_t$ is the number of buildings on a map at scale $1:M_t$.
+According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
+the numbers from the radical law.
+It seems that our result supports the fractal law proposed by \citet{Jiang2015}.
+
 \begin{figure}[tb]
@@
 	ylabel={number of buildings},
-%	xlabel style={below right},
+	xlabel style={below right},
+	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
+	xlabel style={at={(axis description cs:1,0)},anchor=north},
 	%	ylabel style={above left},
@@
 	};
-	\legend{\quad $M=200{,}000$, \quad $M=400{,}000$}
+	\legend{\quad radical law, \quad our results}
 	\end{axis}
 	\end{tikzpicture}
-	\caption{The numbers of regions where our approach was 
-		forced to use the given overestimation factors in order 
-		to 
-		find a solution without exploring more than $M \in 
-		\{200{,}000,~400{,}000\}$ nodes of the subdivision 
-		graph.}
-	\label{fig:OverestimationStatistics}
+	\caption{A comparison of the numbers of building between our results and 
+		T\"opfer's radical law.}
+	\label{fig:BuilidngNumber}
 \end{figure}
+
+\fig\ref{fig:ExperimentalComparison} shows a comparison of 
+our result at time $t=1$
+and the data from IGN at scale $1:50{,}000$.
+No small buildings are removed in our result or the IGN data.
+The boundaries of our built-up areas are more straight than that of IGN data, 
+where we have $1{,}135$ edges while the data has $4{,}968$ edges.
+From this perspective, we would say that our result is 
+more reasonable than the existing data.
+A questionnaire, however, is needed to make a more convincing comparison.
+
+%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.
 
@@
 \end{figure*}
-
-We produce a sequence of $10$ maps, which means $t \in \{0.1, 0.2, \dots, 1\}$.
-This production cost $668.2\,\mathrm{s}$ in total.
-We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
-the marked region in \fig\ref{fig:GoalShape}.
-
-\fig\ref{fig:ExperimentalComparison} shows a comparison of 
-our result at time $t=1$
-and the data from IGN at scale $1:50{,}000$.
-No small buildings are removed in our result or the IGN data.
-The boundaries of our built-up areas are more straight than that of IGN data, 
-where we have $1{,}135$ edges while the data has $4{,}968$ edges.
-From this perspective, we would say that our result is 
-more reasonable than the existing data.
-A questionnaire, however, is needed to compare our result with the data.
-
-Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.
 
@@
 by aggregating and growing.
-Using
+We managed to produce a sequence of maps 
+in which the buildings are always growing and, at the same time, are simplified.
+For the goal map at scale $1:50{,}000$,
+the shapes of our built-up areas are more reasonable than the data from IGN.
 
-Our intermediate results may violate more cartographic rules, but we try to 
-make the results at goal scales violate as few rules as possible.
+It is always interesting to know what is the quantity we should keep on a map.
+We compared the number of buildings between our results and the calculated 
+numbers from T\"opfer's radical law.
+It turned out that our numbers decreased too fast.
+We may also take into account the fractal law of \citet{Jiang2015}.
+Another interesting problem is to compare the area of the buildings.
 
@@
 
-We used radical law. We may also consider the fractal nature of maps proposed 
-by \citet{Jiang2015}.
-
-We did not include streets. We can either put them above the settlement 
-boundaries on map, or use them as restriction for building growing.
-
-Show some results obtained by ArcGIS.
-Show the data at $1:50{,}000$.
-
-A special kind of Voronoi diagram considering miter offset. A buildings is 
-allowed to grow inside its own zone.
-
-\todo[inline]{consider multi bridges; 
-	consider transparency of bridges in stead of enlarging}
+%A special kind of Voronoi diagram considering miter offset. A buildings is 
+%allowed to grow inside its own zone.

### 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
explained in a figure what a bay is, and what is the width of the bay

@@
 \usepackage{gensymb}  % for degree sign, e.g., temperature
+\usepackage{tikz,pgfplots}
+\pgfplotsset{compat=1.3} %make y lable compact in a tikz picture with axes
 
@@
 \begin{document}
-\title{Continuous Generalization of Buildings \\ by Growing and Aggregating}
+\title{Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating 
+and Growing}
 %\titlenote{Produces the permission block, and
@@
 by adding bridges.
-We grow (bridge) original buildings based on buffering 
-and simplify the grown buildings.
+We grow (bridge) original buildings based on buffering, 
+and we also simplify the grown buildings.
 We take into account the shapes of the buildings 

### 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
explained in a figure what a bay is, and what is the width of the bay

@@
 We aggregate original buildings which will be too close at an output scale 
-by introducing bridges.
+by adding bridges.
 We grow (bridged) original buildings by buffering,
@@
 When dilated buildings become too close at time $t$
-and we aggregate them by introducing bridges.
+and we aggregate them by adding bridges.
 We grow the (bridged) original buildings by buffering with miter joins.
@@
 Our proposition is to dilate and erode the buildings, to remove dents and 
-bumps that can occur when buildings grow.
+bumps that can occur when buildings grow
 (see \fig\ref{fig:RemoveDentAndBump}).
-The operations of dilation and erosion are available from library 
-\textsc{Clipper} \citep{Johnson2014}.
 
@@
 
-We wish to remove ``bays'' 
-which have ``widths'' less than $2 r_\mathrm{h}$. 
+A ``bay'' may appear when we grow a bridged building
+(see \fig\ref{fig:RemoveBay}b).
+We remove such a bay by dilating (see \fig\ref{fig:RemoveBay}c)
+and then eroding (see \fig\ref{fig:RemoveBay}d) with distance $\dtrm{D}$.
+We define the width of a bay as the diameter of the largest circle 
+that can be placed in the bay.
+If the width of a bay is smaller than $2\dtrm{D}$, 
+then the bay can be removed by dilating and eroding with distance $\dtrm{D}$.
+We wish to remove bays 
+which have widths less than $2 r_\mathrm{h}$.
 Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
-is the radius of a hole which is just large enough to be presented on map.
-Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
-on map.
+is the radius of a hole 
+which is just large enough to be presented on map.
+Following \citep{Chaudhry2008}, 
+we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ on map.
 Sometimes, our $\dtrm{D}$ is not large enough to do so 
@@
 
-\todo{please explain in a figure what a bay is, and what is the width of the 
-bay}
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{RemoveBay}
+	\caption{Removing a bay by dilating and eroding.
+		(a) An aggregated building by adding bridges 
+		(see \sect\ref{sec:Aggregate}).
+		(b) Growing the aggregated building with distance~$\dtrm{G}$,
+		where the marked a region is a bay.
+		(c) Dilating the grown building with~$\dtrm{D}$.
+		(d) Eroding the dilated building with~$\dtrm{D}$.
+	}
+	\label{fig:RemoveBay}
+\end{figure}
 
@@
 	\includegraphics[draft=false]{GrowAndBridge}
-	\caption{Aggregating original buildings in the same group by introducing 
+	\caption{Aggregating original buildings in the same group by adding 
 		bridges.
@@
 \fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
-In \fig\ref{fig:GoalShape}b,
-the $56$ built-up areas have $2{,}095$ edges before line simplification.
+The $56$ built-up areas have $2{,}095$ edges before line simplification.
 Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
@@
 		which in total have $19{,}255$ edges and have area
-		$448{,}996.8\,\mathrm{mm}^2$.}
+		$448{,}996.8\,\mathrm{m}^2$.}
 	\label{fig:Data}
@@
 	\begin{axis}[
+	height=5cm,
 	width= \linewidth-0.1cm,
@@
 
-%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.
+%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
 

### 2017-09-20 ContinuousGeneralizer/MorphingClass/CHelpFunc.cs

@@ -81,7 +81,7 @@ namespace MorphingClass.CUtility
         //private static string _strPath = "C:\\MyWork\\DailyWork\\ContinuousGeneralisation\\ContinuousGeneralisation_Data\\AreaAggregation\\" + _strDataFolderName + "\\";
 
         //private static string _strDataFolderName = "France";
-        private static string _strDataFolderName = "France_FourTowns";
+        //private static string _strDataFolderName = "France_FourTowns";
         //private static string _strDataFolderName = "France_FourTowns_Several";
         //private static string _strDataFolderName = "France_Part";
         //private static string _strDataFolderName = "France_FourBuildings";
@@ -94,7 +94,7 @@ namespace MorphingClass.CUtility
         //private static string _strDataFolderName = "France_Presenting_RemoveSpikeAndPit";
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Erosion";
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Simplification";
-        //private static string _strDataFolderName = "France_Presenting_RemoveBay";
+        private static string _strDataFolderName = "France_Presenting_RemoveBay";
         //private static string _strDataFolderName = "France_Presenting_Grouping";
         //private static string _strDataFolderName = "France_Presenting_BridgeMoreBuilding";
 

### 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved figures/Buffer_ThreeKinds.pdf

@@
 
-There are two typical ways of buffering a polygon, i.e.,
-using round joins or using miter joins 
-(see \fig\ref{fig:Buffer_TwoKinds}).
-We choose the second way in order to
+There are three typical joins for buffering a polygon, i.e.,
+round, miter, and square joins
+(see \fig\ref{fig:Buffer_ThreeKinds}).
+We choose the miter joins to grow in order to
 preserve the right angles of buildings.
@@
 	\centering
-	\includegraphics{Buffer_TwoKinds}
-	\caption{Buffering a polygon using round joins and using miter joins.}
-	\label{fig:Buffer_TwoKinds}
+	\includegraphics{Buffer_ThreeKinds}
+	\caption{Buffering a polygon using round, miter, and square joins.}
+	\label{fig:Buffer_ThreeKinds}
 \end{figure}
@@
 		(b) Growing the aggregated building with distance~$\dtrm{G}$,
-		where the marked a region is a bay.
+		where the region marked by the dashed circle is a bay.
 		(c) Dilating the grown building with~$\dtrm{D}$.
@@
 Our way of detecting close buildings is simple.
-We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins.
+We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins
+(see \fig\ref{fig:Buffer_ThreeKinds}b).
 We merge the buffers that overlap each other.

### 2017-09-21 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved case study and conclusion

@@
 
+\todo{not intersecting buildings from a previous step?}
+
 The classical way to filter points in a polyline or polygon is the 
@@
 For a group of buildings that will be aggregated into one built-up area at time 
-$t=1$, we consider the area sum of all the buildings at time $t$, 
+$t=1$, we consider the area sum of all the buildings at any time $t$, 
 instead of considering each building individually.
@@
 C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
-The offsetting function and clipping function are from library \textsc{Clipper} 
-of \citet{Johnson2014}.
+The offsetting function and clipping function 
+are available from library \textsc{Clipper} of \citet{Johnson2014}.
 The offsetting function realizes 
@@
 \emph{Stopwatch}.
-\fig\ref{fig:Data} shows our testing data, 
-which is from the French Mapping Agency (IGN).
+Our testing data is from the French Mapping Agency (IGN);
+see \fig\ref{fig:Data}.
 The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
-It represents the buildings of four towns (communes in French), 
+It represents the buildings of four towns, 
 i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
 in the Pyr\'en\'ees-Atlantiques department, south-western France.
+IGN also stores a dataset at scale $1:50{,}000$.
+This dataset was basically obtained from the data at scale $1:15{,}000$ 
+by buffering with distance $25\,\mathrm{m}$.
+Sometimes distance $50\,\mathrm{m}$ was also used when buffering
+in order to identify towns.
+A town is defined by \citet{Boffet2000} that the longest edge in an MST of the 
+buildings should be shorter than $100\,\mathrm{m}$.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Data}
+	\caption{Data.
+		There are $2{,}590$ buildings, 
+		which in total have $19{,}255$ edges and have area
+		$448{,}996.8\,\mathrm{m}^2$.}
+	\label{fig:Data}
+\end{figure}
 
@@
 Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
-In comparison, there are $1{,}597$ edges left if we simplify using
+In comparison, there are $1{,}597$ edges left when we simplified using
 the Douglas--Peucker algorithm.
 
-\begin{figure}[tb]
-	\centering
-	\includegraphics{Data}
-	\caption{Data.
-		There are $2{,}590$ buildings, 
-		which in total have $19{,}255$ edges and have area
-		$448{,}996.8\,\mathrm{m}^2$.}
-	\label{fig:Data}
-\end{figure}
+\begin{figure*}[tb]
+	\centering
+	\includegraphics{GoalShape}
+	\caption{Bridged original buildings 
+		and goal shapes of the built-up areas (without removing small holes), 
+		at scale $1:50{,}000$.
+		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
+		for the region marked by the dashed circle.
+	}
+	\label{fig:GoalShape}
+\end{figure*}
 
@@
 We have unexaggerated-area symbols, 
-so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
-As a result, we computed the number according to
+so for \eq2 of \citet{Topfer1966} we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
+As a result, we computed the numbers according to
 \[
@@
 It seems that our result supports the fractal law proposed by \citet{Jiang2015}.
+
+\begin{figure*}[tb]
+	\centering
+	\includegraphics{ContinuousGeneralization}
+	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
+		for the region marked in \fig\ref{fig:GoalShape}.
+	}
+	\label{fig:ContinuousGeneralization}
+\end{figure*}
 
@@
 	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
+%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
 	\addplot+  coordinates {
@@
 our result at time $t=1$
-and the data from IGN at scale $1:50{,}000$.
-No small buildings are removed in our result or the IGN data.
+and the data at scale $1:50{,}000$.
+No small building is removed in our result or the existing data.
 The boundaries of our built-up areas are more straight than that of IGN data, 
@@
 %Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{GoalShape}
-	\caption{Bridged original buildings 
-		and goal shapes of the built-up areas (without removing small holes), 
-		at scale $1:50{,}000$.
-		There are $56$ built-up areas, which have $1{,}102$ edges in total.
-		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
-		for the region marked by the dashed circle.
-	}
-	\label{fig:GoalShape}
-\end{figure*}
-
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{ContinuousGeneralization}
-	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
-		for the region marked in \fig\ref{fig:GoalShape}.
-	}
-	\label{fig:ContinuousGeneralization}
-\end{figure*}
 
@@
 
+%\section{Case Study}
+%\label{sec:CaseStudy}
+%We have implemented our method based on
+%C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
+%The offsetting function and clipping function are from library 
+%\textsc{Clipper} 
+%of \citet{Johnson2014}.
+%The offsetting function realizes 
+%our operations of buffering, dilating, eroding, and merging.
+%An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
+%We ran our case study under 64-bit 
+%Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
+%We measured processing time by the built-in C\# class 
+%\emph{Stopwatch}.
+%\fig\ref{fig:Data} shows our testing data, 
+%which is from the French Mapping Agency (IGN).
+%The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
+%It represents the buildings of four towns (communes in French), 
+%i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
+%in the Pyr\'en\'ees-Atlantiques department, south-western France.
+%
+%We set our goal scale at $1:50{,}000$, which means $M_\mathrm{g}=50{,}000$,
+%and $d_\mathrm{G}=25\,\mathrm{m}$
+%so that we can compare our result with the exiting data.
+%Also, this setting makes \eq\ref{eq:S_g} hold, 
+%where $l=0.3\,\mathrm{mm}$.
+%In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
+%according to our settings.
+%As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
+%where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
+%according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
+%
+%Our program took $93.6\,\mathrm{s}$ 
+%to compute the goal shapes of the built-up areas.
+%\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
+%The $56$ built-up areas have $2{,}095$ edges before line simplification.
+%Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
+%In comparison, there are $1{,}597$ edges left if we simplify using
+%the Douglas--Peucker algorithm.
+%
+%\begin{figure}[tb]
+%	\centering
+%	\includegraphics{Data}
+%	\caption{Data.
+%		There are $2{,}590$ buildings, 
+%		which in total have $19{,}255$ edges and have area
+%		$448{,}996.8\,\mathrm{m}^2$.}
+%	\label{fig:Data}
+%\end{figure}
+%
+%
+%We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
+%This production cost $668.2\,\mathrm{s}$ in total.
+%We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
+%the marked region in \fig\ref{fig:GoalShape}.
+%We counted the numbers of buildings in our results,
+%and compared our numbers to the numbers calculated by T\"opfer's radical law
+%(see \fig\ref{fig:BuilidngNumber}).
+%We have unexaggerated-area symbols, 
+%so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
+%As a result, we computed the number according to
+%\[
+%n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
+%\]
+%where $n_s=2{,}590$ is the number of buildings on start map
+%and $n_t$ is the number of buildings on a map at scale $1:M_t$.
+%According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
+%the numbers from the radical law.
+%It seems that our result supports the fractal law proposed by 
+%\citet{Jiang2015}.
+%
+%
+%
+%\begin{figure}[tb]
+%	\centering
+%	\begin{tikzpicture}[]
+%	\begin{axis}[
+%	height=5cm,
+%	width= \linewidth-0.1cm,
+%	axis lines = left,
+%	%	axis x line=center,
+%	%	axis y line=left,
+%	xtick={0.1,0.2,...,1},
+%	ytick={500,1000,...,3000},
+%	xlabel={$t$},
+%	ylabel={number of buildings},
+%	xlabel style={below right},
+%	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
+%	xlabel style={at={(axis description cs:1,0)},anchor=north},
+%	%	ylabel style={above left},
+%	xmin=0,
+%	xmax=1.1,
+%	ymin=0,
+%	ymax=3200,
+%	cycle list name=black white,
+%	]
+%	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
+%	\addplot+  coordinates {
+%		(0,2590)
+%		(0.1,1963)
+%		(0.2,758)
+%		(0.3,304)
+%		(0.4,177)
+%		(0.5,122)
+%		(0.6,92)
+%		(0.7,73)
+%		(0.8,66)
+%		(0.9,59)
+%		(1,56)		
+%	};
+%	\legend{\quad radical law, \quad our results}
+%	\end{axis}
+%	\end{tikzpicture}
+%	\caption{A comparison of the numbers of building between our results and 
+%		T\"opfer's radical law.}
+%	\label{fig:BuilidngNumber}
+%\end{figure}
+%
+%\fig\ref{fig:ExperimentalComparison} shows a comparison of 
+%our result at time $t=1$
+%and the data from IGN at scale $1:50{,}000$.
+%No small buildings are removed in our result or the IGN data.
+%The boundaries of our built-up areas are more straight than that of IGN data, 
+%where we have $1{,}135$ edges while the data has $4{,}968$ edges.
+%From this perspective, we would say that our result is 
+%more reasonable than the existing data.
+%A questionnaire, however, is needed to make a more convincing comparison.
+%
+%%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
+%
+%
+%
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{GoalShape}
+%	\caption{Bridged original buildings 
+%		and goal shapes of the built-up areas (without removing small holes), 
+%		at scale $1:50{,}000$.
+%		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+%		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
+%		for the region marked by the dashed circle.
+%	}
+%	\label{fig:GoalShape}
+%\end{figure*}
+%
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{ContinuousGeneralization}
+%	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
+%		for the region marked in \fig\ref{fig:GoalShape}.
+%	}
+%	\label{fig:ContinuousGeneralization}
+%\end{figure*}
+%
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{ExperimentalComparison}
+%	\caption{A comparison of our result and the existing data at scale 
+%	$1:50{,}000$.
+%		The brighter gray polygons represent the original buildings.
+%		The darker gray polygons are our result at time $t=1$.
+%		The gray polylines represent the data of the built-up areas at scale 
+%		$1:50{,}000$ from IGN, where some built-up areas are split because some 
+%		streets cross these areas.
+%	}
+%	\label{fig:ExperimentalComparison}
+%\end{figure*}
+%
+%
+%%The area on start map is $some number\,\text{mm}^2$.
+%%Our area on map is $some number\,\text{mm}^2$.
+%%According to \eq4 of paper \citet{Topfer1966}, 
+%%the area on map should be $some number\,\text{mm}^2$
+%
+%%Although a version with a 
+%%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
+%%version
+
 \section{Conclusion}
@@
 It is always interesting to know what is the quantity we should keep on a map.
-We compared the number of buildings between our results and the calculated 
-numbers from T\"opfer's radical law.
+We compared the numbers of buildings of our results 
+with the numbers calculated by T\"opfer's radical law.
 It turned out that our numbers decreased too fast.

### 2017-09-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
section 3 and conclusion revision

@@
 We have implemented our method based on
-C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
+C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. The code is available in open source on Github \footnote{https://github.com/IGNF/Continuous-Generalisation}.
 The offsetting function and clipping function 
 are available from library \textsc{Clipper} of \citet{Johnson2014}.
-The offsetting function realizes 
-our operations of buffering, dilating, eroding, and merging.
+The offsetting function is used for the buffering, dilation, erodion, and merge operations.
 An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
@@
 \emph{Stopwatch}.
-Our testing data is from the French Mapping Agency (IGN);
+Our testing data is extracted from a dataset produced the French Mapping Agency (IGN);
 see \fig\ref{fig:Data}.
@@
 i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
-in the Pyr\'en\'ees-Atlantiques department, south-western France.
+in the Pyr\'en\'ees-Atlantiques county, south-western France.
 IGN also stores a dataset at scale $1:50{,}000$.
@@
 in order to identify towns.
-A town is defined by \citet{Boffet2000} that the longest edge in an MST of the 
+A town is defined by \citet{Boffet2000} as follows: the longest edge in an MST of the 
 buildings should be shorter than $100\,\mathrm{m}$.
@@
 We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
-This production cost $668.2\,\mathrm{s}$ in total.
+This production costs $668.2\,\mathrm{s}$ in total.
 We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
@@
 It is always interesting to know what is the quantity we should keep on a map.
-We compared the numbers of buildings of our results 
-with the numbers calculated by T\"opfer's radical law.
-It turned out that our numbers decreased too fast.
-We may also take into account the fractal law of \citet{Jiang2015}.
+We compared the numbers of buildings of our results, and it is consistent with the fractak radical law from \citet{Jiang2015}.
 Another interesting problem is to compare the area of the buildings.
-
 Eventually, our result is a set of settlement boundaries. An interesting 
 problem is to compare our method with \citet{Chaudhry2008}.
+This method is supposed to provide a smooth transition between representations with individual buildings and representations with built-up areas, but the only way to verify that smoothness is achieved is to carry out a user survey where our approach is compared to non continuous generalization approaches.
 

### 2017-09-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
a little improvement

--- 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
-The offsetting function and clipping function are from library \textsc{Clipper} 
-of \citet{Johnson2014}.
-The offsetting function realizes 
-our operations of buffering, dilating, eroding, and merging.
+The code is available in open source on 
+Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
+The offsetting function and clipping function 
+are available from library \textsc{Clipper} of \citet{Johnson2014}.
+The offsetting function is used for the buffering, dilation, erodion, and merge operations.
 An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
@@
 \emph{Stopwatch}.
-\fig\ref{fig:Data} shows our testing data, 
-which is from the French Mapping Agency (IGN).
+Our testing data is extracted from a dataset produced 
+by the French Mapping Agency (IGN);
+see \fig\ref{fig:Data}.
 The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
-It represents the buildings of four towns (communes in French), 
+It represents the buildings of four towns, 
 i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
-in the Pyr\'en\'ees-Atlantiques department, south-western France.
+in the Pyr\'en\'ees-Atlantiques county, south-western France.
+IGN also stores a dataset at scale $1:50{,}000$.
+This dataset was basically obtained from the data at scale $1:15{,}000$ 
+by buffering with distance $25\,\mathrm{m}$,
+where sometimes distance $50\,\mathrm{m}$ was also used
+in order to identify towns.
+A restriction for the town from \citet{Boffet2000} is that 
+the longest edge in an MST of the buildings 
+should be shorter than $100\,\mathrm{m}$.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics{Data}
+	\caption{Data.
+		There are $2{,}590$ buildings, 
+		which in total have $19{,}255$ edges and have area
+		$448{,}996.8\,\mathrm{m}^2$.}
+	\label{fig:Data}
+\end{figure}
 
@@
 Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
-In comparison, there are $1{,}597$ edges left if we simplify using
+In comparison, there are $1{,}597$ edges left when we simplified using
 the Douglas--Peucker algorithm.
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
 	\centering
-	\includegraphics{Data}
-	\caption{Data.
-		There are $2{,}590$ buildings, 
-		which in total have $19{,}255$ edges and have area
-		$448{,}996.8\,\mathrm{m}^2$.}
-	\label{fig:Data}
-\end{figure}
+	\includegraphics{GoalShape}
+	\caption{Bridged original buildings 
+		and goal shapes of the built-up areas (without removing small holes), 
+		at scale $1:50{,}000$.
+		There are $56$ built-up areas, which have $1{,}102$ edges in total.
+		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
+		for the region marked by the dashed circle.
+	}
+	\label{fig:GoalShape}
+\end{figure*}
 
 We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
-This production cost $668.2\,\mathrm{s}$ in total.
+This production costs $668.2\,\mathrm{s}$ in total.
 We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
@@
 \end{figure*}
-
-%The area on start map is $some number\,\text{mm}^2$.
-%Our area on map is $some number\,\text{mm}^2$.
-%According to \eq4 of paper \citet{Topfer1966}, 
-%the area on map should be $some number\,\text{mm}^2$
 
@@
 It is always interesting to know what is the quantity we should keep on a map.
-We compared the number of buildings between our results and the calculated 
-numbers from T\"opfer's radical law.
-It turned out that our numbers decreased too fast.
-We may also take into account the fractal law of \citet{Jiang2015}.
+We compared the numbers of buildings of our results, and it is consistent with 
+the fractal law from \citet{Jiang2015}.
 Another interesting problem is to compare the area of the buildings.
-
 Eventually, our result is a set of settlement boundaries. An interesting 
 problem is to compare our method with \citet{Chaudhry2008}.
+Our method is supposed to provide a smooth transition between representations 
+with individual buildings and representations with built-up areas, but the only 
+way to verify that smoothness is achieved is to carry out a user survey where 
+our approach is compared to non continuous generalization approaches.
 

### 2017-10-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved some codes

@@
 are available from library \textsc{Clipper} of \citet{Johnson2014}.
-The offsetting function is used for the buffering, dilation, erodion, and merge operations.
+The offsetting function is used for the buffering, dilation, 
+erosion, and merge operations.
 An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
@@
 
-\begin{figure}[tb]
-	\centering
-	\begin{tikzpicture}[]
-	\begin{axis}[
-	height=5cm,
-	width= \linewidth-0.1cm,
-	axis lines = left,
-	%	axis x line=center,
-	%	axis y line=left,
-	xtick={0.1,0.2,...,1},
-	ytick={500,1000,...,3000},
-	xlabel={$t$},
-	ylabel={number of buildings},
-	xlabel style={below right},
-	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
-	xlabel style={at={(axis description cs:1,0)},anchor=north},
-	%	ylabel style={above left},
-	xmin=0,
-	xmax=1.1,
-	ymin=0,
-	ymax=3200,
-	cycle list name=black white,
-	]
-	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
-%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
-	\addplot+  coordinates {
-		(0,2590)
-		(0.1,1963)
-		(0.2,758)
-		(0.3,304)
-		(0.4,177)
-		(0.5,122)
-		(0.6,92)
-		(0.7,73)
-		(0.8,66)
-		(0.9,59)
-		(1,56)		
-	};
-	\legend{\quad radical law, \quad our results}
-	\end{axis}
-	\end{tikzpicture}
-	\caption{A comparison of the numbers of building between our results and 
-		T\"opfer's radical law.}
-	\label{fig:BuilidngNumber}
-\end{figure}
+%\begin{figure}[tb]
+%	\centering
+%	\begin{tikzpicture}[]
+%	\begin{axis}[
+%	height=5cm,
+%	width= \linewidth-0.1cm,
+%	axis lines = left,
+%	%	axis x line=center,
+%	%	axis y line=left,
+%	xtick={0.1,0.2,...,1},
+%	ytick={500,1000,...,3000},
+%	xlabel={$t$},
+%	ylabel={number of buildings},
+%	xlabel style={below right},
+%	%	ylabel style={at={(axis description 
+%%cs:0,1.1)},rotate=270,anchor=north},
+%	xlabel style={at={(axis description cs:1,0)},anchor=north},
+%	%	ylabel style={above left},
+%	xmin=0,
+%	xmax=1.1,
+%	ymin=0,
+%	ymax=3200,
+%	cycle list name=black white,
+%	]
+%	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
+%%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* 
+%%x))^1.5};
+%	\addplot+  coordinates {
+%		(0,2590)
+%		(0.1,1963)
+%		(0.2,758)
+%		(0.3,304)
+%		(0.4,177)
+%		(0.5,122)
+%		(0.6,92)
+%		(0.7,73)
+%		(0.8,66)
+%		(0.9,59)
+%		(1,56)		
+%	};
+%	\legend{\quad radical law, \quad our results}
+%	\end{axis}
+%	\end{tikzpicture}
+%	\caption{A comparison of the numbers of building between our 
+%results and 
+%		T\"opfer's radical law.}
+%	\label{fig:BuilidngNumber}
+%\end{figure}
 

### 2017-10-16 ContinuousGeneralizer/MorphingClass/CGeneralizationMethods/CAreaAgg_Greedy.cs

@@ -1,236 +1,0 @@
-﻿using System;
-using System.Collections.Generic;
-using System.Diagnostics;
-using System.Linq;
-using System.Text;
-using ESRI.ArcGIS.Carto;
-using ESRI.ArcGIS.Catalog;
-using ESRI.ArcGIS.Controls;
-using ESRI.ArcGIS.DataSourcesFile;
-using ESRI.ArcGIS.Display;
-using ESRI.ArcGIS.Editor;
-using ESRI.ArcGIS.esriSystem;
-using ESRI.ArcGIS.GeoAnalyst;
-using ESRI.ArcGIS.Geodatabase;
-using ESRI.ArcGIS.Geometry;
-using ESRI.ArcGIS.Maplex;
-using ESRI.ArcGIS.Output;
-using ESRI.ArcGIS.SystemUI;
-
-using MorphingClass.CAid;
-using MorphingClass.CEntity;
-using MorphingClass.CMorphingMethods;
-using MorphingClass.CMorphingMethods.CMorphingMethodsBase;
-using MorphingClass.CUtility;
-using MorphingClass.CGeometry;
-using MorphingClass.CGeometry.CGeometryBase;
-using MorphingClass.CCorrepondObjects;
-
-namespace MorphingClass.CGeneralizationMethods
-{
-    public class CAreaAgg_Greedy : CAreaAgg_Base
-    {
-        public CAreaAgg_Greedy()
-        {
-
-        }
-
-        public CAreaAgg_Greedy(CParameterInitialize ParameterInitialize, string strSpecifiedFieldName = null, string strSpecifiedValue = null)
-        {
-            Preprocessing(ParameterInitialize, strSpecifiedFieldName, strSpecifiedValue);
-        }
-
-        public void AreaAggregation()
-        {
-
-            SetupBasic();
-            
-
-            CRegion._lngEstCountEdgeNumber = 0;
-            CRegion._lngEstCountEdgeLength = 0;
-            CRegion._lngEstCountEqual = 0;
-
-            for (int i = _intStart; i < _intEnd; i++)
-            {
-                Greedy(LSCrgLt[i], SSCrgLt[i], this.StrObjLtSD, _ParameterInitialize.strAreaAggregation);
-            }
-
-        }
-
-
-        public CRegion Greedy(CRegion LSCrg, CRegion SSCrg, CStrObjLtSD StrObjLtSD, string strAreaAggregation)
-        {
[…]

### 2017-10-16 ContinuousGeneralizer/MorphingClass/CUtility/CBin.cs

@@ -1,0 +1,1451 @@
+﻿using System;
+using System.Collections.Generic;
+using System.Linq;
+using System.Text;
+using System.Threading.Tasks;
+
+namespace MorphingClass.CUtility
+{
+    class CBin
+    {
+    }
+
+
+}
+
+#region CRegionOverestimationbyfactor
+//using System;
+//using System.Collections.Generic;
+//using System.Linq;
+//using System.Text;
+//using System.Windows.Forms;
+
+//using MorphingClass.CUtility;
+//using MorphingClass.CCorrepondObjects;
+//using MorphingClass.CGeometry.CGeometryBase;
+//using MorphingClass.CGeneralizationMethods;
+
+//namespace MorphingClass.CGeometry
+//{
+//    public class CRegion : CBasicBase
+//    {
+//        public static CRegion _pCrg;
+
+//        public static int _intNodeCount;  //The nodes of a map graph
+//        public static int _intEdgeCount;  //The edges of a map graph
+//        public static int _intStartStaticGIDLast;
+//        public static int _intStartStaticGIDAll;
+//        public static int _intStaticGID;
+//        public static int _intStaticTest;
+
+//        //public LinkedList<int> _IDLk;  //ID of the Region, where the ID is a LinkedList
+//        public static CCmpCRegion_Cost_CphGIDTypeIndex pCmpCRegion_Cost_CphGIDTypeIndex
+//            = new CCmpCRegion_Cost_CphGIDTypeIndex();  //this variable should be used for the queue Q
+
+//        //this comparer should be used for integrate the sequences for output 
+//        public static CCmpCRegion_MinArea_CphGIDTypeIndex pCmpCRegion_MinArea_CphGIDTypeIndex
+//            = new CCmpCRegion_MinArea_CphGIDTypeIndex();
+
+//        //this comparer should be used for integrate the sequences for output 
+//        public static CCmpCRegion_CostExact_CphGIDTypeIndex pCmpCRegion_CostExact_CphGIDTypeIndex
+//            = new CCmpCRegion_CostExact_CphGIDTypeIndex();
+
+//        //this comparer should be used for checking existing Crgs
+//        public static CCmpCRegion_CphGIDTypeIndex pCmpCRegion_CphGIDTypeIndex = new CCmpCRegion_CphGIDTypeIndex();
+
+//        //this comparer should be used for counting uncolored Crgs
+//        public static CCmpCRegion_CphGID pCmpCRegion_CphGID
[…]

### 2017-10-16 ContinuousGeneralizer/MorphingClass/CUtility/CGeoFunc.cs

@@ -49,11 +49,19 @@ namespace MorphingClass.CUtility
         //    CalDistanceParameters<T, T>(pTLt);
         //}
 
-        public static void CalDistanceParameters<T, CGeo>(List<T> pTLt) 
+        public static void CalDistanceParameters<T, CGeo>(List<T> pTLt, bool blnCalDistanceParameters = true) 
             where T : CPolyBase<CGeo>
             where CGeo : class
         {
-            double dblMidLength = CalMidLength<T, CGeo>(pTLt);
+            double dblMidLength = 0;
+            if (blnCalDistanceParameters == true)
+            {
+                dblMidLength = CalMidLength<T, CGeo>(pTLt);
+            }
+            else
+            {
+                dblMidLength = 1;
+            }
             
             CConstants.dblMidLength = dblMidLength;
             //CConstants.dblSmallDis = dblMidLength / CConstants.dblSmallDisDenominator;

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
improved figures/Buffer_ThreeKinds.pdf
improved the authors of some references; balanced the two columns of references at the last page
removed tex files of a branch version
improved some codes
moved a tikz figure to ipe figures/NumberOfBuildings.pdf
added file about copyright

@@
-\documentclass[sigconf, authordraft]{acmart}
+\documentclass[
+sigconf,
+screen, %hyperlinks are colored
+%authorversion,
+%authordraft %Whether author’s draft mode is enabled
+]{acmart}
 
@@
 %\usepackage[disable]{todonotes}
-\usepackage[colorinlistoftodos,prependcaption]{todonotes}
+\usepackage[colorinlistoftodos,prependcaption,disable]{todonotes}
 \usepackage{gensymb}  % for degree sign, e.g., temperature
-\usepackage{tikz,pgfplots}
-\pgfplotsset{compat=1.3} %make y lable compact in a tikz picture with axes
+\usepackage{balance}
+%\usepackage{tikz,pgfplots}
+%\pgfplotsset{compat=1.3} %make y lable compact in a tikz 
+%%picture with axes
 
@@
 
-\newcommand{\e}[1]{\times 10^{#1}}
 \newcommand{\fig}{Figure~}
@@
 \newcommand{\tabs}{Tables~}
-\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}
-
-% Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-\acmDOI{10.475/123_4}
-
-% ISBN
-\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[UrbanGIS'17]{International Workshop on Smart Cities and Urban 
-Analytics}{November 2017}{Redondo Beach, California USA} 
-\acmYear{2017}
-\copyrightyear{2017}
-
-\acmPrice{15.00}
-
-\acmSubmissionID{123-A12-B3}
+\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, 
+t\ifthenelse{\equal{#1}{}}{}{_#1}}}
 
 \begin{document}
-\title{Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating 
-and Growing}
+\title{Continuously Generalizing Buildings to Built-up Areas\\ 
+by Aggregating and Growing}
 %\titlenote{Produces the permission block, and
@@
 %\authornote{Dr.~Trovato insisted his name be first.}
-\orcid{1234-5678-9012}
+\orcid{0000-0001-6848-3545}
 \affiliation{%
@@
 
+\copyrightyear{2017}
+\acmYear{2017}
+\setcopyright{othergov}
+\acmConference[UrbanGIS'17]{UrbanGIS'17:3rd ACM SIGSPATIAL 
+	Workshop on Smart Cities and Urban Analytics }{November 
+	7--10, 
+	2017}{Redondo Beach, CA, USA}
+\acmBooktitle{UrbanGIS'17: UrbanGIS'17:3rd ACM SIGSPATIAL 
+	Workshop on Smart Cities and Urban Analytics , November 
+	7--10, 
+	2017, Redondo Beach, CA, USA}
+\acmPrice{15.00}
+\acmDOI{10.1145/3152178.3152188}
+\acmISBN{978-1-4503-5495-0/17/11}
+
 \keywords{multiple representation, zooming, simplification, buffer}
@@
 \bibliographystyle{ACM-Reference-Format}
+\balance %balance the two columns of references at the last page
 \bibliography{References}

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
moved a tikz figure to ipe figures/NumberOfBuildings.pdf
integrated two figures in case study into one

--- 2017-09-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
@@
 investigated based on 
-dynamic programming \citep{mnwb-mpstc-08}, 
+dynamic programming \citep{Noellenburg2008}, 
 Delaunay triangulations and binary line generalized tree (BLG-tree)  
@@
 
-\begin{figure*}[tb]
+\begin{figure}[tb]
 	\centering
-	\includegraphics[draft=false]{GrowAndBridge}
+	\includegraphics[]{GrowAndBridge}
 	\caption{Aggregating original buildings in the same group by adding 
@@
 	\label{fig:GrowAndBridge}
-\end{figure*}
+\end{figure}
 
@@
 
-%At any time $t$, some of the bridges are picked to aggregate buildings 
+%At any time $t$, some of the bridges are picked to aggregate 
+%buildings 
 %which grow to become too close.
@@
 %and an additional distance $d_{\epsilon, t}/2$
-%(the distance between two buildings should be at least $d_{\epsilon, t}$).
+%(the distance between two buildings should be at least 
+%$d_{\epsilon, t}$).
 %If two buffers overlap, 
 %then the original buildings are put in the same group.
-%However, as some parts of a building grow faster than other parts, 
+%However, as some parts of a building grow faster than other 
+%parts, 
 %this basic idea may cause problems.
@@
 %The advantage is that we guarantee that 
-%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
+%any two buildings have separate distance less than 
+%$d_{\epsilon, t}$ will be 
 %aggregated via bridges.
@@
 A shortcut is valid for a segment 
-if the distance between the segment and the shortcut is at most a specified 
-value
+if the distance between the segment and the shortcut 
+is at most a specified value
 (see \fig\ref{fig:ImaiIri_Shortcut}).
@@
 map polygon because of their isolation.
-That is why we eliminate a building aggregate if the area of this building is 
+That is why we eliminate a building aggregate if its area is 
 smaller than a threshold.
@@
 
-%\subsection{Running time analysis}
-%Although a version with a 
-%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
-%version.
+\subsection{Running time}
+
+Although a version with a 
+lower running time exists \citep[see][]{Chan1992}, we 
+implemented the basic 
+version.
 
@@
 The offsetting function and clipping function 
-are available from library \textsc{Clipper} of \citet{Johnson2014}.
-The offsetting function is used for the buffering, dilation, erodion, and merge operations.
+are available from library \textsc{Clipper} of 
+\citet{Johnson2014}, which is based on the clipping algorithm of
+\citet{Vatti1992Clip}.
+The offsetting function is used for the buffering, dilation, 
+erosion, and merge operations.
 An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
-We ran our case study under 64-bit 
-Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
+We ran our case study under~64-bit 
+Windows~7 on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
 We measured processing time by the built-in C\# class 
@@
 see \fig\ref{fig:Data}.
-The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
+The data is at scal~$1:15{,}000$, 
+which means~$M_\mathrm{s}=15{,}000$.
 It represents the buildings of four towns, 
@@
 in the Pyr\'en\'ees-Atlantiques county, south-western France.
-IGN also stores a dataset at scale $1:50{,}000$.
-This dataset was basically obtained from the data at scale $1:15{,}000$ 
-by buffering with distance $25\,\mathrm{m}$,
-where sometimes distance $50\,\mathrm{m}$ was also used
+IGN also stores a dataset at scale~$1:50{,}000$.
+This dataset was basically obtained 
+from the data at scale~$1:15{,}000$ 
+by buffering with distance~$25\,\mathrm{m}$,
+where sometimes distance~$50\,\mathrm{m}$ was also used
 in order to identify towns.
@@
 the longest edge in an MST of the buildings 
-should be shorter than $100\,\mathrm{m}$.
+should be shorter than~$100\,\mathrm{m}$.
 
@@
 
-We set our goal scale at $1:50{,}000$, which means $M_\mathrm{g}=50{,}000$,
-and $d_\mathrm{G}=25\,\mathrm{m}$
+We set our goal scale at~$1:50{,}000$, 
+which means~$M_\mathrm{g}=50{,}000$,
+and~$d_\mathrm{G}=25\,\mathrm{m}$
 so that we can compare our result with the exiting data.
 Also, this setting makes \eq\ref{eq:S_g} hold, 
-where $l=0.3\,\mathrm{mm}$.
+where~$l=0.3\,\mathrm{mm}$.
 In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
 according to our settings.
-As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
-where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
+As a result~$\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
+where~$\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
 according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
 
-Our program took $93.6\,\mathrm{s}$ 
+Our program took~$93.6\,\mathrm{s}$ 
 to compute the goal shapes of the built-up areas.
-\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
-The $56$ built-up areas have $2{,}095$ edges before line simplification.
-Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
-In comparison, there are $1{,}597$ edges left when we simplified using
+\fig\ref{fig:ExperimentalComparison} shows the bridged buildings 
+and the goal shapes.
+The~$56$ built-up areas have~$2{,}095$ edges before line 
+simplification.
+Using the Imai--Iri algorithm, we have~$1{,}102$ edges left.
+In comparison, there are~$1{,}597$ edges left when we simplified 
+using
 the Douglas--Peucker algorithm.
+
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{GoalShape}
+%	\caption{Bridged original buildings 
+%		and goal shapes of the built-up areas (without removing 
+%small holes), 
+%		at scale~$1:50{,}000$.
+%		There are~$56$ built-up areas, which have~$1{,}102$ 
+%		edges in total.
+%		We show a sequence of maps in 
+%\fig\ref{fig:ContinuousGeneralization} 
+%		for the region marked by the dashed circle.
+%	}
+%	\label{fig:GoalShape}
+%\end{figure*}
 
@@
 	\centering
-	\includegraphics{GoalShape}
-	\caption{Bridged original buildings 
-		and goal shapes of the built-up areas (without removing small holes), 
-		at scale $1:50{,}000$.
-		There are $56$ built-up areas, which have $1{,}102$ edges in total.
-		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
+	\includegraphics{ExperimentalComparison}
+	\caption{Bridged original buildings,
+		goal shapes at scale~$1:50{,}000$ (darker polygons), 
+		and the built-up areas at scale~$1:50{,}000$ 
+		from IGN (transparent polygons).
+		Some built-up areas from IGN are split 
+		because of streets' crossing.
+		There are~$56$ goal shapes, which have~$1{,}135$ 
+		edges in total.
+		We show a sequence of maps in 
+		\fig\ref{fig:ContinuousGeneralization} 
 		for the region marked by the dashed circle.
 	}
-	\label{fig:GoalShape}
+	\label{fig:ExperimentalComparison}
 \end{figure*}
 
-We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
-This production costs $668.2\,\mathrm{s}$ in total.
+We produced a sequence of~$10$ maps,
+i.e.,~$t \in \{0.1, 0.2, \dots, 1\}$.
+This production costs~$668.2\,\mathrm{s}$ in total.
 We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
-the marked region in \fig\ref{fig:GoalShape}.
+the marked region in \fig\ref{fig:ExperimentalComparison}.
 We counted the numbers of buildings in our results,
 and compared our numbers to the numbers calculated by T\"opfer's radical law
-(see \fig\ref{fig:BuilidngNumber}).
+(see \fig\ref{fig:NumberOfBuildings}).
 We have unexaggerated-area symbols, 
-so for \eq2 of \citet{Topfer1966} we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
+so for \eq2 of \citet{Topfer1966} 
+we used~$C_\mathrm{b2}$ and~$C_\mathrm{z3}$.
 As a result, we computed the numbers according to
@@
 \]
-where $n_s=2{,}590$ is the number of buildings on start map
-and $n_t$ is the number of buildings on a map at scale $1:M_t$.
-According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
+where~$n_s=2{,}590$ is the number of buildings on start map
+and~$n_t$ is the number of buildings on a map at scale~$1:M_t$.
+According to \fig\ref{fig:NumberOfBuildings}, 
+our numbers decrease faster than 
 the numbers from the radical law.
@@
 	\includegraphics{ContinuousGeneralization}
-	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
-		for the region marked in \fig\ref{fig:GoalShape}.
+	\caption{A sequence of maps at time~$t \in \{0, 0.1, 0.2, 
+	\dots, 1\}$
+		for the region marked in 
+		\fig\ref{fig:ExperimentalComparison}.
 	}
@@
 	\centering
-	\begin{tikzpicture}[]
-	\begin{axis}[
-	height=5cm,
-	width= \linewidth-0.1cm,
-	axis lines = left,
-	%	axis x line=center,
-	%	axis y line=left,
-	xtick={0.1,0.2,...,1},
-	ytick={500,1000,...,3000},
-	xlabel={$t$},
-	ylabel={number of buildings},
-	xlabel style={below right},
-	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
-	xlabel style={at={(axis description cs:1,0)},anchor=north},
-	%	ylabel style={above left},
-	xmin=0,
-	xmax=1.1,
-	ymin=0,
-	ymax=3200,
-	cycle list name=black white,
-	]
-	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
-%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
-	\addplot+  coordinates {
-		(0,2590)
-		(0.1,1963)
-		(0.2,758)
-		(0.3,304)
-		(0.4,177)
-		(0.5,122)
-		(0.6,92)
-		(0.7,73)
-		(0.8,66)
-		(0.9,59)
-		(1,56)		
-	};
-	\legend{\quad radical law, \quad our results}
-	\end{axis}
-	\end{tikzpicture}
-	\caption{A comparison of the numbers of building between our results and 
+	\includegraphics{NumberOfBuildings}
+	\caption{A comparison of the numbers of building between our 
+results and 
 		T\"opfer's radical law.}
-	\label{fig:BuilidngNumber}
+	\label{fig:NumberOfBuildings}
 \end{figure}
@@
 our result at time $t=1$
-and the data at scale $1:50{,}000$.
+and the data at scale~$1:50{,}000$.
 No small building is removed in our result or the existing data.
 The boundaries of our built-up areas are more straight than that of IGN data, 
-where we have $1{,}135$ edges while the data has $4{,}968$ edges.
+where we have~$1{,}135$ edges while the data has~$4{,}968$ edges.
 From this perspective, we would say that our result is 
@@
 
-\begin{figure*}[tb]
-	\centering
-	\includegraphics{ExperimentalComparison}
-	\caption{A comparison of our result and the existing data at scale 
-		$1:50{,}000$.
-		The brighter gray polygons represent the original buildings.
-		The darker gray polygons are our result at time $t=1$.
-		The gray polylines represent the data of the built-up areas at scale 
-		$1:50{,}000$ from IGN, where some built-up areas are split because some 
-		streets cross these areas.
-	}
-	\label{fig:ExperimentalComparison}
-\end{figure*}
+%\begin{figure*}[tb]
+%	\centering
+%	\includegraphics{ExperimentalComparison}
+%	\caption{A comparison of our result and 
+%		the existing data at scale~$1:50{,}000$.
+%		The brighter gray polygons represent the original 
+%buildings.
+%		The darker gray polygons are our result at time~$t=1$.
+%		The gray polylines represent the data of the built-up 
+%		areas at scale~$1:50{,}000$ from IGN, 
+%		where some built-up areas are split 
+%		because some streets cross these areas.
+%	}
+%	\label{fig:ExperimentalComparison}
+%\end{figure*}
 
@@
 in which the buildings are always growing and, at the same time, are simplified.
-For the goal map at scale $1:50{,}000$,
+For the goal map at scale~$1:50{,}000$,
 the shapes of our built-up areas are more reasonable than the data from IGN.

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added section of running time; improved abstract and introduction

@@
 a straight-line trajectory is often used to interpolate.
+\citet{Peng2013_LSA} defined trajectories based on least-square 
+adjustment in order to obtain more reasonable intermediate-scale 
+polylines.
 Using morphing, \citet{Peng2016_Admin} continuously generalized 
-administrative boundaries based on compatible triangulations. When the number 
-of line features is different in the start and goal maps, a continuous 
-selection is required and \citet{Chimani2014_Eat} proposed to generate a 
+administrative boundaries based on compatible triangulations. 
+When the numbers of line features are different 
+on the start and goal maps, 
+a continuous selection is required and 
+\citet{Chimani2014_Eat} proposed to generate a 
 selection sequence applicable for road network.
@@
 
-These methods are interesting but only work on lines and our problem of 
-building polygon interpolation cannot be achieved by similar morphings. 
-Regarding the continuous generalization of polygon map features,
-\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their 
-method 
-preserves polygons' topology, area-ratios, and relative positions.  In the case 
-where the goal map is an aggregated version of start land-cover map, 
-\citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
-areas.
+These methods are interesting but only work on lines and 
+our problem of building polygon interpolation 
+cannot be achieved by similar morphings. 
+Regarding the continuous generalization of polygon features,
+\citet{Danciger2009} proposed to grow polygons 
+when a map was zoomed out. 
+Their method preserves polygons' topology, area-ratios, and 
+relative positions.  
+In the case where the goal map is an aggregated version of 
+start land-cover map, 
+\citet{Peng2017_AStar} computed optimal aggregation sequences 
+for land-cover areas.
 
-Buildings are important elements on maps, many methods have been proposed to 
-generalize them but not necessarily in a continuous way.
-For example, \citet{haunertwolff2010} simplified a set of buildings 
-based an integer program.
-Their simplification minimizes the number of edges of all the buildings 
-and guarantees that the errors are smaller than a user-defined tolerance.
-At the same time, no topological conflict is introduced by the simplification.
-\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
-One advantage is that their method preserves orientations of the edges.
+Buildings are important elements on maps, 
+many methods have been proposed to generalize them 
+but not necessarily in a continuous way.
+For example, \citet{haunertwolff2010} simplified a set of 
+buildings based an integer program.
+Their simplification minimizes the number of edges of 
+all the buildings and guarantees that 
+the errors are smaller than a user-defined tolerance.
+At the same time, no topological conflict 
+is introduced by the simplification.
+\citet{Buchin2011_Simp} simplified buildings based on 
+edge-move operations.
+Their method preserves orientations of edges.
 
 When users zoom out on digital maps, 
-buildings become smaller and the distances between buildings decrease. So 
-simplification is not the only necessary operation, and buildings can also be 
-aggregated to legible enough \cite{Weibel1997}. Several methods were proposed 
-to aggregate buildings while preserving the shape of buildings (right angles 
-remain) \cite{Regnauld2001}, \cite{RegnauldRevell07}, \cite{Damen2008}. These 
-algorithms can be used as inspirations to define a continuous transformation of 
-buildings.
+buildings become smaller and 
+the distances between buildings decrease. 
+So simplification is not the only necessary operation, 
+and buildings can also be 
+aggregated to legible enough \cite{Weibel1997}. 
+Several methods were proposed 
+to aggregate buildings while preserving their shape 
+(right angles remain) 
+\cite{Regnauld2001,RegnauldRevell07,Damen2008}. 
+These algorithms can be used as inspirations 
+to define a continuous transformation of buildings.
 
-Algorithms were also proposed to create built-up area polygons (that appear in 
-our goal map) from individual building polygons (that appear in our start map). 
-For instance, \citet{Chaudhry2008} identified the boundaries of urban 
-settlement by calculating `citiness' based on buildings. But the method cannot 
-be adapted to provide a continuous transformation from the buildings to the 
-built-up area.
+Algorithms were also proposed to create 
+built-up area polygons (that appear in our goal map) from 
+individual building polygons (that appear in our start map). 
+For instance, \citet{Chaudhry2008} identified the boundaries of 
+urban settlement by calculating `citiness' based on buildings. 
+But the method cannot be adapted 
+to provide a continuous transformation 
+from the buildings to the built-up area.
 
-Finally, some papers directly tackle the continuous transformation of buildings 
-when scale is reduced. \citet{Li2017_Building} morphed between two buildings at 
-different scales.
-They managed to preserve the orthogonal characteristics of buildings, but their 
-algorithm cannot be used in our case as the goal map does not contain buildings 
-anymore. \citet{Touya17b} proposed a progressive transformation of buildings 
-into a built-up area, where buildings are progressively replaced by the shape 
-of the block they belong to. However, this last algorithm is not continuous 
-enough, as each iteration directly transforms a set of buildings in a block 
-into a polygon that covers the whole block. So there is no existing solution 
-for the continuous generalization of building polygons into built-up area 
-polygons.
+Finally, some papers directly tackle 
+the continuous transformation of buildings 
+when scale is reduced. 
+\citet{Li2017_Building} morphed between two buildings 
+at different scales.
+They managed to preserve the orthogonal characteristics of 
+buildings, but their algorithm cannot be used in our case 
+as our goal map does not contain buildings anymore.
+\citet{Touya17b} proposed a progressive transformation of 
+buildings into a built-up area, 
+where buildings are progressively replaced 
+by the shape of the block they belong to. 
+However, this last algorithm is not continuous enough, 
+as each iteration directly transforms 
+a set of buildings in a block into a polygon 
+that covers the whole block. 
+So there is no existing solution 
+for the continuous generalization of building polygons 
+into built-up area polygons.
 
@@
 The generalization consists of aggregating, growing, and simplifying.
-We aggregate original buildings which will be too close at an output scale 
-by adding bridges.
+We aggregate original buildings which will be too close 
+at an output scale by adding bridges.
 We grow (bridged) original buildings by buffering,
@@
 taking the lengths of the line segments as the weights.
-As a results, the line segments corresponding to the edges in the MST
+As a result, the line segments corresponding to the edges in the 
+MST
 are identified as bridges.
@@
 
-Both the erosion and line simplification may result in shrinking a 
-building.
+Both the erosion and line simplification may result in 
+shrinking a building.
 \fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
@@
 \subsection{Running time}
-
-Although a version with a 
-lower running time exists \citep[see][]{Chan1992}, we 
-implemented the basic 
-version.
+Suppose that our input has $n$ edges in total.
+Operations like growing, dilation, erosion, merge, and clip 
+cost time $O(n^2)$ \citep{Greiner1998Clipping,Palfrader2015}.
+Although we iteratively aggregate (see \sect\ref{sec:Aggregate}),
+it is unlikely that we need to repeat the aggregation more than 
+twice.
+Therefore, let us say that the iterative aggregation does not
+take extra running time.
+Simplifying polygons using Imai--Iri algorithm needs time
+$O(n^3)$.
+The improved version of Imai--Iri algorithm by 
+\citet{Chan1996} does not help in our case
+because we have more constraints when simplifying
+(see \sect\ref{sec:ImaiIri}).
+As a result, the simplification dominates our running time,
+which is in $O(n^3)$.
 
@@
 erosion, and merge operations.
-An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
 We ran our case study under~64-bit 

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added an advantage of merge operation

@@
 We also simplify the buildings at the output scale.
+Finally, an analysis of running time 
+is presented at the end of this section.
 We carry out a case study 
@@
 \label{sec:Methodology}
-We name our input map as start map,
-and denote the scale of the start map by $1:M_\mathrm{s}$.
-We generate a goal map at scale $1:M_\mathrm{g}$ 
+The input map is our start map.
+We denote the scale of the start map by~$1:M_\mathrm{s}$.
+We generate a goal map at scale~$1:M_\mathrm{g}$ 
 ($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
-We use time $t\in[0,1]$ to define the continuous generalization
-process. 
-We require that the generalization yields exactly the start map when $t=0$ 
-and the goal map when $t=1$.
+We use time~$t\in[0,1]$ to define 
+the continuous generalization process. 
+We require that 
+the generalization yields exactly the start map when~$t=0$ 
+and the goal map when~$t=1$.
 The start map should be continuously changed to the goal map 
-when $t$ increases from~$0$ to~$1$.
-For the sake of convenience, we define parameter
-$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.
+when~$t$ increases from~$0$ to~$1$.
+For the sake of convenience, we define parameter~$M_t= 
+M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.
 
-The continuous generalization is carried by dilating the original buildings. 
-When dilated buildings become too close at time $t$
-and we aggregate them by adding bridges.
-We grow the (bridged) original buildings by buffering with miter joins.
-At each time, the grown buildings need to be simplified to look like buildings 
-and this simplification is carried out in two steps:
+The continuous generalization is carried 
+by dilating the original buildings. 
+If dilated buildings become too close at time $t$,
+we aggregate the original buildings by adding bridges.
+We grow the (bridged) original buildings 
+by buffering with miter joins.
+At any time $t$, the grown buildings 
+need to be simplified to look like buildings.
+This simplification is carried out in two steps:
 the first one is to use dilation and erosion 
 to remove ``dents'' and ``bumps''; 
-the second step is to remove vertices using Imai--Iri algorithm.
+the second step is to remove vertices 
+using Imai--Iri algorithm \citep{ImaiIri1988}.
 To make sure that buildings never shrink when $t$ is increasing,
-for a building, we merge its shape at time $t$ 
+we merge the shape of a building at time $t$ 
 and its shape at the immediately previous step (before $t$). 
-Also, we clip the building using the shape on goal map to ensure some 
-continuity.
+Also, we clip the building using the shape on goal map to ensure 
+some continuity.
 
-The two main operators of the proposed method, building growth and 
-dilation-erosion-based simplification, are presented in the following 
-subsections:
+The operators of the proposed method
+are presented in the following subsections:
 
@@
 
-There are three typical joins for buffering a polygon, i.e.,
+There are three typical joins when buffering a polygon, i.e.,
 round, miter, and square joins
 (see \fig\ref{fig:Buffer_ThreeKinds}).
-We choose the miter joins to grow in order to
-preserve the right angles of buildings.
+We choose the miter joins to grow buildings in order to
+preserve the right angles.
 If an angle is acute, however, 
@@
 This spike may go across other buildings 
-(see \fig\ref{fig:Buffer_MiterLimits}a).
+(see for example \fig\ref{fig:Buffer_MiterLimits}a).
 To avoid this kind of interruptions, 
@@
 we must have $\alpha \geq \sqrt{2}$. 
-We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
-smaller (more acute) than $83.6 \degree$.
+We set $\alpha  = 1.5$. 
+In this case, a square join will be applied 
+when an angle is smaller (more acute) than $83.6 \degree$.
 
@@
 \citet{Meijers2016} simplified buildings 
-based on offset curves generated from straight skeletons.
+using offset curves generated based on straight skeletons.
 Our method is similar to \citet{Meijers2016}.
-Our proposition is to dilate and erode the buildings, to remove dents and 
+We dilate and erode the buildings to remove dents and 
 bumps that can occur when buildings grow
@@
 	\includegraphics[]{RemoveDentAndBump}
-	\caption{Removing a dent by dilating and then remove a bump by eroding.
+	\caption{Removing a dent by dilating and then 
+		removing a bump by eroding.
 		(a) A polygon with a dent and a bump.
-		(b) Dilating the polygon in (a) with distance $d$ to remove the dent.
-		(c) Eroding the polygon in (b) with $2d$ to remove the bump.
-		(d) Dilating the polygon in (c) with $d$ so that the result has 
-		the same size as the polygon in (a).
+		(b) Dilating the polygon in (a) with distance~$d$ 
+		to remove the dent.
+		(c) Eroding the polygon in (b) with~$2d$ 
+		to remove the bump.
+		(d) Dilating the polygon in (c) with~$d$ so that 
+		the result has the same size as the polygon in (a).
 	}
@@
 
-At time $t$, we grow buildings with distance $\dtrm{G}$.
+At time $t$, we should grow buildings with distance $\dtrm{G}$.
 We dilate with distance $\dtrm{D}$ ($\dtrm{D}>0$),
@@
 and dilate back with $\dtrm{E}$.
-A problem we may have is that 
+A problem of this process is that 
 a building may be split into several parts by erosion
@@
 
-A ``bay'' may appear when we grow a bridged building
-(see \fig\ref{fig:RemoveBay}b).
+when we grow a bridged building,
+A ``bay'' may appear (see \fig\ref{fig:RemoveBay}b).
 We remove such a bay by dilating (see \fig\ref{fig:RemoveBay}c)
@@
 If the width of a bay is smaller than $2\dtrm{D}$, 
-then the bay can be removed by dilating and eroding with distance $\dtrm{D}$.
+then the bay can be removed by dilating with distance $\dtrm{D}$.
 We wish to remove bays 
@@
 we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ on map.
-Sometimes, our $\dtrm{D}$ is not large enough to do so 
+Sometimes, our $\dtrm{D}$ is not large enough to remove a bay 
+with width $r_\mathrm{h}$
 because of the limitation from \eq\ref{eq:d_DtBound}.
@@
 %
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics[]{NearestPoints}
-%	\caption{The nearest points between a pair of buildings may change because 
-%		of growing. 
-%		The two squares and the two circles respectively mark
-%		the nearest points before and after growing.
-%	}
-%	\label{fig:NearestPoints}
-%\end{figure}
 
@@
 
-%\subsection{Grouping buildings based on buffering}
-%\label{sec:Group}
-%There are many research works about grouping buildings.
-%\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
-%However, our two needs, 
-%the distances between buildings are always larger than a specified threshold 
-%and small bays should be removed, 
-%motivate us to develop our own grouping method.
-%
-%Original buildings grow according to time $t$.
-%We put the original buildings in the same group if 
-%they grow so that their distance is less than $d_{\epsilon, t}$.
-%Following \citet{Stoter2009}, 
-%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
-%The real separation threshold at time $t$ is
-%%\begin{equation}
-%%\label{eq:d_epsilont}
-%%d_{\epsilon, t} = \epsilon \cdot M_t.
-%%\end{equation}
-%We group buildings based on buffering.
-%The basic idea is that 
-%we buffer the original buildings with distance $\dtrm{G}$
-%and an additional distance $d_{\epsilon, t}/2$
-%(the distance between two buildings should be at least $d_{\epsilon, t}$).
-%If two buffers overlap, 
-%then the original buildings are put in the same group.
-%However, as some parts of a building grow faster than other parts, 
-%this basic idea may cause problems.
-%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
-%In \fig\ref{fig:CloseDetect}d, 
-%the buffers of buildings $p$ and $q$ overlap each other.
-%So we should aggregate buildings $p$ and $q$ at time $t$
-%because they will grow to become too close.
-%According to the bridges in \fig\ref{fig:CloseDetect}b, 
-%buildings $p$ and $q$ should be aggregated via building $r$.
-%Unfortunately, neither $p$ or $q$ will be too close to $r$.
-%As we use bridges to aggregate buildings 
-%(see \sect\ref{sec:Aggregate}),
-%we are not able to aggregate buildings $p$ and $q$. 
-%To avoid this situation, 
-%we buffer original buildings with distance
-%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
-%This buffering guarantees 
-%that every part of a building grows with the same speed.
-%If the buffers of two buildings overlap each other,
-%then the two buildings are surely aggregated into one.
-%Using this buffering, in most of cases 
-%two buildings are aggregated as soon as 
-%their separation distance is less than 
-%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
-%The advantage is that we guarantee that 
-%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
-%aggregated via bridges.
-%
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics[]{CloseDetect}
-%	\caption{Group buildings based on buffering.
-%		(a) original buildings.
-%		(b) bridges detected to aggregate the three buildings.
-%		(c) grow the original buildings with distance $\dtrm{G}$.
-%		(d) buffer the grown buildings in (c) 
-%		with distance $d_{\epsilon, t} /2$ using round joins.
-%		(e) buffer the original buildings 
-%		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
-%		using round joins, where $\alpha=1.5$
-%		(see \sect\ref{sec:Grow}).
-%		(f) according to the buffer in (e), 
-%		we put the three original buildings in the same group.
-%		We aggregate the original buildings by adding the two bridges 
-%		and grow the aggregated building with distance $\dtrm{G}$.
-%	}
-%	\label{fig:CloseDetect}
-%\end{figure}
-
-%
-%As stated in \sect\ref{sec:DilationErosion}, 
-%we wish to remove ``bays'' 
-%which have widths less than $2 \dtrm{D}$.
-%A bay may come from a complex original building,
-%or from bridging some buildings.
-%\fig\ref{fig:RemoveBay}e shows an example of the later case.
-%To remove a bay,
-%we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
-%and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
-%with distance $\dtrm{D}$.
-%There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
-%so we iteratively group until the number of groups does not decrease.
-%For the buildings in \fig\ref{fig:RemoveBay}a,
-%the final result of removing a bay is the outer polygon of 
-%\fig\ref{fig:RemoveBay}h. 
-%In comparison, the result is \fig\ref{fig:RemoveBay}e 
-%if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
-%Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
-%kind of bay and will be removed by overgrowing.
-%
-%
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics[draft=false]{RemoveBay}
-%	\caption{Group buildings iteratively.
-%		(a) Original buildings.
-%		(b) Dilate each original building with distance 
-%		$\dtrm{G}+\dtrm{D}$.		
-%		(c) Erode the dilated polygons with distance $\dtrm{D}$.
-%		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
-%		If two polygons in (d) intersect, 
-%		the original buildings will be put in the same group 
-%		because they will become too close at time $t$.
-%		There are two groups according to (d).
-%		One consists of the single middle building and 
-%		the surrounding $9$ buildings comprise the other group.
-%		(e) The result of growing and merging at time $t$ 
-%		if we use $\dtrm{D}=0$.
-%		The process of (f), (g), and (h) is similar to 
-%		that of (b), (c), and (d).		
-%		The difference is that 
-%		instead of applying the operators to each single building, 
-%		we do that for the buildings in the same group.
-%		In (f), we manage to remove the bay in (e) by additionally dilating 
-%		with distance $\dtrm{D}$.
-%		There is only one group left according to (h).
-%		We iteratively group buildings in this way until the number of groups 
-%		does not decrease.
-%	}
-%	%in this example, we used _dblTotalGrow *= 5;
-%	\label{fig:RemoveBay}
-%\end{figure*}
-
 %
@@
 Similarly, \fig\ref{fig:Shrink_Uniting}b shows the merged result of buildings 
-in \fig\ref{fig:Shrink_Simplification}c and~h.
+in \fig\ref{fig:Shrink_Simplification}c 
+and~\fig\ref{fig:Shrink_Simplification}h.
 
-Added to this shrinking problem, a building aggregate on an intermediate map 
-should never exceed
+This merge can also avoid bridge's disappearing.
+Recall that we always add a bridge linking the nearest points of 
+two buildings in order to aggregate.
+It can happen that 
+the pair of nearest points change during growing.
+\fig\ref{fig:NearestPoints} shows such an example.
+For this example, at the beginning a bridge will added 
+to link the pair of points marked by the squares. 
+Later at some point, a bridge will be added 
+to link the two points marked by the circles, 
+while the first bridge will disappear.
+This disappearing annoys users.
+Fortunately, the merge operation makes the first bridge stay.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{NearestPoints}
+	\caption{The nearest points between a pair of buildings	
+		change because of growing. 
+		The two squares and the two circles respectively mark
+		the nearest points before and after growing.
+	}
+	\label{fig:NearestPoints}
+\end{figure}
+
+Added to this shrinking problem, 
+a building aggregate on an intermediate map should never exceed
 the goal shape of the aggregated building. 
-Otherwise, the building will need to be shrunk to ensure continuity with the 
-goal built-up polygon.
+Otherwise, the building will need to be shrunk 
+to ensure continuity with the goal built-up polygon.
 To guarantee this consistency, 
@@
 and~$d_\mathrm{G}=25\,\mathrm{m}$
-so that we can compare our result with the exiting data.
+so that we can compare our result with the existing data.
 Also, this setting makes \eq\ref{eq:S_g} hold, 
@@
 where~$\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
-according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
+according to \eq\ref{eq:d_Et} and~$\alpha=1.5$.
 
@@
 to compute the goal shapes of the built-up areas.
-\fig\ref{fig:ExperimentalComparison} shows the bridged buildings 
-and the goal shapes.
 The~$56$ built-up areas have~$2{,}095$ edges before line 
@@
 Using the Imai--Iri algorithm, we have~$1{,}102$ edges left.
-In comparison, there are~$1{,}597$ edges left when we simplified 
-using
-the Douglas--Peucker algorithm.
+In comparison, there are~$1{,}597$ edges left 
+when we simplified using the Douglas--Peucker algorithm.
 
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics{GoalShape}
-%	\caption{Bridged original buildings 
-%		and goal shapes of the built-up areas (without removing 
-%small holes), 
-%		at scale~$1:50{,}000$.
-%		There are~$56$ built-up areas, which have~$1{,}102$ 
-%		edges in total.
-%		We show a sequence of maps in 
-%\fig\ref{fig:ContinuousGeneralization} 
-%		for the region marked by the dashed circle.
-%	}
-%	\label{fig:GoalShape}
-%\end{figure*}
+\fig\ref{fig:ExperimentalComparison} shows 
+the bridged original buildings as well as 
+our result of built-up areas at time $t=1$ (almost the same as 
+the goal shapes).
+The transparent polygons in \fig\ref{fig:ExperimentalComparison}
+are the data of built-up areas at scale~$1:50{,}000$ from IGN.
+No small building was removed in our result or the IGN data.
+The boundaries of our built-up areas 
+are more straight than that of IGN data, 
+where we have~$1{,}135$ edges while the data has~$4{,}968$ edges.
+From this perspective, we would say that our result is 
+more reasonable than the existing data.
+A questionnaire, however, is needed to make a more convincing 
+comparison.
 
@@
 We counted the numbers of buildings in our results,
-and compared our numbers to the numbers calculated by T\"opfer's radical law
-(see \fig\ref{fig:NumberOfBuildings}).
+and compared them to the numbers calculated by T\"opfer's 
+radical law (see \fig\ref{fig:NumberOfBuildings}).
 We have unexaggerated-area symbols, 
@@
 
-\fig\ref{fig:ExperimentalComparison} shows a comparison of 
-our result at time $t=1$
-and the data at scale~$1:50{,}000$.
-No small building is removed in our result or the existing data.
-The boundaries of our built-up areas are more straight than that of IGN data, 
-where we have~$1{,}135$ edges while the data has~$4{,}968$ edges.
-From this perspective, we would say that our result is 
-more reasonable than the existing data.
-A questionnaire, however, is needed to make a more convincing comparison.
-
-%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
-
-%\begin{figure*}[tb]
-%	\centering
-%	\includegraphics{ExperimentalComparison}
-%	\caption{A comparison of our result and 
-%		the existing data at scale~$1:50{,}000$.
-%		The brighter gray polygons represent the original 
-%buildings.
-%		The darker gray polygons are our result at time~$t=1$.
-%		The gray polylines represent the data of the built-up 
-%		areas at scale~$1:50{,}000$ from IGN, 
-%		where some built-up areas are split 
-%		because some streets cross these areas.
-%	}
-%	\label{fig:ExperimentalComparison}
-%\end{figure*}
-
-%Although a version with a 
-%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
-%version
-
 \section{Conclusion}

### 2017-10-21 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/BridgeDisappearing.pdf; improved our paper

@@
 we define that two buildings are too close if their distance is less than
-$\epsilon= 0.2\,\mathrm{mm}$ on map.
+$\varepsilon= 0.2\,\mathrm{mm}$ on map.
 The real separation threshold at time $t$ is
@@
 \label{eq:d_epsilont}
-d_{\epsilon, t} = \epsilon \cdot M_t.
+d_{\varepsilon, t} = \varepsilon \cdot M_t.
 \end{equation}
@@
 Our way of detecting close buildings is simple.
-We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins
+We buffer buildings with distance $d_{\varepsilon, t}/2$ using 
+round joins
 (see \fig\ref{fig:Buffer_ThreeKinds}b).
 We merge the buffers that overlap each other.
-The buildings intersect the same merged buffer 
+The original buildings intersecting the same merged buffer 
 are identified as a group of close buildings.
-The corresponding original buildings 
-are identified as a group of original close buildings.
 For each pair of the original buildings in the same group,
 we connect them by adding a line segment linking the nearest points.
-The line segments for a group of original buildings may cross each other or 
+The line segments may cross each other or 
 even intersect buildings.
@@
 we only select some of the line segments as \emph{bridges}.  
-We consider each building as a node and each line segment as an edge, 
+We consider each building as a node and 
+each line segment as an edge, 
 then we have a graph.
@@
 taking the lengths of the line segments as the weights.
-As a result, the line segments corresponding to the edges in the 
-MST
-are identified as bridges.
-We aggregate the group of original buildings by adding these bridges.
+As a result, the line segments corresponding to the edges 
+in the MST are identified as bridges.
+We aggregate the group of original buildings 
+by adding these bridges.
 
@@
 there is no pair of buildings 
-which has separation distance less than $d_{\epsilon, t}$.
+which has separation distance less than $d_{\varepsilon, t}$.
 
@@
 		(b) Growing the original buildings with distance $\dtrm{G}$.
-		(c) Buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
+		(c) Buffering the grown buildings with distance 
+		$d_{\varepsilon,t}/2$ 
 		using round joins.
@@
 		(f) Buffering the grown buildings in (e) with distance 
-		$d_{\epsilon,t}/2$ using round joins.
+		$d_{\varepsilon,t}/2$ using round joins.
 		(g) Aggregating buildings $p$, $q$ and~$r$ by adding bridges.
@@
 		(i) Buffering the grown buildings in (h) with distance 
-		$d_{\epsilon,t}/2$ using round joins.
+		$d_{\varepsilon,t}/2$ using round joins.
 	}
@@
 %We put the original buildings in the same group if 
-%they grow so that their distance is less than $d_{\epsilon, t}$.
+%they grow so that their distance is less than $d_{\varepsilon, 
+%t}$.
 %Following \citet{Stoter2009}, 
-%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
+%we set the threshold $\varepsilon= 0.2\,\mathrm{mm}$ on map. 
 %The real separation threshold at time $t$ is
@@
 %\label{eq:d_epsilont2}
-%d_{\epsilon, t} = \epsilon \cdot M_t.
+%d_{\varepsilon, t} = \varepsilon \cdot M_t.
 %\end{equation}
@@
 %we buffer the original buildings with distance $\dtrm{G}$
-%and an additional distance $d_{\epsilon, t}/2$
+%and an additional distance $d_{\varepsilon, t}/2$
 %(the distance between two buildings should be at least 
-%$d_{\epsilon, t}$).
+%$d_{\varepsilon, t}$).
 %If two buffers overlap, 
@@
 %we buffer original buildings with distance
-%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
+%$\alpha \dtrm{G}+d_{\varepsilon, t}/2$ using round joins.
 %This buffering guarantees 
@@
 %their separation distance is less than 
-%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
+%$2(\alpha -1) \dtrm{G}+d_{\varepsilon, t}$.
 %The advantage is that we guarantee that 
 %any two buildings have separate distance less than 
-%$d_{\epsilon, t}$ will be 
+%$d_{\varepsilon, t}$ will be 
 %aggregated via bridges.
@@
 and~\fig\ref{fig:Shrink_Simplification}h.
-
-This merge can also avoid bridge's disappearing.
-Recall that we always add a bridge linking the nearest points of 
-two buildings in order to aggregate.
-It can happen that 
-the pair of nearest points change during growing.
-\fig\ref{fig:NearestPoints} shows such an example.
-For this example, at the beginning a bridge will added 
-to link the pair of points marked by the squares. 
-Later at some point, a bridge will be added 
-to link the two points marked by the circles, 
-while the first bridge will disappear.
-This disappearing annoys users.
-Fortunately, the merge operation makes the first bridge stay.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[]{NearestPoints}
-	\caption{The nearest points between a pair of buildings	
-		change because of growing. 
-		The two squares and the two circles respectively mark
-		the nearest points before and after growing.
-	}
-	\label{fig:NearestPoints}
-\end{figure}
-
-Added to this shrinking problem, 
-a building aggregate on an intermediate map should never exceed
-the goal shape of the aggregated building. 
-Otherwise, the building will need to be shrunk 
-to ensure continuity with the goal built-up polygon.
-To guarantee this consistency, 
-we clip the building using the goal shape 
-and remove the outside parts.
+This merge also avoids bridges' shrinking.
+\fig\ref{fig:BridgeDisappearing} shows such an example.
 
@@
 		The gray polygons represent the original building.
-		(a) Growing and Dilating the building with distances $\dtrm[1]{G}$ and 
+		(a) Growing and Dilating the building with distances 
+		$\dtrm[1]{G}$ and 
 		$\dtrm[1]{D}$, respectively;
-		(b) Eroding the polygon in~(a) with $\dtrm[1]{D} + \dtrm[1]{E}$;
+		(b) Eroding the polygon in~(a) with $\dtrm[1]{D} + 
+		\dtrm[1]{E}$;
 		(c) Dilating the polygon in~(b) with $\dtrm[1]{E}$.
 		(d) The goal shape.
-		The process of (e), (f), and~(g) is the same as the process of (a), 
+		The process of (e), (f), and~(g) is the same as the 
+		process of (a), 
 		(b), and~(c).
@@
 		(d) The goal shape.
-		(h) Simplifying the polygon in~(g) using the Imai--Iri algorithm.
+		(h) Simplifying the polygon in~(g) using the Imai--Iri 
+		algorithm.
 		Note that $d_{l,t_1}<d_{l,t_2}$ (see \eq\ref{eq:d_lt}),
@@
 	\includegraphics[]{Shrink_Uniting}
-	\caption{Merging a polygon with the polygon at the immediately previous 
+	\caption{Merging a polygon with the polygon at the 
+	immediately previous 
 		step.
-		(a) Merging the polygons of \fig\ref{fig:Shrink_Erosion}c and 
+		(a) Merging the polygons of 
+		\fig\ref{fig:Shrink_Erosion}c and 
 		\fig\ref{fig:Shrink_Erosion}g.
-		(b) Merging the polygons of \fig\ref{fig:Shrink_Simplification}c and 
+		(b) Merging the polygons of 
+		\fig\ref{fig:Shrink_Simplification}c and 
 		\fig\ref{fig:Shrink_Simplification}h.
@@
 \end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[]{BridgeDisappearing}
+	\caption{Avoiding shrinking resulted by moved bridges,
+		where~$t_1=0.5$ and~$t_2=0.6$.
+		(a) Original buildings.
+		(b) Growing buildings with distance~$\dtrm[1]{G}$ and 
+		dilating with~$d_{\varepsilon,t_1}/2$;
+		buildings~$p$ and~$q$ are identified as in the same 
+		group.
+		(c) Aggregating~$p$ and~$q$	by adding a bridge.
+		(d) Growing the (bridged) buildings in (c)
+		with distance~$\dtrm[1]{G}$.
+		(f) Growing original buildings with 
+		distance~$\dtrm[2]{G}$ and 
+		dilating with~$d_{\varepsilon,t_2}/2$;
+		all the three buildings are in the same group
+		(g) Aggregating	by adding bridges according to the MST.
+		(h) Growing the bridged building in~(g)
+		with distance~$\dtrm[2]{G}$. 
+		The bridge in~(d) shrinks comparing to~(h).
+		(e) Avoiding this shrinking at time~$t_2$ 
+		by merging buildings of~(d) and~(h).
+	}
+	\label{fig:BridgeDisappearing}
+\end{figure}
+
+%\begin{figure}[tb]
+%	\centering
+%	\includegraphics[]{NearestPoints}
+%	\caption{The nearest points between a pair of buildings	
+%		change because of growing. 
+%		The two squares and the two circles respectively mark
+%		the nearest points before and after growing.
+%	}
+%	\label{fig:NearestPoints}
+%\end{figure}
+
+Added to this shrinking problem, 
+a building aggregate on an intermediate map should never exceed
+the goal shape of the aggregated building. 
+Otherwise, the building will need to be shrunk 
+to ensure continuity with the goal built-up polygon.
+To guarantee this consistency, 
+we clip the building using the goal shape 
+and remove the outside parts.
 
@@
 cost time $O(n^2)$ \citep{Greiner1998Clipping,Palfrader2015}.
-Although we iteratively aggregate (see \sect\ref{sec:Aggregate}),
-it is unlikely that we need to repeat the aggregation more than 
-twice.
-Therefore, let us say that the iterative aggregation does not
-take extra running time.
+We iteratively aggregate in \sect\ref{sec:Aggregate}.
+In the worst case, we need to repeat $O(n)$ times,
+which increases our running time to $O(n^3)$.
+It is unlikely that we need to repeat the aggregation more than 
+twice, though.
 Simplifying polygons using Imai--Iri algorithm needs time
@@
 (see \sect\ref{sec:ImaiIri}).
-As a result, the simplification dominates our running time,
-which is in $O(n^3)$.
+As a result, the running time of our method is in $O(n^3)$.
 
@@
 and compared them to the numbers calculated by T\"opfer's 
-radical law (see \fig\ref{fig:NumberOfBuildings}).
+radical law (see \fig\ref{fig:NumberOfBuildings})
+and our \emph{areal law}.
 We have unexaggerated-area symbols, 
@@
 and~$n_t$ is the number of buildings on a map at scale~$1:M_t$.
+For the areal law, we argue that the number of buildings in a 
+unit area on map should be fixed, which leads to
+\[
+n'_t=n_\mathrm{s}\left( \frac{M_\mathrm{s}}{M_t}\right) ^2.
+\]
 According to \fig\ref{fig:NumberOfBuildings}, 
 our numbers decrease faster than 
-the numbers from the radical law.
-It seems that our result supports the fractal law proposed by \citet{Jiang2015}.
+the numbers of both the radical law and the areal law.
 
@@
 	\includegraphics{ContinuousGeneralization}
-	\caption{A sequence of maps at time~$t \in \{0, 0.1, 0.2, 
-	\dots, 1\}$
-		for the region marked in 
-		\fig\ref{fig:ExperimentalComparison}.
+	\caption{A sequence of maps 
+		at time~$t \in \{0, 0.1, 0.2, \dots, 1\}$ for the region 
+		marked in \fig\ref{fig:ExperimentalComparison}.
 	}
@@
 	\includegraphics{NumberOfBuildings}
-	\caption{A comparison of the numbers of building between our 
-results and 
-		T\"opfer's radical law.}
+	\caption{A comparison of the numbers of buildings 
+		between our result, areal law, 
+		and T\"opfer's radical law.}
 	\label{fig:NumberOfBuildings}
@@
 
-It is always interesting to know what is the quantity we should keep on a map.
-We compared the numbers of buildings of our results, and it is consistent with 
-the fractal law from \citet{Jiang2015}.
+It is always interesting to know the quantity we should keep on 
+a map.
+We compared the numbers of buildings, and it is more consistent 
+with the areal law than T\"opfer's radical law.
 Another interesting problem is to compare the area of the buildings.

### 2017-10-21 ContinuousGeneralizer/MorphingClass/CGeneralizationMethods/CBldgGrow.cs

@@ -371,7 +371,7 @@ namespace MorphingClass.CGeneralizationMethods
             double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "Miter",
             double dblMiterLimit = 2)
         {            
-            var CloseCpipeDt = _CloseCpipeDt;
+            var CloseCpipeDt = _CloseCpipeDt; //links between every pair of close buildings, not only the bridges in MST
             if (blnGoalMap == true) //when we want to generate built-up areas at goal map, BridgeCpipeDt == null
             {
                 double dblCloseDis = 3 * dblGrow + Math.Sqrt(5) / 2 * dblEpsilon + dblDilation;
@@ -379,7 +379,7 @@ namespace MorphingClass.CGeneralizationMethods
                 _CloseCpipeDt = CloseCpipeDt;
             }
 
-
+            //Initialize groups of buildings; each group contains one building
             var groupedcpgCptEdgeDisltlt = new List<CValPair<List<CPolygon>, List<CptEdgeDis>>>(cpglt.Count);
             foreach (var cpg in cpglt)
             {
@@ -406,6 +406,7 @@ namespace MorphingClass.CGeneralizationMethods
                             for (int j = i + 1; j < GroupedCpgLt.Count; j++)
                             {
                                 CptEdgeDis outCptEdgeDis;
+                                //CloseCpipeDt: links between every pair of close buildings, not only the bridges in MST
                                 if (CloseCpipeDt.TryGetValue(new CValPairIncr<CPolygon>(GroupedCpgLt[i], GroupedCpgLt[j]),
                                     out outCptEdgeDis))
                                 {
@@ -657,8 +658,8 @@ namespace MorphingClass.CGeneralizationMethods
             }
 
 
-            //CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(AllCEdgeLt, 1 / CConstants.dblFclipper),
-            //    "TestEdgeLt" + CHelpFunc.GetTimeStampWithPrefix());
+            CSaveFeature.SaveCEdgeEb(clipperMethods.ScaleCEdgeEb(AllCEdgeLt, 1 / CConstants.dblFclipper),
+                "MergedToConstructDCEL", blnVisible: false);
 
 
[…]

### 2017-10-21 ContinuousGeneralizer/MorphingClass/CHelpFunc.cs

@@ -86,7 +86,7 @@ namespace MorphingClass.CUtility
         //"C:\\MyWork\\DailyWork\\ContinuousGeneralisation\\ContinuousGeneralisation_Data\\AreaAggregation\\" + _strDataFolderName + "\\";
 
         //private static string _strDataFolderName = "France";
-        private static string _strDataFolderName = "France_FourTowns";
+        //private static string _strDataFolderName = "France_FourTowns";
         //private static string _strDataFolderName = "France_FourTowns_Several";
         //private static string _strDataFolderName = "France_Part";
         //private static string _strDataFolderName = "France_FourBuildings";
@@ -100,7 +100,7 @@ namespace MorphingClass.CUtility
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Erosion";
         //private static string _strDataFolderName = "France_Presenting_UnitingPrevious_Simplification";
         //private static string _strDataFolderName = "France_Presenting_RemoveBay";
-        //private static string _strDataFolderName = "France_Presenting_Grouping";
+        private static string _strDataFolderName = "France_Presenting_Grouping";
         //private static string _strDataFolderName = "France_Presenting_BridgeMoreBuilding";
 
         //private static string _strDataFolderName = "France_Problematic";

### 2017-10-21 ContinuousGeneralizer/MorphingClass/CUtility/clipperMethods.cs

@@ -376,6 +376,8 @@ double dblGrow, double dblDilation, double dblEpsilon, string strBufferStyle = "
             var finalPolyTree = Offset_PolyTree(allbackpaths, dblDisOverlap, "Round");
             var groupedcpgltlt = GroupCpgsByOverlap(cpglt, finalPolyTree);
 
+            CSaveFeature.SavePolyTreeAsCpgEb(finalPolyTree, "PolyTreeForGrouping",
+                pesriSimpleFillStyle: esriSimpleFillStyle.esriSFSNull, blnVisible: false);
 
 
 
